### 2020-10-27 report.Rmd
First Commit

---
title: "Report on Effect Size Translation"
ipsum_meta:
  twitter_card: "Summary info for the Twitter Card"
  twitter_site: "\\@sitehandle"
  twitter_creator: "\\@creatorhandle"
  og_url: "https\\://example.com/open/graph/finalURLfor/this"
  og_description: "A modest size description of the content"
  og_image: "https\\://example.com/open/graph/imageURLfor/this"
output: 
  hrbrthemes::ipsum:
    toc: true
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.retina=2, echo=FALSE,message = FALSE,
                      warnings=FALSE, error = FALSE)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
library(hrbrthemes)
library(tidyverse)
library(targets)
library(gt)

update_geom_font_defaults(font_rc)
```

# Assumptions made

I made the following assumptions which may or may not be reasonable:

1.  That $\beta$ is equivilent to $r$ for $\beta < |.5|$ and undefined otherwise (never the case here)
2.  That, given the large sample sizes involved *Hedge's g* and *Cohen's d* where essentially equivalent and that sample sizes used to make up these effects were approximately equal in treatment and control groups.
3.  In the absence of information that could be used to construct a 2x2 contingency table that ORs and Relative Risk Ratios were equivalent and thus Relative Risk Ratios were converted to $r$ as if they were Odds ratios.
4.  External to any other information that all forms of SMD, weighted means etc. were equivilent to Cohen's d.

# Correspondence

```{r}
targets::tar_load(converted_data)

converted_data %>%
  group_by(std_eff_name, es) %>%
  count(sort = TRUE) %>%
  gt() %>%
  tab_header(
    title = "Coversion of effect sizes",
    subtitle = "New Effect Name - Old Effect Name"
  )
```

# Effect Size Summary: Point Estimates

```{r}

converted_data %>%
  group_by(std_eff_name) %>%
  summarize(Mean = mean(value_consensus_r),
            SD = sd(value_consensus_r),
            Min = min(value_consensus_r),
            Max = max(value_consensus_r)) %>%
  gt() %>%
  tab_header(
    title = "Effect Size Summary",
    subtitle = "Descriptives by Effect Size Type"
  ) %>%
  fmt_number(columns = 2:5,
             decimals = 3)

```

# Project Structure
```{r}
targets::tar_glimpse()
```

### 2020-10-27 R/make.R

@@ -1,0 +1,3 @@
+#targets::tar_outdated()
+#targets::tar_glimpse()
+targets::tar_make()

### 2020-10-27 report.Rmd
Cleaned up rmd

@@
   group_by(std_eff_name) %>%
-  summarize(Mean = mean(value_consensus_r),
-            SD = sd(value_consensus_r),
-            Min = min(value_consensus_r),
-            Max = max(value_consensus_r)) %>%
+  summarize(Mean = mean(value_consensus_r, na.rm = TRUE),
+            SD = sd(value_consensus_r, na.rm = TRUE),
+            Min = min(value_consensus_r, na.rm = TRUE),
+            Max = max(value_consensus_r, na.rm = TRUE)) %>%
   gt() %>%
@@
 ```{r}
-targets::tar_glimpse()
+targets::tar_visnetwork()
 ```

### 2020-10-27 R/make.R

@@ -1,3 +1,5 @@
 #targets::tar_outdated()
-#targets::tar_glimpse()
+#targets::tar_glimpse(targets_only = FALSE)
+#targets::tar_visnetwork()
 targets::tar_make()
+

### 2020-11-24 report.Rmd
Clean missing

@@
   count(sort = TRUE) %>%
+  ungroup() %>%
+  set_names(c("New Name", "Old Name", "n")) %>%
   gt() %>%

### 2021-05-14 report.Rmd
First pass update on report and update to targets.

@@
 ---
-title: "Report on Effect Size Translation"
-ipsum_meta:
-  twitter_card: "Summary info for the Twitter Card"
-  twitter_site: "\\@sitehandle"
-  twitter_creator: "\\@creatorhandle"
-  og_url: "https\\://example.com/open/graph/finalURLfor/this"
-  og_description: "A modest size description of the content"
-  og_image: "https\\://example.com/open/graph/imageURLfor/this"
+title: "Screen Time Review of Reviews Summary"
 output:
-  hrbrthemes::ipsum:
+  rmdformats::html_clean:
+    self_contained: true
+    thumbnails: true
+    lightbox: true
+    gallery: true
+    highlight: tango
+    fig_caption: true
+    use_bookdown: true
+    number_sections: false
     toc: true
@@
 
-```{r include=FALSE}
-knitr::opts_chunk$set(fig.retina=2, echo=FALSE,message = FALSE,
-                      warnings=FALSE, error = FALSE)
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(
+	echo = FALSE,
+	message = FALSE,
+	warning = FALSE,
+	fig.retina=2
+)
 ```
 
-```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
+```{r}
 library(hrbrthemes)
@@
 update_geom_font_defaults(font_rc)
+
 ```
+
+# Results
+
+## Review Characteristics
+
+```{r}
+source("R/reviews_table.R")
+review_table_DT
+```
+
+#### Kable
+```{r}
+review_table_kable
+```
+
+## PRISMA Diagram
+
+```{r}
+source("R/PRISMA.R")
+DiagrammeR::grViz(prisma)
+```
+
+## Forest Plots {.tabset}
+
+###
 

### 2021-05-14 R/PRISMA.R

@@ -137,4 +137,4 @@ prisma <- paste("digraph flowchart {
 DiagrammeR::grViz(prisma) %>%
   DiagrammeRsvg::export_svg() %>%
   charToRaw() %>%
-  rsvg::rsvg_pdf(here::here("flow.pdf"))
+  rsvg::rsvg_pdf(here::here("figure","flow.pdf"))

### 2021-05-14 R/functions.R

@@ -1,47 +1,9 @@
-library(tidyverse)
-library(janitor)
+# Targets functions ####
 
-# Conversion functions ####
-
-#conversion formula from 10.1007/s11162-011-9232-5
-b2r <- function(beta){
-  #test beta: beta = -.02
-  r <- NA
-  if(!is.na(beta)){
-    r <- beta 
-  }
-  r
+get_mod_date <- function(){
+  x <- googledrive::drive_get(id = googledrive::as_id("1z_NZwDomPfrOJg2Rn8-E8cc9yoOjXzqH_Di23vWERu4"))
+  return(x$drive_resource[[1]]$modifiedTime)
 }
-
-b2r <- Vectorize(b2r)
-
-d2r <- function(d, a = 4){
-  #assumes equal groups
-  #https://www.meta-analysis.com/downloads/Meta-analysis%20Converting%20among%20effect%20sizes.pdf
-  #10.1002/jrsm.1218
-  if(is.na(d)){NA}else{d/(sqrt(d^2+a))}
-}
-
-d2r <- Vectorize(d2r)
-
-z2r <- function(z){
-  #test z <- 3.4
-  if(is.na(z)){NA}else{tanh(z)}
-}
-
-z2r <- Vectorize(z2r)
-
-od2r <- function(or, method=c("pearson","digby")){
-  #DOI:10.1037/0003-066X.62.3.254
-  if(is.na(or)){NA
-    }else{switch(method,
-         pearson = cos(pi/(1+or^.5)),
-         digby = (or^(3/4)-1)/(or^(3/4)+1)
-  )
-    }
-}
-
-od2r <- Vectorize(od2r)
 
 ## Convert effects data ####
 
@@ -52,7 +14,50 @@ simplify_effects <- function(data){
   return(d)
 }
 
-convert_data <- function(data){
+convert_effects <- function(data){
+  # Conversion functions
+  
+  b2r <- function(beta){
+    # conversion formula from 10.1007/s11162-011-9232-5
+    r <- NA
+    if(!is.na(beta)){
+      r <- beta 
+    }
+    r
+  }
+  
+  b2r <- Vectorize(b2r)
+  
+  d2r <- function(d, a = 4){
+    #assumes equal groups
+    #https://www.meta-analysis.com/downloads/Meta-analysis%20Converting%20among%20effect%20sizes.pdf
+    #10.1002/jrsm.1218
[…]

### 2021-05-14 _targets.R

@@ -1,28 +1,49 @@
 library(targets)
-
-source(here::here("R","functions.R"))
+library(tarchetypes)
+source(here::here("R", "functions.R"))
 options(tidyverse.quiet = TRUE)
-tar_option_set(packages = c("tidyverse", "janitor","here", "glue", "fuzzyjoin",
-                            "googlesheets4", "refinr", "tidyr")
-)
-tar_pipeline(
+tar_option_set(packages = c(
+  "tidyverse", "janitor", "here", "glue", "fuzzyjoin",
+  "googlesheets4", "refinr", "tidyr"
+))
+
+list(
+  # Data sources
   tar_target(
-    read_data,
-    read_sheet()
+    modified_date,
+    get_mod_date(),
+    # Force run if outdated or doesn't exist
+    cue = tar_cue_force(condition = ifelse(tar_exist_objects("modified_date"),
+                        get_mod_date() != tar_read(modified_date),
+                        TRUE))
   ),
   tar_target(
-    simple_effects,
-    simplify_effects(read_data)
+    effects_raw,
+    read_sheet(modified_date, "EffectSizesValidation")
   ),
   tar_target(
-    converted_data,
-    convert_data(simple_effects)
+    reviews_raw,
+    read_sheet(modified_date, "ReviewLevelValidation")
   ),
-  tar_target(write_out,
-    googlesheets4::write_sheet(converted_data, ss= "1yEdtTxP0RIc3Td7lswTf7ySJJ_Jr6Qu9LWaIYV8_00k")
+  tar_target(
+    rob_raw,
+    read_sheet(modified_date, "QualityAssessment")
   ),
-  tarchetypes::tar_knit(
-    report,
-    "report.Rmd"
+  # Data cleaning
+  tar_target(
+    effects_clean,
+    process_effects(effects_raw),
   )
+  # tar_target(
+  #   simple_effects,
+  #   simplify_effects(read_data)
+  # ),
+  # tar_target(
+  #   converted_data,
+  #   convert_data(simple_effects)
+  # ),
+  # tarchetypes::tar_knit(
+  #   report,
+  #   "report.Rmd"
+  # )
 )

### 2021-05-17 index.Rmd
Fix report

---
title: "Screen Time Review of Reviews Summary"
output:
  rmdformats::html_clean:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    fig_caption: true
    use_bookdown: true
    number_sections: false
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.retina=2
)

library(tidyverse)
library(targets)
library(xfun)
library(DiagrammeR)
```

# Results

## Search Results

```{r, load-targets}
tar_load(prisma)
tar_load(effects_clean)
tar_load(reviews_table)
tar_load(plots)
```

The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were removed as duplicates. After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts inclusion. `r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these studies.

After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total effect size. This process yielded `r prisma$data$value[9]` unique effects/outcome combinations.

```{r, fig.cap="PRISMA Diagram"}
prisma$diag
```

## Review Characteristics {.tabset}

### Interactive

```{r}
reviews_table$DT
```

### Print

```{r}
reviews_table$kable
```

## Forest Plots {.tabset}

### Health Behaviour

```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
plots$`Health Behaviour`
```

### Physical Health

```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
plots$`Physical Health`
```

### Psychology

```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
plots$Psychology
```

### Education

```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
plots$Education
```

# Appendix

## Assumptions

I made the following assumptions which may or may not be reasonable:

1.  That $\beta$ is equivilent to $r$ for $\beta < |.5|$ and undefined otherwise (never the case here)
2.  That, given the large sample sizes involved *Hedge's g* and *Cohen's d* where essentially equivalent and that sample sizes used to make up these effects were approximately equal in treatment and control groups.
3.  In the absence of information that could be used to construct a 2x2 contingency table that ORs and Relative Risk Ratios were equivalent and thus Relative Risk Ratios were converted to $r$ as if they were Odds ratios.
4.  External to any other information that all forms of SMD, weighted means etc. were equivilent to Cohen's d.

## Project Structure
```{r message=FALSE, warning=FALSE}
tar_visnetwork()
```

### 2021-05-17 R/PRISMA.R

@@ -2,10 +2,10 @@ library(DiagrammeR)
 library(tidyverse)
 
 make_prisma <- function(covidence_export, effects_clean) {
-
+  
   # Get Covidence PRISMA data
   covidence_export <- read_file(covidence_export)
-
+  
   dat <-
     # Convert each to a separate line
     tibble(text = unlist(str_split(covidence_export, pattern = "\\n"))) %>%
@@ -33,7 +33,7 @@ make_prisma <- function(covidence_export, effects_clean) {
     if (dat$type[i] == "main") step <- step + 1
     dat$step[i] <- step
   }
-
+  
   exclusion_collapse <- function(data, old_rows, new_row) {
     bind_rows(
       data %>% filter(!text %in% old_rows),
@@ -43,8 +43,8 @@ make_prisma <- function(covidence_export, effects_clean) {
         mutate(text = new_row, type = "exclude_reason")
     )
   }
-
-
+  
+  
   # Modify dataframe (add rows as needed)
   dat <- dat %>%
     exclusion_collapse(
@@ -77,31 +77,31 @@ make_prisma <- function(covidence_export, effects_clean) {
       "Wrong exposure - clinical health intervention"
     ) %>%
     arrange(step, desc(value))
-
+  
   dat <- dat %>% add_row(
     text = "studies contributed unique effects",
     type = "main",
     step = dat$step[nrow(dat)] + 1,
     value = n_distinct(effects_clean$covidence_review_id)
   )
-
+  
   # Generate PRISMA Diagram ####
-
+  
   # Convert excl_reason to new column
   dat <- dat %>%
     mutate(text = paste(value, text, sep = " ")) %>%
     group_by(step, type) %>%
     mutate(text = if_else(type == "exclude_reason",
-      paste("&nbsp;&nbsp;&nbsp;&nbsp;&#8226; ",
-        text,
-        collapse = "<br ALIGN = 'LEFT'/> \n"
-      ),
-      text
+                          paste("&nbsp;&nbsp;&nbsp;&nbsp;&#8226; ",
+                                text,
+                                collapse = "<br ALIGN = 'LEFT'/> \n"
+                          ),
+                          text
     )) %>%
     distinct(step, type, .keep_all = TRUE)
-
+  
   labels <- dat$text
-
+  
   prisma <- paste("digraph flowchart {
       # node definitions with substituted label text
[…]

### 2021-05-17 R/forest_plot_code_overview_screentime.R

@@ -66,7 +66,6 @@ make_plots <- function(effects_clean) {
 
   # Make output lists
   plots <- vector(mode = "list", length = length(unique(q$outcome_category)))
-  plots_files <- character(length = length(unique(q$outcome_category)))
   names(plots) <- unique(q$outcome_category)
 
   for (i in 1:length(unique(q$outcome_category))) {
@@ -234,16 +233,27 @@ make_plots <- function(effects_clean) {
       )
 
     plots[[levels(q$outcome_category)[i]]] <- p1
-    file_name <- here::here("figure", paste("Forest plot for ", levels(q$outcome_category)[i], ".pdf", sep = ""))
+  }
+  return(plots)
+}
 
-    ggsave(
-      filename = file_name,
-      plot = p1,
-      width = 12,
-      height = 10
-    )
-
-    plots_files[i] <- file_name
+save_plots <- function(plots){
+  plots_files <- character(length = length(plots))
+  
+  for (i in seq_along(plots)){
+  
+  file_name <- here::here("figure", paste("Forest plot for ", names(plots)[i], ".pdf", sep = ""))
+  
+  plots[i]
+  ggsave(
+    filename = file_name,
+    #plot = plots[i],
+    width = 12,
+    height = 10
+  )
+  
+  plots_files[i] <- file_name
+  
   }
   return(plots_files)
 }

### 2021-05-20 _targets.R
Add target for reading study level data

@@ -1,6 +1,7 @@
 library(targets)
 library(tarchetypes)
 library(here)
+library(tidyverse)
 
 source(here("R", "functions.R"))
 source(here("R", "reviews_table.R"))
@@ -30,6 +31,11 @@ list(
   tar_target(
     rob_raw,
     read_sheet(modified_date, "QualityAssessment")
+  ),
+  tar_target(
+    studies_raw,
+    read_sheet(modified_date, "StudyLevel") %>% 
+      filter(ok_to_import)
   ),
   tar_target(
     prisma_data,

### 2021-07-28 index.Rmd
Add target for reading study level data
Meta analysis (#6)
* Add target for reading study level data

* Move packages into targets format.

* Convert effect sizes.

* Meta-analyse individual study data

* Add some temporary graphs to compare effect sizes

@@
 tar_load(plots)
+tar_load(studies_results)
+tar_load(comparison_plots)
 ```
@@
 
+# Individual Studies
+
+Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes.
+
+## Forest Plots {.tabset}
+
+### Health Behaviour
+
+```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
+comparison_plots$`health behaviour`
+```
+
+### Physical Health
+
+```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
+comparison_plots$`physical health`
+```
+
+### Psychology
+
+```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
+comparison_plots$psychology
+```
+
+### Education
+
+```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
+comparison_plots$education
+```
+
 # Appendix
@@
 ```{r message=FALSE, warning=FALSE}
-tar_visnetwork()
+tar_visnetwork(targets_only = TRUE)
 ```

### 2021-07-28 R/forest_plot_code_overview_screentime.R

@@ -1,8 +1,3 @@
-library(tidyverse)
-library(janitor)
-library(ggtext)
-library(tidyMB)
-
 make_plots <- function(effects_clean) {
   q <- effects_clean %>%
     filter(use_effect == TRUE) %>%

### 2021-07-28 R/functions.R

@@ -1,107 +1,117 @@
 # Targets functions ####
 
-get_mod_date <- function(){
+get_mod_date <- function() {
   x <- googledrive::drive_get(id = googledrive::as_id("1z_NZwDomPfrOJg2Rn8-E8cc9yoOjXzqH_Di23vWERu4"))
   return(x$drive_resource[[1]]$modifiedTime)
 }
 
-## Convert effects data ####
+# Convert effects data ####
 
-simplify_effects <- function(data){
-  d = data %>%
-    dplyr::filter(es %in% c("b", "d", "r", "or", "z")) %>%
-    dplyr::rename(std_eff_name = es)
-  return(d)
-}
-
-convert_effects <- function(data){
+convert_effects <- function(data) {
   # Conversion functions
-  
-  b2r <- function(beta){
+
+  b2r <- function(beta) {
     # conversion formula from 10.1007/s11162-011-9232-5
     r <- NA
-    if(!is.na(beta)){
-      r <- beta 
+    if (!is.na(beta)) {
+      r <- beta
     }
     r
   }
-  
+
   b2r <- Vectorize(b2r)
-  
-  d2r <- function(d, a = 4){
-    #assumes equal groups
-    #https://www.meta-analysis.com/downloads/Meta-analysis%20Converting%20among%20effect%20sizes.pdf
-    #10.1002/jrsm.1218
-    if(is.na(d)){NA}else{d/(sqrt(d^2+a))}
-  }
-  
-  d2r <- Vectorize(d2r)
-  
-  z2r <- function(z){
-    #test z <- 3.4
-    if(is.na(z)){NA}else{tanh(z)}
-  }
-  
-  z2r <- Vectorize(z2r)
-  
-  od2r <- function(or, method=c("pearson","digby")){
-    #DOI:10.1037/0003-066X.62.3.254
-    if(is.na(or)){NA
-    }else{switch(method,
-                 pearson = cos(pi/(1+or^.5)),
-                 digby = (or^(3/4)-1)/(or^(3/4)+1)
-    )
+
+  d2r <- function(d, a = 4) {
+    # assumes equal groups
+    # https://www.meta-analysis.com/downloads/Meta-analysis%20Converting%20among%20effect%20sizes.pdf
+    # 10.1002/jrsm.1218
+    if (is.na(d)) {
+      NA
+    } else {
+      d / (sqrt(d^2 + a))
     }
   }
-  
+
[…]

### 2021-07-28 _targets_packages.R

@@ -1,0 +1,25 @@
+# Generated by targets::tar_renv(): do not edit by hand
+library(broom)
+library(bs4Dash)
+library(clustermq)
+library(DiagrammeR)
+library(DT)
+library(esc)
+library(future)
+library(ggforce)
+library(ggforestplot)
+library(ggplot2)
+library(ggtext)
+library(gt)
+library(janitor)
+library(kableExtra)
+library(markdown)
+library(metafor)
+library(pingr)
+library(rstudioapi)
+library(shiny)
+library(shinybusy)
+library(shinyWidgets)
+library(tidyMB)
+library(tidyverse)
+library(visNetwork)

### 2021-08-16 index.Rmd
Add reverse coding
Fix Ns with mean imputation

@@
 After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total effect size.
-This process yielded `r prisma$data$value[9]` unique effects/outcome combinations.
+This process yielded `r nrow(effects_clean)` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
 
@@
 
-Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes.
+Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes, out of `r nrow(effects_clean)` total effects (`r scales::percent(nrow(studies_results)/nrow(effects_clean))`) .
 
@@
 ```
+
+The following warnings were noted during the project build:
+
+```{r}
+tar_meta(fields = warnings) %>% filter(!is.na(warnings)) %>% arrange(name)
+```

### 2021-08-16 _targets.R

@@ -22,7 +22,8 @@ tar_option_set(packages = c(
   "kableExtra",
   "metafor",
   "tidyMB",
-  "tidyverse"
+  "tidyverse",
+  "scales"
 ))
 
 list(

### 2021-08-18 index.Rmd

@@
 
-```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
+```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=15}
 comparison_plots$`health behaviour`
@@
 
-```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
+```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=15}
 comparison_plots$`physical health`
@@
 
-```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
+```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=15}
 comparison_plots$psychology
@@
 
-```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
+```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=15}
 comparison_plots$education

### 2021-09-07 index.Rmd
Add results section

@@
     toc: false
+
 ---
@@
 
-# Results
-
-## Search Results
-
 ```{r, load-targets}
@@
 tar_load(comparison_plots)
+tar_load(combined_effects)
+```
+
+# Results
+
+## Search Results
+
+```{r results}
+rename_effects <- function(cur_name) {
+  if (str_detect(cur_name, ":")) {
+
+  cur_name_split <- str_split(cur_name, ": ")
+  return(str_to_lower(paste(cur_name_split[[1]][2], 
+                            cur_name_split[[1]][1])))
+  } else {
+    return(str_to_lower(cur_name))
+  }
+}
+rename_effects <- Vectorize(rename_effects)
+
+unique_effects <- nrow(effects_clean %>% filter(use_effect))
+
+freq_exposures <-  effects_clean %>% 
+  group_by(plain_language_exposure) %>% 
+  summarise(n=n()) %>% 
+  arrange(desc(n)) %>% 
+  mutate(plain_language_exposure = rename_effects(plain_language_exposure),
+         plain_language_exposure = str_replace_all(plain_language_exposure, 
+                                               c("lifestyle risk behaviour (at school) intervention" =                                             "digital interventions for lifestyle risk behaviours")),
+         out = paste0(plain_language_exposure, " (n = ", n, ")"))
+
+freq_outcomes <- effects_clean %>% 
+  group_by(plain_language_outcome) %>% 
+  summarise(n=n()) %>% 
+  arrange(desc(n)) %>%   
+  mutate(plain_language_outcome = rename_effects(plain_language_outcome),
+         out = paste0(plain_language_outcome, " (n = ", n, ")"))
+
+freq_combos <- effects_clean %>% 
+  group_by(plain_language_exposure, plain_language_outcome) %>% 
+  summarise(n=n()) %>% 
+  arrange(desc(n))
 ```
@@
 The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were removed as duplicates.
-After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts inclusion.
+After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
 `r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these studies.
+Figure \@ref(fig:prisma) presents the full results of the study selection process.
 
-After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total effect size.
-This process yielded `r nrow(effects_clean)` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
-
-```{r, fig.cap="PRISMA Diagram"}
+```{r prisma, fig.cap="PRISMA Diagram"}
 prisma$diag
 ```
+
+After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.
+This process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
+The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
+The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:4])`.
+In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` three or more times.
+Full characteristics of the included studies are provided in Table X.
+
+## Study Quality
+
+```{r}
+reviews_count <- reviews_table$data %>% 
+  mutate(across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed", as.factor)) %>% 
+  rowwise() %>% 
+  mutate(count_low = sum(c_across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed")=="Low"))
+
+all_low <- reviews_count %>%
+  filter(count_low==7) %>% 
+  nrow()
+
+reviews_count <-
+  reviews_count %>%
+  select("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed") %>%
+  gather(name, value) %>%
+  count(name, value) %>%
+  arrange(desc(n))
+
+n_low_hetero <- reviews_count[reviews_count$name=="Heterogeneity Assessed" & reviews_count$value=="Low","n"]
+n_low_char <- reviews_count[reviews_count$name=="Included Studies Listed With Important Characteristics And Results Of Each" & reviews_count$value=="Low","n"]
+n_low_search <- reviews_count[reviews_count$name=="Literature Search Strategy Comprehensive And Systematic" & reviews_count$value=="Low","n"]
+
+n_unclear_elig <- reviews_count[reviews_count$name=="Eligibility Criteria Predefined And Specified" & reviews_count$value=="Unclear","n"]
+
+n_high_dualscreen <- reviews_count[reviews_count$name=="Dual Independent Screening Review" & reviews_count$value=="High","n"]
+n_unclear_dualscreen <- reviews_count[reviews_count$name=="Dual Independent Screening Review" & reviews_count$value=="Unclear","n"]
+
+n_high_dualquality <- reviews_count[reviews_count$name=="Dual Independent Quality Assessment" & reviews_count$value=="High","n"]
+n_unclear_dualquality <- reviews_count[reviews_count$name=="Dual Independent Quality Assessment" & reviews_count$value=="Unclear","n"]
+
+```
+
+The quality of the included studies was mixed.
+Most studies assessed heterogeneity (n = `r n_low_hetero`), reported the characteristics of the included studies (n = `r n_low_char`), and used a comprehensive and systematic search strategy (n = `r n_low_search`).
+Most studies did not clearly report if their eligibility criteria was predefined (n unclear = `r n_unclear_elig`).
+Many studies also did not complete dual independent screening of abstracts and full text (n = `r n_high_dualscreen`) or did not clearly report the method of screening (n = `r n_unclear_dualscreen`).
+A similar trend was observed for dual independent quality assessment (n high = `r n_high_dualquality`; n unclear = `r n_unclear_dualquality`).
+Overall, only `r all_low` studies were graded as *low* on all criteria.
+
+## Education Outcomes
+
+```{r}
+n_edu_effect <- nrow(effects_clean %>% filter(outcome_category=="education" & use_effect))
+n_edu_certain <- nrow(combined_effects %>% filter(outcome_category=="education" &
+                                                    certainty == "meets criteria"))
+```
+
+There were `r n_edu_effect` unique effects with education outcomes, including general learning outcomes, literacy, numeracy, and science (see Figure X).
+Of these, `r n_edu_certain` met our criteria for robust evidence.
+General screen use, TV viewing, and video games were all negatively associated with academic performance, and general screen use was further negatively associated with general learning and general literacy outcomes.
+Conversely, numeracy focused video games and screen-based interventions which target mathematics were positively associated with numeracy outcomes.
+There was substantial evidence to suggest that general screen time that occurred with an adult (i.e., coviewing) and education television are not associated with literacy outcomes (i.e., were not significantly different from zero).
+It is notable that of these results, heterogeneity was high for all except for the video games and academic achievement association.
+
+## Health Behaviour Outcomes
+
+```{r}
+n_hb_effect <- nrow(effects_clean %>% filter(outcome_category=="health behaviour" & use_effect))
+n_hb_certain <- nrow(combined_effects %>% filter(outcome_category=="health behaviour" &
+                                                    certainty == "meets criteria"))
+```
+
+We identified `r n_hb_effect` unique health outcome exposure combinations, which were further grouped into diet, healthy behaviour, physical activity, risky behaviour, screen time, and sleep.
+See Figure X for all combinations of exposure and outcome.
+`r xfun::numbers_to_words(n_hb_certain)` effects met the criteria for certainty.
+Advertising of unhealthy foods---both traditional advertising and video games developed by a brand for promotion---were associated higher food intake.
+Social media use was also associated with higher risk of substance abuse, while screen-based interventions which target health behaviours appear effective.
+Television was negatively correlated with sleep duration, but only at the 95% confidence level, and was not statistically significant at our more stringent 99.9% confidence level.
+As with the education outcomes, there was substantial unexplained heterogeneity around the findings.
+
+## Physical Health
+
+```{r}
+n_ph_effect <- nrow(effects_clean %>% filter(outcome_category=="physical health" & use_effect))
+n_ph_certain <- nrow(combined_effects %>% filter(outcome_category=="physical health" &
+                                                    certainty == "meets criteria"))
+```
+
+There were `r n_ph_effect` unique effects identified for physical health, but only `r xfun::numbers_to_words(n_ph_certain)` met the criteria for certainty.
+General screen use, television viewing, and video games were all detrimentally associated with body composition, although all also had high levels of heterogeneity.
+None of the effects in the other categories---cardiometabolic health, eye health, and other physical health---met our criteria for certainty.
+
+## Psychology
+
+```{r}
+n_psyc_effect <- nrow(effects_clean %>% filter(outcome_category=="psychology" & use_effect))
+n_psyc_certain <- nrow(combined_effects %>% filter(outcome_category=="psychology" &
+                                                    certainty == "meets criteria"))
+```
+
+We identified `r n_psyc_effect` unique effects which were categorised as psychological outcomes, with `r xfun::numbers_to_words(n_psyc_certain)` meeting the criteria for certainty.
+General screen use was associated with a small increased risk of depression.
+Social media use was associated with greater risk taking, and with higher instances of safe sex.
+Viewing of sexy media was associated with high sexual activity and with higher initiation of sex.
+All of these effects had substantial heterogeneity.
 
@@
 
-### Health Behaviour
+### `r plots[[1]]$name`
 
-```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
-plots$`Health Behaviour`
+```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12, fig.height=10}
+plots[[1]]$plot
 ```
 
-### Physical Health
+### `r plots[[2]]$name`
 
-```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
-plots$`Physical Health`
+```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12, fig.height=10}
+plots[[2]]$plot
 ```
 
-### Psychology
+### `r plots[[3]]$name`
 
-```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
-plots$Psychology
+```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12, fig.height=10}
+plots[[3]]$plot
 ```
 
-### Education
+### `r plots[[4]]$name`
 
-```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
-plots$Education
+```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12, fig.height=10}
+plots[[4]]$plot
 ```

### 2021-09-16 index.Rmd
Seperate meets vs doesn't meet credibility criteria

@@
 
-```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12, fig.height=10}
+```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12}
 plots[[1]]$plot
@@
 
-```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12, fig.height=10}
+```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12}
 plots[[2]]$plot
@@
 
-```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12, fig.height=10}
+```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12}
 plots[[3]]$plot
@@
 
-```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12, fig.height=10}
+```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12}
 plots[[4]]$plot
@@
 
-## Forest Plots {.tabset}
+## Supplementary Forest Plots {.tabset}
 
-### Health Behaviour
+### `r plots[[1]]$name`
 
-```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=15}
-comparison_plots$`health behaviour`
+```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12}
+plots[[1]]$suppplot
 ```
 
-### Physical Health
+### `r plots[[2]]$name`
 
-```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=15}
-comparison_plots$`physical health`
+```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12}
+plots[[2]]$suppplot
 ```
 
-### Psychology
+### `r plots[[3]]$name`
 
-```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=15}
-comparison_plots$psychology
+```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12}
+plots[[3]]$suppplot
 ```
 
-### Education
+### `r plots[[4]]$name`
 
-```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=15}
-comparison_plots$education
+```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12}
+plots[[4]]$suppplot
 ```

### 2021-09-23 reports/manuscript.Rmd
Update to report format

---
title: "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
author:
  - name: Taren Sanders
    url: https://orcid.org/0000-0002-4504-6008
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4504-6008
  - name: Philip Parker
    url: https://orcid.org/0000-0002-4604-8566 
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-4604-8566
  - name: Michael Noetel
    url: https://orcid.org/0000-0002-6563-8203 
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 0000-0002-6563-8203
  - name: Chris Lonsdale
    url: https://orcid.org/000-0002-2523-5565  
    affiliation: Australian Catholic University
    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
    orcid_id: 000-0002-2523-5565 
date: "`r Sys.Date()`"
repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
bibliography: combined.bib
csl: nature.csl
---

```{r setup, include=FALSE}
# This allows distill to render from a targets pipeline
Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.retina=2
)

# Uncomment to run outside of pipeline
# library(tidyverse)
# library(targets)
# library(xfun)
# library(DiagrammeR)
```

```{r, load-targets}
targets::tar_load(c("prisma", "effects_clean", "reviews_table", "plots", 
           "studies_results", "comparison_plots", "combined_effects", 
           "combined_bib"), 
         store = here::here("_targets"))
```

# Background

In the 16th century, hysteria reigned around a new technology that threatened to be "confusing and harmful" to the mind. The cause of such concern? The widespread availability of books brought about by the invention of the printing press [@blairReadingStrategiesCoping2003]. In the early 19th century, concerns about schooling "exhausting the children's brains" followed, with the medical community accepting that excessive study could be a cause of madness [@bell1883sanitarian]. By the 20th century, the invention of the radio was accompanied by assertions that it would distract children from their reading (which by this point was no longer considered "confusing and harmful") leading to impaired learning [@dill2013oxford].

Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen time (e.g., TV or computers) [@wartellaChildrenComputersNew2000]. Excessive screen time is the number one concern parents have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top]. Yet, the evidence to support parents' concerns is lacking. A 2019 Lancet editorial [@thelancetSocialMediaScreen2019a] suggested that , "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."

While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015a;sweetserActivePassiveScreen2012a], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004a;@warburton2017children]. Thus, efforts to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019]. With concerns over the impact of screen time including education, health, and psychological well-being, a broad overview that acknowledges screen time's potential benefits and risks is needed.

Citing the negative effects on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016;@whoGuidelinesPhysicalActivity2019] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited. For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens. They also recommend that children aged 2-5 years should spend a maximum of one hour exposed to recreational sedentary screen time per day, while children aged 5-12 and adolescents should spend no more than two hours. In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health [@fergusonEverythingModerationModerate2017], and might, in fact, benefit their well being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day). Some research also indicates that content (e.g., video game vs television program) may also play an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017]. Indeed, educational screen time has been found to be positively related to educational outcomes [@sandersTypeScreenTime2019]. This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required.

In 2016, the American Academy of Pediatrics used a narrative review examining the benefits and risks of children and adolescents' electronic media [@chassiakosChildrenAdolescentsDigital2016] as a basis for updating their guidelines [@AAPMediaUseSchoolAged2016]. Since then, a large number of systematic reviews and meta-analyses have provided up-to-date evidence about the potential benefits and risks of screentime. No review has synthesised the evidence available across relevant outcomes, such physical health, health behaviours, education, and psychological well being.

In order to support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen time on young children, children, and adolescents. This review includes the association between electronic media use and any variable that is a plausible outcome of this exposure. Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives. By synthesising across life domains, this review provides evidence to support more targeted guidelines and advice for parents, teachers, and other professionals in order to maximise human functioning.

# Methods

### Eligibility criteria

*Population*: To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents ( age 0-18 years). Meta-analyses containing data from adults and youth were included if meta-analytic effect sizes estimates specific to participants aged 18 years or less could be extracted. We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).
*Exposure*: We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computer, tablet, TV, and mobile phones. We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content  (e.g., television programs, movies, games), homework, and communication (e.g., video chat). In this review we adopted a population-level perspective, meaning that we examined electronic media exposure that occurs during typical daily living activities (e.g., home, school-based electronic media exposure). Consistent with this population-level approach, we excluded technology-based treatments for clinical conditions. 
*Outcomes*: We included all reported outcomes.
*Publications*: We included meta-analyses (or meta-regressions) of quantitative evidence. To be included, meta-analyses needed to analyse data from studies identified in a systematic review. For our purposes, a systematic review is a review in which the authors attempted to acquire all the research evidence that pertained to their research question(s). We excluded meta-analyses that did not attempt to summarise all the available evidence (e.g., a meta-analysis of all studies from one laboratory). We included meta-analyses regardless of the study designs included in the review (e.g., laboratory-based experimental studies, randomised controlled trials. non-randomised controlled trials, longitudinal, cross-sectional, case studies), as long as the studies in the review collected quantitative evidence. We excluded systematic reviews of qualitative evidence. We did not formulate inclusion/exclusion criteria related to the risk of bias of the review. We did, however, employ a risk of bias tool to help us interpret the results. We included full-text, peer-reviewed meta-analyses published or ‘in-press’ in English. We excluded conference abstracts and meta-analyses that were unpublished.

### Information sources

We searched records contained in the following databases: Pubmed, MEDLINE, CINAHL, PsycINFO, SPORTDiscus, Education Source, Embase, Cochrane Library, Scopus, Web of Science, ProQuest Social Science Premium Collection, and ERIC. We conducted an initial search on August 17, 2018 and refreshed the search on May 13, 2020. We searched reference lists of included papers in order to identify additional eligible meta-analyses. We also searched PROSPERO to identify relevant protocols and contacted authors to determine if these reviews have been completed and published.

### Search strategy

The search strategy associated with each of the 12 databases can be found [here](https://docs.google.com/document/d/1hz5Dgw0aVOMeXL3vpRXsNtCIbf6dHZTb8uz7wQ29ke4/edit#heading=h.i6znptfz9nwa). We hand searched reference lists from any relevant umbrella reviews to identify systematic meta-analyses that our search may have missed.

### Selection process

Using Covidence software (Veritas Health Innovation, Melbourne, Australia), two researchers independently screened all titles and abstracts. Two researchers then independently reviewed full-text articles. We resolved disagreements at each stage of the process by consensus, with a third researcher employed, when needed.

### Data collection process
Two researchers independently extracted data from the included meta-analyses into a custom-designed database.

### Data items

From each meta-analysis we extracted the following items: First author, year of publication, earliest and latest study publication dates, sample age, lowest and highest mean age reported, study design restrictions (e.g., cross-sectional, observational, experimental), region restrictions (e.g., specific countries), exposures reported, and outcomes reported.

### Study risk of bias assessment

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014]. We resolved disagreements by consensus, with a third researcher employed, when needed. We did not assess risk of bias in the individual studies that were included in each meta-analysis.

### Effect measures

Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results. Where possible, they also extracted effect sizes from primary studies included in each meta-analysis. To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bonettTransformingOddsRatios2007;@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017]. We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to do so. Effect sizes on the original metric are provided in supplementary materials.

### Synthesis methods

After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size. We excluded effect size estimates when the authors did not provide a sample size. We descriptively present the remaining meta-analytic effect sizes. When the meta-analysis’s authors provided primary study data associated with these effects we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base; version `r paste(R.Version()[c("major", "minor")], collapse = ".")`]. When required, we imputed missing sample sizes using mean imputation from the other studies within that review. From our reanalysis we also extracted I2 values. To test for publication bias, we also conducted Egger's test [@eggerBiasMetaanalysisDetected1997] where the number of studies within the review was ten or more [@pageChapter13Assessing2021], and conducted a test of excess significance [@ioannidisExploratoryTestExcess2007]. We contacted authors who did not provide primary study data in their published article. Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.

# Supplementary Material

### 2021-09-23 reports/sundries.Rmd
Update to report format

--- 2021-08-18 index.Rmd
@@
----
-title: "Screen Time Review of Reviews Summary"
-output:
-  rmdformats::html_clean:
-    self_contained: true
-    thumbnails: true
-    lightbox: true
-    gallery: true
-    highlight: tango
-    fig_caption: true
-    use_bookdown: true
-    number_sections: false
-    toc: false
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = FALSE,
-	warning = FALSE,
-	fig.retina=2
-)
-
-library(tidyverse)
-library(targets)
-library(xfun)
-library(DiagrammeR)
-```
-
-# Results
-
-## Search Results
-
-```{r, load-targets}
-tar_load(prisma)
-tar_load(effects_clean)
-tar_load(reviews_table)
-tar_load(plots)
-tar_load(studies_results)
-tar_load(comparison_plots)
-```
-
-The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were removed as duplicates.
-After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts inclusion.
-`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these studies.
-
-After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total effect size.
-This process yielded `r nrow(effects_clean)` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
-
-```{r, fig.cap="PRISMA Diagram"}
-prisma$diag
-```
-
-## Review Characteristics {.tabset}
-
-### Interactive
-
-```{r}
-reviews_table$DT
-```
-
-### Print
-
-```{r}
-reviews_table$kable
-```
-
-## Forest Plots {.tabset}
-
-### Health Behaviour
-
-```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
-plots$`Health Behaviour`
-```
-
-### Physical Health
-
-```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
-plots$`Physical Health`
-```
-
-### Psychology
-
-```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
-plots$Psychology
-```
-
-### Education
-
-```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
-plots$Education
-```
-
-# Individual Studies
-
-Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes, out of `r nrow(effects_clean)` total effects (`r scales::percent(nrow(studies_results)/nrow(effects_clean))`) .
-
-## Forest Plots {.tabset}
-
-### Health Behaviour
-
-```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=15}
-comparison_plots$`health behaviour`
-```
-
-### Physical Health
-
-```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=15}
-comparison_plots$`physical health`
-```
-
-### Psychology
-
-```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=15}
-comparison_plots$psychology
-```
-
-### Education
-
-```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=15}
-comparison_plots$education
-```
-
-# Appendix
-
 ## Assumptions
@@
 ## Project Structure
+
 ```{r message=FALSE, warning=FALSE}

### 2021-09-23 _targets.R

@@ -6,27 +6,17 @@ source(here("R", "functions.R"))
 source(here("R", "reviews_table.R"))
 source(here("R", "PRISMA.R"))
 source(here("R", "forest_plot_code_overview_screentime.R"))
+source(here("R", "utils.R"))
 
 options(tidyverse.quiet = TRUE, clustermq.scheduler = "multiprocess")
 
-tar_option_set(packages = c(
-  "broom",
-  "DiagrammeR",
-  "DT",
-  "esc",
-  "emojifont",
-  "ggh4x",
-  "ggplot2",
-  "ggtext",
-  "ggforestplot", # TEMP
-  "ggforce", # TEMP
-  "janitor",
-  "kableExtra",
-  "metafor",
-  "tidyMB",
-  "tidyverse",
-  "scales"
-))
+packages <- c("base","broom", "DiagrammeR", "DT", "esc", "emojifont", "ggh4x", 
+               "ggplot2", "ggtext",  "janitor", "knitr", "kableExtra", 
+               "metafor", "tidyMB", "tidyverse", "scales", "xfun",
+               # TEMP
+               "ggforestplot",  "ggforce")
+
+tar_option_set(packages = packages)
 
 list(
   # Data sources
@@ -122,8 +112,21 @@ list(
     format = "file",
     pattern = map(plots)
   ),
+  # REPORTS --------------------------------
+  tar_target(packages_bib, create_packages_bib(packages, 
+                                               here::here("reports",
+                                                          "packages.bib")), 
+             format="file"),
+  tar_target(references_bib, here::here("reports","references.bib"), format="file"),
+  tar_target(combined_bib, combine_bibs(packages_bib, 
+                                        references_bib, 
+                                        here::here("reports","combined.bib")), 
+             format="file"),
   tarchetypes::tar_render(
-    report,
-    "index.Rmd",
+    distill_report,
+    path = here::here("reports","manuscript.Rmd"),
+    output_file = here::here("index.html"),
+    output_yaml = here::here("reports","distill.yaml")
   )
 )
+

### 2021-09-24 reports/manuscript.Rmd
Update report to match GDoc

@@
 csl: nature.csl
+always_allow_html: true
+output:
+  distill::distill_article:
+    toc: true
+    toc_depth: 2
 ---
@@
 	message = FALSE,
-	warning = FALSE,
-	fig.retina=2
+	warning = FALSE
 )
@@
 # Uncomment to run outside of pipeline
-# library(tidyverse)
-# library(targets)
-# library(xfun)
-# library(DiagrammeR)
+library(tidyverse)
+library(targets)
+library(xfun)
+library(DiagrammeR)
 ```
@@
 
-While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015a;sweetserActivePassiveScreen2012a], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004a;@warburton2017children].
+While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015a;@sweetserActivePassiveScreen2012a], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004a;@warburton2017children].
 Thus, efforts to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].
@@
 
+\newpage
+
 # Methods
@@
 We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).
+
 *Exposure*: We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computer, tablet, TV, and mobile phones.
@@
 Consistent with this population-level approach, we excluded technology-based treatments for clinical conditions.
+
 *Outcomes*: We included all reported outcomes.
+
 *Publications*: We included meta-analyses (or meta-regressions) of quantitative evidence.
@@
 We descriptively present the remaining meta-analytic effect sizes.
-When the meta-analysis’s authors provided primary study data associated with these effects we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base; version `r paste(R.Version()[c("major", "minor")], collapse = ".")`].
+When the meta-analysis’s authors provided primary study data associated with these effects we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base] (version `r paste(R.Version()[c("major", "minor")], collapse = ".")`).
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
@@
 
+### Evidence assessment criteria
+
+*Statistical Credibility*.
+We employed a statistical classification approach to grade the statistical credibility of the effect sizes in the literature.
+To be considered credible an effect needed to be derived from a combined sample of >1,000 and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
+
+*Consistency of Effect within the Population*.
+We also examined the consistency of the effect size using the $I^2$ measure.
+We considered $I^2 < 50\%$ to indicate effects that were relatively consistent across the population of interest.
+$I^2$ values of $> 50\%$ were taken to indicate an effect was potentially heterogeneous within the population.
+
+*Direction of Effect*.
+Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
+We used thresholds of $P < .05$ for weak evidence and $P < 10^{-3}$ for strong evidence.
+An effect that was neither significant at $P < .05$ or $10^{-3}$ that also passed the criteria for statistical credibility was taken to indicate no association of interest.
+
+### Deviations from protocol
+
+We initially planned to include systematic reviews without meta-analyses in a narrative summary alongside the main meta-analytic findings.
+However, we determined that combining results from the meta-analyses provided a robust overview.
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in eSupplementary File X.
+
+# Results
+
+### Search Results
+
+```{r results}
+rename_effects <- function(cur_name) {
+  if (str_detect(cur_name, ":")) {
+
+  cur_name_split <- str_split(cur_name, ": ")
+  return(str_to_lower(paste(cur_name_split[[1]][2], 
+                            cur_name_split[[1]][1])))
+  } else {
+    return(str_to_lower(cur_name))
+  }
+}
+rename_effects <- Vectorize(rename_effects)
+
+unique_effects <- nrow(effects_clean %>% filter(use_effect))
+
+freq_exposures <-  effects_clean %>% 
+  group_by(plain_language_exposure) %>% 
+  summarise(n=n()) %>% 
+  arrange(desc(n)) %>% 
+  mutate(plain_language_exposure = rename_effects(plain_language_exposure),
+         plain_language_exposure = case_when(
+           plain_language_exposure=="lifestyle risk behaviour (at school) intervention" ~"screen-based lifestyle risk behaviour interventions (at school)",
+           TRUE ~ plain_language_exposure),
+         out = paste0(plain_language_exposure, " (n = ", n, ")"))
+
+freq_outcomes <- effects_clean %>% 
+  group_by(plain_language_outcome) %>% 
+  summarise(n=n()) %>% 
+  arrange(desc(n)) %>%   
+  mutate(plain_language_outcome = rename_effects(plain_language_outcome),
+         out = paste0(plain_language_outcome, " (n = ", n, ")"))
+
+freq_combos <- effects_clean %>% 
+  group_by(plain_language_exposure, plain_language_outcome) %>% 
+  summarise(n=n()) %>% 
+  arrange(desc(n))
+```
+
+The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were removed as duplicates.
+After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
+`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these studies.
+Figure \@ref(fig:prisma) presents the full results of the study selection process.
+
+```{r prisma, fig.cap="PRISMA Diagram"}
+prisma$diag
+```
+
+After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.
+This process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
+
+The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
+The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
+In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` three or more times.
+Full characteristics of the included studies are provided in Table X.
+
+```{r}
+qual_data <- reviews_table$data %>%
+  filter(`Outcomes Assessed` !="<ul><li></li></ul>")
+
+reviews_count <- qual_data %>% 
+  mutate(across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed", as.factor)) %>% 
+  rowwise() %>% 
+  mutate(count_low = sum(c_across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed")=="Low"))
+
+all_low <- reviews_count %>%
+  filter(count_low==7) %>% 
+  nrow()
+
+reviews_count <-
+  reviews_count %>%
+  select("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed") %>%
+  gather(name, value) %>%
+  count(name, value) %>%
+  arrange(desc(n))
+
+qual_str <- function(n, totaln, ntype="", prefix="(n", suffix=")"){
+  paste0(prefix,ntype,"= ",n,"/",totaln,", ", scales::percent(n/totaln, accuracy = 1), suffix)
+}
+
+n_low_hetero <-
+  reviews_count[reviews_count$name == "Heterogeneity Assessed" &
+                  reviews_count$value == "Low", "n"][[1]]
+n_low_char <-
+  reviews_count[reviews_count$name == "Included Studies Listed With Important Characteristics And Results Of Each" &
+                  reviews_count$value == "Low", "n"][[1]]
+n_low_search <-
+  reviews_count[reviews_count$name == "Literature Search Strategy Comprehensive And Systematic" &
+                  reviews_count$value == "Low", "n"][[1]]
+
+n_unclear_elig <-
+  reviews_count[reviews_count$name == "Eligibility Criteria Predefined And Specified" &
+                  reviews_count$value == "Unclear", "n"][[1]]
+
+n_high_dualscreen <-
+  reviews_count[reviews_count$name == "Dual Independent Screening Review" &
+                  reviews_count$value == "High", "n"][[1]]
+n_unclear_dualscreen <-
+  reviews_count[reviews_count$name == "Dual Independent Screening Review" &
+                  reviews_count$value == "Unclear", "n"][[1]]
+
+n_high_dualquality <-
+  reviews_count[reviews_count$name == "Dual Independent Quality Assessment" &
+                  reviews_count$value == "High", "n"][[1]]
+n_unclear_dualquality <-
+  reviews_count[reviews_count$name == "Dual Independent Quality Assessment" &
+                  reviews_count$value == "Unclear", "n"][[1]]
+
+dualqualstr <- paste0(
+  qual_str(n_high_dualquality, nrow(qual_data), " high ", suffix= "; "),
+  qual_str(n_unclear_dualquality, nrow(qual_data), " unclear ", prefix = "n", suffix = ")"))
+
+```
+
+The quality of the included studies was mixed.
+Most studies assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low ")`.
+Most studies did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
+A similar trend was observed for dual independent quality assessment `r dualqualstr`.
+Overall, only `r all_low` were graded as *low* risk of bias on all criteria.
+
+### Education Outcomes
+
+```{r}
+edu_effect <-   
+  combined_effects %>%
+  filter(outcome_category=="education" & use_effect)
+
+edu_certain <-
+  combined_effects %>%
+  filter(outcome_category == "education" & certainty == "meets criteria")
+
+n_edu_effect <-
+  edu_effect %>%
+  nrow()
+
+n_edu_certain <-
+  edu_certain %>% 
+  nrow()
+
+n_edu_noindiv <- 
+  edu_effect %>% 
+  filter(source == "reported") %>% 
+  nrow()
+
+n_edu_samplesize <- 
+  edu_effect %>%
+  filter(source == "reanalysis" & n < 1000) %>% 
+  nrow()
+
+n_edu_faileggers <- 
+  edu_effect %>%
+  filter(source == "reanalysis" & n > 1000 & 
+           (eggers_p < 0.05 | is.na(eggers_p))) %>% 
+  nrow()
+
+n_edu_failtest <- 
+  edu_effect %>% 
+  filter(source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05) %>% 
+  nrow()
+```
+
+There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
+Of these, `r n_edu_certain` met our criteria for statistical credibility and are described below (see Figure \@ref(fig:eduplot)).
+We removed `r n_edu_noindiv` for not providing individual study-level data, `r n_edu_samplesize` for having meta-analytic effects with samples < 1,000, and `r n_edu_faileggers` had a significant Egger's test or insufficient studies to conduct the test.
+No remaining studies showed evidence of excessive significance.
+Effects not meeting one or more of these standards are presented in the supplementary material.
+
+```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
+plots[[1]]$plot
+```
+Among the statistically credible effects, general screen use, TV viewing, and video games were all negatively associated with academic performance or general learning.
+E-books that included narration, as well as touch screen education interventions, and augmented reality interventions were positively associated with learning.
+General screen use was also negatively associated with literacy outcomes.
+However, if the screen involved co-viewing (e.g., watching with a parent) or the content was educational the association with literacy was positive.
+Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
+
+```{r}
+n_edu_p999 <- edu_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
+n_edu_p95 <- edu_certain %>% filter(reanalysis_p.value<0.05) %>% nrow() - n_edu_p999
+
+n_edu_i2 <- edu_certain %>% filter(i2 > 50) %>% nrow()
+```
+
+As shown in Figure \@ref(fig:eduplot), most of the credible results (`r n_edu_p999` of `r n_edu_certain` effects) showed statistically significant associations, with 99.9% confidence intervals not encompassing zero (strong evidence).
+The remaining `r xfun::numbers_to_words(n_edu_p95)` associations were significant at the 95% confidence level (weak evidence).
+All credible effects related to education outcomes were small-to-moderate.
+Screen-based interventions tended to have larger effect sizes than non-intervention exposure (e.g., TV viewing, e-book reading) with the largest effect size observed for augmented reality-based school interventions on general learning ($r = 0.33$).
+Most effects showed high levels of heterogeneity (`r n_edu_i2` of `r n_edu_certain` with $I^2 > 50\%$).
+
+### Health and Health-related Behaviours
+
+```{r}
+health_effect <-   
+  combined_effects %>%
+  filter(outcome_category != "education" & use_effect)
+
+health_certain <-
+  combined_effects %>%
+  filter(outcome_category != "education" & certainty == "meets criteria")
+
+n_health_effect <-
+  health_effect %>%
+  nrow()
+
+n_health_certain <-
+  health_certain %>% 
+  nrow()
+
+n_health_noindiv <- 
+  health_effect %>% 
+  filter(source == "reported") %>% 
+  nrow()
+
+n_health_samplesize <- 
+  health_effect %>%
+  filter(source == "reanalysis" & n < 1000) %>% 
+  nrow()
+
+n_health_faileggers <- 
+  health_effect %>%
+  filter(source == "reanalysis" & n > 1000 & 
+           (eggers_p < 0.05 | is.na(eggers_p))) %>% 
+  nrow()
+
+n_health_failtest <- 
+  health_effect %>% 
+  filter(source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05) %>% 
+  nrow()
+```
+
+We identified `r n_health_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
+`r `xfun::numbers_to_words(n_health_certain, cap=TRUE)`of these meta-analytic associations met our criteria for credible evidence (see Figure \@ref(fig:healthplot)).
+We removed `r n_health_noindiv` for not providing individual study-level data, `r n_health_samplesize` for having meta-analytic effects with samples < 1,000, and `r n_health_faileggers` had a significant Egger's test or insufficient studies to conduct the test.
+No remaining studies showed evidence of excessive significance.
+Effects not meeting one or more of these standards are presented in the supplementary material.
+
+```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
+plots[[2]]$plot
+```
+
+Advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher food intake.
+Social media use was associated with higher risk of substance abuse, while screen-based interventions which target health behaviours appeared effective.
+
+Television was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
+All forms of observed screen time (general, TV, and video games) were positively associated with body composition (e.g., BMI).
+Risky behaviour (e.g., unsafe sex) was also positively associated with social media and with the use of sexy media.
+General screen use was also associated with depression.
+
+```{r}
+n_health_p999 <- health_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
+n_health_p95 <- health_certain %>% filter(reanalysis_p.value<0.05) %>% nrow() - n_edu_p999
+
+n_health_i2 <- health_certain %>% filter(i2 > 50) %>% nrow()
+n_health_r2 <- health_certain %>% filter(abs(r) < 0.2) %>% nrow()
+```
+
+Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the $P < 10^3$ level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at the $P < .05$ level.
+However, all of the credible effects exhibited high levels of heterogeneity, with the lowest $I^2 = 75%$.
+Additionally, most effects were small, with the association between unhealthy food advertising and food intake the largest at $r = 0.25$.
+Most of the effect sizes (`r n_health_r2`/`r n_health_certain`) had an absolute value of $r < 0.2$.
+
+# Discussion
+
 # Supplementary Material
+
+#### Full Size Forest Plots
+
+* [Education Outcomes](https://drive.google.com/file/d/1ODsKf3jjEGNCpUTz5tju8AHRpk_xIz-e/view?usp=sharing)
+* [Health-Related Outcomes](https://drive.google.com/file/d/1wdKzliWLEFuVveAj6-MzOAsoqBhnkRJW/view?usp=sharing)
+* [Supplemental Education Outcomes](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing)
+* [Supplemental Health-Related Outcomes](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing)
+
+```{r, results='asis'}
+if (knitr::pandoc_to()!="html5") "# References"
+```

### 2021-09-24 R/forest_plot_code_overview_screentime.R

@@ -360,7 +360,7 @@ make_plots <- function(combined_effects) {
   plot_params <- list(
     list(
       filename = "Forest plot for Education.pdf",
-      title = "Effect of Exposures on Education Outcomes",
+      title = "Associations Between Exposures and Education Outcomes",
       categories = "Education",
       certain = TRUE,
       pos = edu_positions$certain,
@@ -368,7 +368,7 @@ make_plots <- function(combined_effects) {
     ),
     list(
       filename = "Forest plot for Health-related Outcomes.pdf",
-      title = "Effect of Exposures on Health-related Outcomes",
+      title = "Associations Between Exposures and Health-related Outcomes",
       categories = c("Psychology", "Health Behaviour", "Physical Health"),
       certain = TRUE,
       pos = nonedu_positions$certain,
@@ -376,7 +376,7 @@ make_plots <- function(combined_effects) {
     ),
     list(
       filename = "Supplemental Forest plot for Education.pdf",
-      title = "Effect of Exposures on Education Outcomes",
+      title = "Associations Between Exposures and Education Outcomes",
       categories = "Education",
       certain = FALSE,
       pos = edu_positions$uncertain,
@@ -384,7 +384,7 @@ make_plots <- function(combined_effects) {
     ),
     list(
       filename = "Supplemental Forest plot for Health-related Outcomes.pdf",
-      title = "Effect of Exposures on Health-related Outcomes",
+      title = "Associations Between Exposures and Health-related Outcomes",
       categories = c("Psychology", "Health Behaviour", "Physical Health"),
       certain = FALSE,
       pos = nonedu_positions$uncertain,
@@ -419,6 +419,10 @@ save_plots <- function(plots) {
     width = plots[[1]]$dims[[1]],
     height = plots[[1]]$dims[[2]]
   )
-
+  
+  # Upload to GDrive
+  drive_put(here::here("figure", plots[[1]]$filename), 
+            path = as_id("https://drive.google.com/drive/folders/1xvn1B4bGH7hr6yBvDGUfEF7F_eO3Qeml"))
+  
   return(file_name)
 }

### 2021-09-26 reports/manuscript.Rmd
Transfer commit

@@
 output:
-  distill::distill_article:
-    toc: true
-    toc_depth: 2
+  github_document:
+    html_preview: false
+    pandoc_args: "--wrap=none"
 ---
@@
 )
+
+render_img <- knitr::pandoc_to()=="html5"
+inc_ref <- knitr::pandoc_to()!="html5"
 
@@
 
+Philip.Parker@acu.edu.au will insert an explanation about why he forced us to move away from our original [evidence assessment plan](https://www.crd.york.ac.uk/prospero/display_record.php?RecordID=76051).
+
 # Results
@@
 
-```{r prisma, fig.cap="PRISMA Diagram"}
+```{r prisma, eval=render_img, fig.cap="PRISMA Diagram"}
 prisma$diag
@@
 
-```{r}
+```{r quality}
 qual_data <- reviews_table$data %>%
@@
 
-```{r}
+```{r eduoutcomes}
 edu_effect <-   
@@
 
-```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
+```{r eduplot, eval=render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
 plots[[1]]$plot
 ```
+
 Among the statistically credible effects, general screen use, TV viewing, and video games were all negatively associated with academic performance or general learning.
@@
 
-```{r}
+```{r educertain}
 n_edu_p999 <- edu_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
@@
 
-```{r}
+```{r healthoutcome}
 health_effect <-   
@@
 We identified `r n_health_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-`r `xfun::numbers_to_words(n_health_certain, cap=TRUE)`of these meta-analytic associations met our criteria for credible evidence (see Figure \@ref(fig:healthplot)).
+`r xfun::numbers_to_words(n_health_certain, cap=TRUE)` of these meta-analytic associations met our criteria for credible evidence (see Figure \@ref(fig:healthplot)).
 We removed `r n_health_noindiv` for not providing individual study-level data, `r n_health_samplesize` for having meta-analytic effects with samples < 1,000, and `r n_health_faileggers` had a significant Egger's test or insufficient studies to conduct the test.
@@
 
-```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
+```{r healthplot, eval=render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
 plots[[2]]$plot
@@
 
-```{r}
+```{r healthcertain}
 n_health_p999 <- health_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
@@
 
-# Supplementary Material
+**Note:** *Below are rough notes on ideas for the discussion. Please feel free to add ideas. We will revise once we agree on the rest of the paper.*
 
-#### Full Size Forest Plots
+#### Broad summary of the findings relating back to the purpose
+When meta-analysis examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with academic performance, literacy, body composition, and depression.
+However, when meta-analyses included a more nuanced examination of exposures a more complex picture appeared.
+Many exposures were likely neither universally harmful nor consistently beneficial.
 
+#### TV
+Strong evidence indicated that watching television programs was associated with poorer academic performance and learning.
+However, there was also weak evidence that if the child watched these programs with a parent (i.e., coviewing) or the content of the program was educational then television viewing was associated with better literacy.
+
+Outside of educational outcomes, there was strong evidence of a harmful association with body composition and marginal associations with sleep duration.
+Overall, there was credible evidence indicating that TV watching was likely to confer benefits for children, but it may not be harmful as long as children watch with their parents or the content is educational.
+
+#### Video games 
+* Weak evidence of harm for body comp.
+* Strong evidence of harm for academic performance.
+* Strong evidence of benefit for numeracy games on numeracy.
+
+#### Screen-based Interventions
+One category of exposure appeared to consistently confer benefits: Interventions delivered via screens.
+This finding indicates that interventions can be effectively delivered using electronic media platforms.
+It does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
+
+* Touch screen = strong evidence of benefit for learning
+* Math interventions = strong evidence on numeracy.
+* Augmented reality on learning, strong evidence.
+* Screen-based interventions. Strong effect on health behaviours.
+
+#### Consistent Harms
+The exposures that were consistently associated with harms: social media and food advertising via screen media.  
+Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.  
+Strong evidence also indicated screen-based food advertising (in general and in advergames), was risky as it was positively associated with food intake.  
+Finally, there was strong evidence that sexy media was associated with sexual activity.
+
+#### Implications of findings for targeted policy and practice
+Screen time is complex.
+We need to stop thinking about it in simplistic terms as “bad” and something that should be minimised in all instances.
+Need to think about how it can best be used.
+For example, recreational television and video games appear to confer few, if any benefits, and appear to be associated with poor body composition and academic performance.
+However, tv programs and video games designed to promote learning may be effective.
+The current literature indicates that social media is likely harmful, but if social media platforms specifically designed to promote learning can be designed and popularised, perhaps they could have benefits.
+
+#### Survey of the field and implications for future research
+
+Screen time research is big and varied and rapidly growing.
+Reviews tended to be quite general (e.g., all screentime) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed.
+
+There is credible evidence for X, we need more evidence for Y.  
+All observational research with self-report evidence.
+
+#### Limitations of the review
+
+Can’t look at fine-grained detail - eg moderators, but we did look at different exposures and outcomes (quasi moderators).  
+GRADE - we did not rate the risk of bias of individual studies in the meta-analyses. Total k  >3,000 (intractable task)  
+We made decisions to present effects that reach certain thresholds (e.g., N>1,000, non-significant Egger’s test) but also provide more complete results in the supplementary files for those who wish to investigate.
+
+#### Conclusions
+
+# Appendix
+
+#### Figures
+
+* [Prisma Diagram](https://drive.google.com/file/d/1ezgeAr2WPhy6MNSESS8bhg3VMOrLAUC7/view?usp=sharing)
 * [Education Outcomes](https://drive.google.com/file/d/1ODsKf3jjEGNCpUTz5tju8AHRpk_xIz-e/view?usp=sharing)
@@
 
-```{r, results='asis'}
-if (knitr::pandoc_to()!="html5") "# References"
+#### Tables
+
+#### Links
+
+* [Manuscript Google Doc](https://docs.google.com/document/d/1NN4yJWQVepNjbX0mND4aidWWXcCDkg-eMepRnWdtQ9o/edit#)
+* [Online Report](https://motivation-and-behaviour.github.io/screen_umbrella/)
+
+```{r refs, eval=inc_ref, results='asis'}
+"# References"
 ```

### 2021-09-26 R/PRISMA.R

@@ -135,7 +135,11 @@ save_prisma <- function(prisma_data){
   prisma_data$diag %>%
     DiagrammeRsvg::export_svg() %>%
     charToRaw() %>%
-    rsvg::rsvg_pdf(here::here("figure", "flow.pdf"))
+    rsvg::rsvg_pdf(here::here("figure", "PRISMA Diagram.pdf"))
   
-  return(here::here("figure", "flow.pdf"))
+  # Upload to GDrive
+  drive_put(here::here("figure", "PRISMA Diagram.pdf"), 
+            path = as_id("https://drive.google.com/drive/folders/1xvn1B4bGH7hr6yBvDGUfEF7F_eO3Qeml"))
+  
+  return(here::here("figure", "PRISMA Diagram.pdf"))
 }

### 2021-09-26 R/functions.R

@@ -1,9 +1,3 @@
-# Targets functions ####
-
-get_mod_date <- function() {
-  x <- googledrive::drive_get(id = googledrive::as_id("1z_NZwDomPfrOJg2Rn8-E8cc9yoOjXzqH_Di23vWERu4"))
-  return(x$drive_resource[[1]]$modifiedTime)
-}
 
 # Convert effects data ####
 
@@ -105,17 +99,6 @@ convert_effects <- function(data) {
 
   return(d)
 }
-
-# General Functions ####
-read_sheet <- function(mod_date, sheet) {
-  d <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1z_NZwDomPfrOJg2Rn8-E8cc9yoOjXzqH_Di23vWERu4/edit#gid=1427279106",
-    sheet = sheet,
-    na = c("-999", "", "#N/A")
-  ) %>%
-    janitor::clean_names()
-  return(d)
-}
-
 
 # Effects data ####
 

### 2021-09-26 R/reports.R

@@ -1,0 +1,49 @@
+# ------------------- SETTINGS -----------------------
+authors_sheet <- "1V-j8oQXI3Y8etUnaRETvUvq9Hr8eAbAoBc_0XoLgb48"
+
+# ------------------- TARGETS ------------------------
+
+## Bibliographies ----
+generate_bibliography <-
+  list(
+    tar_target(
+      packages_bib,
+      create_packages_bib(packages,
+                          here::here("reports", "packages.bib")),
+      format = "file"
+    ),
+    tar_target(
+      references_bib,
+      here::here("reports", "references.bib"),
+      format = "file"
+    ),
+    tar_target(
+      combined_bib,
+      combine_bibs(
+        packages_bib,
+        references_bib,
+        here::here("reports", "combined.bib")
+      ),
+      format = "file"
+    )
+  )
+
+## Metadata ----
+
+## Create reports ----
+
+# ------------------- FUNCTIONS ----------------------
+
+## Bibliography ----
+# Create packages bibliography
+create_packages_bib <- function(packages, bibpath){
+  knitr::write_bib(packages, bibpath)
+  return(bibpath)
+}
+
+# Combine bibliography files
+combine_bibs <- function(packages_bib, references_bib, outpath){
+  fullbib <- lapply(c(packages_bib, references_bib), readLines)
+  write(unlist(fullbib), file=outpath)
+  return(outpath)
+}

### 2021-09-26 R/utils.R

@@ -1,12 +1,26 @@
-# Create packages bibliography
-create_packages_bib <- function(packages, bibpath){
-  knitr::write_bib(packages, bibpath)
-  return(bibpath)
+# ------------------- SETTINGS -----------------------
+
+# ------------------- TARGETS ------------------------
+
+
+
+
+# ------------------- FUNCTIONS ----------------------
+
+## Checking Dates ----
+get_mod_date <- function(id) {
+  x <- googledrive::drive_get(id = googledrive::as_id(id))
+  return(x$drive_resource[[1]]$modifiedTime)
 }
 
-# Combine bibliography files
-combine_bibs <- function(packages_bib, references_bib, outpath){
-  fullbib <- lapply(c(packages_bib, references_bib), readLines)
-  write(unlist(fullbib), file=outpath)
-  return(outpath)
+
+## Reading Data ----
+read_sheet <- function(file, sheet, mod_date) {
+  d <- googlesheets4::read_sheet(file = file,
+                                 sheet = sheet,
+                                 na = c("-999", "", "#N/A")
+  ) %>%
+    janitor::clean_names()
+  return(d)
 }
+

### 2021-09-26 _targets.R

@@ -13,6 +13,7 @@ options(tidyverse.quiet = TRUE, clustermq.scheduler = "multiprocess")
 packages <- c("base","broom", "DiagrammeR", "DT", "esc", "emojifont", "ggh4x", 
               "googledrive", "ggplot2", "ggtext",  "janitor", "knitr", 
               "kableExtra", "metafor", "tidyMB", "tidyverse", "scales", "xfun",
+              "ymlthis",
                # TEMP
                "ggforestplot",  "ggforce")
 
@@ -22,10 +23,10 @@ list(
   # Data sources
   tar_target(
     modified_date,
-    get_mod_date(),
+    get_mod_date(data_sheet),
     # Force run if outdated or doesn't exist
     cue = tar_cue_force(condition = ifelse(tar_exist_objects("modified_date"),
-      get_mod_date() != tar_read(modified_date),
+      get_mod_date(data_sheet) != tar_read(modified_date),
       TRUE
     ))
   ),
@@ -113,15 +114,7 @@ list(
     pattern = map(plots)
   ),
   # REPORTS --------------------------------
-  tar_target(packages_bib, create_packages_bib(packages, 
-                                               here::here("reports",
-                                                          "packages.bib")), 
-             format="file"),
-  tar_target(references_bib, here::here("reports","references.bib"), format="file"),
-  tar_target(combined_bib, combine_bibs(packages_bib, 
-                                        references_bib, 
-                                        here::here("reports","combined.bib")), 
-             format="file"),
+  generate_bibliography,
   tarchetypes::tar_render(
     distill_report,
     path = here::here("reports","manuscript.Rmd"),

### 2021-09-27 reports/manuscript.Rmd
Revise workflow and add table

@@
   - name: Taren Sanders
-    url: https://orcid.org/0000-0002-4504-6008
-    affiliation: Australian Catholic University
+    affiliation: Institute for Positive Psychology and Education, Australian Catholic
+      University
     affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
@@
   - name: Philip Parker
-    url: https://orcid.org/0000-0002-4604-8566 
-    affiliation: Australian Catholic University
+    affiliation: Institute for Positive Psychology and Education, Australian Catholic
+      University
     affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
@@
   - name: Michael Noetel
-    url: https://orcid.org/0000-0002-6563-8203 
-    affiliation: Australian Catholic University
-    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
+    affiliation: School of Health and Behavioural Sciences, Australian Catholic University
+    affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
     orcid_id: 0000-0002-6563-8203
   - name: Chris Lonsdale
-    url: https://orcid.org/000-0002-2523-5565  
-    affiliation: Australian Catholic University
-    affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-    orcid_id: 000-0002-2523-5565 
-date: "`r Sys.Date()`"
+date: '`r format(Sys.Date())`'
 repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
@@
 csl: nature.csl
-always_allow_html: true
-output:
-  github_document:
-    html_preview: false
-    pandoc_args: "--wrap=none"
+params:
+  render_img: true
+  inc_ref: false
 ---
@@
 
-render_img <- knitr::pandoc_to()=="html5"
-inc_ref <- knitr::pandoc_to()!="html5"
-
 # Uncomment to run outside of pipeline
-library(tidyverse)
-library(targets)
-library(xfun)
-library(DiagrammeR)
+# library(tidyverse)
+# library(targets)
+# library(xfun)
 ```
@@
 ```{r, load-targets}
-targets::tar_load(c("prisma", "effects_clean", "reviews_table", "plots", 
-           "studies_results", "comparison_plots", "combined_effects", 
-           "combined_bib"), 
+targets::tar_load(c("prisma", "effects_clean", "reviews_tables", "tables_df",
+                    "plots", "studies_results", "comparison_plots", 
+                    "combined_effects", "combined_bib"), 
          store = here::here("_targets"))
@@
 To be considered credible an effect needed to be derived from a combined sample of >1,000 and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
+We performed these analyses, and tehrefore the review needed to provide usable study-level data in order to be included.
 
@@
 
-The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were removed as duplicates.
+The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were duplicates.
 After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
-`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these studies.
-Figure \@ref(fig:prisma) presents the full results of the study selection process.
+`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these meta-analyses.
+Figure \@ref(fig:prisma) presents the full results of the selection process.
 
-```{r prisma, eval=render_img, fig.cap="PRISMA Diagram"}
+```{r prisma, fig.cap="PRISMA Diagram"}
 prisma$diag
@@
 In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` three or more times.
-Full characteristics of the included studies are provided in Table X.
+Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
+
+```{r desctable, layout="l-screen-inset shaded"}
+reviews_tables[[1]]$table
+```
 
 ```{r quality}
-qual_data <- reviews_table$data %>%
-  filter(`Outcomes Assessed` !="<ul><li></li></ul>")
+qual_data <- 
+  tables_df %>%
+  filter(table=="main") %>% 
+  distinct(covidence_id, .keep_all = TRUE) %>% 
+  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed)
 
 reviews_count <- qual_data %>%
-  mutate(across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed", as.factor)) %>% 
+  mutate(
+    across(
+      eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
+      as.factor
+    )
+  ) %>%
   rowwise() %>%
-  mutate(count_low = sum(c_across("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed")=="Low"))
+  mutate(count_low = sum(
+    c_across(
+      eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) == "low"
+  ))
 
@@
   reviews_count %>%
-  select("Eligibility Criteria Predefined And Specified":"Heterogeneity Assessed") %>%
+  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>%
   gather(name, value) %>%
@@
 n_low_hetero <-
-  reviews_count[reviews_count$name == "Heterogeneity Assessed" &
-                  reviews_count$value == "Low", "n"][[1]]
+  reviews_count[reviews_count$name == "heterogeneity_assessed" &
+                  reviews_count$value == "low", "n"][[1]]
 n_low_char <-
-  reviews_count[reviews_count$name == "Included Studies Listed With Important Characteristics And Results Of Each" &
-                  reviews_count$value == "Low", "n"][[1]]
+  reviews_count[reviews_count$name == "included_studies_listed_with_important_characteristics_and_results_of_each" &
+                  reviews_count$value == "low", "n"][[1]]
 n_low_search <-
-  reviews_count[reviews_count$name == "Literature Search Strategy Comprehensive And Systematic" &
-                  reviews_count$value == "Low", "n"][[1]]
+  reviews_count[reviews_count$name == "literature_search_strategy_comprehensive_and_systematic" &
+                  reviews_count$value == "low", "n"][[1]]
 
 n_unclear_elig <-
-  reviews_count[reviews_count$name == "Eligibility Criteria Predefined And Specified" &
-                  reviews_count$value == "Unclear", "n"][[1]]
+  reviews_count[reviews_count$name == "eligibility_criteria_predefined_and_specified" &
+                  reviews_count$value == "unclear", "n"][[1]]
 
 n_high_dualscreen <-
-  reviews_count[reviews_count$name == "Dual Independent Screening Review" &
-                  reviews_count$value == "High", "n"][[1]]
+  reviews_count[reviews_count$name == "dual_independent_screening_review" &
+                  reviews_count$value == "high", "n"][[1]]
 n_unclear_dualscreen <-
-  reviews_count[reviews_count$name == "Dual Independent Screening Review" &
-                  reviews_count$value == "Unclear", "n"][[1]]
+  reviews_count[reviews_count$name == "dual_independent_screening_review" &
+                  reviews_count$value == "unclear", "n"][[1]]
 
 n_high_dualquality <-
-  reviews_count[reviews_count$name == "Dual Independent Quality Assessment" &
-                  reviews_count$value == "High", "n"][[1]]
+  reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
+                  reviews_count$value == "high", "n"][[1]]
 n_unclear_dualquality <-
-  reviews_count[reviews_count$name == "Dual Independent Quality Assessment" &
-                  reviews_count$value == "Unclear", "n"][[1]]
+  reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
+                  reviews_count$value == "unclear", "n"][[1]]
 
@@
 
-The quality of the included studies was mixed.
-Most studies assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low ")`.
-Most studies did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
-A similar trend was observed for dual independent quality assessment `r dualqualstr`.
-Overall, only `r all_low` were graded as *low* risk of bias on all criteria.
+The quality of the included meta-analyses was mixed.
+Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low ")`.
+Most reviews did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
+Many reviews also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
+Many reviews  also did not complete A similar trend was observed for dual independent quality assessment `r dualqualstr`.
+Overall, only `r all_low` meta-analyses were graded as *low* risk of bias on all criteria.
 
@@
 
-```{r eduplot, eval=render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
+```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
 plots[[1]]$plot
@@
 
-```{r healthplot, eval=render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
+```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
 plots[[2]]$plot
@@
 
-```{r refs, eval=inc_ref, results='asis'}
-"# References"
+```{r refs, results='asis'}
+if (params$inc_ref) "# References"
 ```

### 2021-09-27 R/PRISMA.R

@@ -1,145 +1,0 @@
-make_prisma <- function(covidence_export, effects_clean) {
-  
-  # Get Covidence PRISMA data
-  covidence_export <- read_file(covidence_export)
-  
-  dat <-
-    # Convert each to a separate line
-    tibble(text = unlist(str_split(covidence_export, pattern = "\\n"))) %>%
-    # remove unneeded info
-    filter(
-      !str_detect(text, "studies ongoing"),
-      !str_detect(text, "studies awaiting classification")
-    ) %>%
-    # Determine row type
-    mutate(
-      # type = if_else(startsWith(text, "\t"), "exclude", "main"),
-      type = case_when(
-        startsWith(text, "\t\t") ~ "exclude_reason",
-        startsWith(text, "\t") ~ "exclude",
-        TRUE ~ "main"
-      ),
-      step = 0,
-      text = str_replace_all(text, "\t", ""),
-      value = str_extract(text, "^[0-9]+") %>% as.numeric(),
-      text = str_remove(text, "^[0-9]+") %>% str_trim()
-    )
-  # Generate steps
-  step <- 0
-  for (i in seq_len(nrow(dat))) {
-    if (dat$type[i] == "main") step <- step + 1
-    dat$step[i] <- step
-  }
-  
-  exclusion_collapse <- function(data, old_rows, new_row) {
-    bind_rows(
-      data %>% filter(!text %in% old_rows),
-      data %>%
-        filter(text %in% old_rows) %>%
-        summarise(value = sum(value), step = min(step)) %>%
-        mutate(text = new_row, type = "exclude_reason")
-    )
-  }
-  
-  
-  # Modify dataframe (add rows as needed)
-  dat <- dat %>%
-    exclusion_collapse(
-      c("Not a systematic review", "Not a review"),
-      "Not a systematic review"
-    ) %>%
-    exclusion_collapse(
-      c(
-        "Systematic review without meta-analysis",
-        "Sys review of qual studies", "Review of reviews"
-      ),
-      "Systematic review without meta-analysis"
-    ) %>%
-    exclusion_collapse(
-      c("Duplicated reference", "DUPLICATE TO MERGE LATER"),
-      "Duplicated reference"
-    ) %>%
-    exclusion_collapse(
-      c(
[…]

### 2021-09-27 R/reports.R

@@ -1,5 +1,6 @@
 # ------------------- SETTINGS -----------------------
 authors_sheet <- "1V-j8oQXI3Y8etUnaRETvUvq9Hr8eAbAoBc_0XoLgb48"
+article_title <- "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens An umbrella review"
 
 # ------------------- TARGETS ------------------------
 
@@ -29,8 +30,47 @@ generate_bibliography <-
   )
 
 ## Metadata ----
+create_metadata <-
+  list(
+    tar_target(
+      authors_modified_date,
+      get_mod_date(authors_sheet),
+      # Force run if outdated or doesn't exist
+      cue = tar_cue_force(
+        condition = ifelse(
+          tar_exist_objects("authors_modified_date"),
+          get_mod_date(authors_sheet) != tar_read(authors_modified_date),
+          TRUE
+        )
+      )
+    ),
+    tar_target(
+      authors_details,
+      read_sheet(authors_sheet, "Authors", authors_modified_date)
+    ),
+    tar_target(front_yml,
+               make_yaml(authors_details),
+               format = "file")
+  )
 
 ## Create reports ----
+create_reports <- list(
+  tar_render(
+    distill_report,
+    path = here::here("reports", "manuscript.Rmd"),
+    output_file = here::here("index.html"),
+    output_yaml = here::here("reports", "distill.yaml"),
+    params = list(render_img = TRUE, inc_ref = FALSE)
+  ),
+  tar_render(
+    markdown_report,
+    path = here::here("reports", "manuscript.Rmd"),
+    output_file = here::here("reports", "manuscript.md"),
+    output_yaml = here::here("reports", "md.yaml"),
+    params = list(render_img = FALSE, inc_ref = TRUE)
+  )
+  
+)
 
 # ------------------- FUNCTIONS ----------------------
 
@@ -46,4 +86,31 @@ combine_bibs <- function(packages_bib, references_bib, outpath){
   fullbib <- lapply(c(packages_bib, references_bib), readLines)
   write(unlist(fullbib), file=outpath)
   return(outpath)
+}
+
+## Metadata ----
+
+make_yaml <- function(authors_details){
+  filepath <- here::here("reports","header.yaml")
+  
+  # Remove existing
+  unlink(filepath)
+  
+  yml() %>%
+    yml_title(article_title) %>%    
+    yml_distill_opts(
+      repository_url = 
+        "https://github.com/Motivation-and-Behaviour/screen_umbrella") %>% 
[…]

### 2021-09-27 R/tables.R

@@ -1,0 +1,250 @@
+# ------------------- SETTINGS -----------------------
+
+# ------------------- TARGETS ------------------------
+
+make_tables <- 
+  list(
+    tar_target(
+      tables_df,
+      make_table_data(rob_raw, effects_clean, reviews_raw)),
+    tar_target(
+      reviews_tables,
+      make_desc_tables(tables_df)),
+    tar_target(
+      export_tables,
+      save_tables(reviews_tables),
+      format = "file",
+      pattern = map(reviews_tables)))
+
+
+# ------------------- FUNCTIONS ----------------------
+
+make_table_data <- function(rob_df, effects_df, reviews_df) {
+  # Clean RoB
+  rob <- rob_df %>%
+    filter(reviewer == "Consensus") %>%
+    select(-starts_with("x"), -study_id, -reviewer)
+
+  # Clean effects
+  effects <- effects_df %>%
+    select(
+      covidence_review_id, plain_language_outcome,
+      plain_language_exposure, use_effect
+    ) %>%
+    rename(covidence_id = covidence_review_id)
+
+  reviews <- reviews_df %>%
+    transmute(
+      covidence_id = covidence_review_id_auto,
+      first_author = first_author_consensus,
+      year = year_of_publication_consensus,
+      design_restrictions = study_design_restrictions_extracted_consensus,
+      regions_restrictions = regions_consensus,
+      demographics_restrictions = demographics_consensus,
+      earliest_study_year = earliest_study_publication_year_consensus,
+      latest_study_year = latest_study_publication_year_consensus,
+      sample_age_mean_low = as.numeric(sapply(sample_age_lowest_study_mean_consensus, 
+                                   toString)),
+      sample_age_mean_high = as.numeric(sapply(sample_age_highest_study_mean_concensus, 
+                                    toString)) 
+    )
+
+  use_effects_ids <- 
+    effects %>% 
+    filter(use_effect) %>% 
+    distinct(covidence_id) %>% 
+    pull(covidence_id)
+  
+  # Join datasets
+  joined_df <- 
+    reviews %>%
+    # Merge the datasets
+    left_join(rob) %>%
+    left_join(effects) %>% 
+    mutate(table = if_else(covidence_id %in% use_effects_ids, "main","supp"))
+  
+  return(joined_df)
+}
+  
+make_desc_tables <- function(tables_df) {
+  
+  bullet_list <- function(column) {
+    paste0("<ul style='padding-left:10px'><li>",
+           paste(column %>% unique() %>% sort(),
[…]

### 2021-09-27 R/utils.R

@@ -16,7 +16,7 @@ get_mod_date <- function(id) {
 
 ## Reading Data ----
 read_sheet <- function(file, sheet, mod_date) {
-  d <- googlesheets4::read_sheet(file = file,
+  d <- googlesheets4::read_sheet(ss = file,
                                  sheet = sheet,
                                  na = c("-999", "", "#N/A")
   ) %>%

### 2021-09-28 reports/manuscript.Rmd
Add tables row to index.html
Update manuscript and plots

@@
 - name: Taren Sanders
-    affiliation: Institute for Positive Psychology and Education, Australian Catholic
-      University
+  affiliation: Institute for Positive Psychology and Education, ACU
   affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
   orcid_id: 0000-0002-4504-6008
+- name: Michael Noetel
+  affiliation: School of Health and Behavioural Sciences, ACU
+  affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
+  orcid_id: 0000-0002-6563-8203
 - name: Philip Parker
-    affiliation: Institute for Positive Psychology and Education, Australian Catholic
-      University
+  affiliation: Institute for Positive Psychology and Education, ACU
   affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
   orcid_id: 0000-0002-4604-8566
-  - name: Michael Noetel
-    affiliation: School of Health and Behavioural Sciences, Australian Catholic University
-    affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
-    orcid_id: 0000-0002-6563-8203
+- name: Borja Del Pozo Cruz
+- name: Stuart Biddle
+- name: Rimante Ronto
+- name: Ryan Hulteen
+- name: Rhiannon Parker
+- name: George Thomas
+- name: Katrien De Cocker
+- name: Jo Salmon
+- name: Kylie Hesketh
+- name: Nicole Weeks
+- name: Hugh Arnott
+- name: Emma Devine
+- name: Roberta Vasconcellos
 - name: Chris Lonsdale
+  affiliation: Institute for Positive Psychology and Education, ACU
+  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
+  orcid_id: 000-0002-2523-5565
 date: '`r format(Sys.Date())`'
@@
 bibliography: combined.bib
-csl: nature.csl
+csl: vancouver-brackets.csl
 params:
@@
          store = here::here("_targets"))
+```
+
+```{r, eval=params$inc_ref, results='markup'}
+
 ```
@@
 
-*Population*: To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents ( age 0-18 years).
+*Population*: To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
 Meta-analyses containing data from adults and youth were included if meta-analytic effect sizes estimates specific to participants aged 18 years or less could be extracted.
@@
 To be considered credible an effect needed to be derived from a combined sample of >1,000 and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
-We performed these analyses, and tehrefore the review needed to provide usable study-level data in order to be included.
+We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
 
@@
 
-```{r prisma, fig.cap="PRISMA Diagram"}
+```{r prisma, eval=params$render_img, fig.cap="PRISMA Diagram"}
 prisma$diag
@@
 The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
-In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` three or more times.
+In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
 
-```{r desctable, layout="l-screen-inset shaded"}
+```{r desctable, eval=params$render_img, layout="l-screen-inset shaded"}
 reviews_tables[[1]]$table
@@
 dualqualstr <- paste0(
-  qual_str(n_high_dualquality, nrow(qual_data), " high ", suffix= "; "),
+  qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix= "; "),
   qual_str(n_unclear_dualquality, nrow(qual_data), " unclear  ", prefix = "n", suffix = ")"))
@@
 The quality of the included meta-analyses was mixed.
-Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low ")`.
+Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
 Most reviews did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
-Many reviews also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
-Many reviews  also did not complete A similar trend was observed for dual independent quality assessment `r dualqualstr`.
-Overall, only `r all_low` meta-analyses were graded as *low* risk of bias on all criteria.
+Many reviews also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
+A similar trend was observed for dual independent quality assessment `r dualqualstr`.
+Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
 
@@
 There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
-Of these, `r n_edu_certain` met our criteria for statistical credibility and are described below (see Figure \@ref(fig:eduplot)).
-We removed `r n_edu_noindiv` for not providing individual study-level data, `r n_edu_samplesize` for having meta-analytic effects with samples < 1,000, and `r n_edu_faileggers` had a significant Egger's test or insufficient studies to conduct the test.
+We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` with a significant Egger's test or insufficient studies to conduct the test.
 No remaining studies showed evidence of excessive significance.
 Effects not meeting one or more of these standards are presented in the supplementary material.
+The remaining `r n_edu_certain` met our criteria for statistical credibility and are described below (see Figure \@ref(fig:eduplot)).
 
-```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
+```{r eduplot, eval=params$render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
 plots[[1]]$plot
@@
 E-books that included narration, as well as touch screen education interventions, and augmented reality interventions were positively associated with learning.
-General screen use was also negatively associated with literacy outcomes.
+General screen use was negatively associated with literacy outcomes.
 However, if the screen involved co-viewing (e.g., watching with a parent) or the content was educational the association with literacy was positive.
@@
 We identified `r n_health_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-`r xfun::numbers_to_words(n_health_certain, cap=TRUE)` of these meta-analytic associations met our criteria for credible evidence (see Figure \@ref(fig:healthplot)).
-We removed `r n_health_noindiv` for not providing individual study-level data, `r n_health_samplesize` for having meta-analytic effects with samples < 1,000, and `r n_health_faileggers` had a significant Egger's test or insufficient studies to conduct the test.
+We removed `r n_health_noindiv` effects that did not provide individual study-level data, `r n_health_samplesize` effects with samples < 1,000, and `r n_health_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
 No remaining studies showed evidence of excessive significance.
 Effects not meeting one or more of these standards are presented in the supplementary material.
+The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
 
-```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
+```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
 plots[[2]]$plot
@@
 
-Television was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of observed screen time (general, TV, and video games) were positively associated with body composition (e.g., BMI).
+Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
+All forms of screen time (general, TV, and video games) were positively associated with body composition (e.g., BMI).
 Risky behaviour (e.g., unsafe sex) was also positively associated with social media and with the use of sexy media.
@@
 Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the $P < 10^3$ level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at the $P < .05$ level.
-However, all of the credible effects exhibited high levels of heterogeneity, with the lowest $I^2 = 75%$.
+However, all of the credible effects exhibited high levels of heterogeneity, with the lowest $I^2 = 75\%$.
 Additionally, most effects were small, with the association between unhealthy food advertising and food intake the largest at $r = 0.25$.
@@
 
+* [Descriptive Table](https://drive.google.com/file/d/1t5XvwY2kzsOsbZ2FxbGPsYEecZz5PgD1/view?usp=sharing)
+* Supplemental tables (TBC)
+
 #### Links
@@
 
-```{r refs, results='asis'}
-if (params$inc_ref) "# References"
-```
+# References

### 2021-12-13 reports/manuscript.Rmd
Add age moderation into manuscript and plots

@@
 Yet, the evidence to support parents' concerns is lacking.
-A 2019 Lancet editorial [@thelancetSocialMediaScreen2019a] suggested that , "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
+A 2019 Lancet editorial [@thelancetSocialMediaScreen2019] suggested that , "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
 
-While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015a;@sweetserActivePassiveScreen2012a], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004a;@warburton2017children].
+While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
 Thus, efforts to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].

### 2022-01-04 reports/manuscript.Rmd
Re-sync GDoc with RMD

@@
 In the early 19th century, concerns about schooling "exhausting the children's brains" followed, with the medical community accepting that excessive study could be a cause of madness [@bell1883sanitarian].
-By the 20th century, the invention of the radio was accompanied by assertions that it would distract children from their reading (which by this point was no longer considered "confusing and harmful") leading to impaired learning [@dill2013oxford].
+By the 20th century, the invention of the radio was accompanied by assertions that it would distract children from their reading (which by this point was no longer considered confusing and harmful) leading to impaired learning [@dill2013oxford].
 
-Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen time (e.g., TV or computers) [@wartellaChildrenComputersNew2000].
-Excessive screen time is the number one concern parents have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top].
-Yet, the evidence to support parents' concerns is lacking.
-A 2019 Lancet editorial [@thelancetSocialMediaScreen2019] suggested that , "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
+Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen use (e.g., television, mobile phones, and computers) [@wartellaChildrenComputersNew2000].
+Excessive screen time use is the number one concern parents have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top].
+Yet, the evidence to support parents' concerns is inadequate.
+A Lancet editorial [@thelancetSocialMediaScreen2019] suggested that, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
 
-While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
-Thus, efforts to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].
-With concerns over the impact of screen time including education, health, and psychological well-being, a broad overview that acknowledges screen time's potential benefits and risks is needed.
+While some forms of screen use (e.g., television viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
+Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].
+With concerns over the impact of screen use including education, health, social development, and psychological well-being, a broad overview that identifies potential benefits and risks is needed.
 
-Citing the negative effects on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016;@whoGuidelinesPhysicalActivity2019] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
+Citing the negative effects on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
 For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
-They also recommend that children aged 2-5 years should spend a maximum of one hour exposed to recreational sedentary screen time per day, while children aged 5-12 and adolescents should spend no more than two hours.
-In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health [@fergusonEverythingModerationModerate2017], and might, in fact, benefit their well being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day).
-Some research also indicates that content (e.g., video game vs television program) may also play an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
-Indeed, educational screen time has been found to be positively related to educational outcomes [@sandersTypeScreenTime2019].
+They also recommend that children aged 2-5 years should spend a maximum of one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
+In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health [@fergusonEverythingModerationModerate2017], and might, in fact, benefit their well-being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day).
+Some research also indicates that content (e.g., video games vs television programs) may also play an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
+Indeed, educational screen time is positively related to educational outcomes [@sandersTypeScreenTime2019].
 This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required.
 
-In 2016, the American Academy of Pediatrics used a narrative review examining the benefits and risks of children and adolescents' electronic media [@chassiakosChildrenAdolescentsDigital2016] as a basis for updating their guidelines [@AAPMediaUseSchoolAged2016].
-Since then, a large number of systematic reviews and meta-analyses have provided up-to-date evidence about the potential benefits and risks of screentime.
-No review has synthesised the evidence available across relevant outcomes, such physical health, health behaviours, education, and psychological well being.
+In 2016, the American Academy of Pediatrics used a narrative review to examine the benefits and risks of children and adolescents' electronic media [@chassiakosChildrenAdolescentsDigital2016] as a basis for updating their guidelines about screen use [@AAPMediaUseSchoolAged2016].
+Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
+Yet, no review has synthesised the evidence available across a broad range of outcome domains, such as physical health, education, development, behaviour, and well-being.
 
-In order to support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen time on young children, children, and adolescents.
-This review includes the association between electronic media use and any variable that is a plausible outcome of this exposure.
-Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
-By synthesising across life domains, this review provides evidence to support more targeted guidelines and advice for parents, teachers, and other professionals in order to maximise human functioning.
+In order to crystallise the evidence base and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
+This review synthesises evidence on any plausible outcome of electronic media exposure.
+Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children’s lives.
+By synthesising across life domains (e.g., school and home), this review provides evidence to support better guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
 
@@
 *Population*: To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
-Meta-analyses containing data from adults and youth were included if meta-analytic effect sizes estimates specific to participants aged 18 years or less could be extracted.
+We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).
 We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).
 
-*Exposure*: We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computer, tablet, TV, and mobile phones.
+*Exposure*: We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computer, tablet, and mobile phones.
 We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content (e.g., television programs, movies, games), homework, and communication (e.g., video chat).
@@
 Consistent with this population-level approach, we excluded technology-based treatments for clinical conditions.
+However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning children) for children and youth with a clinical condition.
+For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.
+However, a meta-analysis of interventions designed to treat clinical depression delivered by a mobile phone app would be excluded.
 
@@
 
-*Publications*: We included meta-analyses (or meta-regressions) of quantitative evidence.
+*Publications*:We included meta-analyses (or meta-regressions) of quantitative evidence.
 To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
-For our purposes, a systematic review is a review in which the authors attempted to acquire all the research evidence that pertained to their research question(s).
+For our purposes, a systematic review was one in which the authors attempted to acquire all the research evidence that pertained to their research question(s).
 We excluded meta-analyses that did not attempt to summarise all the available evidence (e.g., a meta-analysis of all studies from one laboratory).
-We included meta-analyses regardless of the study designs included in the review (e.g., laboratory-based experimental studies, randomised controlled trials.
-non-randomised controlled trials, longitudinal, cross-sectional, case studies), as long as the studies in the review collected quantitative evidence.
+We included meta-analyses regardless of the study designs included in the review (e.g., laboratory-based experimental studies, randomised controlled trials, non-randomised controlled trials, longitudinal, cross-sectional, case studies), as long as the studies in the review collected quantitative evidence.
 We excluded systematic reviews of qualitative evidence.
 We did not formulate inclusion/exclusion criteria related to the risk of bias of the review.
-We did, however, employ a risk of bias tool to help us interpret the results.
+We did, however, employ a risk of bias tool to help interpret the results.
 We included full-text, peer-reviewed meta-analyses published or ‘in-press’ in English.
@@
 ### Data collection process
-Two researchers independently extracted data from the included meta-analyses into a custom-designed database.
+
+From each included meta-analysis, two researchers independently extracted data into a custom-designed database.
 
@@
 
-From each meta-analysis we extracted the following items: First author, year of publication, earliest and latest study publication dates, sample age, lowest and highest mean age reported, study design restrictions (e.g., cross-sectional, observational, experimental), region restrictions (e.g., specific countries), exposures reported, and outcomes reported.
+From each meta-analysis we extracted the following items: First author, year of publication, study design restrictions (e.g., cross-sectional, observational, experimental), region restrictions (e.g., specific countries), earliest and latest study publication dates, sample age (mean), lowest and highest mean age reported,  outcomes reported, and exposures reported.
 
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014].
-We resolved disagreements by consensus, with a third researcher employed, when needed.
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab:desctable)).
+We resolved disagreements by consensus, with a third researcher employed when needed.
 We did not assess risk of bias in the individual studies that were included in each meta-analysis.
@@
 After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.
+In instances where effect sizes from the same combination of exposure and outcome were drawn from different populations (e.g., children vs adolescents) we retained both estimates in our dataset.
+
 We excluded effect size estimates when the authors did not provide a sample size.
@@
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
-From our reanalysis we also extracted I2 values.
-To test for publication bias, we also conducted Egger's test [@eggerBiasMetaanalysisDetected1997] where the number of studies within the review was ten or more [@pageChapter13Assessing2021], and conducted a test of excess significance [@ioannidisExploratoryTestExcess2007].
+From our reanalysis we also extracted $I^2$ values.
+To test for publication bias, we conducted Egger's test [@eggerBiasMetaanalysisDetected1997] when the number of studies within the review was ten or more [@pageChapter13Assessing2021], and conducted a test of excess significance [@ioannidisExploratoryTestExcess2007].
 We contacted authors who did not provide primary study data in their published article.
@@
 We employed a statistical classification approach to grade the statistical credibility of the effect sizes in the literature.
-To be considered credible an effect needed to be derived from a combined sample of >1,000 and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
+To be considered credible an effect needed to be derived from a combined sample of >1,000 [@papadimitriouUmbrellaReviewEvidence2021] and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 
-Philip.Parker@acu.edu.au will insert an explanation about why he forced us to move away from our original [evidence assessment plan](https://www.crd.york.ac.uk/prospero/display_record.php?RecordID=76051).
+We altered our evidence assessment plan when we identified that, as written, it would treat effects from large reviews, with limited evidence of publication bias, and with consistency of effect in the population as not credible if the effect size was not statistically significant.
+This would have significantly harmed knowledge gained from our review as it would have restricted our ability to show where the empirical evidence strongly indicated that there was no association between screen time and a given outcome.
 
@@
 After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
-`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data of these meta-analyses.
+`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data from these meta-analyses.
 Figure \@ref(fig:prisma) presents the full results of the selection process.
@@
 
-After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.
-This process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
-
 The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
+Supplementary file X provides a list of all exposures identified.
 The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
@@
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
+Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
 
@@
     ) == "low"
+  ),
+  count_high = sum(
+    c_across(
+      eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) == "high"
   ))
@@
   nrow()
+
+all_high <- reviews_count %>%
+  filter(count_high==7) %>% 
+  nrow()
+
+all_high_txt <- 
+  paste0(str_to_sentence(numbers_to_words(all_high)), 
+         if (all_high>1) " meta-analyses" else " meta-analysis")
 
@@
 
-The quality of the included meta-analyses was mixed.
-Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of studies)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
+The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
+Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of meta-analyses)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
 Most reviews did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
-Many reviews also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
+Many papers also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
 A similar trend was observed for dual independent quality assessment `r dualqualstr`.
 Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
+`r all_high_txt` showed high risk of bias on all criteria.
 
@@
 Effects not meeting one or more of these standards are presented in the supplementary material.
-The remaining `r n_edu_certain` met our criteria for statistical credibility and are described below (see Figure \@ref(fig:eduplot)).
+The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
+<!-- TODO --> These `r n_edu_certain` effects came from X meta-analytic reviews analysing data from XXX empirical studies with XXX,XXXX individual participants.
 
@@
 
-Among the statistically credible effects, general screen use, TV viewing, and video games were all negatively associated with academic performance or general learning.
-E-books that included narration, as well as touch screen education interventions, and augmented reality interventions were positively associated with learning.
+Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
+E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
 General screen use was negatively associated with literacy outcomes.
-However, if the screen involved co-viewing (e.g., watching with a parent) or the content was educational the association with literacy was positive.
+However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95% CI, weak evidence).
 Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
@@
 
-As shown in Figure \@ref(fig:eduplot), most of the credible results (`r n_edu_p999` of `r n_edu_certain` effects) showed statistically significant associations, with 99.9% confidence intervals not encompassing zero (strong evidence).
+As shown in Figure \@ref(fig:eduplot), most of the credible results (`r n_edu_p999` of `r n_edu_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
 The remaining `r xfun::numbers_to_words(n_edu_p95)` associations were significant at the 95% confidence level (weak evidence).
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions tended to have larger effect sizes than non-intervention exposure (e.g., TV viewing, e-book reading) with the largest effect size observed for augmented reality-based school interventions on general learning ($r = 0.33$).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than non-intervention exposure (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
+The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
 Most effects showed high levels of heterogeneity (`r n_edu_i2` of `r n_edu_certain` with $I^2 > 50\%$).
@@
 The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
+<!-- TODO --> These `r n_health_effect` effects came from X meta-analytic reviews analysing data from XXX empirical studies with XXX,XXXX individual participants
 
@@
 
-Advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher food intake.
-Social media use was associated with higher risk of substance abuse, while screen-based interventions which target health behaviours appeared effective.
-
+Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
+Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media use.
+General screen use was positively associated with depression.
 Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen time (general, TV, and video games) were positively associated with body composition (e.g., BMI).
-Risky behaviour (e.g., unsafe sex) was also positively associated with social media and with the use of sexy media.
-General screen use was also associated with depression.
+All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI).
+Screen-based interventions which target health behaviours appeared effective.
 
@@
 
-Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the $P < 10^3$ level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at the $P < .05$ level.
+Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the 99.9\% level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
 However, all of the credible effects exhibited high levels of heterogeneity, with the lowest $I^2 = 75\%$.
-Additionally, most effects were small, with the association between unhealthy food advertising and food intake the largest at $r = 0.25$.
+Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
 Most of the effect sizes (`r n_health_r2`/`r n_health_certain`) had an absolute value of $r < 0.2$.
@@
 #### Broad summary of the findings relating back to the purpose
-When meta-analysis examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with academic performance, literacy, body composition, and depression.
+When meta-analysis examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
 However, when meta-analyses included a more nuanced examination of exposures a more complex picture appeared.
 Many exposures were likely neither universally harmful nor consistently beneficial.
+For example, watching television programs was associated with poorer academic performance and learning.
+However, there was also evidence that if the content of the program was educational or the child watched the program with a parent (i.e., coviewing) then television viewing was associated with better literacy.
+Thus, parents play an important role in selecting content that is likely to benefit their children and, perhaps, interacting with their children in ways that may foster literacy (e.g., asking their children questions about the program).
+Similarly, the credible evidence we identified showed video game playing is associated with poorer body composition and learning.
+When the video game was designed specifically to teach numeracy, playing these games showed learning benefits.
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for credibility (see Supplementary File X).
 
-#### TV
-Strong evidence indicated that watching television programs was associated with poorer academic performance and learning.
-However, there was also weak evidence that if the child watched these programs with a parent (i.e., coviewing) or the content of the program was educational then television viewing was associated with better literacy.
+Social media was one type of exposure that showed consistent risks to health, with no indication of potential benefit.
+Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.
+Meta-analytic evidence from adults indicates that social media use is also associated with increased risk of depression.
+Recent evidence from social media companies themselves suggest there may also be negative effects of
 
-Outside of educational outcomes, there was strong evidence of a harmful association with body composition and marginal associations with sleep duration.
-Overall, there was credible evidence indicating that TV watching was likely to confer benefits for children, but it may not be harmful as long as children watch with their parents or the content is educational.
+Finally, there was strong evidence that sexy media was associated with sexual activity.
 
-#### Video games 
-* Weak evidence of harm for body comp.
-* Strong evidence of harm for academic performance.
-* Strong evidence of benefit for numeracy games on numeracy.
-
-#### Screen-based Interventions
-One category of exposure appeared to consistently confer benefits: Interventions delivered via screens.
-This finding indicates that interventions can be effectively delivered using electronic media platforms.
+One category of exposure appeared to consistently confer benefits: screen-based interventions designed to promote learning or health behaviours.This finding indicates that interventions can be effectively delivered using electronic media platforms.
 It does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
@@
 
-#### Consistent Harms
-The exposures that were consistently associated with harms: social media and food advertising via screen media.  
-Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.  
-Strong evidence also indicated screen-based food advertising (in general and in advergames), was risky as it was positively associated with food intake.  
-Finally, there was strong evidence that sexy media was associated with sexual activity.
+#### Implications of findings for targeted policy and practice
 
-#### Implications of findings for targeted policy and practice
-Screen time is complex.
+Screen use is complex.
 We need to stop thinking about it in simplistic terms as “bad” and something that should be minimised in all instances.
@@
 For example, recreational television and video games appear to confer few, if any benefits, and appear to be associated with poor body composition and academic performance.
-However, tv programs and video games designed to promote learning may be effective.
+However, television programs and video games designed to promote learning may be effective.
 The current literature indicates that social media is likely harmful, but if social media platforms specifically designed to promote learning can be designed and popularised, perhaps they could have benefits.
@@
 
-Screen time research is big and varied and rapidly growing.
-Reviews tended to be quite general (e.g., all screentime) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed.
+Screen use research is big, varied, and rapidly growing.
+Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
+
+Need to unpack the aggression research (violent video games - what happened to those reviews?)
 
@@
 Can’t look at fine-grained detail - eg moderators, but we did look at different exposures and outcomes (quasi moderators).
-GRADE - we did not rate the risk of bias of individual studies in the meta-analyses. Total k  >3,000 (intractable task)  
-We made decisions to present effects that reach certain thresholds (e.g., N>1,000, non-significant Egger’s test) but also provide more complete results in the supplementary files for those who wish to investigate.
+
+We did not rate the risk of bias of the X,XXX individual studies that contributed data to this review.
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment (e.g., GRADE).
+
+Also, we made somewhat arbitrary decisions to present effects that reach certain thresholds (e.g., N>1,000, non-significant Egger’s test).
+We do, however, provide more complete results in the supplementary files for those who wish to consider those meta-analyses.
 

### 2022-01-04 reports/manuscript.Rmd
Add summary data for the effects

@@
 targets::tar_load(c("prisma", "effects_clean", "reviews_tables", "tables_df",
-                    "plots", "studies_results", "comparison_plots", 
-                    "combined_effects", "combined_bib"), 
+                    "plots", "studies_results", "studies_converted",
+                    "comparison_plots", "combined_effects", "combined_bib"), 
          store = here::here("_targets"))
@@
   arrange(desc(n))
+
+effects_sum <- effects_clean %>% 
+  filter(use_effect) %>% 
+  group_by(covidence_review_id, moderator_age) %>% 
+  slice_max(n, with_ties = TRUE) %>% 
+  ungroup() %>% 
+  summarise(sum_k = sum(k, na.rm = TRUE),
+            sum_n = sum(n))
+
 ```
@@
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
-Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.
+Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` reviews.
+These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_m, big.mark=",")` participants.
 
@@
   nrow()
+
+n_edu_unique <- n_distinct(edu_certain$covidence_review_id)
+
+edu_summary <- 
+  studies_converted %>% 
+  filter(effect_size_id %in% edu_certain$effect_size_id) %>% 
+  group_by(study_author, study_year, study_first_page_number) %>% 
+  slice_max(study_n, with_ties = FALSE) %>% 
+  ungroup() %>% 
+  summarise(studies_n = n(),
+            total_n = sum(study_n))
 ```
@@
 The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
-<!-- TODO --> These `r n_edu_certain` effects came from X meta-analytic reviews analysing data from XXX empirical studies with XXX,XXXX individual participants.
+These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$studies_n, big.mark=",")` individual participants.
 
@@
   nrow()
+
+n_health_unique <- n_distinct(health_certain$covidence_review_id)
+
+health_summary <- 
+  studies_converted %>% 
+  filter(effect_size_id %in% health_certain$effect_size_id) %>% 
+  group_by(study_author, study_year, study_first_page_number) %>% 
+  slice_max(study_n, with_ties = FALSE) %>% 
+  ungroup() %>% 
+  summarise(studies_n = n(),
+            total_n = sum(study_n))
 ```
@@
 The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
-<!-- TODO --> These `r n_health_effect` effects came from X meta-analytic reviews analysing data from XXX empirical studies with XXX,XXXX individual participants
+These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$studies_n, big.mark=",")` individual participants.
 

### 2022-01-04 R/tables.R

@@ -134,7 +134,7 @@ make_desc_tables <- function(tables_df) {
   
   gt_table_main <- 
     base_table %>% 
-    gt() %>% 
+    gt(caption = "Review characteristics and quality assessment for studies providing unique effects") %>% 
     # Add color to ROB
     data_color(
       columns = 

### 2022-01-05 reports/manuscript.Rmd
Rerun pipeline.
Fix typo in participant numbers

@@
          store = here::here("_targets"))
-```
-
-```{r, eval=params$inc_ref, results='markup'}
-
 ```
@@
 Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` reviews.
-These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_m, big.mark=",")` participants.
+These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
 
@@
 
+#### Supplementary Files
+
+* [List of Exposures](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing)
+
 #### Links

### 2022-01-06 R/reports.R
Try to automatically fix md for Gdocs

@@ -68,8 +68,10 @@ create_reports <- list(
     output_file = here::here("reports", "manuscript.md"),
     output_yaml = here::here("reports", "md.yaml"),
     params = list(render_img = FALSE, inc_ref = TRUE)
-  )
-  
+  ),
+  tar_target(gdoc_markdown_report,
+             fix_md(markdown_report),
+             format = "file")
 )
 
 # ------------------- FUNCTIONS ----------------------
@@ -112,5 +114,31 @@ make_yaml <- function(authors_details){
                inc_ref= FALSE) %>% 
     use_yml_file(filepath, quiet = TRUE)
   return(filepath)
+  
+}
+
+## Fix reports ----
+
+fix_md <- function(markdown_report){
+  md_file <- readLines(markdown_report[1])
+  
+  # Symbols
+  md_file <- gsub(pattern = "&lt;", replacement = "<", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = "&gt;", replacement = "<", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = "<sup> − 3</sup>", replacement ="^-3", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = "<sup>2</sup>", replacement ="^2", fixed = TRUE, x = md_file)
+  
+  # Spaces
+  md_file <- gsub(pattern = " ", replacement = " ", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = " ", replacement = " ", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = " ", replacement = " ", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = " ", replacement = " ", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = " ", replacement = " ", fixed = TRUE, x = md_file)
+  md_file <- gsub(pattern = " ", replacement = " ", fixed = TRUE, x = md_file)
+
+  out_path <- here::here("reports", "manuscript_gdoc.md")
+  writeLines(text = md_file, con = out_path)
+  
+  return(out_path)
   
 }

### 2022-01-06 reports/manuscript.Rmd
Try to automatically fix md for Gdocs
Switch from Md to docx

@@
   paste0(str_to_sentence(numbers_to_words(all_high)), 
-         if (all_high>1) " meta-analyses" else " meta-analysis")
+         if (all_high>1 | all_high==0) " meta-analyses" else " meta-analysis")
 
@@
 The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
-These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$studies_n, big.mark=",")` individual participants.
+These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$total_n, big.mark=",")` individual participants.
 
@@
 The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
-These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$studies_n, big.mark=",")` individual participants.
+These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
 

### 2022-01-07 reports/manuscript_content.Rmd
Change to Papaja

--- 2022-01-06 reports/manuscript.Rmd
@@
----
-title: "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
-author:
-- name: Taren Sanders
-  affiliation: Institute for Positive Psychology and Education, ACU
-  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-  orcid_id: 0000-0002-4504-6008
-- name: Michael Noetel
-  affiliation: School of Health and Behavioural Sciences, ACU
-  affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
-  orcid_id: 0000-0002-6563-8203
-- name: Philip Parker
-  affiliation: Institute for Positive Psychology and Education, ACU
-  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-  orcid_id: 0000-0002-4604-8566
-- name: Borja Del Pozo Cruz
-- name: Stuart Biddle
-- name: Rimante Ronto
-- name: Ryan Hulteen
-- name: Rhiannon Parker
-- name: George Thomas
-- name: Katrien De Cocker
-- name: Jo Salmon
-- name: Kylie Hesketh
-- name: Nicole Weeks
-- name: Hugh Arnott
-- name: Emma Devine
-- name: Roberta Vasconcellos
-- name: Chris Lonsdale
-  affiliation: Institute for Positive Psychology and Education, ACU
-  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-  orcid_id: 000-0002-2523-5565
-date: '`r format(Sys.Date())`'
-repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
-bibliography: combined.bib
-csl: vancouver-brackets.csl
-params:
-  render_img: true
-  inc_ref: false
----
-
-```{r setup, include=FALSE}
-# This allows distill to render from a targets pipeline
-Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')
-
-knitr::opts_chunk$set(
-	echo = FALSE,
-	message = FALSE,
-	warning = FALSE
-)
-
-# Uncomment to run outside of pipeline
-# library(tidyverse)
-# library(targets)
-# library(xfun)
-```
-
 ```{r, load-targets}
@@
 To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bonettTransformingOddsRatios2007;@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
-We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to do so.
+We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to meaningfully convert.
 Effect sizes on the original metric are provided in supplementary materials.
@@
 However, we determined that combining results from the meta-analyses provided a robust overview.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in eSupplementary File X.
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in [Supplementary File 1](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing).
 
@@
 The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
-Supplementary file X provides a list of all exposures identified.
+[Supplementary file 2](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing) provides a list of all exposures identified.
 The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
-In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
+In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination for an age group, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
@@
 
-```{r desctable, eval=params$render_img, layout="l-screen-inset shaded"}
+```{r desctable, eval=params$inc_tabs, layout="l-screen-inset shaded"}
 reviews_tables[[1]]$table
@@
   rowwise() %>%
-  mutate(count_low = sum(
+  mutate(
+    count_low = sum(
       c_across(
@@
       ) == "high"
-  ))
+    ),
+    count_high_unclear = sum(
+      c_across(
+        eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+      ) %in% c("high", "unclear")
+    )
+  )
 
@@
 
+all_high_unclear <- reviews_count %>% 
+  filter(count_high_unclear==7) %>% 
+  nrow()
+
 all_high_txt <- 
@@
          if (all_high>1 | all_high==0) " meta-analyses" else " meta-analysis")
+
+all_high_unclear_txt <- 
+  paste0(numbers_to_words(all_high_unclear), 
+         if (all_high_unclear>1 | all_high_unclear==0) " meta-analyses" else " meta-analysis")
 
@@
   qual_str(n_unclear_dualquality, nrow(qual_data), " unclear  ", prefix = "n", suffix = ")"))
-
 ```
@@
 Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
-`r all_high_txt` showed high risk of bias on all criteria.
+`r all_high_txt` showed high risk of bias on all criteria (`r all_high_unclear_txt` if 'unclear' was included as 'high').
 
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in the supplementary material.
+Effects not meeting one or more of these standards are presented in [Supplementary File 3](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
 The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in the supplementary material.
-The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
+Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing) The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
 These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
@@
 Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI).
+All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
 Screen-based interventions which target health behaviours appeared effective.
@@
 Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the 99.9\% level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
-However, all of the credible effects exhibited high levels of heterogeneity, with the lowest $I^2 = 75\%$.
+However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
 Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
@@
 
-**Note:** *Below are rough notes on ideas for the discussion. Please feel free to add ideas. We will revise once we agree on the rest of the paper.*
+The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad domain of outcomes.
+We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
+However, when meta-analyses included a more nuanced examination of exposures a more complex picture appeared.
 
 #### Broad summary of the findings relating back to the purpose
-When meta-analysis examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
-However, when meta-analyses included a more nuanced examination of exposures a more complex picture appeared.
-Many exposures were likely neither universally harmful nor consistently beneficial.
+
 For example, watching television programs was associated with poorer academic performance and learning.
@@
 * Screen-based interventions. Strong effect on health behaviours.
+
+Largely owing to small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
+If we expand our view to include those reviews which did meet this threshold, there remains no clear trend.
+For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.
+Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.
 
@@
 #### Conclusions
-
-# Appendix
-
-#### Figures
-
-* [Prisma Diagram](https://drive.google.com/file/d/1ezgeAr2WPhy6MNSESS8bhg3VMOrLAUC7/view?usp=sharing)
-* [Education Outcomes](https://drive.google.com/file/d/1ODsKf3jjEGNCpUTz5tju8AHRpk_xIz-e/view?usp=sharing)
-* [Health-Related Outcomes](https://drive.google.com/file/d/1wdKzliWLEFuVveAj6-MzOAsoqBhnkRJW/view?usp=sharing)
-* [Supplemental Education Outcomes](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing)
-* [Supplemental Health-Related Outcomes](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing)
-
-#### Tables
-
-* [Descriptive Table](https://drive.google.com/file/d/1t5XvwY2kzsOsbZ2FxbGPsYEecZz5PgD1/view?usp=sharing)
-* Supplemental tables (TBC)
-
-#### Supplementary Files
-
-* [List of Exposures](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing)
-
-#### Links
-
-* [Manuscript Google Doc](https://docs.google.com/document/d/1NN4yJWQVepNjbX0mND4aidWWXcCDkg-eMepRnWdtQ9o/edit#)
-* [Online Report](https://motivation-and-behaviour.github.io/screen_umbrella/)
-
-# References

### 2022-01-07 reports/manuscript_distill.Rmd
Change to Papaja

---
title: "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
author:
- name: Taren Sanders
  affiliation: Institute for Positive Psychology and Education, ACU
  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
  orcid_id: 0000-0002-4504-6008
- name: Michael Noetel
  affiliation: School of Health and Behavioural Sciences, ACU
  affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
  orcid_id: 0000-0002-6563-8203
- name: Philip Parker
  affiliation: Institute for Positive Psychology and Education, ACU
  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
  orcid_id: 0000-0002-4604-8566
- name: Borja Del Pozo Cruz
- name: Stuart Biddle
- name: Rimante Ronto
- name: Ryan Hulteen
- name: Rhiannon Parker
- name: George Thomas
- name: Katrien De Cocker
- name: Jo Salmon
- name: Kylie Hesketh
- name: Nicole Weeks
- name: Hugh Arnott
- name: Emma Devine
- name: Roberta Vasconcellos
- name: Chris Lonsdale
  affiliation: Institute for Positive Psychology and Education, ACU
  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
  orcid_id: 000-0002-2523-5565
date: '`r format(Sys.Date())`'
repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
bibliography: combined.bib
csl: vancouver-brackets.csl
nocite: "`r params$nocite_list`"
params:
  render_img: true
  nocite_list : true
  inc_tabs: true
---

```{r setup, include=FALSE}
# This allows distill to render from a targets pipeline
Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

options(dplyr.summarise.inform = FALSE)

# Uncomment to run outside of pipeline
# library(tidyverse)
# library(targets)
# library(xfun)
```

```{r child = 'manuscript_content.Rmd'}
```

# Appendix

#### Figures

* [Prisma Diagram](https://drive.google.com/file/d/1ezgeAr2WPhy6MNSESS8bhg3VMOrLAUC7/view?usp=sharing)
* [Education Outcomes](https://drive.google.com/file/d/1ODsKf3jjEGNCpUTz5tju8AHRpk_xIz-e/view?usp=sharing)
* [Health-Related Outcomes](https://drive.google.com/file/d/1wdKzliWLEFuVveAj6-MzOAsoqBhnkRJW/view?usp=sharing)

#### Tables

* [Descriptive Table](https://drive.google.com/file/d/1t5XvwY2kzsOsbZ2FxbGPsYEecZz5PgD1/view?usp=sharing)
* Supplemental tables (TBC)

#### Supplementary Files

* [Supplementary File 1: List of Reviews Without Meta-analyses](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing)
* [Supplementary File 2: List of Exposures](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing)
* [Supplementary File 3: Education Outcomes Not Meeting Statistical Certainty](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing)
* [Supplementary File 4: Health Outcomes Not Meeting Statistical Certainty](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing)

#### Links

* [Manuscript Google Doc](https://docs.google.com/document/d/1NN4yJWQVepNjbX0mND4aidWWXcCDkg-eMepRnWdtQ9o/edit#)
* [Online Report](https://motivation-and-behaviour.github.io/screen_umbrella/)

# References

### 2022-01-07 reports/manuscript_papaja.Rmd
Change to Papaja

---
title             : "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
shorttitle        : "Benefits and risks of electronic screens"

author: 
  - name          : "Taren Sanders"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "33 Berry St, North Sydney, NSW, Australia"
    email         : "Taren.Sanders@acu.edu.au"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Writing - Original Draft
  - name          : "Michael Noetel"
    affiliation   : "2"
    role:
      - Conceptualization
      - Writing - Original Draft
  - name          : "Philip Parker"
    affiliation   : "1"
    role:
      - Conceptualization
      - Writing - Original Draft
  - name          : "Borja Del Pozo Cruz"
    affiliation   : "3"
    role:
      - Writing - Review & Editing
  - name          : "Stuart Biddle"
    affiliation   : "4"
    role:
      - Writing - Review & Editing
  - name          : "Rimante Ronto"
    affiliation   : "5"
    role:
      - Writing - Review & Editing
  - name          : "Ryan Hulteen"
    affiliation   : "6"
    role:
      - Writing - Review & Editing
  - name          : "Rhiannon Parker"
    affiliation   : "7"
    role:
      - Writing - Review & Editing
  - name          : "George Thomas"
    affiliation   : "8"
    role:
      - Writing - Review & Editing
  - name          : "Katrien De Cocker"
    affiliation   : "5"
    role:
      - Writing - Review & Editing
  - name          : "Jo Salmon"
    affiliation   : "9"
    role:
      - Writing - Review & Editing
  - name          : "Kylie Hesketh"
    affiliation   : "9"
    role:
      - Writing - Review & Editing
  - name          : "Nicole Weeks"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Hugh Arnott"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Emma Devine"
    affiliation   : "10"
    role:
      - Writing - Review & Editing
  - name          : "Roberta Vasconcellos"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Chris Lonsdale"
    affiliation   : "1"
    role:
      - Writing - Original Draft
      - Project Administration

affiliation:
  - id            : "1"
    institution   : "Institute for Positive Psychology and Education, Australian Catholic University"
  - id            : "2"
    institution   : "School of Health and Behavioural Sciences, Australian Catholic University"
  - id            : "3"
    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark"
  - id            : "4"
    institution   : "School of Psychology and Counselling, University of Southern Queensland"
  - id            : "5"
    institution   : "Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University"
  - id            : "6"
    institution   : "School of Kinesiology, Louisiana State University"
  - id            : "7"
    institution   : "School of Medicine and Health, Sydney University"
  - id            : "8"
    institution   : "Faculty of Health Sciences, Curtin University"
  - id            : "9"
    institution   : "Institute for Physical Activity and Nutrition, Deakin University"
  - id            : "10"
    institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["combined.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : yes

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output            : papaja::apa6_pdf
nocite            : "`r params$nocite_list`"
params:
  render_img: true
  nocite_list : true
  inc_tabs: false
---

```{r setup, include=FALSE}
Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

options(dplyr.summarise.inform = FALSE)

# Uncomment to run outside of pipeline
# library(tidyverse)
# library(targets)
# library(xfun)
```

```{r child = 'manuscript_content.Rmd'}
```

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
References marked with an asterisk indicate studies which were included in the synthesis.
<div id = "refs"></div>
\endgroup

### 2022-01-07 R/reports.R

@@ -23,52 +23,45 @@ generate_bibliography <-
       combine_bibs(
         packages_bib,
         references_bib,
+        reviews_raw,
         here::here("reports", "combined.bib")
       ),
       format = "file"
     )
   )
 
-## Metadata ----
-create_metadata <-
-  list(
-    tar_target(
-      authors_modified_date,
-      get_mod_date(authors_sheet),
-      # Force run if outdated or doesn't exist
-      cue = tar_cue_force(
-        condition = ifelse(
-          tar_exist_objects("authors_modified_date"),
-          get_mod_date(authors_sheet) != tar_read(authors_modified_date),
-          TRUE
-        )
-      )
-    ),
-    tar_target(
-      authors_details,
-      read_sheet(authors_sheet, "Authors", authors_modified_date)
-    ),
-    tar_target(front_yml,
-               make_yaml(authors_details),
-               format = "file")
-  )
-
 ## Create reports ----
 create_reports <- list(
   tar_render(
     distill_report,
-    path = here::here("reports", "manuscript.Rmd"),
+    path = here::here("reports", "manuscript_distill.Rmd"),
     output_file = here::here("index.html"),
     output_yaml = here::here("reports", "distill.yaml"),
-    params = list(render_img = TRUE, inc_ref = FALSE)
+    params = list(render_img = TRUE, inc_tabs = TRUE,
+                  nocite_list = 
+                    paste0("@",
+                           paste(reviews_raw$bibtex_key, collapse = ", @")))
   ),
   tar_render(
     word_report,
-    path = here::here("reports", "manuscript.Rmd"),
-    output_file = here::here("reports", "manuscript_raw.docx"),
+    path = here::here("reports", "manuscript_papaja.Rmd"),
+    output_file = here::here("reports", "manuscript.docx"),
     output_yaml = here::here("reports", "docx.yaml"),
-    params = list(render_img = TRUE, inc_ref = TRUE)
+    params = list(render_img = TRUE, inc_tabs = TRUE,
+                  nocite_list = 
+                    paste0("@",
+                           paste(reviews_raw$bibtex_key, collapse = ", @")))
   )
+  # tar_render(
+  #   pdf_report,
+  #   path = here::here("reports", "manuscript_papaja.Rmd"),
+  #   output_file = here::here("reports", "manuscript.pdf"),
[…]

### 2022-01-07 _targets.R

@@ -4,12 +4,12 @@ library(here)
 
 options(tidyverse.quiet = TRUE, clustermq.scheduler = "multiprocess")
 
-packages <- c("base","broom", "DiagrammeR", "DT", "esc", "emojifont", "ggh4x", 
-              "googledrive", "ggplot2", "ggtext", "gt", "janitor", "knitr", 
-              "kableExtra", "magrittr", "metafor", "targets", "tarchetypes",
-              "tidyMB", "tidyverse", "scales", "xfun", "ymlthis")
+packages <- c("base","broom", "bib2df", "DiagrammeR", "distill", "DT", "esc", "emojifont", 
+              "ggh4x", "googledrive", "ggplot2", "ggtext", "gt", "janitor", 
+              "knitr", "kableExtra", "magrittr", "metafor", "papaja", "targets", 
+              "tarchetypes", "tidyMB", "tidyverse", "scales", "xfun")
 
-tar_option_set(packages = packages, debug = "yml_base")
+tar_option_set(packages = packages, debug = "yml_base", workspace_on_error = TRUE)
 
 googledrive::drive_auth()
 googlesheets4::gs4_auth()
@@ -34,6 +34,5 @@ list(
   make_supps,
   # Create reports (reports.R)
   generate_bibliography,
-  create_metadata,
   create_reports
 )

### 2022-01-07 _targets_packages.R

@@ -5,6 +5,7 @@ library(broom)
 library(bs4Dash)
 library(clustermq)
 library(DiagrammeR)
+library(distill)
 library(DT)
 library(emojifont)
 library(esc)
@@ -20,6 +21,7 @@ library(knitr)
 library(magrittr)
 library(markdown)
 library(metafor)
+library(papaja)
 library(pingr)
 library(rstudioapi)
 library(scales)

### 2022-01-11 reports/manuscript_content.Rmd
Add first pass of discussion

@@
 We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to meaningfully convert.
-Effect sizes on the original metric are provided in supplementary materials.
+Effect sizes on the original metric are provided in [Supplementary File 1](https://drive.google.com/file/d/1icdKoSdaOs5c8X6Ugmm0qLW_CEFSWDDu/view?usp=sharing).
 
@@
 However, we determined that combining results from the meta-analyses provided a robust overview.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in [Supplementary File 1](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing).
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in [Supplementary File 2](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing).
 
@@
 The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
-[Supplementary file 2](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing) provides a list of all exposures identified.
+[Supplementary File 3](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing) provides a list of all exposures identified.
 The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in [Supplementary File 3](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
+Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
 The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
@@
 General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95% CI, weak evidence).
+However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95\% CI, weak evidence).
 Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing) The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
+Effects not meeting one or more of these standards are presented in [Supplementary File 5](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing) The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
 These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
@@
 
-#### Broad summary of the findings relating back to the purpose
-
-For example, watching television programs was associated with poorer academic performance and learning.
-However, there was also evidence that if the content of the program was educational or the child watched the program with a parent (i.e., coviewing) then television viewing was associated with better literacy.
+Consider children watching television programs---an often cited form of screen time harm.
+Indeed, we find robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
+However, we also found evidence that if the content of the program was education, or the child was watching the program with a parent (i.e., coviewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
 Thus, parents play an important role in selecting content that is likely to benefit their children and, perhaps, interacting with their children in ways that may foster literacy (e.g., asking their children questions about the program).
-Similarly, the credible evidence we identified showed video game playing is associated with poorer body composition and learning.
-When the video game was designed specifically to teach numeracy, playing these games showed learning benefits.
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for credibility (see Supplementary File X).
+Similarly, the credible evidence we identified showed video game playing is associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
+When the video game was designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5).
 
 Social media was one type of exposure that showed consistent risks to health, with no indication of potential benefit.
-Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.
-Meta-analytic evidence from adults indicates that social media use is also associated with increased risk of depression.
-Recent evidence from social media companies themselves suggest there may also be negative effects of
+Social media showed strong evidence of harmful associations with risk taking in general , as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
+These results align with meta-analytic evidence from adults indicates that social media use is also associated with increased risk of depression [@yoonSocialNetworkSite2019;@vahediAssociationSelfreportedDepressive2021].
+Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls [@seetharamanFacebookKnowsInstagram2021].
 
-Finally, there was strong evidence that sexy media was associated with sexual activity.
-
-One category of exposure appeared to consistently confer benefits: screen-based interventions designed to promote learning or health behaviours.This finding indicates that interventions can be effectively delivered using electronic media platforms.
-It does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
-
-* Touch screen = strong evidence of benefit for learning
-* Math interventions = strong evidence on numeracy.
-* Augmented reality on learning, strong evidence.
-* Screen-based interventions. Strong effect on health behaviours.
+One category of exposure appeared to consistently confer benefits: screen-based interventions designed to promote learning or health behaviours.
+This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
+Rather, it reinforces that the content of the screen time may be the most important aspect.
+Similarly, the way that a young person interacts with digital screens may also be important.
+We found evidence that touch screens had strong evidence for benefits on learning [@xieCanTouchscreenDevices2018], as did augmented reality [@tekedereExaminingEffectivenessAugmented2016].
 
 Largely owing to small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand our view to include those reviews which did meet this threshold, there remains no clear trend.
-For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.
-Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.
+If we expand our view to include those reviews which did meet this threshold, there remains no clear pattern.
+For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
+Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups [@marshallRelationshipsMediaUse2004].
 
-#### Implications of findings for targeted policy and practice
+## Implications for Policy and Practice
 
-Screen use is complex.
-We need to stop thinking about it in simplistic terms as “bad” and something that should be minimised in all instances.
-Need to think about how it can best be used.
-For example, recreational television and video games appear to confer few, if any benefits, and appear to be associated with poor body composition and academic performance.
-However, television programs and video games designed to promote learning may be effective.
-The current literature indicates that social media is likely harmful, but if social media platforms specifically designed to promote learning can be designed and popularised, perhaps they could have benefits.
+Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue [@elsonPolicyStatementsMedia2019;@ashtonScreenTimeChildren2019;@royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019].
+Instead, our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
+Many current guidelines simplify this complex relationship as something that should be minimised in all instances.
+We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians the information to weigh the pros and cons of interactions with screens.
 
-#### Survey of the field and implications for future research
+#### Implications for Future Research
 
@@
 
-Need to unpack the aggression research (violent video games - what happened to those reviews?)
+Screen time research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
+The vast majority of screen time research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen time, but may also be inaccurate.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, @parrySystematicReviewMetaanalysis2021 found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
+It may be that the field of screen time research cannot be sufficiently advanced until more accurate and nuanced measures are available.
 
-There is credible evidence for X, we need more evidence for Y.
-All observational research with self-report evidence.
+#### Strengths and Limitations
 
-#### Limitations of the review
+Our primary goal for this umbrella review was to provide a high-level synthesis of screen time research, by examining a range of exposures and the associations with a broad scope of outcomes.
+Our results represent the findings from `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
+To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
 
-Can’t look at fine-grained detail - eg moderators, but we did look at different exposures and outcomes (quasi moderators).
-
-We did not rate the risk of bias of the X,XXX individual studies that contributed data to this review.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment (e.g., GRADE).
-
-Also, we made somewhat arbitrary decisions to present effects that reach certain thresholds (e.g., N>1,000, non-significant Egger’s test).
-We do, however, provide more complete results in the supplementary files for those who wish to consider those meta-analyses.
+However, our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
+For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
+As such, we made decisions regarding the credibility of evidence, where others may have made used different thresholds or metrics.
+For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
 

### 2022-01-11 reports/manuscript_papaja.Rmd
Add first pass of discussion

@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  Add author notes here
 
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Add abstract here
 

### 2022-01-11 reports/manuscript_content.Rmd
Tweak images and formatting

@@
 
-```{r prisma, eval=params$render_img, fig.cap="PRISMA Diagram"}
+```{r prisma, eval=params$render_img, fig.cap="PRISMA Diagram", out.extra ='WIDTH="75%"'}
 prisma$diag
@@
 
-```{r eduplot, eval=params$render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
+```{r eduplot, eval=params$render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes", dev='cairo_pdf'}
 plots[[1]]$plot
@@
 
-```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
+```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
 plots[[2]]$plot

### 2022-02-14 reports/manuscript_content.Rmd
Minor revisions and add conclusion

@@
 ```{r, load-targets}
-targets::tar_load(c("prisma", "effects_clean", "reviews_tables", "tables_df",
+targets::tar_load(c(
+  "prisma", "effects_clean", "reviews_tables", "tables_df",
   "plots", "studies_results", "studies_converted",
-                    "comparison_plots", "combined_effects", "combined_bib"), 
-         store = here::here("_targets"))
+  "comparison_plots", "combined_effects", "combined_bib"
+),
+store = here::here("_targets")
+)
 ```
@@
 When the meta-analysis’s authors provided primary study data associated with these effects we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base] (version `r paste(R.Version()[c("major", "minor")], collapse = ".")`).
-When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
+When required, we imputed missing sample sizes from the primary studies using mean imputation from the other studies within that review.
 From our reanalysis we also extracted $I^2$ values.
@@
 We contacted authors who did not provide primary study data in their published article.
-Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.
+Where authors did not provide data in a format that could be re-analysed, we present the published results of their original meta-analysis.
 
@@
   if (str_detect(cur_name, ":")) {
-
     cur_name_split <- str_split(cur_name, ": ")
-  return(str_to_lower(paste(cur_name_split[[1]][2], 
-                            cur_name_split[[1]][1])))
+    return(str_to_lower(paste(
+      cur_name_split[[1]][2],
+      cur_name_split[[1]][1]
+    )))
   } else {
@@
   group_by(plain_language_exposure) %>%
-  summarise(n=n()) %>% 
+  summarise(n = n()) %>%
   arrange(desc(n)) %>%
-  mutate(plain_language_exposure = rename_effects(plain_language_exposure),
+  mutate(
+    plain_language_exposure = rename_effects(plain_language_exposure),
     plain_language_exposure = case_when(
-           plain_language_exposure=="lifestyle risk behaviour (at school) intervention" ~"screen-based lifestyle risk behaviour interventions (at school)",
-           TRUE ~ plain_language_exposure),
-         out = paste0(plain_language_exposure, " (n = ", n, ")"))
+      plain_language_exposure ==
+        "lifestyle risk behaviour (at school) intervention" ~
+      "screen-based lifestyle risk behaviour interventions (at school)",
+      TRUE ~ plain_language_exposure
+    ),
+    out = paste0(plain_language_exposure, " (n = ", n, ")")
+  )
 
@@
   group_by(plain_language_outcome) %>%
-  summarise(n=n()) %>% 
+  summarise(n = n()) %>%
   arrange(desc(n)) %>%
-  mutate(plain_language_outcome = rename_effects(plain_language_outcome),
-         out = paste0(plain_language_outcome, " (n = ", n, ")"))
+  mutate(
+    plain_language_outcome = rename_effects(plain_language_outcome),
+    out = paste0(plain_language_outcome, " (n = ", n, ")")
+  )
 
@@
   group_by(plain_language_exposure, plain_language_outcome) %>%
-  summarise(n=n()) %>% 
+  summarise(n = n()) %>%
   arrange(desc(n))
@@
   ungroup() %>%
-  summarise(sum_k = sum(k, na.rm = TRUE),
-            sum_n = sum(n))
-
+  summarise(
+    sum_k = sum(k, na.rm = TRUE),
+    sum_n = sum(n)
+  )
 ```
@@
 Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` reviews.
-These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
+These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies with data from `r format(effects_sum$sum_n, big.mark=",")` participants.
 
@@
   tables_df %>%
-  filter(table=="main") %>% 
+  filter(table == "main") %>%
   distinct(covidence_id, .keep_all = TRUE) %>%
@@
 all_low <- reviews_count %>%
-  filter(count_low==7) %>% 
+  filter(count_low == 7) %>%
   nrow()
@@
 all_high <- reviews_count %>%
-  filter(count_high==7) %>% 
+  filter(count_high == 7) %>%
   nrow()
@@
 all_high_unclear <- reviews_count %>%
-  filter(count_high_unclear==7) %>% 
+  filter(count_high_unclear == 7) %>%
   nrow()
@@
 all_high_txt <-
-  paste0(str_to_sentence(numbers_to_words(all_high)), 
-         if (all_high>1 | all_high==0) " meta-analyses" else " meta-analysis")
+  paste0(
+    str_to_sentence(numbers_to_words(all_high)),
+    if (all_high > 1 | all_high == 0) " meta-analyses" else " meta-analysis"
+  )
 
 all_high_unclear_txt <-
-  paste0(numbers_to_words(all_high_unclear), 
-         if (all_high_unclear>1 | all_high_unclear==0) " meta-analyses" else " meta-analysis")
+  paste0(
+    numbers_to_words(all_high_unclear),
+    if (all_high_unclear > 1 | all_high_unclear == 0) {
+      " meta-analyses"
+    } else {
+      " meta-analysis"
+    }
+  )
 
@@
 
-qual_str <- function(n, totaln, ntype="", prefix="(n", suffix=")"){
-  paste0(prefix,ntype,"= ",n,"/",totaln,", ", scales::percent(n/totaln, accuracy = 1), suffix)
+qual_str <- function(n, totaln, ntype = "", prefix = "(n", suffix = ")") {
+  paste0(prefix, ntype, "= ", n, "/", totaln, ", ", scales::percent(n / totaln, accuracy = 1), suffix)
 }
@@
 dualqualstr <- paste0(
-  qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix= "; "),
-  qual_str(n_unclear_dualquality, nrow(qual_data), " unclear  ", prefix = "n", suffix = ")"))
+  qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix = "; "),
+  qual_str(n_unclear_dualquality, nrow(qual_data), " unclear  ", prefix = "n", suffix = ")")
+)
 ```
@@
 Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of meta-analyses)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
-Most reviews did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
+Most reviews did not clearly report if their eligibility criteria were predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
 Many papers also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
@@
 Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
-`r all_high_txt` showed high risk of bias on all criteria (`r all_high_unclear_txt` if 'unclear' was included as 'high').
+`r all_high_txt` showed high risk of bias on all criteria (if 'unclear' was treated as 'high' then `r all_high_unclear_txt` would be considered all 'high risk').
 
@@
   combined_effects %>%
-  filter(outcome_category=="education" & use_effect)
+  filter(outcome_category == "education" & use_effect)
 
@@
   ungroup() %>%
-  summarise(studies_n = n(),
-            total_n = sum(study_n))
+  summarise(
+    studies_n = n(),
+    total_n = sum(study_n)
+  )
 ```
@@
 There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
-We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` with a significant Egger's test or insufficient studies to conduct the test.
-No remaining studies showed evidence of excessive significance.
+We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
 Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
-The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
+The remaining `r n_edu_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
 These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$total_n, big.mark=",")` individual participants.
@@
 However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95\% CI, weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
+Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
 
 ```{r educertain}
-n_edu_p999 <- edu_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
-n_edu_p95 <- edu_certain %>% filter(reanalysis_p.value<0.05) %>% nrow() - n_edu_p999
+n_edu_p999 <- edu_certain %>%
+  filter(reanalysis_p.value < 0.001) %>%
+  nrow()
+n_edu_p95 <- edu_certain %>%
+  filter(reanalysis_p.value < 0.05) %>%
+  nrow() - n_edu_p999
 
-n_edu_i2 <- edu_certain %>% filter(i2 > 50) %>% nrow()
+n_edu_i2 <- edu_certain %>%
+  filter(i2 > 50) %>%
+  nrow()
 ```
@@
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than non-intervention exposure (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
 The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
@@
 Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media use.
+Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media exposure.
 General screen use was positively associated with depression.
 Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
-Screen-based interventions which target health behaviours appeared effective.
+All forms of screen use (general, television, and video games) were positively associated with poor body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
+Screen-based interventions which targeted health behaviours appeared effective.
 
 ```{r healthcertain}
-n_health_p999 <- health_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
-n_health_p95 <- health_certain %>% filter(reanalysis_p.value<0.05) %>% nrow() - n_edu_p999
+n_health_p999 <- health_certain %>%
+  filter(reanalysis_p.value < 0.001) %>%
+  nrow()
+n_health_p95 <- health_certain %>%
+  filter(reanalysis_p.value < 0.05) %>%
+  nrow() - n_health_p999
 
-n_health_i2 <- health_certain %>% filter(i2 > 50) %>% nrow()
-n_health_r2 <- health_certain %>% filter(abs(r) < 0.2) %>% nrow()
+n_health_i2 <- health_certain %>%
+  filter(i2 > 50) %>%
+  nrow()
+n_health_r2 <- health_certain %>%
+  filter(abs(r) < 0.2) %>%
+  nrow()
 ```
@@
 Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the 99.9\% level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
-However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
+Most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
 Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
@@
 The vast majority of screen time research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen time, but may also be inaccurate.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, @parrySystematicReviewMetaanalysis2021 found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
 It may be that the field of screen time research cannot be sufficiently advanced until more accurate and nuanced measures are available.
@@
 #### Conclusions
+
+Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the intrusion into society.
+Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
+The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each acitivty for potential harms and benefits.
+However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content and environment in which the exposure occurs.

### 2022-02-14 reports/manuscript_papaja.Rmd
Tweak images and formatting
Minor revisions and add conclusion

@@
 ```{r setup, include=FALSE}
-Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')
+Sys.setenv("RSTUDIO_VERSION" = "1.4.1725")
 knitr::opts_chunk$set(
@@
 # Uncomment to run outside of pipeline
-# library(tidyverse)
-# library(targets)
-# library(xfun)
+library(tidyverse)
+library(targets)
+library(xfun)
 ```
@@
 ```{r child = 'manuscript_content.Rmd'}
+
 ```

### 2022-02-14 R/plots.R

@@ -56,6 +56,10 @@ make_prisma <- function(covidence_export, effects_clean) {
         startsWith(text, "\t") ~ "exclude",
         TRUE ~ "main"
       ),
+      text = str_replace_all(
+        text, "studies included",
+        "met inclusion criteria"
+      ),
       step = 0,
       text = str_replace_all(text, "\t", ""),
       value = str_extract(text, "^[0-9]+") %>% as.numeric(),
@@ -97,7 +101,7 @@ make_prisma <- function(covidence_export, effects_clean) {
     ) %>%
     exclusion_collapse(
       c(
-        "Meta analysis that meets inclusion criteria, but youth results not presented and authors did not/could not provide individual study data when contacted.",
+        "Meta analysis that meets inclusion criteria, but youth results not presented and authors did not/could not provide individual study data when contacted.", # nolint
         "Individual level data only"
       ),
       "All meta-analyses results include non-target samples (e.g., adults)"
@@ -143,7 +147,10 @@ make_prisma <- function(covidence_export, effects_clean) {
     text = "studies contributed unique effects",
     type = "main",
     step = dat$step[nrow(dat)] + 1,
-    value = effects_clean %>% filter(use_effect) %>% distinct(covidence_review_id) %>% nrow()
+    value = effects_clean %>%
+      filter(use_effect) %>%
+      distinct(covidence_review_id) %>%
+      nrow()
   )
 
 
@@ -174,9 +181,11 @@ make_prisma <- function(covidence_export, effects_clean) {
       tab3 [label = '", labels[3], "']
       tab4 [label = '", labels[4], "']
       tab5 [label = '", labels[5], "']
-      tab6 [label = <", labels[6], "<br ALIGN = 'LEFT'/>", labels[7], "<br ALIGN = 'LEFT'/>>]
+      tab6 [label = <", labels[6],
+    "<br ALIGN = 'LEFT'/>", labels[7], "<br ALIGN = 'LEFT'/>>]
       tab7 [label = '", labels[8], "']
-      tab8 [label = <", labels[9], "<br ALIGN = 'LEFT'/>", labels[10], "<br ALIGN = 'LEFT'/>>]
+      tab8 [label = <", labels[9],
+    "<br ALIGN = 'LEFT'/>", labels[10], "<br ALIGN = 'LEFT'/>>]
       tab9 [label = '", labels[11], "']
 
[…]

### 2022-03-03 reports/manuscript_content.Rmd
Lint manuscript

@@
 When the meta-analysis’s authors provided primary study data associated with these effects we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base] (version `r paste(R.Version()[c("major", "minor")], collapse = ".")`).
-When required, we imputed missing sample sizes from the primary studies using mean imputation from the other studies within that review.
+When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
 From our reanalysis we also extracted $I^2$ values.
@@
 We contacted authors who did not provide primary study data in their published article.
-Where authors did not provide data in a format that could be re-analysed, we present the published results of their original meta-analysis.
+Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.
 
@@
 Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` reviews.
-These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies with data from `r format(effects_sum$sum_n, big.mark=",")` participants.
+These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
 
@@
     numbers_to_words(all_high_unclear),
-    if (all_high_unclear > 1 | all_high_unclear == 0) {
-      " meta-analyses"
-    } else {
-      " meta-analysis"
-    }
+    if (all_high_unclear > 1 | all_high_unclear == 0) " meta-analyses" else " meta-analysis" # nolint
   )
@@
   reviews_count %>%
-  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>%
+  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>% # nolint
   gather(name, value) %>%
@@
 qual_str <- function(n, totaln, ntype = "", prefix = "(n", suffix = ")") {
-  paste0(prefix, ntype, "= ", n, "/", totaln, ", ", scales::percent(n / totaln, accuracy = 1), suffix)
+  paste0(
+    prefix, ntype, "= ", n, "/",
+    totaln, ", ", scales::percent(n / totaln, accuracy = 1), suffix
+  )
 }
@@
 n_low_char <-
-  reviews_count[reviews_count$name == "included_studies_listed_with_important_characteristics_and_results_of_each" &
+  reviews_count[reviews_count$name ==
+    "included_studies_listed_with_important_characteristics_and_results_of_each" & # nolint
     reviews_count$value == "low", "n"][[1]]
 n_low_search <-
-  reviews_count[reviews_count$name == "literature_search_strategy_comprehensive_and_systematic" &
+  reviews_count[reviews_count$name ==
+    "literature_search_strategy_comprehensive_and_systematic" &
     reviews_count$value == "low", "n"][[1]]
@@
 n_unclear_elig <-
-  reviews_count[reviews_count$name == "eligibility_criteria_predefined_and_specified" &
+  reviews_count[reviews_count$name ==
+    "eligibility_criteria_predefined_and_specified" &
     reviews_count$value == "unclear", "n"][[1]]
@@
   qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix = "; "),
-  qual_str(n_unclear_dualquality, nrow(qual_data), " unclear  ", prefix = "n", suffix = ")")
+  qual_str(
+    n_unclear_dualquality,
+    nrow(qual_data), " unclear  ",
+    prefix = "n", suffix = ")"
+  )
 )
@@
 Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of meta-analyses)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
-Most reviews did not clearly report if their eligibility criteria were predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
+Most reviews did not clearly report if their eligibility criteria was predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
 Many papers also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
@@
 Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
-`r all_high_txt` showed high risk of bias on all criteria (if 'unclear' was treated as 'high' then `r all_high_unclear_txt` would be considered all 'high risk').
+`r all_high_txt` showed high risk of bias on all criteria (`r all_high_unclear_txt` if 'unclear' was included as 'high').
 
@@
 There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
-We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
+We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` with a significant Egger's test or insufficient studies to conduct the test.
+No remaining studies showed evidence of excessive significance.
 Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
-The remaining `r n_edu_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
+The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
 These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$total_n, big.mark=",")` individual participants.
@@
 However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95\% CI, weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
+Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
 
@@
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than non-intervention exposure (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
 The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
@@
 Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media exposure.
+Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media use.
 General screen use was positively associated with depression.
 Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen use (general, television, and video games) were positively associated with poor body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
-Screen-based interventions which targeted health behaviours appeared effective.
+All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
+Screen-based interventions which target health behaviours appeared effective.
 
@@
   filter(reanalysis_p.value < 0.05) %>%
-  nrow() - n_health_p999
+  nrow() - n_edu_p999
 
@@
 Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the 99.9\% level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
-Most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
+However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
 Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
@@
 The vast majority of screen time research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen time, but may also be inaccurate.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, @parrySystematicReviewMetaanalysis2021 found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
 It may be that the field of screen time research cannot be sufficiently advanced until more accurate and nuanced measures are available.
@@
 #### Conclusions
-
-Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the intrusion into society.
-Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
-The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each acitivty for potential harms and benefits.
-However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content and environment in which the exposure occurs.

### 2022-03-03 reports/manuscript_content.Rmd
First pass of comments

@@
 Indeed, educational screen time is positively related to educational outcomes [@sandersTypeScreenTime2019].
-This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required.
+This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required [@kayeConceptualMethodologicalMayhem2020].
 
@@
 
-*Publications*:We included meta-analyses (or meta-regressions) of quantitative evidence.
+*Publications*: We included meta-analyses (or meta-regressions) of quantitative evidence.
 To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
@@
 We descriptively present the remaining meta-analytic effect sizes.
-When the meta-analysis’s authors provided primary study data associated with these effects we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base] (version `r paste(R.Version()[c("major", "minor")], collapse = ".")`).
+To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package [@R-metafor] in R [@R-base] (version `r paste(R.Version()[c("major", "minor")], collapse = ".")`) when the meta-analysis’s authors provided primary study data associated with these effects.
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
@@
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
-Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` reviews.
+Our process yielded `r unique_effects` unique effect/outcome combinations contributed from `r prisma$data$value[9]` reviews.
 These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in [Supplementary File 5](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing) The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
+Effects not meeting one or more of these standards are presented in [Supplementary File 5](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing).
+The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
 These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
@@
 Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media use.
+S ocial media use and sexy media exposure were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
 General screen use was positively associated with depression.
@@
 
-Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the 99.9\% level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
+Across the health outcomes, most (`r n_health_p999` of `r n_health_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
 However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
@@
 Indeed, we find robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
-However, we also found evidence that if the content of the program was education, or the child was watching the program with a parent (i.e., coviewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
-Thus, parents play an important role in selecting content that is likely to benefit their children and, perhaps, interacting with their children in ways that may foster literacy (e.g., asking their children questions about the program).
-Similarly, the credible evidence we identified showed video game playing is associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
-When the video game was designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5).
+However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
+Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
+Similar nuanced findings occur for video games.
+The credible evidence we identified showed that video game playing is associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
+However, when the video game was designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5) therefore this hypothesis could not be addressed.
 
 Social media was one type of exposure that showed consistent risks to health, with no indication of potential benefit.
-Social media showed strong evidence of harmful associations with risk taking in general , as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
-These results align with meta-analytic evidence from adults indicates that social media use is also associated with increased risk of depression [@yoonSocialNetworkSite2019;@vahediAssociationSelfreportedDepressive2021].
+Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
+These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression [@yoonSocialNetworkSite2019;@vahediAssociationSelfreportedDepressive2021].
 Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls [@seetharamanFacebookKnowsInstagram2021].
@@
 Rather, it reinforces that the content of the screen time may be the most important aspect.
-Similarly, the way that a young person interacts with digital screens may also be important.
+The way that a young person interacts with digital screens may also be important.
 We found evidence that touch screens had strong evidence for benefits on learning [@xieCanTouchscreenDevices2018], as did augmented reality [@tekedereExaminingEffectivenessAugmented2016].
 
-Largely owing to small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand our view to include those reviews which did meet this threshold, there remains no clear pattern.
+Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
+If we expand to include those reviews which did meet this threshold, there remains no clear pattern although there were some age-specific differences in associations.
 For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
@@
 Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue [@elsonPolicyStatementsMedia2019;@ashtonScreenTimeChildren2019;@royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019].
-Instead, our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
+Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
 Many current guidelines simplify this complex relationship as something that should be minimised in all instances.
-We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians the information to weigh the pros and cons of interactions with screens.
+We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.
 
@@
 
-However, our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
+Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
 For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
 Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
-As such, we made decisions regarding the credibility of evidence, where others may have made used different thresholds or metrics.
+As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
 For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.

### 2022-03-03 reports/manuscript_content.Rmd

@@
     numbers_to_words(all_high_unclear),
-    if (all_high_unclear > 1 | all_high_unclear == 0) " meta-analyses" else " meta-analysis" # nolint
+    if (all_high_unclear > 1 | all_high_unclear == 0) {
+      " meta-analyses"
+    } else {
+      " meta-analysis"
+    }
   )
@@
 However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95\% CI, weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
+Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
 
@@
   filter(reanalysis_p.value < 0.05) %>%
-  nrow() - n_edu_p999
+  nrow() - n_health_p999
 

### 2022-03-03 reports/manuscript_content.Rmd
Rerender report

@@
 
-Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the intrusion into society.
+Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the growing pervasiveness into society.
 Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
-The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each acitivty for potential harms and benefits.
-However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content and environment in which the exposure occurs.
+The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content, context, and environment in which the exposure occurs.

### 2022-03-03 reports/manuscript_papaja.Rmd
Rerender report

@@
 csl               : vancouver-brackets-meta.csl
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 nocite            : "`r params$nocite_list`"

### 2022-03-07 reports/manuscript_content.Rmd
Second pass of comments

@@
 
-While some forms of screen use (e.g., television viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
+While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
 Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].
@@
 
-Citing the negative effects on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
+Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
 For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
 They also recommend that children aged 2-5 years should spend a maximum of one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
-In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health [@fergusonEverythingModerationModerate2017], and might, in fact, benefit their well-being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day).
-Some research also indicates that content (e.g., video games vs television programs) may also play an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
+In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health, and might, in fact, benefit their well-being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day)[@fergusonEverythingModerationModerate2017].
+Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
 Indeed, educational screen time is positively related to educational outcomes [@sandersTypeScreenTime2019].
@@
 
-*Population*: To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
+*Population*: 
+To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
 We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).
@@
 
-*Exposure*: We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computer, tablet, and mobile phones.
+*Exposure*: 
+We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computers, tablets, and mobile phones.
 We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content (e.g., television programs, movies, games), homework, and communication (e.g., video chat).
@@
 Consistent with this population-level approach, we excluded technology-based treatments for clinical conditions.
-However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning children) for children and youth with a clinical condition.
+However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning) for children and youth with a clinical condition.
 For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.
@@
 
-*Publications*: We included meta-analyses (or meta-regressions) of quantitative evidence.
+*Publications*: 
+We included meta-analyses (or meta-regressions) of quantitative evidence.
 To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
@@
 *Statistical Credibility*.
-We employed a statistical classification approach to grade the statistical credibility of the effect sizes in the literature.
-To be considered credible an effect needed to be derived from a combined sample of >1,000 [@papadimitriouUmbrellaReviewEvidence2021] and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
+We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
+To be considered 'credible' an effect needed to be derived from a combined sample of >1,000 [@papadimitriouUmbrellaReviewEvidence2021] and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 We initially planned to include systematic reviews without meta-analyses in a narrative summary alongside the main meta-analytic findings.
-However, we determined that combining results from the meta-analyses provided a robust overview.
+However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
 Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in [Supplementary File 2](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing).
 
-We altered our evidence assessment plan when we identified that, as written, it would treat effects from large reviews, with limited evidence of publication bias, and with consistency of effect in the population as not credible if the effect size was not statistically significant.
+We altered our evidence assessment plan when we identified that, as written, it could not classify precise evidence of null effects (i.e., from large reviews with low heterogeneity and low risk of publication bias) as 'credible' because a highly-significant *P*-value was a criteria.
 This would have significantly harmed knowledge gained from our review as it would have restricted our ability to show where the empirical evidence strongly indicated that there was no association between screen time and a given outcome.
@@
       "screen-based lifestyle risk behaviour interventions (at school)",
+      plain_language_exposure == "general tv programs and movies" ~
+      "general TV programs and movies",
       TRUE ~ plain_language_exposure
     ),
-    out = paste0(plain_language_exposure, " (n = ", n, ")")
+    out = paste0(plain_language_exposure, " (*n* = ", n, ")")
   )
@@
     plain_language_outcome = rename_effects(plain_language_outcome),
-    out = paste0(plain_language_outcome, " (n = ", n, ")")
+    plain_language_outcome = case_when(
+      plain_language_outcome == "duration sleep" ~ "sleep duration",
+      TRUE ~ plain_language_outcome
+    ),
+    out = paste0(plain_language_outcome, " (*n* = ", n, ")")
   )
@@
 After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
-`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data from these meta-analyses.
+Of those, `r prisma$data$value[8]` met the inclusion criteria and we extracted the data from all of these meta-analyses.
 Figure \@ref(fig:prisma) presents the full results of the selection process.
@@
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
-Our process yielded `r unique_effects` unique effect/outcome combinations contributed from `r prisma$data$value[9]` reviews.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded `r unique_effects` unique effect/outcome combinations contributed from `r prisma$data$value[9]` reviews.
 These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
@@
 
-qual_str <- function(n, totaln, ntype = "", prefix = "(n", suffix = ")") {
+qual_str <- function(n, totaln, ntype = "", prefix = "(*n*", suffix = ")") {
   paste0(
@@
 Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
-`r all_high_txt` showed high risk of bias on all criteria (if 'unclear' was treated as 'high' then `r all_high_unclear_txt` would be considered all 'high risk').
 
@@
 General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95\% CI, weak evidence).
+However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
 Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
@@
 The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
-These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
+These `r n_health_certain` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
 
@@
 Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-S ocial media use and sexy media exposure were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
+Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
 General screen use was positively associated with depression.
@@
 We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
-However, when meta-analyses included a more nuanced examination of exposures a more complex picture appeared.
+However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.
 
@@
 Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
-Many current guidelines simplify this complex relationship as something that should be minimised in all instances.
+Many current guidelines simplify this complex relationship as something that should be minimised in all instances [@australiangovernmentPhysicalActivityExercise2021;@whoGuidelinesPhysicalActivity2019].
 We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.
 
-#### Implications for Future Research
+## Implications for Future Research
 
@@
 Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
+Fewer than 20\% of the effects identified met our criteria for statistical credibility.
+Most studies which did not meet our critiera did so because they failed to provide study-level data (or, did not provide sufficent study level data such as including effect sizes but not sample sizes), despite <!--TODO: add reference-->
 
@@
 
-#### Strengths and Limitations
+## Strengths and Limitations
 
@@
 For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
+While our synthesis of the existing evidence provides good information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
 
-#### Conclusions
+## Conclusions
 

### 2022-03-07 _targets.R

@@ -4,12 +4,18 @@ library(here)
 
 options(tidyverse.quiet = TRUE, clustermq.scheduler = "multiprocess")
 
-packages <- c("base","broom", "bib2df", "DiagrammeR", "distill", "DT", "esc", "emojifont", 
-              "ggh4x", "googledrive", "ggplot2", "ggtext", "gt", "janitor", 
-              "knitr", "kableExtra", "magrittr", "metafor", "papaja", "targets", 
-              "tarchetypes", "tidyMB", "tidyverse", "scales", "xfun")
+packages <- c(
+  "base", "broom", "bib2df", "DiagrammeR", "distill", "DT", "esc",
+  "emojifont", "ggh4x", "googledrive", "ggplot2", "ggtext", "gt", "janitor",
+  "knitr", "kableExtra", "magrittr", "metafor", "papaja", "targets",
+  "tarchetypes", "tidyMB", "tidyverse", "scales", "xfun"
+)
 
-tar_option_set(packages = packages, debug = "yml_base", workspace_on_error = TRUE)
+tar_option_set(
+  packages = packages,
+  debug = "yml_base",
+  workspace_on_error = TRUE
+)
 
 googledrive::drive_auth()
 googlesheets4::gs4_auth()

### 2022-03-08 reports/manuscript_content.Rmd
Finish changes based on comments

@@
 Consider children watching television programs---an often cited form of screen time harm.
-Indeed, we find robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
+We found robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
 However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
@@
 
+Among studies that met our criteria for statistical certainty heterogeneity was high, with almost all effects having $I^2 > 50\%$.
+Much of this heterogeneity is likely explained by differences in measures across pooled studies, or in some cases, the generic nature of some of the exposures.
+For example, "TV programs and movies" covers a substantial range of content, which may explain the heterogeneous association with education outcomes.
+
 ## Implications for Policy and Practice
@@
 Fewer than 20\% of the effects identified met our criteria for statistical credibility.
-Most studies which did not meet our critiera did so because they failed to provide study-level data (or, did not provide sufficent study level data such as including effect sizes but not sample sizes), despite <!--TODO: add reference-->
+Most studies which did not meet our critiera failed to provide study-level data (or did not provide sufficent data, such as including effect estimates but not sample sizes).
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
+When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
+It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.
 
@@
 In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
-It may be that the field of screen time research cannot be sufficiently advanced until more accurate and nuanced measures are available.
+Indeed, of 622 studies which measured the screen time of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity [@byrneMeasurementScreenTime2021].
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras [@smithFeasibilityAutomatedCameras2019] or device-based loggers [@rydingPassiveObjectiveMeasures2020]---these are still not widely used.
+It may be that the field of screen time research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
 

### 2022-03-10 reports/manuscript_content.Rmd
Draft summary
#9

@@
 ```
+
+# Summary
+
+Children's engagement is a screen time is a complex issue.
+Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
+Hampering efforts to make an informed decision is the lack of comprehensive evidence.
+As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
+In this study, we systematically harmonize data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
+We show that some forms of screen time---such as social media---show consistent evidence of harm for children, with no clear evidence of a benefit.
+Other relationships are more complex.
+Video games, for example, are associated with poorer body composition and learning outcomes.
+However, video games for a specific educational purpose (such as numeracy) are associated with improvements in that subject area.
+Caregivers must therefore weigh the health risk against the educational benefit.
+The findings of this study provide parents and other caregivers with the information to make these informed decisions.
+
+\newpage
 

### 2022-03-10 reports/manuscript.Rmd
Add single rmd for manuscript

@@
 ---
-title: "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
+title             : "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
+shorttitle        : "Benefits and risks of electronic screens"
+
 author: 
-- name: Taren Sanders
-  affiliation: Institute for Positive Psychology and Education, ACU
-  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-  orcid_id: 0000-0002-4504-6008
-- name: Michael Noetel
-  affiliation: School of Health and Behavioural Sciences, ACU
-  affiliation_url: https://www.acu.edu.au/about-acu/faculties-directorates-and-staff/faculty-of-health-sciences/school-of-behavioural-and-health-sciences
-  orcid_id: 0000-0002-6563-8203
-- name: Philip Parker
-  affiliation: Institute for Positive Psychology and Education, ACU
-  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-  orcid_id: 0000-0002-4604-8566
-- name: Borja Del Pozo Cruz
-- name: Stuart Biddle
-- name: Rimante Ronto
-- name: Ryan Hulteen
-- name: Rhiannon Parker
-- name: George Thomas
-- name: Katrien De Cocker
-- name: Jo Salmon
-- name: Kylie Hesketh
-- name: Nicole Weeks
-- name: Hugh Arnott
-- name: Emma Devine
-- name: Roberta Vasconcellos
-- name: Chris Lonsdale
-  affiliation: Institute for Positive Psychology and Education, ACU
-  affiliation_url: https://www.acu.edu.au/research/our-research-institutes/institute-for-positive-psychology-and-education
-  orcid_id: 000-0002-2523-5565
-date: '`r format(Sys.Date())`'
-repository_url: https://github.com/Motivation-and-Behaviour/screen_umbrella
-bibliography: combined.bib
-csl: vancouver-brackets.csl
+  - name          : "Taren Sanders"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "33 Berry St, North Sydney, NSW, Australia"
+    email         : "Taren.Sanders@acu.edu.au"
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - Conceptualization
+      - Data curation
+      - Writing - Original Draft
+  - name          : "Michael Noetel"
+    affiliation   : "2"
+    role:
+      - Conceptualization
+      - Writing - Original Draft
+  - name          : "Philip Parker"
+    affiliation   : "1"
+    role:
+      - Conceptualization
+      - Writing - Original Draft
+  - name          : "Borja Del Pozo Cruz"
+    affiliation   : "3"
+    role:
+      - Writing - Review & Editing
+  - name          : "Stuart Biddle"
+    affiliation   : "4"
+    role:
+      - Writing - Review & Editing
+  - name          : "Rimante Ronto"
+    affiliation   : "5"
+    role:
+      - Writing - Review & Editing
+  - name          : "Ryan Hulteen"
+    affiliation   : "6"
+    role:
+      - Writing - Review & Editing
+  - name          : "Rhiannon Parker"
+    affiliation   : "7"
+    role:
+      - Writing - Review & Editing
+  - name          : "George Thomas"
+    affiliation   : "8"
+    role:
+      - Writing - Review & Editing
+  - name          : "Katrien De Cocker"
+    affiliation   : "5"
+    role:
+      - Writing - Review & Editing
+  - name          : "Jo Salmon"
+    affiliation   : "9"
+    role:
+      - Writing - Review & Editing
+  - name          : "Kylie Hesketh"
+    affiliation   : "9"
+    role:
+      - Writing - Review & Editing
+  - name          : "Nicole Weeks"
+    affiliation   : "1"
+    role:
+      - Writing - Review & Editing
+  - name          : "Hugh Arnott"
+    affiliation   : "1"
+    role:
+      - Writing - Review & Editing
+  - name          : "Emma Devine"
+    affiliation   : "10"
+    role:
+      - Writing - Review & Editing
+  - name          : "Roberta Vasconcellos"
+    affiliation   : "1"
+    role:
+      - Writing - Review & Editing
+  - name          : "Chris Lonsdale"
+    affiliation   : "1"
+    role:
+      - Writing - Original Draft
+      - Project Administration
+
+affiliation:
+  - id            : "1"
+    institution   : "Institute for Positive Psychology and Education, Australian Catholic University"
+  - id            : "2"
+    institution   : "School of Health and Behavioural Sciences, Australian Catholic University"
+  - id            : "3"
+    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark"
+  - id            : "4"
+    institution   : "School of Psychology and Counselling, University of Southern Queensland"
+  - id            : "5"
+    institution   : "Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University"
+  - id            : "6"
+    institution   : "School of Kinesiology, Louisiana State University"
+  - id            : "7"
+    institution   : "School of Medicine and Health, Sydney University"
+  - id            : "8"
+    institution   : "Faculty of Health Sciences, Curtin University"
+  - id            : "9"
+    institution   : "Institute for Physical Activity and Nutrition, Deakin University"
+  - id            : "10"
+    institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney"
+
+authornote: |
+  Add author notes here
+
+abstract: |
+  Add abstract here
+
+keywords          : "keywords"
+wordcount         : "X"
+
+bibliography      : ["combined.bib"]
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+csl               : vancouver-brackets-meta.csl
+output            : papaja::apa6_pdf
+nocite            : "`r params$nocite_list`"
 params:
   render_img: true
-  inc_ref: false
+  nocite_list : true
+  inc_tabs: true
 ---
@@
 ```{r setup, include=FALSE}
-# This allows distill to render from a targets pipeline
-Sys.setenv("RSTUDIO_VERSION" = '1.4.1725')
-
+Sys.setenv("RSTUDIO_VERSION" = "1.4.1725")
 knitr::opts_chunk$set(
@@
 
+options(dplyr.summarise.inform = FALSE)
+
 # Uncomment to run outside of pipeline
-# library(tidyverse)
-# library(targets)
-# library(xfun)
+library(tidyverse)
+library(targets)
+library(xfun)
+library(DiagrammeR)
+library(gt)
 ```
@@
 ```{r, load-targets}
-targets::tar_load(c("prisma", "effects_clean", "reviews_tables", "tables_df",
+targets::tar_load(c(
+    "prisma", "effects_clean", "reviews_tables", "tables_df",
     "plots", "studies_results", "studies_converted",
-                    "comparison_plots", "combined_effects", "combined_bib"), 
-         store = here::here("_targets"))
+    "comparison_plots", "combined_effects", "combined_bib"
+),
+store = here::here("_targets")
+)
 ```
+
+# Summary
+
+Children's engagement is a screen time is a complex issue.
+Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
+Hampering efforts to make an informed decision is the lack of comprehensive evidence.
+As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
+In this study, we systematically harmonize data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
+We show that some forms of screen time---such as social media---show consistent evidence of harm for children, with no clear evidence of a benefit.
+Other relationships are more complex.
+Video games, for example, are associated with poorer body composition and learning outcomes.
+However, video games for a specific educational purpose (such as numeracy) are associated with improvements in that subject area.
+Caregivers must therefore weigh the health risk against the educational benefit.
+The findings of this study provide parents and other caregivers with the information to make these informed decisions.
+
+\newpage
 
@@
 
-Citing the negative effects on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
+Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
 For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
 They also recommend that children aged 2-5 years should spend a maximum of one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
-In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health [@fergusonEverythingModerationModerate2017], and might, in fact, benefit their well-being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day).
-Some research also indicates that content (e.g., video games vs television programs) may also play an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
+In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health, and might, in fact, benefit their well-being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day)[@fergusonEverythingModerationModerate2017].
+Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
 Indeed, educational screen time is positively related to educational outcomes [@sandersTypeScreenTime2019].
-This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required.
+This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required [@kayeConceptualMethodologicalMayhem2020].
 
@@
 
-*Publications*:We included meta-analyses (or meta-regressions) of quantitative evidence.
+*Publications*: 
+We included meta-analyses (or meta-regressions) of quantitative evidence.
 To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
@@
 To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bonettTransformingOddsRatios2007;@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
-We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to do so.
-Effect sizes on the original metric are provided in supplementary materials.
+We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to meaningfully convert.
+Effect sizes on the original metric are provided in [Supplementary File 1](https://drive.google.com/file/d/1icdKoSdaOs5c8X6Ugmm0qLW_CEFSWDDu/view?usp=sharing).
 
@@
 We initially planned to include systematic reviews without meta-analyses in a narrative summary alongside the main meta-analytic findings.
-However, we determined that combining results from the meta-analyses provided a robust overview.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in eSupplementary File X.
+However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in [Supplementary File 2](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing).
 
-We altered our evidence assessment plan when we identified that, as written, it would treat effects from large reviews, with limited evidence of publication bias, and with consistency of effect in the population as not credible if the effect size was not statistically significant.
+We altered our evidence assessment plan when we identified that, as written, it could not classify precise evidence of null effects (i.e., from large reviews with low heterogeneity and low risk of publication bias) as 'credible' because a highly-significant *P*-value was a criteria.
 This would have significantly harmed knowledge gained from our review as it would have restricted our ability to show where the empirical evidence strongly indicated that there was no association between screen time and a given outcome.
@@
     if (str_detect(cur_name, ":")) {
-
         cur_name_split <- str_split(cur_name, ": ")
-  return(str_to_lower(paste(cur_name_split[[1]][2], 
-                            cur_name_split[[1]][1])))
+        return(str_to_lower(paste(
+            cur_name_split[[1]][2],
+            cur_name_split[[1]][1]
+        )))
     } else {
@@
     group_by(plain_language_exposure) %>%
-  summarise(n=n()) %>% 
+    summarise(n = n()) %>%
     arrange(desc(n)) %>%
-  mutate(plain_language_exposure = rename_effects(plain_language_exposure),
+    mutate(
+        plain_language_exposure = rename_effects(plain_language_exposure),
         plain_language_exposure = case_when(
-           plain_language_exposure=="lifestyle risk behaviour (at school) intervention" ~"screen-based lifestyle risk behaviour interventions (at school)",
-           TRUE ~ plain_language_exposure),
-         out = paste0(plain_language_exposure, " (n = ", n, ")"))
+            plain_language_exposure ==
+                "lifestyle risk behaviour (at school) intervention" ~
+            "screen-based lifestyle risk behaviour interventions (at school)",
+            plain_language_exposure == "general tv programs and movies" ~
+            "general TV programs and movies",
+            TRUE ~ plain_language_exposure
+        ),
+        out = paste0(plain_language_exposure, " (*n* = ", n, ")")
+    )
 
@@
     group_by(plain_language_outcome) %>%
-  summarise(n=n()) %>% 
+    summarise(n = n()) %>%
     arrange(desc(n)) %>%
-  mutate(plain_language_outcome = rename_effects(plain_language_outcome),
-         out = paste0(plain_language_outcome, " (n = ", n, ")"))
+    mutate(
+        plain_language_outcome = rename_effects(plain_language_outcome),
+        plain_language_outcome = case_when(
+            plain_language_outcome == "duration sleep" ~ "sleep duration",
+            TRUE ~ plain_language_outcome
+        ),
+        out = paste0(plain_language_outcome, " (*n* = ", n, ")")
+    )
 
@@
     group_by(plain_language_exposure, plain_language_outcome) %>%
-  summarise(n=n()) %>% 
+    summarise(n = n()) %>%
     arrange(desc(n))
@@
     ungroup() %>%
-  summarise(sum_k = sum(k, na.rm = TRUE),
-            sum_n = sum(n))
-
+    summarise(
+        sum_k = sum(k, na.rm = TRUE),
+        sum_n = sum(n)
+    )
 ```
@@
 After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
-`r str_to_sentence(numbers_to_words(prisma$data$value[8], and=TRUE))` met the inclusion criteria and we extracted the data from these meta-analyses.
+Of those, `r prisma$data$value[8]` met the inclusion criteria and we extracted the data from all of these meta-analyses.
 Figure \@ref(fig:prisma) presents the full results of the selection process.
 
-```{r prisma, eval=params$render_img, fig.cap="PRISMA Diagram"}
+```{r prisma, fig.cap="PRISMA Diagram"}
 prisma$diag
@@
 The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
-Supplementary file X provides a list of all exposures identified.
+[Supplementary File 3](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing) provides a list of all exposures identified.
 The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
-In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
+In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination for an age group, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
-Our process yielded `r unique_effects` unique effects/outcome combinations contributed from `r prisma$data$value[9]` reviews.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded `r unique_effects` unique effect/outcome combinations contributed from `r prisma$data$value[9]` reviews.
 These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
 
-```{r desctable, eval=params$render_img, layout="l-screen-inset shaded"}
+```{r desctable, eval=params$inc_tabs}
 reviews_tables[[1]]$table
@@
     tables_df %>%
-  filter(table=="main") %>% 
+    filter(table == "main") %>%
     distinct(covidence_id, .keep_all = TRUE) %>%
@@
     rowwise() %>%
-  mutate(count_low = sum(
+    mutate(
+        count_low = sum(
             c_across(
@@
             ) == "high"
-  ))
+        ),
+        count_high_unclear = sum(
+            c_across(
+                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+            ) %in% c("high", "unclear")
+        )
+    )
 
 all_low <- reviews_count %>%
-  filter(count_low==7) %>% 
+    filter(count_low == 7) %>%
     nrow()
@@
 all_high <- reviews_count %>%
-  filter(count_high==7) %>% 
+    filter(count_high == 7) %>%
+    nrow()
+
+all_high_unclear <- reviews_count %>%
+    filter(count_high_unclear == 7) %>%
     nrow()
@@
 all_high_txt <-
-  paste0(str_to_sentence(numbers_to_words(all_high)), 
-         if (all_high>1 | all_high==0) " meta-analyses" else " meta-analysis")
+    paste0(
+        str_to_sentence(numbers_to_words(all_high)),
+        if (all_high > 1 | all_high == 0) " meta-analyses" else " meta-analysis"
+    )
+
+all_high_unclear_txt <-
+    paste0(
+        numbers_to_words(all_high_unclear),
+        if (all_high_unclear > 1 | all_high_unclear == 0) {
+            " meta-analyses"
+        } else {
+            " meta-analysis"
+        }
+    )
 
@@
     reviews_count %>%
-  select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>%
+    select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>% # nolint
     gather(name, value) %>%
@@
 
-qual_str <- function(n, totaln, ntype="", prefix="(n", suffix=")"){
-  paste0(prefix,ntype,"= ",n,"/",totaln,", ", scales::percent(n/totaln, accuracy = 1), suffix)
+qual_str <- function(n, totaln, ntype = "", prefix = "(*n*", suffix = ")") {
+    paste0(
+        prefix, ntype, "= ", n, "/",
+        totaln, ", ", scales::percent(n / totaln, accuracy = 1), suffix
+    )
 }
@@
 n_low_char <-
-  reviews_count[reviews_count$name == "included_studies_listed_with_important_characteristics_and_results_of_each" &
+    reviews_count[reviews_count$name ==
+        "included_studies_listed_with_important_characteristics_and_results_of_each" & # nolint
         reviews_count$value == "low", "n"][[1]]
 n_low_search <-
-  reviews_count[reviews_count$name == "literature_search_strategy_comprehensive_and_systematic" &
+    reviews_count[reviews_count$name ==
+        "literature_search_strategy_comprehensive_and_systematic" &
         reviews_count$value == "low", "n"][[1]]
@@
 n_unclear_elig <-
-  reviews_count[reviews_count$name == "eligibility_criteria_predefined_and_specified" &
+    reviews_count[reviews_count$name ==
+        "eligibility_criteria_predefined_and_specified" &
         reviews_count$value == "unclear", "n"][[1]]
@@
 dualqualstr <- paste0(
-  qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix= "; "),
-  qual_str(n_unclear_dualquality, nrow(qual_data), " unclear  ", prefix = "n", suffix = ")"))
-
+    qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix = "; "),
+    qual_str(
+        n_unclear_dualquality,
+        nrow(qual_data), " unclear  ",
+        prefix = "n", suffix = ")"
+    )
+)
 ```
@@
 Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
-`r all_high_txt` showed high risk of bias on all criteria.
 
@@
     combined_effects %>%
-  filter(outcome_category=="education" & use_effect)
+    filter(outcome_category == "education" & use_effect)
 
@@
     ungroup() %>%
-  summarise(studies_n = n(),
-            total_n = sum(study_n))
+    summarise(
+        studies_n = n(),
+        total_n = sum(study_n)
+    )
 ```
@@
 There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
-We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` with a significant Egger's test or insufficient studies to conduct the test.
-No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in the supplementary material.
-The remaining `r n_edu_certain` met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
+We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
+Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
+The remaining `r n_edu_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
 These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$total_n, big.mark=",")` individual participants.
@@
 General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive (95% CI, weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games with numeracy content.
+However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
+Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
 
 ```{r educertain}
-n_edu_p999 <- edu_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
-n_edu_p95 <- edu_certain %>% filter(reanalysis_p.value<0.05) %>% nrow() - n_edu_p999
+n_edu_p999 <- edu_certain %>%
+    filter(reanalysis_p.value < 0.001) %>%
+    nrow()
+n_edu_p95 <- edu_certain %>%
+    filter(reanalysis_p.value < 0.05) %>%
+    nrow() - n_edu_p999
 
-n_edu_i2 <- edu_certain %>% filter(i2 > 50) %>% nrow()
+n_edu_i2 <- edu_certain %>%
+    filter(i2 > 50) %>%
+    nrow()
 ```
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in the supplementary material.
+Effects not meeting one or more of these standards are presented in [Supplementary File 5](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing).
 The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
-These `r n_health_effect` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
+These `r n_health_certain` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
 
-```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes"}
+```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
 plots[[2]]$plot
@@
 Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-Risky behaviors (e.g., sexual activity, risk taking, and substance abuse) were positively associated with social media use and sexy media use.
+Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
 General screen use was positively associated with depression.
 Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI).
+All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
 Screen-based interventions which target health behaviours appeared effective.
@@
 ```{r healthcertain}
-n_health_p999 <- health_certain %>% filter(reanalysis_p.value<0.001) %>% nrow()
-n_health_p95 <- health_certain %>% filter(reanalysis_p.value<0.05) %>% nrow() - n_edu_p999
+n_health_p999 <- health_certain %>%
+    filter(reanalysis_p.value < 0.001) %>%
+    nrow()
+n_health_p95 <- health_certain %>%
+    filter(reanalysis_p.value < 0.05) %>%
+    nrow() - n_health_p999
 
-n_health_i2 <- health_certain %>% filter(i2 > 50) %>% nrow()
-n_health_r2 <- health_certain %>% filter(abs(r) < 0.2) %>% nrow()
+n_health_i2 <- health_certain %>%
+    filter(i2 > 50) %>%
+    nrow()
+n_health_r2 <- health_certain %>%
+    filter(abs(r) < 0.2) %>%
+    nrow()
 ```
 
-Across the health outcomes, most (`r n_health_p999` of `r n_health_certain` effects) were statistically significant at the 99.9\% level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
-However, all of the credible effects exhibited high levels of heterogeneity, with the lowest $I^2 = 75\%$.
+Across the health outcomes, most (`r n_health_p999` of `r n_health_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
+However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
 Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
@@
 
-**Note:** *Below are rough notes on ideas for the discussion. Please feel free to add ideas. We will revise once we agree on the rest of the paper.*
+The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad domain of outcomes.
+We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
+However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.
 
-#### Broad summary of the findings relating back to the purpose
-When meta-analysis examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
-However, when meta-analyses included a more nuanced examination of exposures a more complex picture appeared.
-Many exposures were likely neither universally harmful nor consistently beneficial.
-For example, watching television programs was associated with poorer academic performance and learning.
-However, there was also evidence that if the content of the program was educational or the child watched the program with a parent (i.e., coviewing) then television viewing was associated with better literacy.
-Thus, parents play an important role in selecting content that is likely to benefit their children and, perhaps, interacting with their children in ways that may foster literacy (e.g., asking their children questions about the program).
-Similarly, the credible evidence we identified showed video game playing is associated with poorer body composition and learning.
-When the video game was designed specifically to teach numeracy, playing these games showed learning benefits.
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for credibility (see Supplementary File X).
+Consider children watching television programs---an often cited form of screen time harm.
+We found robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
+However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
+Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
+Similar nuanced findings occur for video games.
+The credible evidence we identified showed that video game playing is associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
+However, when the video game was designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5) therefore this hypothesis could not be addressed.
 
 Social media was one type of exposure that showed consistent risks to health, with no indication of potential benefit.
-Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.
-Meta-analytic evidence from adults indicates that social media use is also associated with increased risk of depression.
-Recent evidence from social media companies themselves suggest there may also be negative effects of
+Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
+These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression [@yoonSocialNetworkSite2019;@vahediAssociationSelfreportedDepressive2021].
+Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls [@seetharamanFacebookKnowsInstagram2021].
 
-Finally, there was strong evidence that sexy media was associated with sexual activity.
+One category of exposure appeared to consistently confer benefits: screen-based interventions designed to promote learning or health behaviours.
+This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
+Rather, it reinforces that the content of the screen time may be the most important aspect.
+The way that a young person interacts with digital screens may also be important.
+We found evidence that touch screens had strong evidence for benefits on learning [@xieCanTouchscreenDevices2018], as did augmented reality [@tekedereExaminingEffectivenessAugmented2016].
 
-One category of exposure appeared to consistently confer benefits: screen-based interventions designed to promote learning or health behaviours.This finding indicates that interventions can be effectively delivered using electronic media platforms.
-It does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
+Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
+If we expand to include those reviews which did meet this threshold, there remains no clear pattern although there were some age-specific differences in associations.
+For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
+Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups [@marshallRelationshipsMediaUse2004].
 
-* Touch screen = strong evidence of benefit for learning
-* Math interventions = strong evidence on numeracy.
-* Augmented reality on learning, strong evidence.
-* Screen-based interventions. Strong effect on health behaviours.
+Among studies that met our criteria for statistical certainty heterogeneity was high, with almost all effects having $I^2 > 50\%$.
+Much of this heterogeneity is likely explained by differences in measures across pooled studies, or in some cases, the generic nature of some of the exposures.
+For example, "TV programs and movies" covers a substantial range of content, which may explain the heterogeneous association with education outcomes.
 
-#### Implications of findings for targeted policy and practice
+## Implications for Policy and Practice
 
-Screen use is complex.
-We need to stop thinking about it in simplistic terms as “bad” and something that should be minimised in all instances.
-Need to think about how it can best be used.
-For example, recreational television and video games appear to confer few, if any benefits, and appear to be associated with poor body composition and academic performance.
-However, television programs and video games designed to promote learning may be effective.
-The current literature indicates that social media is likely harmful, but if social media platforms specifically designed to promote learning can be designed and popularised, perhaps they could have benefits.
+Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue [@elsonPolicyStatementsMedia2019;@ashtonScreenTimeChildren2019;@royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019].
+Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
+Many current guidelines simplify this complex relationship as something that should be minimised in all instances [@australiangovernmentPhysicalActivityExercise2021;@whoGuidelinesPhysicalActivity2019].
+We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.
 
-#### Survey of the field and implications for future research
+## Implications for Future Research
 
@@
 Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
+Fewer than 20\% of the effects identified met our criteria for statistical credibility.
+Most studies which did not meet our critiera failed to provide study-level data (or did not provide sufficent data, such as including effect estimates but not sample sizes).
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
+When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
+It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.
 
-Need to unpack the aggression research (violent video games - what happened to those reviews?)
+Screen time research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
+The vast majority of screen time research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen time, but may also be inaccurate.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
+Indeed, of 622 studies which measured the screen time of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity [@byrneMeasurementScreenTime2021].
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras [@smithFeasibilityAutomatedCameras2019] or device-based loggers [@rydingPassiveObjectiveMeasures2020]---these are still not widely used.
+It may be that the field of screen time research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
 
-There is credible evidence for X, we need more evidence for Y.
-All observational research with self-report evidence.
+## Strengths and Limitations
 
-#### Limitations of the review
+Our primary goal for this umbrella review was to provide a high-level synthesis of screen time research, by examining a range of exposures and the associations with a broad scope of outcomes.
+Our results represent the findings from `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
+To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
 
-Can’t look at fine-grained detail - eg moderators, but we did look at different exposures and outcomes (quasi moderators).
+Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
+For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
+As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
+For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
+While our synthesis of the existing evidence provides good information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
 
-We did not rate the risk of bias of the X,XXX individual studies that contributed data to this review.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment (e.g., GRADE).
+## Conclusions
 
-Also, we made somewhat arbitrary decisions to present effects that reach certain thresholds (e.g., N>1,000, non-significant Egger’s test).
-We do, however, provide more complete results in the supplementary files for those who wish to consider those meta-analyses.
+Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the growing pervasiveness into society.
+Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
+The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content, context, and environment in which the exposure occurs.
 
-#### Conclusions
-
-# Appendix
-
-#### Figures
-
-* [Prisma Diagram](https://drive.google.com/file/d/1ezgeAr2WPhy6MNSESS8bhg3VMOrLAUC7/view?usp=sharing)
-* [Education Outcomes](https://drive.google.com/file/d/1ODsKf3jjEGNCpUTz5tju8AHRpk_xIz-e/view?usp=sharing)
-* [Health-Related Outcomes](https://drive.google.com/file/d/1wdKzliWLEFuVveAj6-MzOAsoqBhnkRJW/view?usp=sharing)
-* [Supplemental Education Outcomes](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing)
-* [Supplemental Health-Related Outcomes](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing)
-
-#### Tables
-
-* [Descriptive Table](https://drive.google.com/file/d/1t5XvwY2kzsOsbZ2FxbGPsYEecZz5PgD1/view?usp=sharing)
-* Supplemental tables (TBC)
-
-#### Supplementary Files
-
-* [List of Exposures](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing)
-
-#### Links
-
-* [Manuscript Google Doc](https://docs.google.com/document/d/1NN4yJWQVepNjbX0mND4aidWWXcCDkg-eMepRnWdtQ9o/edit#)
-* [Online Report](https://motivation-and-behaviour.github.io/screen_umbrella/)
+\newpage
 
 # References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+References marked with an asterisk indicate studies which were included in the synthesis.
+<div id = "refs"></div>
+\endgroup

### 2022-03-10 reports/manuscript_papaja.Rmd
Second pass of comments
Add single rmd for manuscript

--- 2022-02-14 reports/manuscript_papaja.Rmd
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
-draft             : yes
+draft             : no
 
@@
 library(xfun)
+library(DiagrammeR)
+library(gt)
 ```
@@
 ```{r child = 'manuscript_content.Rmd'}
-
 ```

### 2022-03-11 reports/manuscript.Rmd
Remove params from manuscript file

@@
 csl               : vancouver-brackets-meta.csl
-output            : papaja::apa6_pdf
+output:papaja::apa6_pdf
 nocite            : "`r params$nocite_list`"
-params:
-  render_img: true
-  nocite_list : true
-  inc_tabs: true
 ---
@@
 
-```{r desctable, eval=params$inc_tabs}
+```{r desctable, eval = TRUE, results="asis"}
 reviews_tables[[1]]$table
@@
 
-```{r eduplot, eval=params$render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
+```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
 plots[[1]]$plot
@@
 
-```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
+```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
 plots[[2]]$plot

### 2022-03-15 reports/manuscript.Rmd
Fix typo in manuscript

@@
 
-Children's engagement is a screen time is a complex issue.
+Children's engagement in screen time is a complex issue.
 Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
@@
 While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
-Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019].
+Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
 With concerns over the impact of screen use including education, health, social development, and psychological well-being, a broad overview that identifies potential benefits and risks is needed.

### 2022-03-24 reports/manuscript.Rmd
Fix descriptive table

@@
 csl               : vancouver-brackets-meta.csl
-output:papaja::apa6_pdf
-nocite            : "`r params$nocite_list`"
+output            : papaja::apa6_pdf
+header-includes:
+    - \usepackage{makecell}
+    - \usepackage{booktabs}
+    - \usepackage{colortbl}
+# nocite            : "`r # params$nocite_list`"
 ---
@@
 ```{r desctable, eval = TRUE, results="asis"}
-reviews_tables[[1]]$table
+reviews_tables$kable$table %>%
+    kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%
+    kableExtra::row_spec(0, bold = TRUE) %>%
+    kableExtra::column_spec(3:4, width = "2cm") %>%
+    kableExtra::column_spec(5, width = "1.5cm") %>%
+    kableExtra::column_spec(6:8, width = "3cm") %>%
+    kableExtra::kable_styling(
+        latex_options = c("repeat_header"),
+        font_size = 5
+    ) %>%
+    kableExtra::landscape()
 ```

### 2022-03-24 R/tables.R

@@ -76,25 +76,53 @@ make_table_data <- function(rob_df, effects_df, reviews_df) {
 
 make_desc_tables <- function(tables_df) {
   bullet_list <- function(column) {
-    paste0("<ul style='padding-left:10px'><li>",
+    paste0(
+      "<ul style='padding-left:10px'><li>",
       paste(column %>% unique() %>% sort(),
         collapse = "</li><li>"
-      ), "</li></ul>",
+      ),
+      "</li></ul>",
+      collapse = ""
+    )
+  }
+
+  bullet_list_markdown <- function(column) {
+    paste0(
+      "* ",
+      paste(column %>% unique() %>% sort(),
+        collapse = "<br>* "
+      ),
+      "",
+      collapse = ""
+    )
+  }
+
+  bullet_list_latex <- function(column) {
+    paste0(
+      "\\begin{itemize} \n  \\item ",
+      paste(column %>% unique() %>% sort(),
+        collapse = "\n  \\item "
+      ),
+      " \n  \\end{itemize}",
       collapse = ""
     )
   }
 
   unique_list <- function(column) {
     paste(column %>% unique() %>% sort(),
-      collapse = "<br><br>"
+      collapse = "\n"
     )
   }
 
   rob_cols <- c("#b7e1cd", "#fce8b2", "#f4c7c3")
 
-  # Main table
-  base_table <- tables_df %>%
+  desc_df <- tables_df %>%
     filter(table == "main") %>%
+    select(-(eligibility_criteria_predefined_and_specified:heterogeneity_assessed))
+
+
+  # Main table
+  base_table <- desc_df %>%
     group_by(covidence_id) %>%
     mutate(
       outcomes_assessed = map(bullet_list(plain_language_outcome), gt::html),
@@ -127,12 +155,12 @@ make_desc_tables <- function(tables_df) {
       ),
       sample_ages = map(sample_ages, gt::html)
     ) %>%
-    mutate_at(
-      vars(
-        "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
-      ),
-      str_to_title
-    ) %>%
+    # mutate_at(
+    #   vars(
+    #     "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
+    #   ),
+    #   str_to_title
+    # ) %>%
     # Reorder the columns
     select(
       -starts_with("sample_age_mean"),
[…]

### 2022-05-03 reports/manuscript.Rmd
Changes based on Jo's comments Part of #9

@@
 ---
-title             : "Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review"
+title             : "Benefits and risks associated with children's and adolescents' interactions with electronic screens: An umbrella review"
 shorttitle        : "Benefits and risks of electronic screens"
@@
     - \usepackage{colortbl}
-# nocite            : "`r # params$nocite_list`"
+# remember to add no cite back in here
 ---
@@
 
-While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
+While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom&trade;) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
 Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-Yet, no review has synthesised the evidence available across a broad range of outcome domains, such as physical health, education, development, behaviour, and well-being.
+Yet, no review has synthesised the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
 
-In order to crystallise the evidence base and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
+In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
 This review synthesises evidence on any plausible outcome of electronic media exposure.
 Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children’s lives.
-By synthesising across life domains (e.g., school and home), this review provides evidence to support better guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
+By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
 
@@
 For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.
-However, a meta-analysis of interventions designed to treat clinical depression delivered by a mobile phone app would be excluded.
+However, a meta-analysis of interventions designed to *treat* clinical depression delivered by a mobile phone app would be excluded.
 
@@
 Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen use (general, television, and video games) were positively associated with body composition (e.g., BMI), although the association was smaller for children than for adolescents or for combined populations.
+All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI), although the association was smaller for children than for adolescents or for combined populations.
 Screen-based interventions which target health behaviours appeared effective.
@@
 
-The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad domain of outcomes.
+The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad range of outcomes.
 We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
@@
 
-Consider children watching television programs---an often cited form of screen time harm.
+As an example, consider children watching television programs---an often cited form of screen time harm.
 We found robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
@@
 Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
-Similar nuanced findings occur for video games.
-The credible evidence we identified showed that video game playing is associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
-However, when the video game was designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
+Similar nuanced findings were observed for video games.
+The credible evidence we identified showed that video game playing was associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
+However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
 One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5) therefore this hypothesis could not be addressed.
@@
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did meet this threshold, there remains no clear pattern although there were some age-specific differences in associations.
+If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data avilable in Supplementary Materials).
 For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
@@
 
-Screen use research is big, varied, and rapidly growing.
+Screen use research is extensive, varied, and rapidly growing.
 Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
@@
 The vast majority of screen time research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen time, but may also be inaccurate.
+In one systematic review on screen time and sleep [@haleScreenTimeSleep2015], 66 of the 67 included studies used self-reported data for *both* the exposure and outcome variable.
+It has been established that self-reported screen time data has questionnable validity.
 In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
 Indeed, of 622 studies which measured the screen time of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity [@byrneMeasurementScreenTime2021].
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras [@smithFeasibilityAutomatedCameras2019] or device-based loggers [@rydingPassiveObjectiveMeasures2020]---these are still not widely used.
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras [@smithFeasibilityAutomatedCameras2019] or device-based loggers [@rydingPassiveObjectiveMeasures2020]---these are still not widely adopted.
 It may be that the field of screen time research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
@@
 In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
-While our synthesis of the existing evidence provides good information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
+While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
 
@@
 
-Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved and the growing pervasiveness into society.
+Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved, parents' concerns, and the growing pervasiveness into society.
 Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).

### 2022-05-03 reports/manuscript.Rmd
Minor tweak to manuscript

@@
     - \usepackage{colortbl}
-# remember to add no cite back in here
+nocite            : "`r params$nocite_list`"
 ---

### 2022-05-10 reports/manuscript.Rmd
Fix issue for table and prisma

@@
     - \usepackage{colortbl}
+params:
+    nocite_list: !r list()
 nocite            : "`r params$nocite_list`"
@@
 ```{r prisma, fig.cap="PRISMA Diagram"}
-prisma$diag
+knitr::include_graphics(here::here("figure", "PRISMA Diagram.pdf"))
 ```
@@
 
-```{r desctable, eval = TRUE, results="asis"}
+```{r desctable, results="asis"}
 reviews_tables$kable$table %>%

### 2022-05-10 R/reports.R

@@ -37,7 +37,6 @@ create_reports <- list(
   tar_render(
     manuscript,
     path = here::here("reports", "manuscript.Rmd"),
-    output_file = here::here("reports", "manuscript.pdf"),
     params = list(
       nocite_list =
         paste0(

### 2022-05-10 R/plots.R
Fix issue for table and prisma

@@ -203,7 +203,7 @@ make_prisma <- function(covidence_export, effects_clean) {
     collapse = ""
   )
 
-  prisma_diag <- DiagrammeR::grViz(prisma)
+  prisma_diag <- DiagrammeR::grViz(prisma, width = 1000, height = 700)
   prisma_data <- list(data = dat, diag = prisma_diag)
 
   return(prisma_data)

### 2022-05-13 reports/manuscript.Rmd
Move references to supp file

@@
 classoption       : "man"
-csl               : vancouver-brackets-meta.csl
+csl               : nature.csl
 output            : papaja::apa6_pdf
@@
     - \usepackage{colortbl}
-params:
-    nocite_list: !r list()
-nocite            : "`r params$nocite_list`"
 ---
@@
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-References marked with an asterisk indicate studies which were included in the synthesis.
 <div id = "refs"></div>
-\endgroup

### 2022-05-13 R/reports.R
Move references to supp file

@@ -36,7 +36,12 @@ generate_bibliography <-
 create_reports <- list(
   tar_render(
     manuscript,
-    path = here::here("reports", "manuscript.Rmd"),
+    path = here::here("reports", "manuscript.Rmd")
+  ),
+  tar_render(
+    references,
+    path = here::here("reports", "references.Rmd"),
+    output_file = here::here("supplementary_files", "References.pdf"),
     params = list(
       nocite_list =
         paste0(
@@ -47,7 +52,11 @@ create_reports <- list(
   ),
   tar_target(
     uploaded_manuscripts,
-    upload_manuscript(manuscript)
+    upload_files(manuscript)
+  ),
+  tar_target(
+    uploaded_references,
+    upload_files(references)
   )
 )
 
@@ -87,10 +96,17 @@ combine_bibs <- function(packages_bib, references_bib, reviews_raw, outpath) {
 }
 
 # Upload to GDrive
-upload_manuscript <- function(word_report) {
+upload_files <- function(target_file, type = "manuscript") {
+  gdrive_path <- switch(type,
+    "manuscript" =
+      "https://drive.google.com/drive/folders/1WQiAUmDanOL2GPPBoYxUoNkHmZUjpbPj", # nolint
+    "supp" =
+      "https://drive.google.com/drive/folders/1gW5k2CIRJf1w2FP0dbUHCXwpAxtV1Gxp" # nolint
+  )
+
   drive_val <- drive_put(
-    word_report[1],
-    path = as_id("https://drive.google.com/drive/folders/1WQiAUmDanOL2GPPBoYxUoNkHmZUjpbPj")
+    target_file[1],
+    path = as_id(gdrive_path)
   )
 
   return(drive_val)

### 2022-05-13 reports/manuscript.Rmd
Fix link to table in text

@@
 
-```{r desctable, results="asis"}
-reviews_tables$kable$table %>%
+```{r desctable}
+reviews_tables$kable$data %>%
+    knitr::kable("latex",
+        caption = "Review characteristics for studies providing unique effects",
+        col.names = c(
+            "First Author", "Year", "Design Restrictions",
+            "Regions Restrictions", "Study Range",
+            "Sample Age Restrictions",
+            "Outcomes Assessed", "Exposures Assessed"
+        ),
+        escape = FALSE,
+        booktabs = TRUE,
+        align = c("l", "c", "l", "l", "c", "l", "l", "l"),
+        linesep = "",
+        longtable = TRUE
+    ) %>%
     kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%

### 2022-05-13 R/tables.R

@@ -279,23 +279,6 @@ make_desc_tables <- function(tables_df) {
     arrange(first_author, year) %>%
     mutate_all(kableExtra::linebreak, align = "l")
 
-  kable_table_main <-
-    base_table_latex %>%
-    knitr::kable("latex",
-      caption = "Review characteristics for studies providing unique effects",
-      col.names = c(
-        "First Author", "Year", "Design Restrictions",
-        "Regions Restrictions", "Study Range",
-        "Sample Age Restrictions",
-        "Outcomes Assessed", "Exposures Assessed"
-      ),
-      escape = FALSE,
-      booktabs = TRUE,
-      align = c("l", "c", "l", "l", "c", "l", "l", "l"),
-      linesep = "",
-      longtable = TRUE
-    )
-
   rob_table <-
     rob_df %>%
     distinct() %>%
@@ -416,8 +399,7 @@ make_desc_tables <- function(tables_df) {
   reviews_tables[["original"]]$table <- gt_table_main_original
   reviews_tables[["original"]]$filename <- "Descriptive table.pdf"
 
-  reviews_tables[["kable"]]$table <- kable_table_main
-  reviews_tables[["kable"]]$filename <- "Descriptive table_kable.pdf"
+  reviews_tables[["kable"]]$data <- base_table_latex
   reviews_tables[["kable"]]$nrow <- nrow(base_table_latex)
 
   reviews_tables[["rob"]]$table <- rob_table
@@ -429,6 +411,8 @@ make_desc_tables <- function(tables_df) {
 save_tables <- function(tables) {
   file_name <- here::here("figure", tables[[1]]$filename)
 
+  if (is.null(file_name)) file_name <- "NA"
+
   if ("gt_tbl" %in% class(tables[[1]]$table)) {
     gtsave(
       data = tables[[1]]$table,
@@ -436,21 +420,14 @@ save_tables <- function(tables) {
       path = here::here("figure"),
       zoom = 1
     )
-  }
 
-  if ("knitr_kable" %in% class(tables[[1]]$table)) {
-    save_kable(
-      x = tables[[1]]$table,
-      file = here::here("figure", tables[[1]]$filename)
+    # Upload to GDrive
+    drive_put(file_name,
+      path = as_id(
+        "https://drive.google.com/drive/folders/1xvn1B4bGH7hr6yBvDGUfEF7F_eO3Qeml" # nolint
+      )
[…]

### 2022-05-13 reports/manuscript.Rmd
Rename supplementary files

@@
 We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to meaningfully convert.
-Effect sizes on the original metric are provided in [Supplementary File 1](https://drive.google.com/file/d/1icdKoSdaOs5c8X6Ugmm0qLW_CEFSWDDu/view?usp=sharing).
+Effect sizes on the original metric are provided in Supplementary File 1.
 
@@
 However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in [Supplementary File 2](https://drive.google.com/file/d/1JhMsySEyfby5MtcUcIVpp0LjDDfTA5IH/view?usp=sharing).
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 2.
 
@@
 The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
-[Supplementary File 3](https://drive.google.com/file/d/12rB0ihW9Hi1kxM-8AIBfjdCMO6TqP28n/view?usp=sharing) provides a list of all exposures identified.
+Supplementary File 3 provides a list of all exposures identified.
 The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
@@
 We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in [Supplementary File 4](https://drive.google.com/file/d/1wUotZRh-jvdBJh5dkstkMtvcz7DPn-vS/view?usp=sharing).
+Effects not meeting one or more of these standards are presented in Supplementary File 4.
 The remaining `r n_edu_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in [Supplementary File 5](https://drive.google.com/file/d/1-3frrZ3woWjPqkO84Dn3_1CCaE8thIZn/view?usp=sharing).
+Effects not meeting one or more of these standards are presented in Supplementary File 5.
 The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).

### 2022-05-13 reports/manuscript.Rmd
Add wordcount
Inital refactor of manuscript info

@@
 
-authornote: |
-  Add author notes here
-
 abstract: |
-  Add abstract here
+  Can i have `r print('words')` here?
 
 keywords          : "keywords"
-wordcount         : "X"
+wordcount         : "`r wordcountaddin::word_count(here::here('reports', 'manuscript.Rmd'))`"
 
@@
 ```{r setup, include=FALSE}
-Sys.setenv("RSTUDIO_VERSION" = "1.4.1725")
 knitr::opts_chunk$set(
@@
 targets::tar_load(c(
-    "prisma", "effects_clean", "reviews_tables", "tables_df",
+    "manuscript_info", "combined_bib", "reviews_tables",
     "plots", "studies_results", "studies_converted",
@@
 
-```{r results}
-rename_effects <- function(cur_name) {
-    if (str_detect(cur_name, ":")) {
-        cur_name_split <- str_split(cur_name, ": ")
-        return(str_to_lower(paste(
-            cur_name_split[[1]][2],
-            cur_name_split[[1]][1]
-        )))
-    } else {
-        return(str_to_lower(cur_name))
-    }
-}
-rename_effects <- Vectorize(rename_effects)
-
-unique_effects <- nrow(effects_clean %>% filter(use_effect))
-
-freq_exposures <- effects_clean %>%
-    group_by(plain_language_exposure) %>%
-    summarise(n = n()) %>%
-    arrange(desc(n)) %>%
-    mutate(
-        plain_language_exposure = rename_effects(plain_language_exposure),
-        plain_language_exposure = case_when(
-            plain_language_exposure ==
-                "lifestyle risk behaviour (at school) intervention" ~
-            "screen-based lifestyle risk behaviour interventions (at school)",
-            plain_language_exposure == "general tv programs and movies" ~
-            "general TV programs and movies",
-            TRUE ~ plain_language_exposure
-        ),
-        out = paste0(plain_language_exposure, " (*n* = ", n, ")")
-    )
-
-freq_outcomes <- effects_clean %>%
-    group_by(plain_language_outcome) %>%
-    summarise(n = n()) %>%
-    arrange(desc(n)) %>%
-    mutate(
-        plain_language_outcome = rename_effects(plain_language_outcome),
-        plain_language_outcome = case_when(
-            plain_language_outcome == "duration sleep" ~ "sleep duration",
-            TRUE ~ plain_language_outcome
-        ),
-        out = paste0(plain_language_outcome, " (*n* = ", n, ")")
-    )
-
-freq_combos <- effects_clean %>%
-    group_by(plain_language_exposure, plain_language_outcome) %>%
-    summarise(n = n()) %>%
-    arrange(desc(n))
-
-effects_sum <- effects_clean %>%
-    filter(use_effect) %>%
-    group_by(covidence_review_id, moderator_age) %>%
-    slice_max(n, with_ties = TRUE) %>%
-    ungroup() %>%
-    summarise(
-        sum_k = sum(k, na.rm = TRUE),
-        sum_n = sum(n)
-    )
-```
-
-The searches yielded `r format(prisma$data$value[1], big.mark=",")` results, of which `r format(prisma$data$value[2], big.mark=",")` were duplicates.
-After screening titles and abstracts, we assessed `r format(prisma$data$value[5], big.mark=",")` full-texts for inclusion.
-Of those, `r prisma$data$value[8]` met the inclusion criteria and we extracted the data from all of these meta-analyses.
+The searches yielded `r format(manuscript_info$prisma$search, big.mark=",")` results, of which `r format(manuscript_info$prisma$duplicates, big.mark=",")` were duplicates.
+After screening titles and abstracts, we assessed `r format(manuscript_info$prisma$full_text, big.mark=",")` full-texts for inclusion.
+Of those, `r manuscript_info$prisma$included` met the inclusion criteria and we extracted the data from all of these meta-analyses.
 Figure \@ref(fig:prisma) presents the full results of the selection process.
@@
 
-The most frequently reported exposures were `r knitr::combine_words(freq_exposures$out[1:4])`.
+The most frequently reported exposures were `r manuscript_info$freq_exposures`.
 Supplementary File 3 provides a list of all exposures identified.
-The most frequently reported outcomes were `r knitr::combine_words(freq_outcomes$out[1:5])`.
-In most cases (`r paste0(sum(freq_combos$n==1), "/", nrow(effects_clean))`), there was only one exposure/outcome combination for an age group, with `r sum(freq_combos$n==2)` appearing twice, and `r sum(freq_combos$n>2)` appearing three or more times.
+The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
+In most cases (`r paste0(manuscript_info$freq_combos$n1, "/", manuscript_info$effects_clean_n)`), there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
-After removing reviews with duplicate exposure/outcome combinations, our process yielded `r unique_effects` unique effect/outcome combinations contributed from `r prisma$data$value[9]` reviews.
-These effects represent the findings of `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
+These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
 
@@
 
-```{r quality}
-qual_data <-
-    tables_df %>%
-    filter(table == "main") %>%
-    distinct(covidence_id, .keep_all = TRUE) %>%
-    select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed)
-
-reviews_count <- qual_data %>%
-    mutate(
-        across(
-            eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
-            as.factor
-        )
-    ) %>%
-    rowwise() %>%
-    mutate(
-        count_low = sum(
-            c_across(
-                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
-            ) == "low"
-        ),
-        count_high = sum(
-            c_across(
-                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
-            ) == "high"
-        ),
-        count_high_unclear = sum(
-            c_across(
-                eligibility_criteria_predefined_and_specified:heterogeneity_assessed
-            ) %in% c("high", "unclear")
-        )
-    )
-
-all_low <- reviews_count %>%
-    filter(count_low == 7) %>%
-    nrow()
-
-all_high <- reviews_count %>%
-    filter(count_high == 7) %>%
-    nrow()
-
-all_high_unclear <- reviews_count %>%
-    filter(count_high_unclear == 7) %>%
-    nrow()
-
-all_high_txt <-
-    paste0(
-        str_to_sentence(numbers_to_words(all_high)),
-        if (all_high > 1 | all_high == 0) " meta-analyses" else " meta-analysis"
-    )
-
-all_high_unclear_txt <-
-    paste0(
-        numbers_to_words(all_high_unclear),
-        if (all_high_unclear > 1 | all_high_unclear == 0) {
-            " meta-analyses"
-        } else {
-            " meta-analysis"
-        }
-    )
-
-reviews_count <-
-    reviews_count %>%
-    select(eligibility_criteria_predefined_and_specified:heterogeneity_assessed) %>% # nolint
-    gather(name, value) %>%
-    count(name, value) %>%
-    arrange(desc(n))
-
-qual_str <- function(n, totaln, ntype = "", prefix = "(*n*", suffix = ")") {
-    paste0(
-        prefix, ntype, "= ", n, "/",
-        totaln, ", ", scales::percent(n / totaln, accuracy = 1), suffix
-    )
-}
-
-n_low_hetero <-
-    reviews_count[reviews_count$name == "heterogeneity_assessed" &
-        reviews_count$value == "low", "n"][[1]]
-n_low_char <-
-    reviews_count[reviews_count$name ==
-        "included_studies_listed_with_important_characteristics_and_results_of_each" & # nolint
-        reviews_count$value == "low", "n"][[1]]
-n_low_search <-
-    reviews_count[reviews_count$name ==
-        "literature_search_strategy_comprehensive_and_systematic" &
-        reviews_count$value == "low", "n"][[1]]
-
-n_unclear_elig <-
-    reviews_count[reviews_count$name ==
-        "eligibility_criteria_predefined_and_specified" &
-        reviews_count$value == "unclear", "n"][[1]]
-
-n_high_dualscreen <-
-    reviews_count[reviews_count$name == "dual_independent_screening_review" &
-        reviews_count$value == "high", "n"][[1]]
-n_unclear_dualscreen <-
-    reviews_count[reviews_count$name == "dual_independent_screening_review" &
-        reviews_count$value == "unclear", "n"][[1]]
-
-n_high_dualquality <-
-    reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
-        reviews_count$value == "high", "n"][[1]]
-n_unclear_dualquality <-
-    reviews_count[reviews_count$name == "dual_independent_quality_assessment" &
-        reviews_count$value == "unclear", "n"][[1]]
-
-dualqualstr <- paste0(
-    qual_str(n_high_dualquality, nrow(qual_data), " high risk ", suffix = "; "),
-    qual_str(
-        n_unclear_dualquality,
-        nrow(qual_data), " unclear  ",
-        prefix = "n", suffix = ")"
-    )
-)
-```
-
 The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
-Most assessed heterogeneity `r qual_str(n_low_hetero, nrow(qual_data), " low risk ", suffix=" of meta-analyses)")`, reported the characteristics of the included studies `r qual_str(n_low_char, nrow(qual_data), " low risk ")`, and used a comprehensive and systematic search strategy `r qual_str(n_low_search, nrow(qual_data), " low risk ")`.
-Most reviews did not clearly report if their eligibility criteria were predefined `r qual_str(n_unclear_elig, nrow(qual_data), " unclear ")`.
-Many papers also did not complete dual independent screening of abstracts and full text `r qual_str(n_high_dualscreen, nrow(qual_data), " high risk ")` or did not clearly report the method of screening `r qual_str(n_unclear_dualscreen, nrow(qual_data), " unclear ")`.
-A similar trend was observed for dual independent quality assessment `r dualqualstr`.
-Overall, only `r all_low` meta-analyses were graded as low risk of bias on all criteria.
+Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
+Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
+Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
+A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
+Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.
 
@@
 Our primary goal for this umbrella review was to provide a high-level synthesis of screen time research, by examining a range of exposures and the associations with a broad scope of outcomes.
-Our results represent the findings from `r format(effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(effects_sum$sum_n, big.mark=",")` participants.
+Our results represent the findings from `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
 To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.

### 2022-05-13 reports/manuscript.Rmd
Finish refactor of manuscript

@@
 keywords          : "keywords"
-wordcount         : "`r wordcountaddin::word_count(here::here('reports', 'manuscript.Rmd'))`"
 
@@
 targets::tar_load(c(
-    "manuscript_info", "combined_bib", "reviews_tables",
-    "plots", "studies_results", "studies_converted",
-    "comparison_plots", "combined_effects", "combined_bib"
+    "manuscript_info", "combined_bib", "reviews_tables", "combined_bib", "plots"
 ),
@@
 
-```{r eduoutcomes}
-edu_effect <-
-    combined_effects %>%
-    filter(outcome_category == "education" & use_effect)
-
-edu_certain <-
-    combined_effects %>%
-    filter(outcome_category == "education" & certainty == "meets criteria")
-
-n_edu_effect <-
-    edu_effect %>%
-    nrow()
-
-n_edu_certain <-
-    edu_certain %>%
-    nrow()
-
-n_edu_noindiv <-
-    edu_effect %>%
-    filter(source == "reported") %>%
-    nrow()
-
-n_edu_samplesize <-
-    edu_effect %>%
-    filter(source == "reanalysis" & n < 1000) %>%
-    nrow()
-
-n_edu_faileggers <-
-    edu_effect %>%
-    filter(source == "reanalysis" & n > 1000 &
-        (eggers_p < 0.05 | is.na(eggers_p))) %>%
-    nrow()
-
-n_edu_failtest <-
-    edu_effect %>%
-    filter(source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05) %>%
-    nrow()
-
-n_edu_unique <- n_distinct(edu_certain$covidence_review_id)
-
-edu_summary <-
-    studies_converted %>%
-    filter(effect_size_id %in% edu_certain$effect_size_id) %>%
-    group_by(study_author, study_year, study_first_page_number) %>%
-    slice_max(study_n, with_ties = FALSE) %>%
-    ungroup() %>%
-    summarise(
-        studies_n = n(),
-        total_n = sum(study_n)
-    )
-```
-
-There were `r n_edu_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
-We removed `r n_edu_noindiv` effects that did not provide individual study-level data, `r n_edu_samplesize` effects with samples < 1,000, and `r n_edu_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
+There were `r manuscript_info$edu$n_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
+We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
 Effects not meeting one or more of these standards are presented in Supplementary File 4.
-The remaining `r n_edu_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
-These `r n_edu_certain` effects came from `r n_edu_unique` meta-analytic reviews analysing data from `r edu_summary$studies_n` empirical studies with `r format(edu_summary$total_n, big.mark=",")` individual participants.
+The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
+These `r manuscript_info$edu$n_certain` effects came from `r manuscript_info$edu$n_unique` meta-analytic reviews analysing data from `r manuscript_info$edu$summary$studies_n` empirical studies with `r format(manuscript_info$edu$summary$total_n, big.mark=",")` individual participants.
 
@@
 
-```{r educertain}
-n_edu_p999 <- edu_certain %>%
-    filter(reanalysis_p.value < 0.001) %>%
-    nrow()
-n_edu_p95 <- edu_certain %>%
-    filter(reanalysis_p.value < 0.05) %>%
-    nrow() - n_edu_p999
-
-n_edu_i2 <- edu_certain %>%
-    filter(i2 > 50) %>%
-    nrow()
-```
-
-As shown in Figure \@ref(fig:eduplot), most of the credible results (`r n_edu_p999` of `r n_edu_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
-The remaining `r xfun::numbers_to_words(n_edu_p95)` associations were significant at the 95% confidence level (weak evidence).
+As shown in Figure \@ref(fig:eduplot), most of the credible results (`r manuscript_info$edu$n_p999` of `r manuscript_info$edu$n_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
+The remaining `r xfun::numbers_to_words(manuscript_info$edu$n_p95)` associations were significant at the 95% confidence level (weak evidence).
 All credible effects related to education outcomes were small-to-moderate.
@@
 The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
-Most effects showed high levels of heterogeneity (`r n_edu_i2` of `r n_edu_certain` with $I^2 > 50\%$).
+Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).
 
@@
 
-```{r healthoutcome}
-health_effect <-
-    combined_effects %>%
-    filter(outcome_category != "education" & use_effect)
-
-health_certain <-
-    combined_effects %>%
-    filter(outcome_category != "education" & certainty == "meets criteria")
-
-n_health_effect <-
-    health_effect %>%
-    nrow()
-
-n_health_certain <-
-    health_certain %>%
-    nrow()
-
-n_health_noindiv <-
-    health_effect %>%
-    filter(source == "reported") %>%
-    nrow()
-
-n_health_samplesize <-
-    health_effect %>%
-    filter(source == "reanalysis" & n < 1000) %>%
-    nrow()
-
-n_health_faileggers <-
-    health_effect %>%
-    filter(source == "reanalysis" & n > 1000 &
-        (eggers_p < 0.05 | is.na(eggers_p))) %>%
-    nrow()
-
-n_health_failtest <-
-    health_effect %>%
-    filter(source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05) %>%
-    nrow()
-
-n_health_unique <- n_distinct(health_certain$covidence_review_id)
-
-health_summary <-
-    studies_converted %>%
-    filter(effect_size_id %in% health_certain$effect_size_id) %>%
-    group_by(study_author, study_year, study_first_page_number) %>%
-    slice_max(study_n, with_ties = FALSE) %>%
-    ungroup() %>%
-    summarise(
-        studies_n = n(),
-        total_n = sum(study_n)
-    )
-```
-
-We identified `r n_health_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-We removed `r n_health_noindiv` effects that did not provide individual study-level data, `r n_health_samplesize` effects with samples < 1,000, and `r n_health_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
+We identified `r manuscript_info$health$n_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
+We removed `r manuscript_info$health$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$health$n_samplesize` effects with samples < 1,000, and `r manuscript_info$health$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
 No remaining studies showed evidence of excessive significance.
 Effects not meeting one or more of these standards are presented in Supplementary File 5.
-The remaining `r n_health_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
-These `r n_health_certain` effects came from `r n_health_unique` meta-analytic reviews analysing data from `r health_summary$studies_n` empirical studies with `r format(health_summary$total_n, big.mark=",")` individual participants.
+The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
+These `r manuscript_info$health$n_certain` effects came from `r manuscript_info$health$n_unique` meta-analytic reviews analysing data from `r manuscript_info$health$summary$studies_n` empirical studies with `r format(manuscript_info$health$summary$total_n, big.mark=",")` individual participants.
 
@@
 
-```{r healthcertain}
-n_health_p999 <- health_certain %>%
-    filter(reanalysis_p.value < 0.001) %>%
-    nrow()
-n_health_p95 <- health_certain %>%
-    filter(reanalysis_p.value < 0.05) %>%
-    nrow() - n_health_p999
-
-n_health_i2 <- health_certain %>%
-    filter(i2 > 50) %>%
-    nrow()
-n_health_r2 <- health_certain %>%
-    filter(abs(r) < 0.2) %>%
-    nrow()
-```
-
-Across the health outcomes, most (`r n_health_p999` of `r n_health_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(n_health_p95)` significant at 95\% confidence.
+Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
 However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
 Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
-Most of the effect sizes (`r n_health_r2`/`r n_health_certain`) had an absolute value of $r < 0.2$.
+Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.
 

### 2022-05-13 R/reports.R
Finish refactor of manuscript

@@ -36,7 +36,9 @@ generate_bibliography <-
 create_reports <- list(
   tar_target(
     manuscript_info,
-    create_manuscript_info(effects_clean, prisma, tables_df)
+    create_manuscript_info(
+      effects_clean, prisma, tables_df, combined_effects, studies_converted
+    )
   ),
   tar_render(
     manuscript,
@@ -120,7 +122,8 @@ upload_files <- function(target_file, type = "manuscript") {
 }
 
 # Make info required for manuscript
-create_manuscript_info <- function(effects_clean, prisma, tables_df) {
+create_manuscript_info <- function(effects_clean, prisma, tables_df,
+                                   combined_effects, studies_converted) {
   manuscript_info <- list()
 
   # Results --------------------------------------------------
@@ -334,6 +337,129 @@ create_manuscript_info <- function(effects_clean, prisma, tables_df) {
       suffix = ")"
     )
   )
+
+  # Education Results ---------------------------------------------
+  edu_effect <-
+    combined_effects %>%
+    filter(outcome_category == "education" & use_effect)
+
+  edu_certain <-
+    combined_effects %>%
+    filter(outcome_category == "education" & certainty == "meets criteria")
+
+  manuscript_info$edu$n_effect <- edu_effect %>% nrow()
+  manuscript_info$edu$n_certain <- edu_certain %>% nrow()
+
+  manuscript_info$edu$n_noindiv <-
+    edu_effect %>%
+    filter(source == "reported") %>%
+    nrow()
+
+  manuscript_info$edu$n_samplesize <-
+    edu_effect %>%
+    filter(source == "reanalysis" & n < 1000) %>%
+    nrow()
+
+  manuscript_info$edu$n_faileggers <-
+    edu_effect %>%
+    filter(source == "reanalysis" & n > 1000 &
+      (eggers_p < 0.05 | is.na(eggers_p))) %>%
+    nrow()
+
+  manuscript_info$edu$n_failtest <-
+    edu_effect %>%
+    filter(
+      source == "reanalysis" & n > 1000 & eggers_p > 0.05 & tes_p < 0.05
+    ) %>%
+    nrow()
+
+  manuscript_info$edu$n_unique <- n_distinct(edu_certain$covidence_review_id)
+  manuscript_info$edu$summary <-
+    studies_converted %>%
[…]

### 2022-05-16 reports/manuscript.Rmd
Add abstract and update supplementary files

@@
 abstract: |
-  Can i have `r print('words')` here?
+  Children's engagement in screen time is a complex issue.
+  While some forms of screen time have consistently been associated with harm, others have been associated with gains, making it difficult to weigh the risks and benefits of use.
+  In this umbrella review, we systematically collate and synthesise meta-analyses examining the effects of screen use on children and youth.
+  We converted results onto a common metric to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
+  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations.
+  These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
+  When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potentially harmful impacts on learning, literacy, body composition, and depression.
+  Like-wise, social media was consistently associated with risks to health, with no identified benefits.
+  However, we also found that these harms could often be mitigated by certain kinds of content (e.g., educational), or by modifying the context (e.g., co-viewing with a parent).
+  In summary, our findings point to the need for careful and nuanced guidelines that support parents to make the best deicsions for their children.
 
-keywords          : "keywords"
+keywords          : "screen time; youth; health; education"
+wordcount         : "`r wordcountaddin::word_count(here::here('reports', 'manuscript.Rmd'))`"
 
@@
 
+We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051).
+
 ### Eligibility criteria
@@
 
-The search strategy associated with each of the 12 databases can be found [here](https://docs.google.com/document/d/1hz5Dgw0aVOMeXL3vpRXsNtCIbf6dHZTb8uz7wQ29ke4/edit#heading=h.i6znptfz9nwa).
+The search strategy associated with each of the 12 databases can be found in Supplementary File 1.
 We hand searched reference lists from any relevant umbrella reviews to identify systematic meta-analyses that our search may have missed.
@@
 We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to meaningfully convert.
-Effect sizes on the original metric are provided in Supplementary File 1.
+Effect sizes on the original metric are provided in Supplementary File 2.
 
@@
 However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 2.
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 3.
 
@@
 The most frequently reported exposures were `r manuscript_info$freq_exposures`.
-Supplementary File 3 provides a list of all exposures identified.
+Supplementary File 4 provides a list of all exposures identified.
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
@@
 We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in Supplementary File 4.
+Effects not meeting one or more of these standards are presented in Supplementary File 5.
 The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in Supplementary File 5.
+Effects not meeting one or more of these standards are presented in Supplementary File 6.
 The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
@@
 As an example, consider children watching television programs---an often cited form of screen time harm.
-We found robust evidence for a small association with poorer academic performance and literacy skills [@adelantado-renauAssociationScreenMedia2019].
+We found robust evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
 However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
@@
 However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5) therefore this hypothesis could not be addressed.
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 5 & 6) therefore this hypothesis could not be addressed.
 

### 2022-05-16 README.Rmd
Update README

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

<!-- badges: start -->
<!-- badges: end -->

Contains all of the project files to conduct the analysis and generate the manuscript for the umbrella review.

## Using this Repo

1. Clone the repository, ensuring that you are using the latest version.
1. Open directory and run `renv::restore()` to download/update the required packages.
1. You must run `googledrive::drive_auth()` and `googlesheets4::gs4_auth()` before running targets in order the cache your oAuth token.
1. To build the project, run `targets::tar_make()`.

### Notes

You should be able to run the analysis to examine the reproducability. However, some of the pipeline targets also write data to Google Sheets, which will cause these targets to fail. If you are not a project contributor, you may need to manually exclude these targets.

You can also run the build in parallel using `targets::tar_make_clustermq(workers=<num_workers>)`. This can be faster, but not always. There's usually no benefit beyond 3 or 4 workers.

## Links

* [PROSPERO Registration](https://www.crd.york.ac.uk/prospero/display_record.php?RecordID=76051)
* [Open Science Framework](https://osf.io/3ubqp/)

### 2022-05-16 reports/manuscript.Rmd
Fix typo in abstract
Fix affiliations

@@
   - name          : "Katrien De Cocker"
-    affiliation   : "5"
+    affiliation   : "9"
     role:
@@
   - name          : "Jo Salmon"
-    affiliation   : "9"
+    affiliation   : "10"
     role:
@@
   - name          : "Kylie Hesketh"
-    affiliation   : "9"
+    affiliation   : "10"
     role:
@@
   - name          : "Emma Devine"
-    affiliation   : "10"
+    affiliation   : "11"
     role:
@@
   - id            : "9"
+    institution   : "Faculty of Medicine and Health Sciences, Ghent University"
+  - id            : "10"
     institution   : "Institute for Physical Activity and Nutrition, Deakin University"
-  - id            : "10"
+  - id            : "11"
     institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney"
@@
   However, we also found that these harms could often be mitigated by certain kinds of content (e.g., educational), or by modifying the context (e.g., co-viewing with a parent).
-  In summary, our findings point to the need for careful and nuanced guidelines that support parents to make the best deicsions for their children.
+  In summary, our findings point to the need for careful and nuanced guidelines that support parents to make the best decisions for their children.
 

### 2022-05-21 reports/manuscript.Rmd
Rerun pipeline

@@
     role:
+      - Conceptualization
       - Writing - Original Draft

### 2022-07-20 reports/manuscript.Rmd
Change Stuart's affiliation

@@
   - id            : "4"
-    institution   : "School of Psychology and Counselling, University of Southern Queensland"
+    institution   : "Centre for Health Research, University of Southern Queensland"
   - id            : "5"
@@
   - id            : "9"
-    institution   : "Faculty of Medicine and Health Sciences, Ghent University"
+    institution   : "Department of Movement and Sport Science, Ghent University"
   - id            : "10"

### 2023-03-02 reports/manuscript.Rmd
Fix manuscript rendering

@@
 ```{r, load-targets}
-targets::tar_load(c(
-  "manuscript_info", "combined_bib", "reviews_tables", "combined_bib", "plots"
+targets::tar_load(
+  c(
+    "manuscript_info", "combined_bib", "plots", "prisma", "table_desc_latex",
+    "edu_certain_params", "plot_edu_certain",
+    "nonedu_certain_params", "plot_nonedu_certain"
   ),
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab:desctable)).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab::desctable)).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 ```{r prisma, fig.cap="PRISMA Diagram"}
-knitr::include_graphics(here::here("figure", "PRISMA Diagram.pdf"))
+knitr::include_graphics("../figures/PRISMA Diagram.pdf", error = FALSE)
 ```
@@
 In most cases (`r paste0(manuscript_info$freq_combos$n1, "/", manuscript_info$effects_clean_n)`), there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
+Full characteristics of the included studies are provided in Table \@ref(tab::desctable).
 After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
@@
 ```{r desctable}
-reviews_tables$kable$data %>%
-  knitr::kable("latex",
+table_desc_latex %>%
+  knitr::kable(
+    "latex",
     caption = "Review characteristics for studies providing unique effects",
@@
   ) %>%
-  kableExtra::row_spec(1:reviews_tables$kable$nrow, hline_after = TRUE) %>%
+  kableExtra::row_spec(1:nrow(table_desc_latex), hline_after = TRUE) %>%
   kableExtra::row_spec(0, bold = TRUE) %>%
@@
 
-The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
+The quality of the included meta-analyses was mixed (see Table \@ref(tab::desctable)).
 Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
@@
 
-```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
-plots[[1]]$plot
+```{r eduplot, fig.width=edu_certain_params$dims[[1]], fig.height=edu_certain_params$dims[[2]], fig.cap="Education outcomes"}
+plot_edu_certain
 ```
@@
 
-```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
-plots[[2]]$plot
+```{r healthplot, fig.width=nonedu_certain_params$dims[[1]], fig.height=nonedu_certain_params$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
+plot_nonedu_certain
 ```

### 2023-03-02 reports/manuscript.Rmd
Updated data and restructure codebase (#17)
* Add description and license

* Update renv

* Move all targets into _targets.R

* Add bibtex keys and update bib

* Move to local datasets
Fixes #12

* Refactor and tidy codebase

* Rerun full pipeline

* Update results

@@
 # Uncomment to run outside of pipeline
-library(tidyverse)
-library(targets)
-library(xfun)
-library(DiagrammeR)
-library(gt)
+# library(targets)
+# library(xfun)
+# library(DiagrammeR)
+# library(gt)
 ```
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab::desctable)).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab:desctable)).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
-In most cases (`r paste0(manuscript_info$freq_combos$n1, "/", manuscript_info$effects_clean_n)`), there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table \@ref(tab::desctable).
+In `r manuscript_info$freq_combos$n1` cases there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
+Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
 After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
@@
 
-The quality of the included meta-analyses was mixed (see Table \@ref(tab::desctable)).
+The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
 Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
@@
 Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
-General screen use was positively associated with depression.
-Television viewing was negatively correlated with sleep duration, but only at the 95% confidence level (weak evidence).
-All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI), although the association was smaller for children than for adolescents or for combined populations.
-Screen-based interventions which target health behaviours appeared effective.
+General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
+All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
+Screen-based interventions which target health behaviours appeared mostly effective.
 
 Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
-However, most of the credible effects exhibited high levels of heterogeneity, with all but one having $I^2 > 75\%$.
-Additionally, most effects were small, with the association between unhealthy food advertising and intake the largest at $r = 0.25$ ($k = 13, N = 1,756$).
+However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
+Additionally, most effects were small, with the association between screen use and sleep duration the largest at $r = -0.37$ ($k = 10, N = 56,720$).
 Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.

### 2023-03-02 R/clean_effects.R

@@ -1,0 +1,103 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param effects_raw
+#' @param reviews_clean
+#' @param age_codes
+#' @return
+#' @author Taren Sanders
+#' @export
+clean_effects <- function(effects_raw, reviews_clean, age_codes) {
+  effects_clean <-
+    effects_raw %>%
+    # Remove any unusable effects (must have value and N)
+    filter(!is.na(value) & !is.na(combined_n) & use_moderator) %>%
+    # Translate the statistical tests to common abbreviations
+    mutate(stat_test_clean = translate_tests(statistical_test)) %>%
+    # Can only use some of the metric types
+    filter(stat_test_clean %in% c("b", "d", "r", "or", "z")) %>%
+    convert_effects() %>%
+    rename(
+      outcome_category = outcome_level_1,
+      outcome = outcome_level_2,
+      moderator_level = moderator_level_recoded,
+      moderator_category = moderator_category_recoded,
+      k = k_number_of_effects_informing_this_test,
+      n = combined_n,
+      i2 = i2_calculated,
+      plain_language_outcome = outcome_plain_language_descriptor,
+      raw_value = value,
+      raw_cilb = value_ci_lower_bound,
+      raw_ciub = value_ci_upper_bound
+    ) %>%
+    # Add the demographics in from the review-level data
+    left_join(
+      select(reviews_clean, review_id, author_year, demographics_coded),
+      by = "review_id"
+    ) %>%
+    rename(moderator_age = demographics_coded)
+
+  # Check for ages within the normal moderators and change moderator_age
+  age_moderator_categories <- c(
+    "age", "Age", "Educational level", "Grade Level",
+    "School level", "Level of education"
+  )
+  effects_clean <- effects_clean %>%
+    mutate(moderator_age = case_when(
+      moderator_category %in% age_moderator_categories &
+        moderator_level %in% age_codes$mixed ~ "Mixed",
+      moderator_category %in% age_moderator_categories &
+        moderator_level %in% age_codes$adolescents ~ "Adolescents",
+      moderator_category %in% age_moderator_categories &
+        moderator_level %in% age_codes$children ~ "Children",
+      moderator_category %in% age_moderator_categories &
+        moderator_level %in% age_codes$young_children ~ "Young children",
[…]

### 2023-03-02 R/clean_reviews.R

@@ -1,0 +1,69 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param reviews_raw
+#' @param effects_raw
+#' @param age_codes
+#' @return
+#' @author Taren Sanders
+#' @export
+clean_reviews <- function(reviews_raw, effects_raw, age_codes) {
+  zero_effects_ids <-
+    effects_raw %>%
+    group_by(review_id) %>%
+    summarise(n_valid_effects = sum(
+      !is.na(value) & !is.na(combined_n) & use_moderator
+    )) %>%
+    filter(n_valid_effects == 0) %>%
+    pull(review_id)
+
+  reviews_clean <-
+    reviews_raw %>%
+    mutate(
+      demographics_coded = case_when(
+        demographics %in% age_codes$mixed ~ "Mixed",
+        demographics %in% age_codes$adolescents ~ "Adolescents",
+        demographics %in% age_codes$children ~ "Children",
+        demographics %in% age_codes$young_children ~ "Young children",
+        TRUE ~ demographics
+      ),
+      # Tidy up the sample age variables
+      sample_age_lowest_study_mean =
+        as.numeric(case_when(
+          grepl("months", sample_age_lowest_study_mean) ~
+            as.character(as.numeric(
+              str_remove(sample_age_lowest_study_mean, " months")
+            ) / 12),
+          TRUE ~ sample_age_lowest_study_mean
+        )),
+      sample_age_highest_study_mean =
+        as.numeric(case_when(
+          grepl("months", sample_age_highest_study_mean) ~
+            as.character(as.numeric(
+              str_remove(sample_age_highest_study_mean, " months")
+            ) / 12),
+          TRUE ~ sample_age_highest_study_mean
+        )),
+      # Double check the coding based on the age variables
+      demographics_coded = case_when(
+        sample_age_lowest_study_mean < 8 & sample_age_highest_study_mean > 16 ~
+          "Mixed",
+        sample_age_lowest_study_mean < 1 & sample_age_highest_study_mean > 10 ~
+          "Mixed",
+        sample_age_lowest_study_mean >= 12 ~ "Adolescents",
+        sample_age_highest_study_mean < 7 ~ "Young children",
+        sample_age_lowest_study_mean >= 4 & sample_age_highest_study_mean < 13 ~
+          "Children",
+        TRUE ~ demographics_coded
+      )
[…]

### 2023-03-02 R/combine_study_results.R

@@ -1,0 +1,41 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param meta_aggregated_r
+#' @param eggers_results_r
+#' @param excess_sig_results_r
+#' @param meta_aggregated_z
+#' @param eggers_results_z
+#' @param excess_sig_results_z
+#' @return
+#' @author Taren Sanders
+#' @export
+combine_study_results <- function(meta_aggregated_r, eggers_results_r,
+                                  excess_sig_results_r, meta_aggregated_z,
+                                  eggers_results_z, excess_sig_results_z) {
+  main_df <-
+    full_join(meta_aggregated_r, eggers_results_r, by = "effect_size_id") %>%
+    full_join(excess_sig_results_r, by = "effect_size_id") %>%
+    select(-type, -term) %>%
+    relocate(effect_size_id) %>%
+    rename_with(
+      .cols = estimate:tes_thetalim,
+      .fn = ~ paste0("reanalysis_", .x)
+    )
+
+  z_df <-
+    full_join(meta_aggregated_z, eggers_results_z, by = "effect_size_id") %>%
+    full_join(excess_sig_results_z, by = "effect_size_id") %>%
+    select(-type, -term, -k, , n, -n_max) %>%
+    relocate(effect_size_id) %>%
+    rename_with(
+      .cols = estimate:tes_thetalim,
+      .fn = ~ paste0("reanalysis_", .x, "_z")
+    )
+
+  joined_df <- full_join(main_df, z_df, by = "effect_size_id")
+
+  return(joined_df)
+}

### 2023-03-02 R/make_forest_plot.R

@@ -1,0 +1,329 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param combined_effects
+#' @param plot_params
+#' @param debug
+#' @return
+#' @author Taren Sanders
+#' @export
+make_forest_plot <- function(combined_effects, plot_params, debug = FALSE) {
+  if (debug) labsize <- 1 else labsize <- NA
+
+  plot_effects <-
+    combined_effects %>%
+    filter(use_effect) %>%
+    mutate(
+      # Truncate large effects
+      cilb999 = if_else(cilb999 < -1, -1, cilb999),
+      ciub999 = if_else(ciub999 > 1, 1, ciub999),
+      # Overall outcome into a variable and remove that from the sub-variable
+      outcome_lvl_1 = factor(gsub(":.*", "", plain_language_outcome)),
+      plain_language_outcome = gsub(".*: ", "", plain_language_outcome),
+      outcome_category = factor(str_to_title(outcome_category)),
+      plain_language_exposure = str_replace(
+        plain_language_exposure,
+        "^Intervention:",
+        "Screen-based intervention:"
+      ),
+      # Fix long labels
+      plain_language_outcome = trimmer(plain_language_outcome, 40),
+      plain_language_exposure = trimmer(plain_language_exposure, 40),
+      i2 = scales::percent(i2, 2, scale = 1),
+      n = scales::label_comma(accuracy = 1)(n),
+      k = as.character(k),
+      rci = paste(format(round(r, 2), nsmall = 2),
+        " [", format(round(cilb95, 2), nsmall = 2), ", ",
+        format(round(ciub95, 2), nsmall = 2), "]",
+        sep = ""
+      ),
+      indiv_data = fontawesome(if_else(source == "reanalysis",
+        "fa-check", "fa-times"
+      )),
+      eggers = case_when(
+        source == "reported" ~ fontawesome("fa-minus"),
+        reanalysis_eggers_p > 0.05 ~ fontawesome("fa-check"),
+        TRUE ~ fontawesome("fa-times")
+      ),
+      esig = case_when(
+        source == "reported" ~ fontawesome("fa-minus"),
+        reanalysis_tes_p > 0.05 ~ fontawesome("fa-check"),
+        TRUE ~ fontawesome("fa-times")
+      ),
+      font_fam = "fontawesome-webfont",
[…]

### 2023-03-02 R/make_manuscript_info.R

@@ -1,0 +1,378 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param effects_clean
+#' @param prisma
+#' @param tables_df
+#' @param combined_effects
+#' @param studies_clean
+#' @return
+#' @author Taren Sanders
+#' @export
+make_manuscript_info <- function(effects_clean, prisma, tables_df,
+                                 combined_effects, studies_clean) {
+  manuscript_info <- list()
+
+  # Results --------------------------------------------------
+
+  ## Number of effects
+  manuscript_info$effects_clean_n <- nrow(effects_clean)
+
+  ## Number of unique effects
+  manuscript_info$unique_effects <- nrow(effects_clean %>% filter(use_effect))
+
+  ## List of frequent exposures
+  manuscript_info$freq_exposures <- effects_clean %>%
+    group_by(plain_language_exposure) %>%
+    summarise(n = n()) %>%
+    arrange(desc(n)) %>%
+    mutate(
+      plain_language_exposure = rename_effects(plain_language_exposure),
+      plain_language_exposure = case_when(
+        plain_language_exposure ==
+          "lifestyle risk behaviour (at school) intervention" ~
+          "screen-based lifestyle risk behaviour interventions (at school)",
+        plain_language_exposure == "general tv programs and movies" ~
+          "general TV programs and movies",
+        TRUE ~ plain_language_exposure
+      ),
+      out = paste0(plain_language_exposure, " (*n* = ", n, ")")
+    ) %>%
+    head(4) %>%
+    pull(out) %>%
+    knitr::combine_words()
+
+  ## List of frequent outcomes
+  manuscript_info$freq_outcomes <- effects_clean %>%
+    group_by(plain_language_outcome) %>%
+    summarise(n = n()) %>%
+    arrange(desc(n)) %>%
+    mutate(
+      plain_language_outcome = rename_effects(plain_language_outcome),
+      plain_language_outcome = case_when(
+        plain_language_outcome == "duration sleep" ~ "sleep duration",
+        TRUE ~ plain_language_outcome
+      ),
+      out = paste0(plain_language_outcome, " (*n* = ", n, ")")
+    ) %>%
+    head(5) %>%
[…]

### 2023-03-02 R/make_prisma.R

@@ -1,0 +1,193 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param prisma_path
+#' @param effects_clean
+#' @param reviews_clean
+#' @return
+#' @author Taren Sanders
+#' @export
+make_prisma <- function(prisma_path, effects_clean, reviews_clean) {
+  prisma_data <- readr::read_file(prisma_path)
+
+  prisma_df <-
+    # Convert each to a separate line
+    tibble(text = unlist(str_split(prisma_data, pattern = "\\n"))) %>%
+    filter(
+      !str_detect(text, "studies ongoing"),
+      !str_detect(text, "studies awaiting classification")
+    ) %>%
+    # Determine row type
+    mutate(
+      type = case_when(
+        startsWith(text, "\t\t") ~ "exclude_reason",
+        startsWith(text, "\t") ~ "exclude",
+        TRUE ~ "main"
+      ),
+      text = str_replace_all(
+        text, "studies included",
+        "met inclusion criteria"
+      ),
+      step = 0,
+      text = str_replace_all(text, "\t", ""),
+      value = str_extract(text, "^[0-9]+") %>% as.numeric(),
+      text = str_remove(text, "^[0-9]+") %>% str_trim()
+    )
+
+  step <- 0
+  for (i in seq_len(nrow(prisma_df))) {
+    if (prisma_df$type[i] == "main") step <- step + 1
+    prisma_df$step[i] <- step
+  }
+
+  prisma_df <- prisma_df %>%
+    exclusion_collapse(
+      c("Not a systematic review", "Not a review"),
+      "Not a systematic review"
+    ) %>%
+    exclusion_collapse(
+      c(
+        "Systematic review without meta-analysis",
+        "Sys review of qual studies", "Review of reviews"
+      ),
+      "Systematic review without meta-analysis"
+    ) %>%
+    exclusion_collapse(
+      c("Duplicated reference", "DUPLICATE TO MERGE LATER"),
+      "Duplicated reference"
+    ) %>%
+    exclusion_collapse(
+      c(
+        "Meta analysis that meets inclusion criteria, but youth results not presented and authors did not/could not provide individual study data when contacted.", # nolint
+        "Individual level data only",
+        "Analysis not moderated by age",
[…]

### 2023-03-02 R/run_excess_sig.R

@@ -1,0 +1,23 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param meta_results
+#' @return
+#' @author Taren Sanders
+#' @export
+run_excess_sig <- function(meta_results) {
+  exc_sig <- tes(meta_results)
+  tes_df <- tibble(
+    effect_size_id = meta_results$effect_size_id,
+    tes_obser = exc_sig$O,
+    tes_expect = exc_sig$E,
+    tes_ratio = exc_sig$OEratio,
+    tes_power = list(exc_sig$power),
+    tes_p = exc_sig$pval,
+    tes_theta = exc_sig$theta,
+    tes_thetalim = exc_sig$theta.lim
+  )
+  return(tes_df)
+}

### 2023-03-02 R/run_metaanalysis.R

@@ -1,0 +1,38 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param studies_clean
+#' @param type
+#' @return
+#' @author Taren Sanders
+#' @export
+run_metaanalysis <- function(studies_clean, type = "r") {
+  stopifnot(type %in% c("r", "z"))
+
+  if (type == "r") {
+    meta_out <- rma(
+      data = studies_clean,
+      measure = "COR",
+      ri = r_estimate,
+      ni = study_n,
+      slab = study_name
+    )
+  }
+
+  if (type == "z") {
+    meta_out <- rma(
+      data = studies_clean,
+      measure = "ZCOR",
+      ri = r_estimate,
+      ni = study_n,
+      slab = study_name
+    )
+  }
+
+  # Add the ID for later matching
+  meta_out$effect_size_id <- studies_clean$effect_size_id[1]
+
+  return(meta_out)
+}

### 2023-03-02 R/translate_tests.R

@@ -1,0 +1,46 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param stat
+#' @return
+#' @author Taren Sanders
+#' @export
+translate_tests <- function(stat) {
+  case_match(
+    str_trim(str_to_lower(stat)),
+    c(
+      "beta", "beta coefficient", "standardised regression coefficient"
+    ) ~ "b",
+    c(
+      "adjusted smd", "average effect size", "cohen d", "cohen's d",
+      "effect size (type unclear)", "g", "g+", "hedge's g", "hedges g",
+      "hedges' d", "hedge's d", "hedges' g", "median effect size",
+      "pooled mean effect size", "smd", "standard mean difference",
+      "standardised difference in the means", "standardized mean difference",
+      "standarised mean difference", "std mean difference",
+      "std. mean difference", "standardised mean difference"
+    ) ~ "d",
+    c("log odds ratio") ~ "lor",
+    c(
+      "mean", "mean difference", "pooled mean difference",
+      "pre-post difference mean", "unstandardized mean difference",
+      "weighted mean", "weighted mean difference"
+    ) ~ "md",
+    c(
+      "odd ratio", "odds ratio", "odds ratio iv",
+      "pooled fixed effect -odd ratio", "pooled odds ratio"
+    ) ~ "or",
+    c(
+      "attenuated correlation (uncorrected correlation)",
+      "corrected correlation", "correlation", "correlation coefficient",
+      "pearson's r", "weighted mean correlation coefficient",
+      "r = uncorrected sample-weighted mean effect size"
+    ) ~ "r",
+    c("rate ratio", "relative risk", "risk ratio") ~ "rr",
+    c("fisher z", "fisher's z", "z fischer", "z fisher") ~ "z",
+    c("mean tau-u", "tau-u") ~ NA,
+    .default = str_trim(str_to_lower(stat))
+  )
+}

### 2023-03-02 _targets.R

@@ -1,44 +1,259 @@
-library(targets)
-library(tarchetypes)
-library(here)
-
+# Set options
 options(tidyverse.quiet = TRUE, clustermq.scheduler = "multiprocess")
 
-packages <- c(
-  "base", "broom", "bib2df", "DiagrammeR", "distill", "DT", "esc",
-  "emojifont", "ggh4x", "googledrive", "ggplot2", "ggtext", "gt", "janitor",
-  "knitr", "kableExtra", "magick", "magrittr", "metafor", "papaja", "targets",
-  "tarchetypes", "tidyMB", "tidyverse", "scales", "xfun"
-)
-
-tar_option_set(
-  packages = packages,
-  debug = "yml_base",
-  workspace_on_error = TRUE
-)
-
-googledrive::drive_auth()
-googlesheets4::gs4_auth()
-source(here::here("R", "utils.R"))
-source(here::here("R", "data.R"))
-source(here::here("R", "tables.R"))
-source(here::here("R", "plots.R"))
-source(here::here("R", "supplementary.R"))
-source(here::here("R", "reports.R"))
+# Load required functions and packages
+lapply(list.files("./R", full.names = TRUE), source)
+load_packages()
 
 list(
-  # Fetch and analyse (data.R)
-  fetch_data,
-  clean_and_convert,
-  reanalyse,
-  # Make tables (tables.R)
-  make_tables,
-  # Make plots (plots.R)
-  make_prisma_figure,
-  make_forest_plots,
-  # Make sundry supplementary material (supplementary.R)
-  make_supps,
-  # Create reports (reports.R)
-  generate_bibliography,
-  create_reports
+  # Read data ---------------------------------------------------------------
+  tar_file_read(
+    effects_raw,
+    "data/Effects.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_file_read(
+    reviews_raw,
+    "data/Reviews.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_file_read(
+    studies_raw,
+    "data/Studies.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_file_read(
+    rob_raw,
+    "data/QualityAssessment.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_target(prisma_path,
+    here::here("data/covidence_prisma.txt"),
+    format = "file"
+  ),
+  # Set params --------------------------------------------------------------
+  tar_target(
+    age_codes,
+    list(
+      mixed = mixed_codes, adolescents = adolescents_codes,
[…]

### 2023-03-02 packages.R

@@ -1,0 +1,36 @@
+library(base)
+library(bib2df)
+library(broom)
+library(clustermq)
+library(correlation)
+library(DiagrammeR)
+library(distill)
+library(dplyr)
+library(DT)
+library(effectsize)
+library(emojifont)
+library(esc)
+library(forcats)
+library(future)
+library(ggplot2)
+library(ggh4x)
+library(ggtext)
+library(gt)
+library(kableExtra)
+library(knitr)
+library(magick)
+library(magrittr)
+library(markdown)
+library(Matrix)
+library(metadat)
+library(metafor)
+library(tinylabels)
+library(papaja)
+library(purrr)
+library(scales)
+library(stringr)
+library(tarchetypes)
+library(targets)
+library(tidyMB)
+library(tidyr)
+library(xfun)

### 2023-03-02 reports/manuscript.Rmd
Add revision letter and address R1 first comment

@@
 
+[Our results highlight the need for the field to more carefully consider if the term 'screen time' remains appropriate for providing advice to parents.
+Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
+Rather than suggesting parents limit 'screen time', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.]{#r1_1}
+
 Screen time research has a well-established measurement problem, which impacts the individual studies of this umbrella review.

### 2023-03-02 reports/revision_letter.Rmd
Add revision letter and address R1 first comment

---
title             : "Benefits and risks associated with children's and adolescents' interactions with electronic screens: An umbrella review"
authors           : "Taren Sanders on behalf of co-authors"
journal           : "Nature Human Behaviour"
manuscript        : "NATHUMBEHAV-22071805"
handling_editor   : "Charlotte Payne"

class             : "draft"

output            : revise::letter.pdf
---

Dear Dr `r rmarkdown::metadata$handling_editor`,

Thank you for considering our manuscript for publication at _`r rmarkdown::metadata$journal`_. We appreciate the feedback that you and the reviewers have provided. In the following itemised list we respond to each comment point-by-point.

```{r setup-chunk, include = FALSE}
targets::tar_load(manuscript)
manuscript <- revise::read_manuscript("reports/manuscript.Rmd", PDF = TRUE)
```

# Reviewer 1

```{asis}
As the authors note, “screen time” as a metric is highly criticized and problematic. This begs the question, though, of whether a wide-scale review of this sort, which retains a focus on screen time (although it also acknowledges other more nuanced metrics of exposure), is further perpetuating the issues seen by the broader field.
```

We agree with the reviewer that the term 'screen time' is problematic. 
Indeed, as our results show, the influence of screen time on children is a less a function of a physical screen, and more a function of the activity that the screen provides. 
But, we feel that a review such as this is needed in order to emphasise the diverse influence that screens can have. 
If the results are not collated into a single place, it is difficult to see how the field will begin to progress away from 'screen time' as a concept. 
We have included this in the *Implications for Future Research* section:

`r revise::get_revision("r1_1")`

```{asis}
The authors note that “no review has synthesized the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviours, and wellbeing.” The authors end up concluding that there are different magnitude and directions of associations for different outcomes and exposures (and, indeed, the mechanisms of these are highly different depending on the predictor-outcome combination), which makes me wonder whether casting such a wide net is helping the reader understand more or less about the research to date on technology use and child/adolescent outcomes? I would want to hear more justification in the manuscript itself on why they assert it is helpful to try and paint them with one broad brush?
```

```{asis}
Page 10 notes that the study “examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.” Did this take into consideration whether some meta-analyses of the same exposure-outcome pairs may have included mostly different studies (i.e., because they focused on different date ranges or some other inclusion criteria)?

```

```{asis}
Causal language- The present study sought to “provide a holistic perspective on the influence of screens on children’s lives across a broad range of outcomes,” but I am not convinced that the studies included in the meta-analyses are designed in ways that allow us to understand causal IMPACT at all. Many have criticized this literature for being largely self-reported (with flaws inherent to this method, which are reviewed in the present manuscript's discussion), observational, and cross-sectional, with very few rigorous experimental or well-controlled longitudinal designs that would enable researchers or the public to draw robust conclusions about the direction of associations. I fear that this comprehensive review, though rigorous, does not adequately attend to the fact that we do not usually know whether screens are causing helps or harms for youth, if different types of youth behaviors may be causing them to engage more with screens (e.g., sedentary youth may seek
out more screen time; depressed youth may turn more to social media as an avoidance strategy), or if indeed there are third variables driving observed associations. Although the review here does a great job of summarizing the direction and strengths of associations across studies, I fear that it does not attend to these important issues in terms of how one ought to interpret them.

```

```{asis}
The manuscript notes that the nature of the data allowed for few age-based conclusions- I fear that this is a substantial limitation that deserves more discussion. It seems difficult to characterize all children’s media use from age 0-18 in the same way, especially across such a wide range of developmental outcomes. A more nuanced treatment of developmental considerations would have been appreciated.

```

\clearpage

### 2023-03-02 reports/manuscript.Rmd
Address R1 comment 2

@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-Yet, no review has synthesised the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
+[Yet, no review has synthesised the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
+We aim to provide a summary on the current research into children's screen time.
+By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.]{#r1_2}
 

### 2023-03-02 reports/revision_letter.Rmd
Address R1 comment 2

@@
 
+\WorkInProgress
+\todo{Suggestions welcome here}
+
+Our goal with this review was to provide an overview of the field of screen time research.
+A summary of the field will, out of necessasity, be more broad that a typical systematic review.
+We beleive that there is significant value in providing a single overview to summarise the state of the field.
+We have added some additional information to the introduction on this point.
+
+`r revise::get_revision("r1_2")`
+
 ```{asis}
@@
 Many have criticized this literature for being largely self-reported (with flaws inherent to this method, which are reviewed in the present manuscript's discussion), observational, and cross-sectional, with very few rigorous experimental or well-controlled longitudinal designs that would enable researchers or the public to draw robust conclusions about the direction of associations.
-I fear that this comprehensive review, though rigorous, does not adequately attend to the fact that we do not usually know whether screens are causing helps or harms for youth, if different types of youth behaviors may be causing them to engage more with screens (e.g., sedentary youth may seek
-out more screen time; depressed youth may turn more to social media as an avoidance strategy), or if indeed there are third variables driving observed associations.
+I fear that this comprehensive review, though rigorous, does not adequately attend to the fact that we do not usually know whether screens are causing helps or harms for youth, if different types of youth behaviors may be causing them to engage more with screens (e.g., sedentary youth may seek out more screen time; depressed youth may turn more to social media as an avoidance strategy), or if indeed there are third variables driving observed associations.
 Although the review here does a great job of summarizing the direction and strengths of associations across studies, I fear that it does not attend to these important issues in terms of how one ought to interpret them.

### 2023-03-02 reports/revision_letter.Rmd
Address R1 comment 3

@@
 
+We intended to include the review which best captured the information on the exposure/outcome combination.
+The assumption was that the largest review would be the most recent, unless a more recent review had been targeted at a specific population (e.g., those with a disability). 
+Manual inspection of the reviews which did not contribute any effects suggests that this heuristic was successful.
+
+\todo{Does anyone know if we based this on a previous review? It's not cited in the registration.}
+
 ```{asis}
@@
 Although the review here does a great job of summarizing the direction and strengths of associations across studies, I fear that it does not attend to these important issues in terms of how one ought to interpret them.
-
 ```
@@
 A more nuanced treatment of developmental considerations would have been appreciated.
-
 ```

### 2023-03-02 reports/manuscript.Rmd
Add new authors

@@
       - Writing - Review & Editing
+  - name          : "Rebecca Pagano"
+    affiliation   : "12"
+    role:
+      - Writing - Review & Editing
+  - name          : "Jamie Sherson"
+    affiliation   : "12"
+    role:
+      - Writing - Review & Editing
+  - name          : "James Conigrave"
+    affiliation   : "1"
+    role:
+      - Writing - Review & Editing
   - name          : "Chris Lonsdale"
@@
     institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney"
+  - id            : "12"
+    institution   : "School of Education, Australian Catholic University"
 

### 2023-03-02 reports/manuscript.Rmd
Address R1 comment 4

@@
   These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
-  When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potentially harmful impacts on learning, literacy, body composition, and depression.
+  When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potential harm on learning, literacy, body composition, and depression.
   Like-wise, social media was consistently associated with risks to health, with no identified benefits.
@@
 For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+[Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
+Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.]{#r1_4}
 In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
@@
 Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved, parents' concerns, and the growing pervasiveness into society.
-Our findings showed that the impact of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
+Our findings showed that the influence of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
 The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.

### 2023-03-02 reports/revision_letter.Rmd
Address R1 comment 4

@@
 
+Yes, we agree that the body of evidence does not lend itself to strong causal conclusions.
+We note that we deliberately chose to avoid using strong causal language as much as possible, instead indicating that the evidence suggests associations with outcomes.
+We have reread the manuscript and removed any remaining causal language that we found.
+We have also added the following to the *Discussion* section:
+
+`r revise::get_revision("r1_4")`
+
+Note that we do use causal langauge when describing hypothesised mechanisms, and when describing guidelines.
+We feel that this is sensible --- guidelines are based on causal assumptions, and while our evidence does not always support them, we are refering to them in the context that they are made (i.e., to instruct parents).
+
 ```{asis}

### 2023-03-02 reports/revision_letter.Rmd
Address R1 comment 5

@@
 
+One of the benefits of the other reviewers' and editor's suggestion to update the search is that some of this limitation has been addressed in more recent literature.
+Newer papers were more likely to provide moderation by age group, or new reviews targeting specific age groups were now available.
+Unfortunately, many of these still failed to meet our criteria for statistical certainty.
+Inspecting the results in the supplementary material still reveal fewer differences by age group than may be expected.
+In some cases this is because there is still only an effect for a single age group, as many reviews target behaviours or outcomes which are more common in one age group (e.g., sexting in adolescents, or developmental outcome in young children).
+For the effects where there were multiple age groups, differences tended to be small (e.g., body composition).
+
 \clearpage

### 2023-03-02 reports/manuscript.Rmd
Work on some of the comments

@@
   While some forms of screen time have consistently been associated with harm, others have been associated with gains, making it difficult to weigh the risks and benefits of use.
-  In this umbrella review, we systematically collate and synthesise meta-analyses examining the effects of screen use on children and youth.
-  We converted results onto a common metric to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
-  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations.
+  In this umbrella review, we systematically collate and examined meta-analyses examining the effects of screen use on children and youth.
+  We converted results onto a common metric (Pearson's r) to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
+  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations from `r targets::tar_read(manuscript_info)$prisma$unique_reviews`.
   These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
@@
 Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
-Hampering efforts to make an informed decision is the lack of comprehensive evidence.
+The lack of comprehensive evidence hampers efforts to make an informed decision.
 As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-[Yet, no review has synthesised the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
-We aim to provide a summary on the current research into children's screen time.
+[Yet, no review has examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
 By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.]{#r1_2}
@@
 In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
-This review synthesises evidence on any plausible outcome of electronic media exposure.
+This review synthesises evidence on any outcome of electronic media exposure.
 Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children’s lives.
@@
 
-### Data collection process
+### Data items
 
 From each included meta-analysis, two researchers independently extracted data into a custom-designed database.
-
-### Data items
-
-From each meta-analysis we extracted the following items: First author, year of publication, study design restrictions (e.g., cross-sectional, observational, experimental), region restrictions (e.g., specific countries), earliest and latest study publication dates, sample age (mean), lowest and highest mean age reported,  outcomes reported, and exposures reported.
+We extracted the following items: First author, year of publication, study design restrictions (e.g., cross-sectional, observational, experimental), region restrictions (e.g., specific countries), earliest and latest study publication dates, sample age (mean), lowest and highest mean age reported,  outcomes reported, and exposures reported.
 
@@
 
-Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
-Where possible, they also extracted effect sizes from primary studies included in each meta-analysis.
+<span id ="r2_17">Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
+We excluded effect sizes which were reported as relative risk ratios, as meta-analyses did not contain sufficient information to meaningfully convert.
+We also excluded effect size estimates when the authors did not provide a sample size.
+Where possible, we also extracted effect sizes from the primary studies included in each meta-analysis.
+
 To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bonettTransformingOddsRatios2007;@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
-We excluded relative risk ratios from this conversion because meta-analyses did not contain sufficient information to meaningfully convert.
-Effect sizes on the original metric are provided in Supplementary File 2.
+Effect sizes on the original metric are provided in Supplementary File 2.</span>
 
@@
 
-We excluded effect size estimates when the authors did not provide a sample size.
 We descriptively present the remaining meta-analytic effect sizes.
@@
 We used thresholds of $P < .05$ for weak evidence and $P < 10^{-3}$ for strong evidence.
-An effect that was neither significant at $P < .05$ or $10^{-3}$ that also passed the criteria for statistical credibility was taken to indicate no association of interest.
+An effect with statistical credibility but with $P > .05$ was taken to indicate no association of interest.
 
@@
 Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
-After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.
+<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
 These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.

### 2023-03-02 reports/revision_letter.Rmd
Work on some of the comments

@@
 ```{r setup-chunk, include = FALSE}
-targets::tar_load(manuscript)
-manuscript <- revise::read_manuscript("reports/manuscript.Rmd", PDF = TRUE)
+targets::tar_load(c(manuscript, manuscript_md))
+manuscript <- revise::read_manuscript("reports/manuscript.md", PDF = TRUE)
 ```
+
+\newpage
+
+# Editor Comments
+```{asis}
+Reviewer 3 points out that your last search date is May 2020.
+We agree that this means the review is not as timely as it could be and ask that you update your search to September 2022, and redo your analyses with all newly included studies.
+```
+
+\WorkInProgress
+
+```{asis}
+Reviewer 2's concerns about the appropriateness of your technical approach (notably: subjective characteristics of review selection, your statistical approach, and your choice to harmonize metrics of effect sizes) are significant and we ask that you prioritise addressing these issues when redoing your analyses.
+```
+
+\WorkInProgress
+
+```{asis}
+Both reviewers 2 and 3 are concerned about the lack of information on risk of bias assessment and population characteristics.
+Please ensure this information is clearly available and add data on both to Table 1.
+```
+
+\WorkInProgress
+
+```{asis}
+Reviewer 1 highlights the inappropriateness of causal language given that the majority of included studies speak to association, not causation.
+Please remove all inappropriate use of causal language accordingly.
+```
+
+Please see response to Reviewer 1, \Comment{causal_lang}.
+
+\newpage
 
@@
 ```
-
 \WorkInProgress
@@
 Page 10 notes that the study “examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.” Did this take into consideration whether some meta-analyses of the same exposure-outcome pairs may have included mostly different studies (i.e., because they focused on different date ranges or some other inclusion criteria)?
-
 ```
@@
 
-```{asis}
-Causal language- The present study sought to “provide a holistic perspective on the influence of screens on children’s lives across a broad range of outcomes,” but I am not convinced that the studies included in the meta-analyses are designed in ways that allow us to understand causal IMPACT at all.
+```{asis causal_lang}
+Causal language- The present study sought to “provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes,” but I am not convinced that the studies included in the meta-analyses are designed in ways that allow us to understand causal IMPACT at all.
 Many have criticized this literature for being largely self-reported (with flaws inherent to this method, which are reviewed in the present manuscript's discussion), observational, and cross-sectional, with very few rigorous experimental or well-controlled longitudinal designs that would enable researchers or the public to draw robust conclusions about the direction of associations.
@@
 The manuscript notes that the nature of the data allowed for few age-based conclusions- I fear that this is a substantial limitation that deserves more discussion.
-It seems difficult to characterize all children’s media use from age 0-18 in the same way, especially across such a wide range of developmental outcomes.
+It seems difficult to characterize all children's media use from age 0-18 in the same way, especially across such a wide range of developmental outcomes.
 A more nuanced treatment of developmental considerations would have been appreciated.
@@
 
+\newpage
+# Reviewer 2
+
+```{asis}
+I appreciate the opportunity to review this manuscript focusing on the impact of screen use on child well-being.
+This umbrella review organized findings from meta-analyses by child outcomes and screen types, converted pooled data into Pearson correlations as a unified estimate to facilitate cross-study comparisons, and reached a conclusion that general screen use and social media were associated with harmful impacts on child learning, literacy, body composition, and depression, and the potential risks could be mitigated by the content and context of screen use.
+This conclusion is somewhat similar to that of another umbrella review conducted by Stiglic and Viner in 2019 (PMID: 30606703).
+However, the current one made advances on including studies examining educational screen time and social media and harmonizing data from meta-analyses.
+```
+
+We are grateful to the reviewer for seeing the value in our review.
+
+```{asis}
+Abstract:
+
+Page 3 Line 38: In my opinion, “examined” is a better than “synthesized”. Because the data from meta-analyses were not pooled.
+
+Page 3 Line 39: I suggest replacing “common metric” with “Pearson's r”.
+
+Page 3 line 41-42: “extracted 165 unique exposure/outcome combinations from 66 studies.”
+```
+
+We have made all of these changes.
+
+```{asis}
+Summary:
+Page 4 line 59: the lack of comprehensive evidence hampers efforts to make an informed decision.
+```
+
+We have made this change.
+
+```{asis}
+Introduction:
+Page 5 line 84-86: please further justify how a review study would make the limited evidence base less lacking or generate new findings.
+```
+
+The quote from the *Lancet* editorial is that the understanding is lacking, rather than the evidence.
+Our understanding is lacking partly because benefits of screen time (as seen in some educational literature) and reviewed seperately from harms.
+Our review aims to address this.
+See additional context in the *Introduction*:
+
+`r revise::get_revision("r1_2")`
+
+```{asis}
+Page 5 line 87-90: I suggest improving the logic flow and citing more recent studies (2016 or newer) to highlight the potentially new additions of the current review. 
+```
+
+\WorkInProgress
+
+```{asis}
+Page 5 line 91-94: Please provide a more in-depth explanation on the advantages of a review study to include a broad spectrum of health outcomes. 
+```
+
+\WorkInProgress
+
+```{asis}
+Page 6 line 96-104: these guidelines provide age-staged recommendations and mainly target on recreational screen time.
+New evidence to support or reject these recommendations are important breakthroughs.
+So how does the current review contribute to the refinement of these guidelines?
+It could be proposed here to strengthen the justification of this study, and also need to be addressed in the discussion section.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 6 line 104-107: this is not a direct contrast.
+Longer screen time is needed to pose mental health risks, but short screen time can lead to other health issues.
+While guidelines are built on a comprehensive examination of health outcomes.
+Thus, I consider here as a weak argument/transition.
+The organization of the introduction section need to be improved.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 6 line 117-119: Stiglic and Viner's umbrella review summarized evidence across a broad range of outcome domains. Please further justify the current study in addition to theirs.
+```
+
+\WorkInProgress
+
+```{asis outcomes}
+Page 7 line 122: please define “any plausible outcomes” to make the scope more scientifically sound and robust.
+In addition, the result section included findings of behavioral outcomes (physical activity and sleep duration) which I was not considered as academic, health, and social-psychological outcomes.
+Thus, it is better to be clear about the types of outcomes at the beginning of the manuscript.
+```
+
+We did not *a-priori* choose which outcomes would be included.
+Instead, we chose to summarise the literature on for any meta-analysis where screen exposure was the independent variable.
+We have removed the word "plausible", as we agree that makes the sentence less clear and this phrasing is more aligned with the eligibility critiera.
+Our intention in the introduction is not to preempt the results, which means we do not outline the outcomes found in the introduction.
+
+```{asis}
+Page 7 line 123: the authors stated the application of “a broad approach”, while highlighted the importance of nuanced findings and guidelines.
+The introduction section would be improved by balancing these two important aspects.
+```
+
+\WorkInProgress
+
+```{asis}
+Methods:
+Page 8 line 146-148: the effects of screen use on youth with a clinical condition are likely be different from those of the general population.
+If this review included any, the population characteristics should be specified in the result section or in the figures.
+```
+
+\WorkInProgress
+\todo{Will add to table 1}
+
+```{asis}
+Page 8 line 152: please define outcomes.
+```
+
+Per /comment{outcomes} above, we did not pre-specify outcomes and feel it would be inappropriate to revise our inclusion criteria.
+
+```{asis}
+Page 10 line 181-187: these two sections could be combined. 
+```
+
+We agree and have made this change.
+
+```{asis}
+Page 10 line 190: Table 1 does not contain RoB info. 
+```
+
+\WorkInProgress
+\todo{Will add to table 1}
+
+```{asis}
+Page 10 line 195-196: the description of data conversion is not transparent.
+Pearson's r assumes linear relationship.
+But associations between screen use and well-being are often non-monotonic (Twenge 2020, PMID: 32303719).
+In addition, meta-analyses reporting odd ratios defined exposure outcomes in various ways.
+For example, Zhang et.
+al.
+2016 compared the obesity risk by the lowest and highest TV viewing time, whereas Poorolajal et.
+al.
+2020 compared watching TV > 1-2h/d with an unclear group.
+Can the harmonization of OR into R guarantee that the two values are comparable?
+Therefore, further justification is needed.
+```
+
+\WorkInProgress
+\todo{For linear - yeah, but this is always a problem in meta-analyses.
+Need to think about ORs.}
+
+```{asis}
+Page 10 Line 201-206: The inclusion/exclusion criteria are here and there (page 10 line 197-198, page 11 line 221-222, etc.).
+Please provide specific and full criteria of effect size inclusion/exclusion in one section.
+
+Page 11 line 211 and 223-226: same issue as above. 
+```
+
+We agree this is could be confusing to the reader.
+The previous sections outlined the inclusion criteria for including a *review*, whereas these sections focus on reasons for excluding an *effect size* from the review.
+We did not require all effect sizes within a review to be eligible or usable for the review to still be included.
+
+`r revise::get_revision("r2_17")`
+
+```{asis}
+Page 11 line 222: Egger's test is not suitable for evaluating publication bias of ORs.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 11 line 229-231: An effect with statistical credibility but showing P < .05 indicate no association of interest. 
+```
+
+We have made this change.
+
+```{asis}
+Page 12 line 232-233: “include systematic reviews without meta-analyses” conflicts “alongside the main meta-analytic findings”.
+```
+
+We are not clear on what the reviewer means here.
+Per the quoted sentence, we intended to include all systematic reviews (not just meta-analyses), but the volume of meta-analyses was such that we felt this was unneeded.
+This was a change from our protocol, and thus reported as such.
+We are happy to revise this section if the reviewer has a suggestion.
+
+```{asis}
+Page 12 line 235: Harmonizing the metric of effect size does not guarantee the comparability of the strength of associations.
+Please fully justify the current practice with a thorough analysis of the pros and cons.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 12 line 238-243: A significant P was not a criterion to consider studies as credible in other reviews. Not sure why it is a reason for altering the original plan. 
+```
+
+\WorkInProgress
+\todo{We cite a paper in the protocol on this.}
+
+```{asis}
+Results
+Page 12 line 247-248: please add a description that 66 studies contributed unique effect sizes to the current review. 
+```
+
+This information is available here (not that the updated search increased the number of reviews):
+
+`r revise::get_revision("r2_23")`
+
+```{asis}
+Figure 1: 1) what's the difference between references and studies in this figure?
+For those seven entries categorized as “non-studies”, what are they?
+2) “other(explain)” is not self-explanatory.
+3) what's the difference between non-target samples and wrong population?
+In addition, the total number in this box is 1848.
+4) “larger study available”: I'm not confident about using sample size as a sole criterium of selecting studies.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 12 line 249-256: 1) I suggest adding a summary table (counts and percentages) of the basic characteristics of the included references/studies which including year range of publication, types of study designs, sample age categories, outcome types, and exposure types, quality assessment scores, etc.
+2) The current description is quite confusing to me, for example, what does “cases” mean?
+How did you calculate up 197 cases?
+What appeared twice or more times, the combination of exposure/outcome by age group?
+3) table 1: I suggest adding data of the original effect sizes.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 26 line 260-268, Information on quality assessment was provided in a supplementary file, not table 1. Please revise. 
+```
+
+\WorkInProgress
+
+```{asis}
+Page 27 line 291: Please provide pre-determined criteria of the magnitude of effects with supporting references. 
+```
+
+\WorkInProgress
+
+```{asis}
+Page 28 line 299-304: 119-31-30-43 = 15, not 17. 
+Three methodological issues needs to be clarified or justified. 
+1. The selection of reviews to generate “unique” comparisons appeared to be subjective/unclear.
+2. The statistical approach extensively reduced the evidence pool. For example, 46 unique effects on education outcomes was reduced to 12 and 119 unique effects on health outcomes was reduced to 17. 
+3.
+Harmonizing the metrics of effect sizes into r may be invalid and placing the converted effect sizes in forest plot is somewhat deceiving.
+Because across-study comparisons are not guaranteed due to variations in study design, setups of exposure and outcome variables.
+```
+
+\WorkInProgress
+
+```{asis}
+Discussion
+Page 31 line 362-368: I think these are important nuances.
+If the analytical plan was subjective altered in order to generate more consistent associations.
+Then, the practice can introduce selection bias.
+I suggest adding qualitative syntheses of those studies removed by not meeting the “statistical credibility” criteria.
+```
+
+\WorkInProgress
+
+```{asis}
+Page 31 line 380-383: both guidelines mentioned recreational sedentary screen time. It is not in all instances. 
+```
+
+\WorkInProgress
+
+```{asis}
+Page 32 line 389-391: I assume that the data of primary studies was retrieved by the team whenever possible.
+But “failed to provide study-level data” make me wonder did not those reviews provide reference information of the included studies?
+```
+
+\WorkInProgress
+
+```{asis}
+Page 32 line 395: from my point of view, the evidence strength generated from data from ten loosely designed cross-sectional studies is weaker than 5 rigorously designed intervention studies or longitudinal studies.
+I wonder how the quality and quantity of studies were balanced in the current study.
+```
+
+\WorkInProgress
+
+\newpage
+
+## Reviewer 3
+
+```{asis}
+OVERALL IMPRESSION
+
+The article by Sanders et al is an umbrella review of the literature on benefits and risks associated with screen interaction in children and adolescents.
+This is a noteworthy and hotly debated topic, with significant social and political implications.
+Therefore, the current study can certainly inform and impact policy and society in general.
+
+Overall, the methodology is sound and follows current guidelines on how to carry out systematic reviews and meta-analysis.
+Moreover, an umbrella review is an apt choice to summarize the wide and heterogeneous literature on the topic.
+It is the first of its kind, and therefore represents an significant evidence-based advance in summarizing a complex topic.
+All in all, there are not any unexpected or highly controversial results but the final document is a good quality common-sense summary of the literature that should probably be read by anybody with extreme positions in the topic.
+
+The umbrella review was registered in PROSPERO and the (rather small) deviations from the protocol are adequately reasoned by the authors.
+Indeed, I would like to praise authors for centering their efforts in interpreting mainly “credible” effects that are either significant or non-significant.
+```
+
+\WorkInProgress
+
+```{asis}
+MAJOR COMMENTS
+
+My biggest issue with the article as it stands is in regards to the date of the last search.
+This was carried out in May 2020, so two years and a half have already passed, so the review is quite outdated.
+Moreover, these two years and half with the Covid pandemic have likely changed how many children interact with technologies and screens.
+I suspect that many primary articles have been published on the issue at hand, and, quite likely some meta-analyses too.
+I would recommend the authors to update their search and results, even acknowledging that that means quite a lot of work.
+That being said, this update might yield some meta-analyses that include primary articles carried out during the pandemic, when the positive and negative outcomes in relation to screen-time might be correlated with factors that differ greatly from previous years, and this should probably be mentioned in the discussion.
+```
+
+\WorkInProgress
+
+```{asis}
+Another main issue that I have with the article is that I feel that a better description of supplementary materials is needed.
+I have not been able to find a consistent description of the materials that can be found in them.
+Moreover, in the case of the CSV documents a variable dictionary would be most welcome.
+Somewhat relatedly, in line 190 (and 260) it says “see table 1”, so I was hoping to see some summary on the risk of bias evaluation in the table.
+I have not been able to find it there.
+In the Prisma checklist item 18 it says that risk of bias assessments can be found in OSF, but no mention of OSF is provided in the main text.
+After going through all the supplementary materials, I have been able to find the ratings in a file.
+My reading from all this is that the article has gone through several iterations and some systematizing and cleaning should be carried out to present in a more clear way the supplementary materials (an index of contents with a short description,
+table and figure captions, variable dictionary…)
+```
+
+\WorkInProgress
+
+```{asis}
+MINOR COMMENTS
+
+The selection of the “the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses” as opposed to the more standardized AMSTAR-2 is slighthly suprising (even if it does not likely have any real consequences in the final product).
+```
+
+\WorkInProgress
+
+```{asis}
+The paragraph on age within the eligibility criteria is unclear to me: “(i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).”: is it a mean age below eighteen (hence, potentially including some adults), or is it the oldest participant being under 18 (more clear-cut, but on the other hand limiting the number of outcomes)?
+```
+
+\WorkInProgress
+
+```{asis}
+“In this review we adopted a population-level perspective, meaning that we examined electronic media exposure that occurs during typical daily living activities (e.g., home, school-based electronic media exposure).”: I do not think this paragraph is fully clear.
+```
+
+\WorkInProgress
+
+```{asis}
+“Outcomes: We included all reported outcomes.”: it might be worth adding “on benefits and risks”
+Lines 200-204: it is unclear to me whether this refers to effects found within the same meta-analysis, across meta-analysis on the same outcome, or both.
+Some additional clarification would be welcome.
+```
+
+\WorkInProgress
+
+```{asis}
+While PRISMA is named along the review, it is not specifically indicated that it was followed. I would recommend that authors explicitely say it. 
+```
+
+\WorkInProgress
+
+```{asis}
+Education outcomes: text indicates 12 effects from 8 reviews, but figure 2 only shows 11 effects from 7 reviews.
+A similar issue happens with Helath related outcomes: text indicates 17 effects, but I only see 15 in figure 3.
+What is going on?
+```
+
+\WorkInProgress
+
+```{asis}
+“For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.” This seems a strange choice, as it mixes very different populations.
+At the very least, the type of population should be indicated in table 1, and the impact of this discussed in the discussion.
+```
+
+\WorkInProgress
+
 \clearpage

### 2023-03-06 reports/manuscript.Rmd
Address additional comments

@@
   We converted results onto a common metric (Pearson's r) to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
-  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations from `r targets::tar_read(manuscript_info)$prisma$unique_reviews`.
+  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
   These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-[Yet, no review has examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
-By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.]{#r1_2}
+<span id = "r1_2">Yet, no review has examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
+By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span>
 
@@
 We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051).
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines [@pagePRISMA2020Statement2020].
 
@@
 To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
-We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).
-We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).
+<span id = "r3_5">We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was < 18 years).
+A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
+We excluded meta-analyses that only contained evidence gathered from adults (age >18 years). </span>
 
@@
 We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content (e.g., television programs, movies, games), homework, and communication (e.g., video chat).
-In this review we adopted a population-level perspective, meaning that we examined electronic media exposure that occurs during typical daily living activities (e.g., home, school-based electronic media exposure).
-Consistent with this population-level approach, we excluded technology-based treatments for clinical conditions.
+<span id = "r3_6">
+In this review we focused on electronic media exposure that would be considered typical for children and youth.
+That is, exposure that may occur in the home setting, or during schooling.
+Consistent with this approach, we excluded technology-based treatments for clinical conditions. 
+</span>
 However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning) for children and youth with a clinical condition.
@@
 However, a meta-analysis of interventions designed to *treat* clinical depression delivered by a mobile phone app would be excluded.
-
-*Outcomes*: We included all reported outcomes.
+<span id = "r3_7">
+*Outcomes*: We included all reported outcomes on benefits and risks.
+</span>
 
@@
 We searched records contained in the following databases: Pubmed, MEDLINE, CINAHL, PsycINFO, SPORTDiscus, Education Source, Embase, Cochrane Library, Scopus, Web of Science, ProQuest Social Science Premium Collection, and ERIC.
-We conducted an initial search on August 17, 2018 and refreshed the search on May 13, 2020.
+<span id = "r3_2">We conducted an initial search on August 17, 2018 and refreshed the search on September 27, 2022.</span>
 We searched reference lists of included papers in order to identify additional eligible meta-analyses.
@@
 
-After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.
+<span id = "r3_8">After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
 In instances where effect sizes from the same combination of exposure and outcome were drawn from different populations (e.g., children vs adolescents) we retained both estimates in our dataset.
+</span>
 
@@
 To test for publication bias, we conducted Egger's test [@eggerBiasMetaanalysisDetected1997] when the number of studies within the review was ten or more [@pageChapter13Assessing2021], and conducted a test of excess significance [@ioannidisExploratoryTestExcess2007].
-We contacted authors who did not provide primary study data in their published article.
-Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.
+<span id = "r2_32">We contacted authors who did not provide primary study data in their published article.
+Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.</span>
 
@@
 
-[Our results highlight the need for the field to more carefully consider if the term 'screen time' remains appropriate for providing advice to parents.
+<span id = "r1_1">Our results highlight the need for the field to more carefully consider if the term 'screen time' remains appropriate for providing advice to parents.
 Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
-Rather than suggesting parents limit 'screen time', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.]{#r1_1}
+Rather than suggesting parents limit 'screen time', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.</span>
 
@@
 For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
-[Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
-Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.]{#r1_4}
-In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
-While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
+<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
+Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
+<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
+While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>
 

### 2023-03-06 reports/revision_letter.Rmd
Address additional comments

@@
 targets::tar_load(c(manuscript, manuscript_md))
-manuscript <- revise::read_manuscript("reports/manuscript.md", PDF = TRUE)
+options(revise_errors = FALSE)
+manuscript <- suppressWarnings(
+  revise::read_manuscript("reports/manuscript.md", PDF = TRUE)
+)
+get_revision <- function(id, ...) {
+  suppressWarnings(revise::get_revision(id, ...))
+}
 ```
@@
 # Editor Comments
-```{asis}
+```{asis e1}
 Reviewer 3 points out that your last search date is May 2020.
@@
 
-\WorkInProgress
+We have updated the search to September 2022.
+We found a substantial amount of new literature had been published since our inital search, with an additional 108 meta-analyses included in the review.
+While many of these were updates to existing reviews, we also included 110 new exposure/outcome combinations (or existing combinations for new age groups) that were not found in the original search.
+We think that this increase in research demonstrates the level of interest in this area.
 
-```{asis}
+We'd also like to thank the editor and reviewers for their patience while we screened and extracted data from these additional reviews.
+
+```{asis e2}
 Reviewer 2's concerns about the appropriateness of your technical approach (notably: subjective characteristics of review selection, your statistical approach, and your choice to harmonize metrics of effect sizes) are significant and we ask that you prioritise addressing these issues when redoing your analyses.
@@
 
-```{asis}
+```{asis e3}
 Both reviewers 2 and 3 are concerned about the lack of information on risk of bias assessment and population characteristics.
@@
 
-```{asis}
+```{asis e4}
 Reviewer 1 highlights the inappropriateness of causal language given that the majority of included studies speak to association, not causation.
@@
 
-Please see response to Reviewer 1, \Comment{causal_lang}.
+Please see response to Reviewer 1, \Comment{r1_4}.
 
@@
 
-```{asis}
+```{asis r1_1}
 As the authors note, “screen time” as a metric is highly criticized and problematic.
@@
 
-`r revise::get_revision("r1_1")`
+`r get_revision("r1_1")`
 
-```{asis}
+```{asis r1_2}
 The authors note that “no review has synthesized the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviours, and wellbeing.” The authors end up concluding that there are different magnitude and directions of associations for different outcomes and exposures (and, indeed, the mechanisms of these are highly different depending on the predictor-outcome combination), which makes me wonder whether casting such a wide net is helping the reader understand more or less about the research to date on technology use and child/adolescent outcomes?
@@
 
-`r revise::get_revision("r1_2")`
+`r get_revision("r1_2")`
 
-```{asis}
+```{asis r1_3}
 Page 10 notes that the study “examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.” Did this take into consideration whether some meta-analyses of the same exposure-outcome pairs may have included mostly different studies (i.e., because they focused on different date ranges or some other inclusion criteria)?
@@
 
-```{asis causal_lang}
+```{asis r1_4}
 Causal language- The present study sought to “provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes,” but I am not convinced that the studies included in the meta-analyses are designed in ways that allow us to understand causal IMPACT at all.
@@
 
-`r revise::get_revision("r1_4")`
+`r get_revision("r1_4")`
 
@@
 
-```{asis}
+```{asis r1_5}
 The manuscript notes that the nature of the data allowed for few age-based conclusions- I fear that this is a substantial limitation that deserves more discussion.
@@
 
-```{asis}
+```{asis r2_1}
 I appreciate the opportunity to review this manuscript focusing on the impact of screen use on child well-being.
@@
 
-```{asis}
+```{asis r2_2}
 Abstract:
@@
 
-```{asis}
+```{asis r2_3}
 Summary:
@@
 
-```{asis}
+```{asis r2_4}
 Introduction:
@@
 
-`r revise::get_revision("r1_2")`
+`r get_revision("r1_2")`
 
-```{asis}
+```{asis r2_5}
 Page 5 line 87-90: I suggest improving the logic flow and citing more recent studies (2016 or newer) to highlight the potentially new additions of the current review. 
@@
 
-```{asis}
+```{asis r2_6}
 Page 5 line 91-94: Please provide a more in-depth explanation on the advantages of a review study to include a broad spectrum of health outcomes. 
@@
 
-```{asis}
+```{asis r2_7}
 Page 6 line 96-104: these guidelines provide age-staged recommendations and mainly target on recreational screen time.
@@
 
-```{asis}
+```{asis r2_8}
 Page 6 line 104-107: this is not a direct contrast.
@@
 
-```{asis}
+```{asis r2_9}
 Page 6 line 117-119: Stiglic and Viner's umbrella review summarized evidence across a broad range of outcome domains. Please further justify the current study in addition to theirs.
@@
 
-```{asis outcomes}
+```{asis r2_10}
 Page 7 line 122: please define “any plausible outcomes” to make the scope more scientifically sound and robust.
@@
 Instead, we chose to summarise the literature on for any meta-analysis where screen exposure was the independent variable.
-We have removed the word "plausible", as we agree that makes the sentence less clear and this phrasing is more aligned with the eligibility critiera.
+We have removed the word "plausible", as we agree that makes the sentence unclear and the revised phrasing is more aligned with the eligibility critiera.
 Our intention in the introduction is not to preempt the results, which means we do not outline the outcomes found in the introduction.
 
-```{asis}
+```{asis r2_11}
 Page 7 line 123: the authors stated the application of “a broad approach”, while highlighted the importance of nuanced findings and guidelines.
@@
 
-```{asis}
+```{asis r2_12}
 Methods:
@@
 
-```{asis}
+```{asis r2_13}
 Page 8 line 152: please define outcomes.
@@
 
-Per /comment{outcomes} above, we did not pre-specify outcomes and feel it would be inappropriate to revise our inclusion criteria.
+Per \comment{r2_10} above, we did not pre-specify outcomes and feel it would be inappropriate to revise our inclusion criteria.
 
-```{asis}
+```{asis r2_14}
 Page 10 line 181-187: these two sections could be combined. 
@@
 
-```{asis}
+```{asis r2_15}
 Page 10 line 190: Table 1 does not contain RoB info. 
@@
 
-```{asis}
+```{asis r2_16}
 Page 10 line 195-196: the description of data conversion is not transparent.
@@
 
-```{asis}
+```{asis r2_17}
 Page 10 Line 201-206: The inclusion/exclusion criteria are here and there (page 10 line 197-198, page 11 line 221-222, etc.).
@@
 
-`r revise::get_revision("r2_17")`
+`r get_revision("r2_17")`
 
-```{asis}
+```{asis r2_18}
 Page 11 line 222: Egger's test is not suitable for evaluating publication bias of ORs.
@@
 
-```{asis}
+```{asis r2_19}
 Page 11 line 229-231: An effect with statistical credibility but showing P < .05 indicate no association of interest. 
@@
 
-```{asis}
+```{asis r2_20}
 Page 12 line 232-233: “include systematic reviews without meta-analyses” conflicts “alongside the main meta-analytic findings”.
@@
 
-```{asis}
+```{asis r2_21}
 Page 12 line 235: Harmonizing the metric of effect size does not guarantee the comparability of the strength of associations.
@@
 
-```{asis}
+```{asis r2_22}
 Page 12 line 238-243: A significant P was not a criterion to consider studies as credible in other reviews. Not sure why it is a reason for altering the original plan. 
@@
 
-```{asis}
+```{asis r2_23}
 Results
@@
 
-This information is available here (not that the updated search increased the number of reviews):
+This information is available here (note that the updated search increased the number of reviews):
 
-`r revise::get_revision("r2_23")`
+`r get_revision("r2_23")`
 
-```{asis}
+```{asis r2_24}
 Figure 1: 1) what's the difference between references and studies in this figure?
@@
 
-```{asis}
+```{asis r2_25}
 Page 12 line 249-256: 1) I suggest adding a summary table (counts and percentages) of the basic characteristics of the included references/studies which including year range of publication, types of study designs, sample age categories, outcome types, and exposure types, quality assessment scores, etc.
@@
 
-```{asis}
+```{asis r2_26}
 Page 26 line 260-268, Information on quality assessment was provided in a supplementary file, not table 1. Please revise. 
@@
 
-```{asis}
+```{asis r2_27}
 Page 27 line 291: Please provide pre-determined criteria of the magnitude of effects with supporting references. 
@@
 
-```{asis}
+```{asis r2_28}
 Page 28 line 299-304: 119-31-30-43 = 15, not 17. 
+```
+
+Thank you for the attention to detail.
+The reported numbers are now correct (note that they are different due to the updated search).
+
+```{asis r2_29}
 Three methodological issues needs to be clarified or justified. 
@@
 
-```{asis}
+1. (Not sure what to address)
+2. xyz
+3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
+We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric, it would not be possible to make any comparisons between the effect sizes.
+
+\todo{Add more to discussion about interpreting sizes carefully.}
+
+```{asis r2_30}
 Discussion
@@
 
-```{asis}
+```{asis r2_31}
 Page 31 line 380-383: both guidelines mentioned recreational sedentary screen time. It is not in all instances. 
@@
 
-```{asis}
+```{asis r2_32}
 Page 32 line 389-391: I assume that the data of primary studies was retrieved by the team whenever possible.
@@
 
-\WorkInProgress
+There were two ways that the data from the primary studies could be included in our review:
+* The data were provided in the paper (i.e., in forest plots, tables, or supplementary files); or
+* The authors provided the data when contacted.
 
-```{asis}
+`r get_revision("r2_32")`
+
+We did not retrive data from the primary studies when the data were not provided in the paper or by the author.
+We did originally consider it, but the scope was such that it was not feasible.
+
+```{asis r2_33}
 Page 32 line 395: from my point of view, the evidence strength generated from data from ten loosely designed cross-sectional studies is weaker than 5 rigorously designed intervention studies or longitudinal studies.
@@
 \WorkInProgress
+todo{include study design in the forest plots?}
 
@@
 
-```{asis}
+```{asis r3_1}
 OVERALL IMPRESSION
@@
 
-\WorkInProgress
+Thank you for the kind comments.
+We are glad that you saw the value in our review.
 
-```{asis}
+```{asis r3_2}
 MAJOR COMMENTS
@@
 
-\WorkInProgress
+We agree that our search was out of date.
+We reran the search in September 2022, which revealed a substantial amount of new literature.
 
-```{asis}
+`r get_revision("r3_2")`
+
+Our updated search did reveal some meta-analyses on screen use during or post-pandemic, but these tended to be small and it would be difficult to draw too many conclusions from these reviews.
+The historic nature of reviews is an issue we acknowledge in our limitations:
+
+`r get_revision("r3_2_2")`
+
+```{asis r3_3}
 Another main issue that I have with the article is that I feel that a better description of supplementary materials is needed.
@@
 After going through all the supplementary materials, I have been able to find the ratings in a file.
-My reading from all this is that the article has gone through several iterations and some systematizing and cleaning should be carried out to present in a more clear way the supplementary materials (an index of contents with a short description,
-table and figure captions, variable dictionary…)
+My reading from all this is that the article has gone through several iterations and some systematizing and cleaning should be carried out to present in a more clear way the supplementary materials (an index of contents with a short description, table and figure captions, variable dictionary…)
 ```
@@
 
-```{asis}
+```{asis r3_4}
 MINOR COMMENTS
@@
 
-\WorkInProgress
+Our rationale for choosing the NHLBI was that we felt it could be applied equally to all fields than AMSTAR-2.
+Reporting standards differ by discipline, and several of the items in AMSTAR-2 are typically only reported in medical fields.
+While these should maybe be reported in all fields, we felt that the NHLBI was a more appropriate standard for our review.
 
-```{asis}
+```{asis r3_5}
 The paragraph on age within the eligibility criteria is unclear to me: “(i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).”: is it a mean age below eighteen (hence, potentially including some adults), or is it the oldest participant being under 18 (more clear-cut, but on the other hand limiting the number of outcomes)?
@@
 
-\WorkInProgress
+It is the former, which we have now clarified here:
 
-```{asis}
+`r get_revision("r3_5")`
+
+We chose this as most reviews provided mean ages for individual studies but not age ranges, which meant we would not have been able to consistently apply the critiera.
+
+```{asis r3_6}
 “In this review we adopted a population-level perspective, meaning that we examined electronic media exposure that occurs during typical daily living activities (e.g., home, school-based electronic media exposure).”: I do not think this paragraph is fully clear.
@@
 
-\WorkInProgress
+We agree that this was not clear, and have revised it:
 
-```{asis}
+`r get_revision("r3_6")`
+
+```{asis r3_7}
 “Outcomes: We included all reported outcomes.”: it might be worth adding “on benefits and risks”
+```
+
+We have updated this text.
+
+`r get_revision("r3_7")`
+
+```{asis r3_8}
 Lines 200-204: it is unclear to me whether this refers to effects found within the same meta-analysis, across meta-analysis on the same outcome, or both.
 Some additional clarification would be welcome.
+
 ```
 
-\WorkInProgress
+We agree this could have been clearer.
+We have revised the text to indicate that it was both:
 
-```{asis}
+`r get_revision("r3_8")`
+
+```{asis r3_9}
 While PRISMA is named along the review, it is not specifically indicated that it was followed. I would recommend that authors explicitely say it. 
@@
 
-\WorkInProgress
+We have noted this under the *Methods* section.
 
-```{asis}
+```{asis r3_10}
 Education outcomes: text indicates 12 effects from 8 reviews, but figure 2 only shows 11 effects from 7 reviews.
@@
 
-\WorkInProgress
+Thank you for this attention to detail.
+This is the same issue raised by Reviewer 2 (\comment{r2_28}), and we have corrected these numbers.
 
-```{asis}
+```{asis r3_11}
 “For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.” This seems a strange choice, as it mixes very different populations.

### 2023-03-06 _targets.R

@@ -244,7 +244,7 @@ list(
   tar_render(
     manuscript_md,
     path = here::here("reports", "manuscript.Rmd"),
-    output_format = rmarkdown::md_document()
+    output_format = rmarkdown::md_document(pandoc_args = "--wrap=none")
   ),
   tar_render(
     references,

### 2023-03-07 reports/manuscript.Rmd
Address some small comments

@@
   c(
-    "manuscript_info", "combined_bib", "plots", "prisma", "table_desc_latex",
+    "manuscript_info", "combined_bib", "plots", "prisma",
     "edu_certain_params", "plot_edu_certain",
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table \@ref(tab:desctable)).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table 1).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 In `r manuscript_info$freq_combos$n1` cases there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table \@ref(tab:desctable).
+Full characteristics of the included studies are provided in Table 1.
 <span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
@@
 
-```{r desctable}
-table_desc_latex %>%
-  knitr::kable(
-    "latex",
-    caption = "Review characteristics for studies providing unique effects",
-    col.names = c(
-      "First Author", "Year", "Design Restrictions",
-      "Regions Restrictions", "Study Range",
-      "Sample Age Restrictions",
-      "Outcomes Assessed", "Exposures Assessed"
-    ),
-    escape = FALSE,
-    booktabs = TRUE,
-    align = c("l", "c", "l", "l", "c", "l", "l", "l"),
-    linesep = "",
-    longtable = TRUE
-  ) %>%
-  kableExtra::row_spec(1:nrow(table_desc_latex), hline_after = TRUE) %>%
-  kableExtra::row_spec(0, bold = TRUE) %>%
-  kableExtra::column_spec(3:4, width = "2cm") %>%
-  kableExtra::column_spec(5, width = "1.5cm") %>%
-  kableExtra::column_spec(6:8, width = "3cm") %>%
-  kableExtra::kable_styling(
-    latex_options = c("repeat_header"),
-    font_size = 5
-  ) %>%
-  kableExtra::landscape()
-```
+**TABLE 1**
 
-The quality of the included meta-analyses was mixed (see Table \@ref(tab:desctable)).
+The quality of the included meta-analyses was mixed (see Table 1).
 Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.

### 2023-03-07 reports/revision_letter.Rmd
Address some small comments

@@
 
-\WorkInProgress
+We apologise that the quality assessment information was not included in the original submission.
+We have added this information to Table 1, along with the information about the sample characteristics requested by the reviewers.
+We note that this increases the size of the table, and we have removed it from the text of the manuscript and instead included it as a seperate file.
 
@@
 \WorkInProgress
-\todo{Will add to table 1}
+\todo{Havea added to table 1. Should we indicate on forest plots?}
 
@@
 
-\WorkInProgress
-\todo{Will add to table 1}
+Our apologies for this oversight.
+We initially intended to include the quality assessment in Table 1, but felt it made the table too large and moved it to a seperate table.
+It seems we inadvertently did not upload the seperate file when submitting the review.
+We have now included the quality assessment in Table 1.
 
@@
 
+3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
+Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
+We have included all of this information in the supplementary file.
+
 ```{asis r2_26}
@@
 
-\WorkInProgress
+As noted in \comment{r2_15}, this has been corrected.
 
@@
 \WorkInProgress
+\todo{I think this is misleading. It differs by field, outcome, etc.}
 
@@
 There were two ways that the data from the primary studies could be included in our review:
+
 * The data were provided in the paper (i.e., in forest plots, tables, or supplementary files); or
@@
 
-We did not retrive data from the primary studies when the data were not provided in the paper or by the author.
-We did originally consider it, but the scope was such that it was not feasible.
+We did not retrive data from the primary studies when the data were not provided in the paper or by contacting the author.
+Our results include more than 3,000 primary studies, and even after accounting for those that provided data in the paper, it would not be feasible to extract all of the remaining data.
+
+\todo{I kind of want to say "also those reviews are probably bad anyway, because it's not hard to put data in forest plots", but I'm not sure there's a professional way to say that.}
 
@@
 
-\WorkInProgress
+Our apologies for this oversight.
+Per our response to Reviewer 2 (\comment{r2_15}), we initially intended to include the quality assessment in Table 1.
+We removed it because it made the table very large, but did not include the new file with the seperate table.
+We have now included the quality assessment in Table 1.
 
@@
 
-\WorkInProgress
+Yes, we agree that this information is important.
+We have included information about the sample in Table 1.
+We also note that our criteria for choosing effect sizes in the case of duplicates (i.e., taking the one with the largest N) meant that we would generally take the effect size for the 'typical' population.
+More concretely: in the example cited we would typically choose the effect size of television watching on learning for the general population, rather than for those who are depressed, because the sample size would be larger for the former.
+
+\todo{should 'clinical pops' be indicated in the forest plots?}
 

### 2023-03-07 reports/revision_letter.Rmd
Small changes to revision letter

@@
 
+1. \todo{I don't really want to add this - I think tables of counts are dumb. Thoughts?}
+2. \todo{Yes, we should not have used the term "cases". Clear this up}
 3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
-Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
+Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
 We have included all of this information in the supplementary file.
@@
 
-1. (Not sure what to address)
-2. xyz
+1. \todo{Argue not subjective (pre-specified, objective), and we say in limitations that others might choose other options}
+2.
+\todo{Agree - we pre-specified our approaching thinking that it balanced the need to be conservative with the need to be inclusive.
+But, many effects fail this (fairly low) bar.
+Add more on this to the discussion.}
 3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
@@
 \WorkInProgress
-todo{include study design in the forest plots?}
+\todo{include study design in the forest plots?}
 

### 2023-03-08 reports/manuscript.Rmd
Update dataset and rerun pipeline

@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-<span id = "r1_2">Yet, no review has examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
+While there have been other overviews of reviews on screen time, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
+<span id = "r1_2">No review has yet examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
 By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span>
@@
 As an example, consider children watching television programs---an often cited form of screen time harm.
-We found robust evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
+We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
 However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
@@
 
-Social media was one type of exposure that showed consistent risks to health, with no indication of potential benefit.
+Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
 Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
@@
 
-One category of exposure appeared to consistently confer benefits: screen-based interventions designed to promote learning or health behaviours.
+One category of exposure appeared to consistently associated with benefits: screen-based interventions designed to promote learning or health behaviours.
 This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).

### 2023-03-08 reports/manuscript.Rmd
Remove ORs and rerun pipeline
Fixes #23

@@
 For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+
 <span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
 Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
+<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship.
+Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].</span>
 <span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.

### 2023-03-08 reports/revision_letter.Rmd
Update dataset and rerun pipeline
Remove ORs and rerun pipeline
Fixes #23

@@
 Please see response to Reviewer 1, \Comment{r1_4}.
+We agree that the use of causal langauge from an evidence-base that is mostly cross-sectional would be misleading.
+We did not intend to make causal statements, and have reviewed the manuscript for any remaining instances.
 
@@
 
-\WorkInProgress
-\todo{For linear - yeah, but this is always a problem in meta-analyses.
-Need to think about ORs.}
+We agree that the relationship between some outcomes and screen time may not always be linear.
+However, our previous research (e.g., 10.1186/s12966-019-0881-7) looking at a range of health and education outcomes in a high-quality dataset found little evidence for curvilinear relationships.
+We therefore felt that the linear model was appropriate for the majority of the outcomes in this review.
+Additionally, almost none of the reviews we included reported information that would allow us to calculate non-linear effects.
+We agree that this is an important limitation though, and have added information on this to the *Discussion* section:
+
+`r get_revision("r2_16")`
+
+Regarding odds ratios, we initially included these based on several papers that suggested that a conversion to *r* was possible (e.g., 10.1037/0003-066X.62.3.254). 
+On further consideration, we agree with the reviewer that it is difficult to ensure that this conversion produces comparable estimates when the categories used across studies is inconsistent.
+We have therefore removed effect sizes calculated from odds ratios from our results.
+In our efforts to remain completely transparent, these data remain available in the supplementary material.
 
@@
 
-\WorkInProgress
+Per \comment{r2_16}, we decided not to include ORs in the meta-analyses.
 

### 2023-03-08 R/clean_effects.R

@@ -10,15 +10,17 @@
 #' @author Taren Sanders
 #' @export
 clean_effects <- function(effects_raw, reviews_clean, age_codes) {
+  age_moderator_categories <- c(
+    "age", "Age", "Educational level", "Grade Level",
+    "School level", "Level of education"
+  )
+
   effects_clean <-
     effects_raw %>%
     # Remove any unusable effects (must have value and N)
     filter(!is.na(value) & !is.na(combined_n) & use_moderator) %>%
     # Translate the statistical tests to common abbreviations
     mutate(stat_test_clean = translate_tests(statistical_test)) %>%
-    # Can only use some of the metric types
-    filter(stat_test_clean %in% c("b", "d", "r", "or", "z")) %>%
-    convert_effects() %>%
     rename(
       outcome_category = outcome_level_1,
       outcome = outcome_level_2,
@@ -37,14 +39,8 @@ clean_effects <- function(effects_raw, reviews_clean, age_codes) {
       select(reviews_clean, review_id, author_year, demographics_coded),
       by = "review_id"
     ) %>%
-    rename(moderator_age = demographics_coded)
-
-  # Check for ages within the normal moderators and change moderator_age
-  age_moderator_categories <- c(
-    "age", "Age", "Educational level", "Grade Level",
-    "School level", "Level of education"
-  )
-  effects_clean <- effects_clean %>%
+    rename(moderator_age = demographics_coded) %>%
+    # Check for ages within the normal moderators and change moderator_age
     mutate(moderator_age = case_when(
       moderator_category %in% age_moderator_categories &
         moderator_level %in% age_codes$mixed ~ "Mixed",
@@ -57,8 +53,15 @@ clean_effects <- function(effects_raw, reviews_clean, age_codes) {
       TRUE ~ moderator_age
     ))
 
+  effects_converted <-
+    effects_clean %>%
+    # Can only use some of the metric types
+    filter(stat_test_clean %in% c("b", "d", "r", "z")) %>%
+    convert_effects()
+
   # Pick the largest review by N for each outcome/exposure pair and age group
-  effects_use <- effects_clean %>%
+  effects_use <-
+    effects_converted %>%
     group_by(
       plain_language_outcome,
       plain_language_exposure,
@@ -70,7 +73,10 @@ clean_effects <- function(effects_raw, reviews_clean, age_codes) {
       main_effect = TRUE
     ) %>%
     ungroup() %>%
[…]

### 2023-03-08 R/clean_studies.R

@@ -20,9 +20,11 @@ clean_studies <- function(studies_raw) {
 
   data <- studies_clean %>%
     mutate(converted_metric = translate_tests(metric)) %>%
-    filter(converted_metric %in% c("b", "d", "r", "or", "z", "md")) %>%
+    filter(converted_metric %in% c("b", "d", "r", "z", "md")) %>%
     convert_studies() %>%
     drop_na(r_estimate, study_n) %>%
     group_by(effect_size_id) %>%
     tar_group()
+
+  return(data)
 }

### 2023-03-08 R/convert_studies.R

@@ -24,10 +24,6 @@ convert_studies <- function(data) {
         converted_metric == "r" ~ estimate,
         converted_metric == "b" ~ b2r(estimate),
         converted_metric == "d" ~ effectsize::d_to_r(estimate),
-        converted_metric == "or" ~
-          suppressWarnings(effectsize::oddsratio_to_r(estimate)),
-        converted_metric == "lor" ~
-          effectsize::oddsratio_to_r(estimate, log = TRUE),
         converted_metric == "z" ~ correlation::z_fisher(z = estimate),
         # Calculate d from mean difference where possible
         converted_metric == "md" & !is.na(estimate) &
@@ -39,10 +35,6 @@ convert_studies <- function(data) {
         converted_metric == "r" ~ lower_ci,
         converted_metric == "b" ~ b2r(lower_ci),
         converted_metric == "d" ~ effectsize::d_to_r(lower_ci),
-        converted_metric == "or" ~
-          suppressWarnings(effectsize::oddsratio_to_r(lower_ci)),
-        converted_metric == "lor" ~
-          effectsize::oddsratio_to_r(lower_ci, log = TRUE),
         converted_metric == "z" ~ correlation::z_fisher(z = lower_ci),
         # Calculate d from mean difference where possible
         converted_metric == "md" & !is.na(lower_ci) &
@@ -54,10 +46,6 @@ convert_studies <- function(data) {
         converted_metric == "r" ~ upper_ci,
         converted_metric == "b" ~ b2r(upper_ci),
         converted_metric == "d" ~ effectsize::d_to_r(upper_ci),
-        converted_metric == "or" ~
-          suppressWarnings(effectsize::oddsratio_to_r(upper_ci)),
-        converted_metric == "lor" ~
-          effectsize::oddsratio_to_r(upper_ci, log = TRUE),
         converted_metric == "z" ~ correlation::z_fisher(z = upper_ci),
         # Calculate d from mean difference where possible
         converted_metric == "md" & !is.na(upper_ci) &

### 2023-03-08 reports/manuscript.Rmd
Remove unused reference

@@
 
-To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bonettTransformingOddsRatios2007;@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
+To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
 Effect sizes on the original metric are provided in Supplementary File 2.</span>

### 2023-03-09 reports/revision_letter.Rmd
Add population and design to plots
Fixes #24
Fixes #22

@@
 
+We agree that study design should have been a larger factor when choosing which effects to use.
+
+We note that while limiting to certain study designs may improve the quality of the evidence, we are simply summarising what previous reviews have done.
+that is, if previous reviews have not limited their evidence to certain designs (or moderated by design), we do not have that information to present.
+We also found that there were not a lot of reviews which examined the same exposure and outcome, but differed on choice of study design.
+When we included study design as part of our method of choosing effects, it only increased the number of effects by 5 (from 241 to 246).
+That is, there are not a lot of instances where the same exposure and outcome are examined in different study designs.
+
 \WorkInProgress

### 2023-03-09 R/codes.R

@@ -246,7 +246,12 @@ design_codes_list <- list(
     "Include: observational and intervention studies",
     "Include: quantitative designs",
     "None",
-    "None specified"
+    "None specified",
+    "Exclude: Qualitative; Case studies",
+    "Exclude: Non-empirical studies; Qualitative; Systematic reviews or meta-analyses",
+    "Exclude: clinical trials, reliability or validity studies, perspectives or theories with no empircal data, qualitative studies, and case studies of one patient.",
+    "Exclude: Qualitative designs",
+    "Exclude: Qualitative; focus groups"
   ),
   design_obs_mixed = c(
     "Include: Cohort; Case-control; Cross-sectional",

### 2023-03-09 R/plot_settings.R

@@ -5,24 +5,26 @@ edu_certain <- list(
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = TRUE,
-  dims = c(11, 7.5),
+  dims = c(12, 8),
   moderators = FALSE,
   caption = FALSE,
   pos =
     list(
-      lims = c(-4.0, 0.5),
+      lims = c(-5.0, 0.5),
       breaks = c(-0.4, -.2, 0, .2, 0.4),
       esig = NULL,
       eggers = NULL,
       indiv_data = NULL,
-      n = -0.6,
-      k = -0.85,
-      i2 = -1.05,
-      rci = -1.45,
-      author_year = -2.3,
-      mod = -2.7,
-      expo = -3.65,
-      outcome = -4.25,
+      n = -0.55,
+      k = -0.75,
+      i2 = -0.95,
+      rci = -1.3,
+      author_year = -2.2,
+      design = -2.85,
+      pop = -3.2,
+      mod = -3.6,
+      expo = -4.65,
+      outcome = -5.3,
       tag = NA
     )
 )
@@ -32,12 +34,12 @@ edu_uncertain <- list(
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = FALSE,
-  dims = c(16, 18),
+  dims = c(17, 18.5),
   moderators = FALSE,
   caption = TRUE,
   pos =
     list(
-      lims = c(-4.5, 0.8),
+      lims = c(-5.3, 0.7),
       breaks = c(-0.8, -0.6, -0.4, -.2, 0, .2, 0.4, 0.6, 0.8, 1),
       esig = -0.9,
       eggers = -1.1,
@@ -46,11 +48,13 @@ edu_uncertain <- list(
       k = -1.7,
       i2 = -1.85,
       rci = -2.15,
-      author_year = -2.8,
-      mod = -3.15,
-      expo = -4.05,
-      outcome = -4.75,
-      tag = c(0.2, 0.01)
+      author_year = -2.9,
+      design = -3.35,
+      pop = -3.655,
+      mod = -4.0,
+      expo = -4.9,
+      outcome = -5.6,
+      tag = c(0.15, 0.00)
     )
 )
 
@@ -59,23 +63,25 @@ nonedu_certain <- list(
   title = "Associations Between Exposures and Health-related Outcomes",
[…]

### 2023-03-09 reports/revision_letter.Rmd
Finish reviewer 1 comments
Closes #13

@@
 ```
-\WorkInProgress
+
 \todo{Suggestions welcome here}
@@
 Our goal with this review was to provide an overview of the field of screen time research.
-A summary of the field will, out of necessasity, be more broad that a typical systematic review.
+A summary of an entire field will, out of necessasity, be more broad that a typical systematic review.
 We beleive that there is significant value in providing a single overview to summarise the state of the field.
-We have added some additional information to the introduction on this point.
+We have added some additional information to the introduction on this point:
 
@@
 
-We intended to include the review which best captured the information on the exposure/outcome combination.
-The assumption was that the largest review would be the most recent, unless a more recent review had been targeted at a specific population (e.g., those with a disability). 
-Manual inspection of the reviews which did not contribute any effects suggests that this heuristic was successful.
-
-\todo{Does anyone know if we based this on a previous review? It's not cited in the registration.}
+We intended to include the review which captured the most information on the exposure/outcome combination for each effect size.
+The assumption was that the largest review would be the most recent, and that he newer reviews would contain the studies located in previous reviews. 
+Manual inspection of the reviews which did not contribute any effects suggests that this was sucessful - older reviews tended to only be included if they focused on the general population while a newer review focused on a sub-population.
 

### 2023-03-09 reports/manuscript.Rmd
Address additional comments

@@
   We converted results onto a common metric (Pearson's r) to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
-  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_effects` unique exposure/outcome combinations from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
+  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_combos` unique combinations of exposures and outcomes.
+  If duplicate effect sizes from the same combination of exposure and outcome were drawn from different age groups or study designs we retained them, otherwise we chose the effect size with the largest total sample size.
+  We removed effect sizes that could not be harmonized, resulting in `r targets::tar_read(manuscript_info)$unique_effects` from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
   These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
@@
 Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
-With concerns over the impact of screen use including education, health, social development, and psychological well-being, a broad overview that identifies potential benefits and risks is needed.
+With concerns over the impact of screen use including education, health, social development, and psychological well-being, an overview that identifies potential benefits and risks is needed.
 
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
+<span id = "r2_9">
 While there have been other overviews of reviews on screen time, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
 <span id = "r1_2">No review has yet examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
-By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span>
+By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span></span>
 
 In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
-This review synthesises evidence on any outcome of electronic media exposure.
-Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children’s lives.
-By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
+<span id = "r2_6">This review synthesises evidence on any outcome of electronic media exposure.
+We deliberately do not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
+Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
+By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.</span>
 
@@
 A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
-We excluded meta-analyses that only contained evidence gathered from adults (age >18 years). </span>
+We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).</span>
 
@@
 We did, however, employ a risk of bias tool to help interpret the results.
-We included full-text, peer-reviewed meta-analyses published or ‘in-press’ in English.
+We included full-text, peer-reviewed meta-analyses published or 'in-press' in English.
 We excluded conference abstracts and meta-analyses that were unpublished.
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute’s Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table 1).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool [@NHLBIQualityAssessmentSystematic2014] (see Table 1).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 <span id ="r2_17">Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
-We excluded effect sizes which were reported as relative risk ratios, as meta-analyses did not contain sufficient information to meaningfully convert.
+We excluded effect sizes which were reported as relative risk ratios or odds ratios, as meta-analyses did not contain sufficient information to meaningfully convert to a correlation.
 We also excluded effect size estimates when the authors did not provide a sample size.
@@
 
-To facilitate comparisons, we converted effect sizes to Pearson’s $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
+To facilitate comparisons, we converted effect sizes to Pearson's $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
 Effect sizes on the original metric are provided in Supplementary File 2.</span>
+<span id ="r2_27">Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines [@funderEvaluatingEffectSize2019]: very small (0.05 < r <= 0.1), small (0.1 < r <= 0.2), medium (0.2 < r <= 0.2), large (0.3 < r <= 0.4), and very large (r >= 0.4).
+These are similar to other interpretations based on empircal data [@gignacEffectSizeGuidelines2016].</span>
 
@@
 <span id = "r3_8">After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
-In instances where effect sizes from the same combination of exposure and outcome were drawn from different populations (e.g., children vs adolescents) we retained both estimates in our dataset.
+In instances where effect sizes from the same combination of exposure and outcome were drawn from different age-groups (e.g., children vs adolescents), or were drawn using different study designs (e.g., cross-sectional vs longitudinal) we retained both estimates in our dataset.
 </span>
@@
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
-In `r manuscript_info$freq_combos$n1` cases there was only one exposure/outcome combination for an age group, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.
-<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
+<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occured in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
+Full characteristics of the included studies are provided in Table 1.</span>
+<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
 These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
@@
 Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
-Fewer than 20\% of the effects identified met our criteria for statistical credibility.
+<span id = "r2_29">Fewer than 20\% of the effects identified met our criteria for statistical credibility.
 Most studies which did not meet our critiera failed to provide study-level data (or did not provide sufficent data, such as including effect estimates but not sample sizes).
@@
 When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
-It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.
+It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.<span>
 
@@
 Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
-However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].</span>
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].
+Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
+Care is needed, therefore, when interpreting the effect sizes.</span>
 <span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.

### 2023-03-09 reports/revision_letter.Rmd
Address additional comments

@@
 output            : revise::letter.pdf
+header-includes:
+    - \usepackage[utf8x]{inputenc}
 ---
@@
 
-\WorkInProgress
+Please see our response to Reviewer 2, in particular \comment{r2_29}.
+The reviewer raised some important concerns, especially regarding odds ratios which we have decided should not have been included.
+For the other issues, we have provided stronger justification for our decisions.
 
@@
 
-\WorkInProgress
+We have revised the introduction with new papers, with a particular focus on other umbrella reviews.
 
@@
 
-\WorkInProgress
+\todo{I'm open to suggestions for what to include here}
+
+One of the key strengths of our review is that it summarises what is available in the literature, rather than trying to *a-priori* predict what areas should be investigated.
+That is, our review provides a comprehensive summary of what meta-analytic evidence exists.
+We have added some additional text to this effect in the *Introduction*:
+
+`r get_revision("r1_6")`
 
@@
 
-\WorkInProgress
+\todo{Open to suggestions here. I feel like the other changes cover this.}
+
+We feel that we have amply addressed the contribution of this review to the field.
+Guidelines should reflect both the most recent evidence, and the most comprehensive evidence.
+Many of the previous reviews used to justify guidelines focused on narrow ranges of outcomes (e.g., the impact on adiposity).
+We think this is a mistake - you cannot make an informed decision about an action if you only examine the risks, you must also examine potential benefits.
 
@@
 
-\WorkInProgress
+\todo{Open to suggestions here.}
+
+We had difficulty understanding the reviewers exact concern here.
+We are happy to revise this further if the reviewer does not feel that the other changes made to the introduction improve the set of arguements.
 
@@
 
-\WorkInProgress
+We have included information on this in our summary of previous umbrella reviews.
+
+`r get_revision("r2_9")`
 
@@
 
-\WorkInProgress
+We agree that "broad approach" does not correctly convey our meaning.
+We intended to indicate that in order to make nuanced recommendations, you must have all of the information.
+Our approach allowed for a broad set of exposures and outcomes in order to capture all of this information, which is what we intended to convey.
+We think our changes elsewhere (see \comment{r1_2} to Reviewer 1, and \comment{r2_6} above) address this.
 
@@
 
-\WorkInProgress
-\todo{Havea added to table 1. Should we indicate on forest plots?}
+Yes this is a good suggestion.
+We have added a column to indicate if the review was conducted on a general population or not in all of the forest plots.
+This information is also available in Table 1.
 
@@
 
-\WorkInProgress
-\todo{We cite a paper in the protocol on this.}
+It's possible the reviewer has misunderstood.
+In our original plan, we wrote that $P < 0.001$ would be *one of* the criteria for indicating strong evidence (alongside other metrics, such as sample size and heterogeneity).
+We realised that this would restrict our 'strong' evidence to only statistically significant effects.
+What would mean that we could not include evidence for no effect as strong evidence, which is clearly a mistake.
+Our deviation from the protocol (removing the requirement for a P-value threshold) was intended to rectify this.
 
@@
 
-\WorkInProgress
+1. Yes, we agree that this is confusing.
+The use of both 'references' and 'studies' comes from the screening software we used (Covidence; https://www.covidence.org/).
+It is intended to capture instances where there are multiple papers ('references') reporting on the same study.
+In our case, there were seven instances where a review was conducted but the results of the review were reported in multiple papers.
+While we merged these in Covidence for completeness, in all seven cases all of the information that we needed could be retrieved from just one of the papers (which is the one we provide the citation to).
+To make this clearer for readers, we've removed this confusing additional extra information.
+2. Yes, we agree.
+We've collapsed all of the "wrong exposure" codings together.
+3.
+We originally used these when screening full-texts for those where the inclusion criteria targeted the wrong population (e.g., the exclusion criteria was >18 years; coded as "wrong population") vs those where the inclusion criteria included youth, but none of the meta-analytic results could be used because they included adults.
+We think for most readers this is an unimportant distinction, and have collapsed these into one category.
+We also appreciate the attention to detail.
+The updated PRISMA diagram has the correct value in this box.
+4.
+We used sample size as the heuristic for selecting which effect to keep in instances where the same exposure and outcome combination was present, and where the effects represented the same population with the same study designs.
+To create a non-subjective method for choosing which effect size to report we chose to use the sample size, under the assumption that the larger study size would provide the most information.
+Inspection of the effects that were excluded reveal that this decision is not that impactful: we would have ended up with almost exactly the same set of results had we instead chosen to use the number of included studies (*k*) or the most recent review by publication year.
+
+`r get_revision("r3_8")`
 
@@
 
-1. \todo{I don't really want to add this - I think tables of counts are dumb. Thoughts?}
-2. \todo{Yes, we should not have used the term "cases". Clear this up}
+1. \todo{I don't really want to add this - I don't think it adds much value}
+2. We agree that this section was not entirely clear, and we should not have introduced the term 'cases'.
+We have revised the language in this section:
+
+`r get_revision("r2_25")`
+
 3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
-Some reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
-We have included all of this information in the supplementary file.
+Most reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
+All of the effect sizes (in their original, converted, and recalculated forms) are available in the supplementary material.
 
@@
 
-\WorkInProgress
-\todo{I think this is misleading. It differs by field, outcome, etc.}
+We have included this information in the *Methods* section:
+
+`r get_revision("r2_27")`
 
@@
 
-\WorkInProgress
+1. We agree that the our reporting of the method could have been clearer, and have revised the text in this section to more clearly explain our method.
+We disagree with the reviewer that the method was "subjective".
+If we had multiple effects for the same exposure/outcome combination, and which had the same sample age restrictions and the same study design restrictions, we chose the one with the largest sample size.
+We can certainly see how others might use a different method for eliminating duplicate effects (and we state this in the discussion section), but it is difficult to see how using the sample size could be considered "subjective".
 
-1. \todo{Argue not subjective (pre-specified, objective), and we say in limitations that others might choose other options}
-2.
-\todo{Agree - we pre-specified our approaching thinking that it balanced the need to be conservative with the need to be inclusive.
-But, many effects fail this (fairly low) bar.
-Add more on this to the discussion.}
-3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
-We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric, it would not be possible to make any comparisons between the effect sizes.
+`r get_revision("r3_8")`
 
-\todo{Add more to discussion about interpreting sizes carefully.}
+2. We were also suprised by the volume of effects which did not meet the criteria for statistical credibility.
+We were suprised, for example, that almost a quarter of all effects did not provide study-level data (as might be presented in a forest plot), which we thought would be a low bar to clear.
+Almost 40% of those that did have study-level data were derived from samples of less than 1,000 participants (a threshold that has been used by others; 10.1038/s41467-021-24861-8).
+And, it seems unwise to place too much emphasis on results where there is an indication of publication bias (i.e., statistically significant Egger's test).
+Given that we pre-specified this criteria, we think that it would be inappropriate to lower the standard because the majority of reviews did not reach it.
+Instead, we think it reflects the need for the field to raise its standards, especially when it comes to reporting (i.e., making data available, reducing file-drawer problem).
+
+`r get_revision("r3_8")`
+
+3. We understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
+We chose Pearson's *r* as we wanted to focus not on the precise size of the association, but instead on the *direction* and the *magnitude*.
+We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric readers would likely still make comparisons, but these would be subjective.
+We agree that readers should interpret the effect sizes carefully, and have included text to this effect in the *Discussion*:
+
+`r get_revision("r2_16")`
 
@@
 
-\WorkInProgress
+We are unclear what the reviewer is referring to here, although we think many of the concerns were addressed in \comment{r2_29}.
+We feel that a qualitative sytheses of more than 200 effect sizes is outside the scope of this paper.
 
@@
 
-\WorkInProgress
+Even within recreational screen time, our findings do not support guidelines which focus just on minimisation. 
+Video games, for example, are a recreational form of screen time which appear to have some benefits for educational and cognitive outcomes.
 
@@
 
-\todo{I kind of want to say "also those reviews are probably bad anyway, because it's not hard to put data in forest plots", but I'm not sure there's a professional way to say that.}
-
 ```{asis r2_33}
@@
 We agree that study design should have been a larger factor when choosing which effects to use.
+We have rectified this by including study design as a factor in our method of choosing effects.
+That is, if there was the same exposure and outcome for the same age group, but one review used cross-sectional evidence and another used longitudinal, we retained both in the dataset.
+However, we found that there were not a lot of reviews which examined the same exposure and outcome, but differed on choice of study design.
+When we included study design as part of our method of choosing effects, it only increased the number of effects by 5 (from 241 to 246).
 
-We note that while limiting to certain study designs may improve the quality of the evidence, we are simply summarising what previous reviews have done.
-that is, if previous reviews have not limited their evidence to certain designs (or moderated by design), we do not have that information to present.
-We also found that there were not a lot of reviews which examined the same exposure and outcome, but differed on choice of study design.
-When we included study design as part of our method of choosing effects, it only increased the number of effects by 5 (from 241 to 246).
-That is, there are not a lot of instances where the same exposure and outcome are examined in different study designs.
-
-\WorkInProgress
-\todo{include study design in the forest plots?}
+We agree that readers should include study design in their interpretation of the results, and have therefore included this information in all forest plots.
 
@@
 
+\WorkInProgress
+
 Our apologies for this oversight.
@@
 We have now included the quality assessment in Table 1.
+
+\todo{Add a data dictionary}
 
@@
 Yes, we agree that this information is important.
-We have included information about the sample in Table 1.
+We have included information about the sample in Table 1, and have indicated it on all forest plots.
 We also note that our criteria for choosing effect sizes in the case of duplicates (i.e., taking the one with the largest N) meant that we would generally take the effect size for the 'typical' population.
@@
 
-\todo{should 'clinical pops' be indicated in the forest plots?}
-
 \clearpage

### 2023-03-09 R/clean_effects.R

@@ -91,13 +91,18 @@ clean_effects <- function(
 
   effects_converted <-
     effects_clean %>%
+    convert_effects()
+
+  # Identify effects that are usable
+  effects_usable <-
+    effects_converted %>%
     # Can only use some of the metric types
     filter(stat_test_clean %in% c("b", "d", "r", "z")) %>%
-    convert_effects()
+    mutate(usable = TRUE)
 
   # Pick the largest review by N for each outcome/exposure pair and age group
   effects_use <-
-    effects_converted %>%
+    effects_usable %>%
     group_by(
       plain_language_outcome,
       plain_language_exposure,
@@ -105,18 +110,17 @@ clean_effects <- function(
       study_design
     ) %>%
     slice_max(n, with_ties = TRUE) %>%
-    mutate(
-      use_effect = TRUE,
-      main_effect = TRUE
-    ) %>%
+    mutate(use_effect = TRUE) %>%
     ungroup() %>%
-    select(
-      effect_size_id, r, cilb, ciub, z, cilb_z, ciub_z, use_effect,
-      main_effect
-    )
+    select(effect_size_id, r, cilb, ciub, z, cilb_z, ciub_z, use_effect)
 
   effects_clean_use <-
-    left_join(effects_clean, effects_use, by = "effect_size_id")
+    left_join(
+      effects_clean,
+      select(effects_usable, effect_size_id, usable),
+      by = "effect_size_id"
+    ) %>%
+    left_join(effects_use, by = "effect_size_id")
 
   effects_clean_renamed <-
     effects_clean_use %>%

### 2023-03-09 R/convert_effects.R

@@ -25,21 +25,24 @@ convert_effects <- function(data) {
         stat_test_clean == "r" ~ raw_value,
         stat_test_clean == "b" ~ b2r(raw_value),
         stat_test_clean == "d" ~ effectsize::d_to_r(raw_value),
-        stat_test_clean == "z" ~ correlation::z_fisher(z = raw_value)
+        stat_test_clean == "z" ~ correlation::z_fisher(z = raw_value),
+        TRUE ~ NA_real_
       ),
       cilb = case_when(
         is.na(cilb) ~ NA_real_,
         stat_test_clean == "r" ~ cilb,
         stat_test_clean == "b" ~ b2r(cilb),
         stat_test_clean == "d" ~ effectsize::d_to_r(cilb),
-        stat_test_clean == "z" ~ correlation::z_fisher(z = cilb)
+        stat_test_clean == "z" ~ correlation::z_fisher(z = cilb),
+        TRUE ~ NA_real_
       ),
       ciub = case_when(
         is.na(ciub) ~ NA_real_,
         stat_test_clean == "r" ~ ciub,
         stat_test_clean == "b" ~ b2r(ciub),
         stat_test_clean == "d" ~ effectsize::d_to_r(ciub),
-        stat_test_clean == "z" ~ correlation::z_fisher(z = ciub)
+        stat_test_clean == "z" ~ correlation::z_fisher(z = ciub),
+        TRUE ~ NA_real_
       ),
       z = correlation::z_fisher(r = r),
       cilb_z = suppressWarnings(correlation::z_fisher(r = cilb)),

### 2023-03-10 reports/manuscript.Rmd
Some small tweaks

@@
   - id            : "8"
-    institution   : "Faculty of Health Sciences, Curtin University"
+    institution   : "Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland"
   - id            : "9"
@@
 csl               : nature.csl
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 header-includes:
@@
 <span id ="r2_27">Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines [@funderEvaluatingEffectSize2019]: very small (0.05 < r <= 0.1), small (0.1 < r <= 0.2), medium (0.2 < r <= 0.2), large (0.3 < r <= 0.4), and very large (r >= 0.4).
-These are similar to other interpretations based on empircal data [@gignacEffectSizeGuidelines2016].</span>
+These are similar to other interpretations based on empirical data [@gignacEffectSizeGuidelines2016].</span>
 
@@
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
-<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occured in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
+<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
 Full characteristics of the included studies are provided in Table 1.</span>
@@
 <span id = "r2_29">Fewer than 20\% of the effects identified met our criteria for statistical credibility.
-Most studies which did not meet our critiera failed to provide study-level data (or did not provide sufficent data, such as including effect estimates but not sample sizes).
+Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
 Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
@@
 In one systematic review on screen time and sleep [@haleScreenTimeSleep2015], 66 of the 67 included studies used self-reported data for *both* the exposure and outcome variable.
-It has been established that self-reported screen time data has questionnable validity.
+It has been established that self-reported screen time data has questionable validity.
 In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).

### 2023-03-10 reports/revision_letter.Rmd
Some small tweaks

@@
 handling_editor   : "Charlotte Payne"
-
-class             : "draft"
-
+link-citations    : true
 output            : revise::letter.pdf
@@
 We have updated the search to September 2022.
-We found a substantial amount of new literature had been published since our inital search, with an additional 108 meta-analyses included in the review.
+We found a substantial amount of new literature had been published since our initial search, with an additional 108 meta-analyses included in the review.
 While many of these were updates to existing reviews, we also included 110 new exposure/outcome combinations (or existing combinations for new age groups) that were not found in the original search.
@@
 We have added this information to Table 1, along with the information about the sample characteristics requested by the reviewers.
-We note that this increases the size of the table, and we have removed it from the text of the manuscript and instead included it as a seperate file.
+We note that this increases the size of the table, and we have removed it from the text of the manuscript and instead included it as a separate file.
 
@@
 Please see response to Reviewer 1, \Comment{r1_4}.
-We agree that the use of causal langauge from an evidence-base that is mostly cross-sectional would be misleading.
+We agree that the use of causal language from an evidence-base that is mostly cross-sectional would be misleading.
 We did not intend to make causal statements, and have reviewed the manuscript for any remaining instances.
@@
 Our goal with this review was to provide an overview of the field of screen time research.
-A summary of an entire field will, out of necessasity, be more broad that a typical systematic review.
-We beleive that there is significant value in providing a single overview to summarise the state of the field.
+A summary of an entire field will, out of necessity, be more broad that a typical systematic review.
+We believe that there is significant value in providing a single overview to summarise the state of the field.
 We have added some additional information to the introduction on this point:
@@
 The assumption was that the largest review would be the most recent, and that he newer reviews would contain the studies located in previous reviews. 
-Manual inspection of the reviews which did not contribute any effects suggests that this was sucessful - older reviews tended to only be included if they focused on the general population while a newer review focused on a sub-population.
+Manual inspection of the reviews which did not contribute any effects suggests that this was successful - older reviews tended to only be included if they focused on the general population while a newer review focused on a sub-population.
 
@@
 
-Note that we do use causal langauge when describing hypothesised mechanisms, and when describing guidelines.
-We feel that this is sensible --- guidelines are based on causal assumptions, and while our evidence does not always support them, we are refering to them in the context that they are made (i.e., to instruct parents).
+Note that we do use causal language when describing hypothesised mechanisms, and when describing guidelines.
+We feel that this is sensible --- guidelines are based on causal assumptions, and while our evidence does not always support them, we are referring to them in the context that they are made (i.e., to instruct parents).
 
@@
 The quote from the *Lancet* editorial is that the understanding is lacking, rather than the evidence.
-Our understanding is lacking partly because benefits of screen time (as seen in some educational literature) and reviewed seperately from harms.
+Our understanding is lacking partly because benefits of screen time (as seen in some educational literature) and reviewed separately from harms.
 Our review aims to address this.
@@
 
-`r get_revision("r1_6")`
+`r get_revision("r2_6")`
 
@@
 We had difficulty understanding the reviewers exact concern here.
-We are happy to revise this further if the reviewer does not feel that the other changes made to the introduction improve the set of arguements.
+We are happy to revise this further if the reviewer does not feel that the other changes made to the introduction improve the set of arguments.
 
@@
 Instead, we chose to summarise the literature on for any meta-analysis where screen exposure was the independent variable.
-We have removed the word "plausible", as we agree that makes the sentence unclear and the revised phrasing is more aligned with the eligibility critiera.
+We have removed the word "plausible", as we agree that makes the sentence unclear and the revised phrasing is more aligned with the eligibility criteria.
 Our intention in the introduction is not to preempt the results, which means we do not outline the outcomes found in the introduction.
@@
 Our apologies for this oversight.
-We initially intended to include the quality assessment in Table 1, but felt it made the table too large and moved it to a seperate table.
-It seems we inadvertently did not upload the seperate file when submitting the review.
+We initially intended to include the quality assessment in Table 1, but felt it made the table too large and moved it to a separate table.
+It seems we inadvertently did not upload the separate file when submitting the review.
 We have now included the quality assessment in Table 1.
@@
 
-2. We were also suprised by the volume of effects which did not meet the criteria for statistical credibility.
-We were suprised, for example, that almost a quarter of all effects did not provide study-level data (as might be presented in a forest plot), which we thought would be a low bar to clear.
+2. We were also surprised by the volume of effects which did not meet the criteria for statistical credibility.
+We were surprised, for example, that almost a quarter of all effects did not provide study-level data (as might be presented in a forest plot), which we thought would be a low bar to clear.
 Almost 40% of those that did have study-level data were derived from samples of less than 1,000 participants (a threshold that has been used by others; 10.1038/s41467-021-24861-8).
@@
 We chose Pearson's *r* as we wanted to focus not on the precise size of the association, but instead on the *direction* and the *magnitude*.
-We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric readers would likely still make comparisons, but these would be subjective.
+We think it is worth considering the counterfactual to our approach: had we not converted effect sizes to a common metric readers would likely still make comparisons, but these would be subjective.
 We agree that readers should interpret the effect sizes carefully, and have included text to this effect in the *Discussion*:
@@
 We are unclear what the reviewer is referring to here, although we think many of the concerns were addressed in \comment{r2_29}.
-We feel that a qualitative sytheses of more than 200 effect sizes is outside the scope of this paper.
+We feel that a qualitative synthesis of more than 200 effect sizes is outside the scope of this paper.
 
@@
 
-We did not retrive data from the primary studies when the data were not provided in the paper or by contacting the author.
+We did not retrieve data from the primary studies when the data were not provided in the paper or by contacting the author.
 Our results include more than 3,000 primary studies, and even after accounting for those that provided data in the paper, it would not be feasible to extract all of the remaining data.
@@
 Per our response to Reviewer 2 (\comment{r2_15}), we initially intended to include the quality assessment in Table 1.
-We removed it because it made the table very large, but did not include the new file with the seperate table.
+We removed it because it made the table very large, but did not include the new file with the separate table.
 We have now included the quality assessment in Table 1.
@@
 
-We chose this as most reviews provided mean ages for individual studies but not age ranges, which meant we would not have been able to consistently apply the critiera.
+We chose this as most reviews provided mean ages for individual studies but not age ranges, which meant we would not have been able to consistently apply the criteria.
 

### 2023-03-10 R/utils.R

@@ -32,11 +32,11 @@ upload_all_files <- function(files = c(
                              )) {
   file_details <- list(
     "manuscript" = list(
-      path = "reports/manuscript.pdf",
+      path = c("reports/manuscript.pdf", "reports/manuscript.docx"),
       type = "main"
     ),
     "revision_letter" = list(
-      path = "reports/revision_letter.pdf",
+      path = c("reports/revision_letter.pdf", "reports/revision_letter.docx"),
       type = "main"
     ),
     "prisma" = list(

### 2023-03-10 _targets.R

@@ -240,6 +240,11 @@ list(
     output_format = rmarkdown::md_document(pandoc_args = "--wrap=none")
   ),
   tar_render(
+    manuscript_docx,
+    path = here::here("reports", "manuscript.Rmd"),
+    output_format = papaja::apa6_docx()
+  ),
+  tar_render(
     references,
     path = here::here("reports", "references.Rmd"),
     output_file = here::here(
@@ -257,5 +262,10 @@ list(
   tar_render(
     revision_letter,
     path = here::here("reports", "revision_letter.Rmd")
+  ),
+  tar_render(
+    revision_letter_docx,
+    path = here::here("reports", "revision_letter.Rmd"),
+    output_format = revise::letter.docx()
   )
 )

### 2023-03-11 reports/manuscript.Rmd
Fix some data quality issues

@@
 csl               : nature.csl
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 header-includes:

### 2023-03-11 R/convert_effects.R

@@ -16,9 +16,9 @@ convert_effects <- function(data) {
         raw_cilb
       ),
       ciub = if_else(
-        is.na(raw_cilb) & !is.na(value_raw_se),
+        is.na(raw_ciub) & !is.na(value_raw_se),
         raw_value + 1.96 * value_raw_se,
-        raw_cilb,
+        raw_ciub,
       ),
       r = case_when(
         is.na(raw_value) ~ NA_real_,

### 2023-03-12 reports/manuscript.Rmd
Finish addressing reviewer comments
And rerun the pipeline

@@
 However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 3.
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 4.
 
@@
 The most frequently reported exposures were `r manuscript_info$freq_exposures`.
-Supplementary File 4 provides a list of all exposures identified.
+Supplementary File 5 provides a list of all exposures identified.
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
@@
 These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
+The characteristics of the included effects are available in Supplementary File 9.
 
@@
 We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in Supplementary File 5.
+Effects not meeting one or more of these standards are presented in Supplementary File 6.
 The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in Supplementary File 6.
+Effects not meeting one or more of these standards are presented in Supplementary File 7.
 The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
@@
 However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 5 & 6) therefore this hypothesis could not be addressed.
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 & 7) therefore this hypothesis could not be addressed.
 

### 2023-03-12 reports/revision_letter.Rmd
Finish addressing reviewer comments
And rerun the pipeline

@@
 
-\todo{Suggestions welcome here}
-
 Our goal with this review was to provide an overview of the field of screen time research.
@@
 Summary:
+
 Page 4 line 59: the lack of comprehensive evidence hampers efforts to make an informed decision.
@@
 Introduction:
+
 Page 5 line 84-86: please further justify how a review study would make the limited evidence base less lacking or generate new findings.
@@
 
-\todo{I'm open to suggestions for what to include here}
-
 One of the key strengths of our review is that it summarises what is available in the literature, rather than trying to *a-priori* predict what areas should be investigated.
@@
 
-\todo{Open to suggestions here. I feel like the other changes cover this.}
-
 We feel that we have amply addressed the contribution of this review to the field.
@@
 ```
-
-\todo{Open to suggestions here.}
 
@@
 Methods:
+
 Page 8 line 146-148: the effects of screen use on youth with a clinical condition are likely be different from those of the general population.
@@
 Results
+
 Page 12 line 247-248: please add a description that 66 studies contributed unique effect sizes to the current review. 
@@
 
-1. \todo{I don't really want to add this - I don't think it adds much value}
+1. We have added a table to summarise the effects (including some information on the reviews these effects were drawn from) as Supplementary File 9.
 2. We agree that this section was not entirely clear, and we should not have introduced the term 'cases'.
@@
 Discussion
+
 Page 31 line 362-368: I think these are important nuances.
@@
 
-\todo{Add a data dictionary}
+We agree that the supplementary materials are difficult to navigate.
+We have added a codebook (as Supplementary File 3) as suggested.
 

### 2023-03-12 R/plot_settings.R

@@ -1,7 +1,7 @@
 # Settings for each of the outcome plots
 
 edu_certain <- list(
-  filename = "Forest plot for Education.pdf",
+  filename = "figures/Forest plot for Education.pdf",
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = TRUE,
@@ -30,7 +30,8 @@ edu_certain <- list(
 )
 
 edu_uncertain <- list(
-  filename = "Supplementary File 5 - Education Outcomes.pdf",
+  filename =
+    "supplementary_files/Supplementary File 6 - Education Outcomes.pdf",
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = FALSE,
@@ -59,7 +60,7 @@ edu_uncertain <- list(
 )
 
 nonedu_certain <- list(
-  filename = "Forest plot for Health-related Outcomes.pdf",
+  filename = "figures/Forest plot for Health-related Outcomes.pdf",
   title = "Associations Between Exposures and Health-related Outcomes",
   categories = c("Psychology", "Health Behaviour", "Physical Health"),
   certain = TRUE,
@@ -88,7 +89,8 @@ nonedu_certain <- list(
 
 nonedu_uncertain <-
   list(
-    filename = "Supplementary File 6 - Health-related Outcomes.pdf",
+    filename =
+      "supplementary_files/Supplementary File 7 - Health-related Outcomes.pdf",
     title = "Associations Between Exposures and Health-related Outcomes",
     categories = c("Psychology", "Health Behaviour", "Physical Health"),
     certain = FALSE,

### 2023-03-12 R/utils.R

@@ -51,15 +51,17 @@ upload_all_files <- function(files = c(
       type = "figs"
     ),
     "supp_files" = list(
-      path = c(
-        "figures/Supplementary File 5 - Education Outcomes.pdf",
-        "figures/Supplementary File 6 - Health-related Outcomes.pdf",
+      path = c( # nolint start
         "supplementary_files/Supplementary File 1 - Search Strategy.pdf",
-        "supplementary_files/Supplementary File 2 - Complete Effects Data.csv", # nolint
-        "supplementary_files/Supplementary File 3 - List of reviews without meta-analyses.csv", # nolint
-        "supplementary_files/Supplementary File 4 - List of Exposures.csv",
-        "supplementary_files/Supplementary File 7 - Included Studies.pdf"
-      ),
+        "supplementary_files/Supplementary File 2 - Complete Effects Data.csv",
+        "supplementary_files/Supplementary File 3 - Effect Size Codebook.pdf",
+        "supplementary_files/Supplementary File 4 - List of reviews without meta-analyses.csv",
+        "supplementary_files/Supplementary File 5 - List of Exposures.csv",
+        "supplementary_files/Supplementary File 6 - Education Outcomes.pdf",
+        "supplementary_files/Supplementary File 7 - Health-related Outcomes.pdf",
+        "supplementary_files/Supplementary File 8 - Included Studies.pdf",
+        "supplementary_files/Supplementary File 9 - Effect Characteristics.pdf"
+      ), # nolint end
       type = "supp"
     ),
     "tables" = list(

### 2023-03-12 _targets.R

@@ -78,31 +78,9 @@ list(
     pattern = map(meta_results_r)
   ),
   tar_target(
-    meta_results_z,
-    run_metaanalysis(studies_clean, type = "z"),
-    pattern = map(studies_clean),
-    iteration = "list"
-  ),
-  tar_target(
-    meta_aggregated_z,
-    tidy_meta(meta_results_z),
-    pattern = map(meta_results_z)
-  ),
-  tar_target(
-    eggers_results_z,
-    run_eggers(meta_results_z),
-    pattern = map(meta_results_z)
-  ),
-  tar_target(
-    excess_sig_results_z,
-    run_excess_sig(meta_results_z),
-    pattern = map(meta_results_z)
-  ),
-  tar_target(
     studies_results,
     combine_study_results(
-      meta_aggregated_r, eggers_results_r, excess_sig_results_r,
-      meta_aggregated_z, eggers_results_z, excess_sig_results_z
+      meta_aggregated_r, eggers_results_r, excess_sig_results_r
     )
   ),
   tar_target(
@@ -124,7 +102,19 @@ list(
   ),
   tar_target(
     table_desc_saved,
-    save_table(table_desc_gt, "Review characteristics.pdf"),
+    save_table(table_desc_gt, "tables/Review characteristics.pdf"),
+    format = "file",
+  ),
+  tar_target(
+    table_effects,
+    make_table_effects(combined_effects)
+  ),
+  tar_target(
+    table_effects_saved,
+    save_table(
+      table_effects,
+      "supplementary_files/Supplementary File 9 - Effect Characteristics.pdf"
+    ),
     format = "file",
   ),
   # Make plots --------------------------------------------------------------
@@ -249,7 +239,7 @@ list(
     path = here::here("reports", "references.Rmd"),
     output_file = here::here(
       "supplementary_files",
-      "Supplementary File 7 - Included Studies.pdf"
+      "Supplementary File 8 - Included Studies.pdf"
     ),
     params = list(
       nocite_list =

### 2023-03-12 reports/manuscript.Rmd
Address James' comments on manuscript

@@
   If duplicate effect sizes from the same combination of exposure and outcome were drawn from different age groups or study designs we retained them, otherwise we chose the effect size with the largest total sample size.
-  We removed effect sizes that could not be harmonized, resulting in `r targets::tar_read(manuscript_info)$unique_effects` from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
+  We removed effect sizes that could not be harmonised, resulting in `r targets::tar_read(manuscript_info)$unique_effects` effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
   These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
   When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potential harm on learning, literacy, body composition, and depression.
-  Like-wise, social media was consistently associated with risks to health, with no identified benefits.
+  Likewise, social media was consistently associated with risks to health, with no identified benefits.
   However, we also found that these harms could often be mitigated by certain kinds of content (e.g., educational), or by modifying the context (e.g., co-viewing with a parent).
@@
 options(dplyr.summarise.inform = FALSE)
-
-# Uncomment to run outside of pipeline
-# library(targets)
-# library(xfun)
-# library(DiagrammeR)
-# library(gt)
 ```
@@
   c(
-    "manuscript_info", "combined_bib", "plots", "prisma",
-    "edu_certain_params", "plot_edu_certain",
-    "nonedu_certain_params", "plot_nonedu_certain"
+    "manuscript_info", "combined_bib", "prisma", "edu_certain_params",
+    "plot_edu_certain", "nonedu_certain_params", "plot_nonedu_certain"
   ),
@@
 Children's engagement in screen time is a complex issue.
-Parents, policymakers, and educators needing to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
+Parents, policymakers, and educators need to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
 The lack of comprehensive evidence hampers efforts to make an informed decision.
 As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
-In this study, we systematically harmonize data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
+In this study, we systematically harmonise data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
 We show that some forms of screen time---such as social media---show consistent evidence of harm for children, with no clear evidence of a benefit.
@@
 Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen use (e.g., television, mobile phones, and computers) [@wartellaChildrenComputersNew2000].
-Excessive screen time use is the number one concern parents have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top].
+Excessive screen time use is the number one concern parents in Western countries have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top].
 Yet, the evidence to support parents' concerns is inadequate.
@@
 For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
-They also recommend that children aged 2-5 years should spend a maximum of one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
-In contrast, some recent evidence suggests that exposure to electronic entertainment media that exceeds these guidelines (e.g., 3-4 hours per day) may not have meaningful adverse effects on children's behaviour or mental health, and might, in fact, benefit their well-being, as long as this exposure does not reach extreme levels (e.g., 7 hours per day)[@fergusonEverythingModerationModerate2017].
+They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
+However, recent evidence suggests that longer exposures may not have adverse effects on children's behaviour or mental health---and might, in fact, benefit their well-being---as long as exposure does not reach extreme levels (e.g., 7 hours per day)[@fergusonEverythingModerationModerate2017].
 Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
@@
 We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
-To be considered 'credible' an effect needed to be derived from a combined sample of >1,000 [@papadimitriouUmbrellaReviewEvidence2021] and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
+To be considered 'credible' an effect needed to be derived from a combined sample of >1,000 participants [@papadimitriouUmbrellaReviewEvidence2021] and have non-significant tests of publication bias (i.e., Egger’s test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 
-We initially planned to include systematic reviews without meta-analyses in a narrative summary alongside the main meta-analytic findings.
+We initially planned to describe the findings of systematic reviews that did not include meta-analyses in a narrative summary alongside the main findings from meta-analytic studies.
 However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
@@
 
-One category of exposure appeared to consistently associated with benefits: screen-based interventions designed to promote learning or health behaviours.
+One category of exposure appeared to be consistently associated with benefits: screen-based interventions designed to promote learning or health behaviours.
 This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
@@
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data avilable in Supplementary Materials).
+If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
 For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].

### 2023-03-12 reports/manuscript.Rmd
Address some coauthor comments

@@
 While there have been other overviews of reviews on screen time, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
-<span id = "r1_2">No review has yet examined the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviour, and well-being.
-By summarising and synthesising all evidence in one overview, we provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span></span>
+<span id = "r1_2">
+Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
+For example, prohibiting screen use might reduce exposure to advertising but may also thwart learning opportunities from interactive educational tools.
+Reviews on either of these exposures or outcomes would likely miss being able to quantify these trade-offs.
+Overviews are one method of evidence synthesis that helps address these trade-offs, by providing 'user-friendly' summaries of a field of research [@pollockChapterOverviewsReviews2022].
+These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span></span>
 
@@
 
+<span id = "r1_5">
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
@@
 Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups [@marshallRelationshipsMediaUse2004].
+Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
+However, in the absence of this work, our study has shown how children are affected by screens in general.
+</span>
 
@@
 
-<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot comment on the evidence for causality.
-Instead, readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
+<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
+These likely depend on the specific exposure and outcome.
+It is tempting for people to draw inferences that the associations are due to screen time causing these outcomes, but we cannot rule out reverse causality, a third variable, or some combination of influences.
+Many of the individual reviews go into more detail about the strength of the evidence for causal associations, but those judgements were difficult to synthesise across more than 200 reviews.
+Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
 <span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship.

### 2023-03-12 reports/revision_letter.Rmd
Address some coauthor comments

@@
 Please see our response to Reviewer 2, in particular \comment{r2_29}.
-The reviewer raised some important concerns, especially regarding odds ratios which we have decided should not have been included.
+The reviewer raised some important concerns, especially regarding the interpretability of odds ratios which we have decided should not have been included (see \comment{r2_16}).
 For the other issues, we have provided stronger justification for our decisions.
@@
 
-We agree with the reviewer that the term 'screen time' is problematic. 
-Indeed, as our results show, the influence of screen time on children is a less a function of a physical screen, and more a function of the activity that the screen provides. 
+We agree with the reviewer that the term 'screen time' is problematic as it fails to acknowledge the diversity of experiences screens provide.
+Indeed, our motivation for conducting this review was to counter this narrative in the literature.
+To do this, it was necessary to invoke the concept of 'screen time'.
+As our results show, the influence of screen time on children is less a function of a physical screen, and more a function of the activity that the screen provides.
 But, we feel that a review such as this is needed in order to emphasise the diverse influence that screens can have. 
@@
 
-Our goal with this review was to provide an overview of the field of screen time research.
-A summary of an entire field will, out of necessity, be more broad that a typical systematic review.
-We believe that there is significant value in providing a single overview to summarise the state of the field.
-We have added some additional information to the introduction on this point:
+We acknowledge that the field contains a range of different effects with different magnitudes and directions.
+We want to make clear what trade-offs are involved in any guidelines around screen use.
+For example, prohibiting screen use might reduce exposure to advertising but may also thwart learning opportunities from interactive educational tools.
+Reviews on either of these exposures or outcomes would likely miss being able to quantify these trade-offs.
+As a result, we think casting a wide net and using a meta-review methodology is one of the few ways of pragmatically outlining and quantifying the trade-offs.
+As Cochrane says, "Overviews are an increasingly popular form of evidence synthesis, as they aim to provide 'user-friendly' summaries of the breadth of research relevant to a decision without decision makers needing to assimilate the results of multiple systematic reviews themselves (https://training.cochrane.org/handbook/current/chapter-v).
 
@@
 We intended to include the review which captured the most information on the exposure/outcome combination for each effect size.
-The assumption was that the largest review would be the most recent, and that he newer reviews would contain the studies located in previous reviews. 
-Manual inspection of the reviews which did not contribute any effects suggests that this was successful - older reviews tended to only be included if they focused on the general population while a newer review focused on a sub-population.
+The assumption was that the largest review would be the most recent, and that newer reviews would contain the studies located in previous reviews. 
+We inspected the reviews that did not contribute any effects.
+This inspection suggested our assumptions were correct: older reviews tended to only be included if they focused on the general population while a newer review focused on a specific sub-population.
 
@@
 Yes, we agree that the body of evidence does not lend itself to strong causal conclusions.
+A strength of our study is that it points out issues with how research has been conducted in this field, which we hope will make future research more ambitious.
 We note that we deliberately chose to avoid using strong causal language as much as possible, instead indicating that the evidence suggests associations with outcomes.
-We have reread the manuscript and removed any remaining causal language that we found.
+We have carefully reread the manuscript and removed any remaining unjustified causal language.
 We have also added the following to the *Discussion* section:
@@
 Note that we do use causal language when describing hypothesised mechanisms, and when describing guidelines.
-We feel that this is sensible --- guidelines are based on causal assumptions, and while our evidence does not always support them, we are referring to them in the context that they are made (i.e., to instruct parents).
+We feel that this is sensible---guidelines are based on causal assumptions, and while our evidence does not always support them, we are referring to them in the context that they are made (i.e., to instruct parents).
 
@@
 
-One of the benefits of the other reviewers' and editor's suggestion to update the search is that some of this limitation has been addressed in more recent literature.
-Newer papers were more likely to provide moderation by age group, or new reviews targeting specific age groups were now available.
-Unfortunately, many of these still failed to meet our criteria for statistical certainty.
-Inspecting the results in the supplementary material still reveal fewer differences by age group than may be expected.
-In some cases this is because there is still only an effect for a single age group, as many reviews target behaviours or outcomes which are more common in one age group (e.g., sexting in adolescents, or developmental outcome in young children).
-For the effects where there were multiple age groups, differences tended to be small (e.g., body composition).
+We agree that it would be useful to break down findings by age.
+However, for us to accomplish this we need meta-analyses which examine the developmental span for each exposure and outcome combination.
+While the addition of further reviews based on the reviewers' and editor's suggestion to update the search helped address this limiation (ewer papers were more likely to provide moderation by age group, and new reviews targeting specific age groups have been added), there were still too few age-based comparisons to make strong claims.
+This is because many reviews target behaviours or outcomes which are more common in one age group (e.g., sexting in adolescents, or developmental outcome in young children).
+For the effects where there were multiple age groups (e.g., body composition), differences tended to be small.
+
+We have included some additional information on this in the *Discussion* section:
+
+`r get_revision("r1_5")`
 
@@
 
-The quote from the *Lancet* editorial is that the understanding is lacking, rather than the evidence.
+The reviewer was pointing to the following quote from the *Lancet*: "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking.".
+It is not that the evidence is lacking, per se, but that our *understanding* is weak.
 Our understanding is lacking partly because benefits of screen time (as seen in some educational literature) and reviewed separately from harms.
-Our review aims to address this.
-See additional context in the *Introduction*:
+Our review aims to address this (see also Reviewer 1, \comment{r1_2}).
+We think synthesising the trade-offs in one review can help us understand when screen time might be associated with good/poor outcomes, helping to better understand why.
+
+We have added this additional context to the *Introduction*:
 
@@
 
-We have revised the introduction with new papers, with a particular focus on other umbrella reviews.
+We have revised the introduction with new papers, with a particular focus on other umbrella reviews. See the below for an example of the changes:
+
+`r get_revision("r2_9")`
 

### 2023-03-12 reports/manuscript.Rmd
Address current coauthor comments

@@
 Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
-For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
+<span id = "r2_8">For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
 They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
@@
 This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required [@kayeConceptualMethodologicalMayhem2020].
+</span>
 
@@
 Overviews are one method of evidence synthesis that helps address these trade-offs, by providing 'user-friendly' summaries of a field of research [@pollockChapterOverviewsReviews2022].
-These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.</span></span>
+These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.
+By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.</span></span>
 
@@
 <span id = "r2_6">This review synthesises evidence on any outcome of electronic media exposure.
-We deliberately do not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
+We deliberately did not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
 Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
@@
 
-We initially planned to describe the findings of systematic reviews that did not include meta-analyses in a narrative summary alongside the main findings from meta-analytic studies.
-However, we determined that combining results from the meta-analyses allowed readers to compare relative strength of associations more easily.
+<span id = "r2_20">
+As described above, we have summarised the meta-analytic findings from all included systematic reviews.
+In our protocol, we originally planned to also conduct a narrative synthesis of all systematic reviews, even those without meta-analyses.
+However, we determined that combining results from the meta-analyses alone allow readers to compare relative strength of associations more easily.
 Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 4.
+</span>
 
@@
 Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
-Many current guidelines simplify this complex relationship as something that should be minimised in all instances [@australiangovernmentPhysicalActivityExercise2021;@whoGuidelinesPhysicalActivity2019].
+Many current guidelines simplify this complex relationship as something that should be minimised [@australiangovernmentPhysicalActivityExercise2021;@whoGuidelinesPhysicalActivity2019].
 We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.
+
+<span id = "r2_7">
+In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce 'screen time', and instead focusing on the type of screen time.
+For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
+</span>
 
@@
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
-For this reason, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+<span id = "r2_24">In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
+Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (*k*) or the most recent review by publication year.
+However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.</span>
 
@@
 Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
-<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship.
+
+<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
 Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].

### 2023-03-12 reports/revision_letter.Rmd
Address current coauthor comments

@@
 
-One of the key strengths of our review is that it summarises what is available in the literature, rather than trying to *a-priori* predict what areas should be investigated.
-That is, our review provides a comprehensive summary of what meta-analytic evidence exists.
+Screen use is associated with a range of widespread outcomes.
+Many reviews focus on a single exposure outcome pairing and miss the trade-offs that are inherent in focusing on just one area (see Reviewer 1, \comment{r1_2} for further discussion).
+By focusing on a broad range of outcomes (health and non-health), without trying to *a-priori* predict what areas should be investigated, we simultaneously quantify and compare these trade-offs.
+
 We have added some additional text to this effect in the *Introduction*:
@@
 `r get_revision("r2_6")`
+
+and
+
+`r get_revision("r1_2")`
 
@@
 
-We feel that we have amply addressed the contribution of this review to the field.
-Guidelines should reflect both the most recent evidence, and the most comprehensive evidence.
+Guidelines are important and useful, but they should reflect both the most recent and the most comprehensive evidence.
 Many of the previous reviews used to justify guidelines focused on narrow ranges of outcomes (e.g., the impact on adiposity).
-We think this is a mistake - you cannot make an informed decision about an action if you only examine the risks, you must also examine potential benefits.
+We think this is a mistake---you cannot make an informed decision about an action if you only examine the risks, you must weigh these against any potential benefits.
+We have included a discussion of this in the *Discussion* section:
+
+`r get_revision("r2_7")`
 
@@
 
-We had difficulty understanding the reviewers exact concern here.
-We are happy to revise this further if the reviewer does not feel that the other changes made to the introduction improve the set of arguments.
+We appreciate it is not a direct contrast to compare overall limits of screen time against deleterious effects of screen time over 3-4 hours. As a result, we have removed the words 'in contrast':
+
+`r get_revision("r2_8")`
 
@@
 `r get_revision("r2_9")`
+
+As mentioned in other author responses, we have made a stronger effort to organise the review toward a cohesive purpose.
 
@@
 We have removed the word "plausible", as we agree that makes the sentence unclear and the revised phrasing is more aligned with the eligibility criteria.
-Our intention in the introduction is not to preempt the results, which means we do not outline the outcomes found in the introduction.
+We have tried not to preempt the results section in the introduction, but do now refer to some expected outcomes.
+For example:
+
+`r get_revision("r2_9")`
 
@@
 We agree that "broad approach" does not correctly convey our meaning.
-We intended to indicate that in order to make nuanced recommendations, you must have all of the information.
+We intended to indicate that in order to make nuanced recommendations, you must have all of the information regarding benefits and risks.
 Our approach allowed for a broad set of exposures and outcomes in order to capture all of this information, which is what we intended to convey.
 We think our changes elsewhere (see \comment{r1_2} to Reviewer 1, and \comment{r2_6} above) address this.
+
+`r get_revision("r1_2")`
+
+`r get_revision("r2_6")`
 
@@
 
-Per \comment{r2_10} above, we did not pre-specify outcomes and feel it would be inappropriate to revise our inclusion criteria.
+As per \comment{r2_10} above, we did not pre-specify outcomes and do not want to mislead readers on the process.
+We have indicated some anticiapted outcomes, however.
+
+`r get_revision("r2_9")`
 
@@
 
-We agree this is could be confusing to the reader.
-The previous sections outlined the inclusion criteria for including a *review*, whereas these sections focus on reasons for excluding an *effect size* from the review.
+We agree this could be confusing to the reader.
+The reason that we had inclusion/exclusion criteria across two sections is that we have separate criteria for reviews, and for the effect sizes within reviews.
+The first section outlines the inclusion criteria for including a *review*, whereas the subsequent sections focus on reasons for excluding an *effect size* from the review.
 We did not require all effect sizes within a review to be eligible or usable for the review to still be included.
+This section now reads:
 
@@
 
-We are not clear on what the reviewer means here.
-Per the quoted sentence, we intended to include all systematic reviews (not just meta-analyses), but the volume of meta-analyses was such that we felt this was unneeded.
-This was a change from our protocol, and thus reported as such.
-We are happy to revise this section if the reviewer has a suggestion.
+We agree our phrasing here was unclear. We meant that we intended to narratively summarise systematic reviews, as well as meta-analytic studies. We have changed this phrase to:
+
+`r get_revision("r2_20")`
 
@@
 
-\WorkInProgress
+It is true that harmonising effect sizes does not perfectly retain the original information.
+Different measures are able to capture different aspects of the underlying phenomenon.
+However, it is better to harmonise for the purposes of crude comparisons than to try and subjectively compare completely different classes of effect sizes. We make this point in the limitations:
+
+`r get_revision("r2_16")`
+
+In this study we had to choose between subjectively comparing various classes of effect sizes, or attempt to harmonise all effects so quantitative comparisons could easily be made.
+We elected to harmise the effect sizes so that we could better illustrate differences between studies.
+However, harmonisation is imperfect, and so to better understand the exact effect from meta-analyses we refer readers back to the original meta-analyses.
 
@@
 
-It's possible the reviewer has misunderstood.
-In our original plan, we wrote that $P < 0.001$ would be *one of* the criteria for indicating strong evidence (alongside other metrics, such as sample size and heterogeneity).
+We appreciate we may have not explained this clearly.
+We have brought our methods into line with other reviews.
+In our protocol, we wrote that $P < 0.001$ would be *one of* the criteria for indicating strong evidence (alongside other metrics, such as sample size and heterogeneity).
 We realised that this would restrict our 'strong' evidence to only statistically significant effects.
-What would mean that we could not include evidence for no effect as strong evidence, which is clearly a mistake.
+But using this criteria meant that we could never classify non-significant findings as strong evidence regardless of their precision, which is clearly a mistake.
 Our deviation from the protocol (removing the requirement for a P-value threshold) was intended to rectify this.
@@
 
-`r get_revision("r3_8")`
+`r get_revision("r2_24")`
 
@@
 
-\WorkInProgress
-
 1. We have added a table to summarise the effects (including some information on the reviews these effects were drawn from) as Supplementary File 9.
@@
 3. While we agree that this information might be useful for some readers, we found that this made the table difficult to read.
-Most reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specifc outcome, exposure, age group, and moderator), the table became overwhelming.
+Most reviews presented multiple effect sizes, and once the information to describe each effect was added (e.g., the specific outcome, exposure, age group, and moderator), the table became overwhelming.
 All of the effect sizes (in their original, converted, and recalculated forms) are available in the supplementary material.
@@
 
-1. We agree that the our reporting of the method could have been clearer, and have revised the text in this section to more clearly explain our method.
-We disagree with the reviewer that the method was "subjective".
+1. We agree that our reporting of the method could have been clearer, and have revised the text in this section to more clearly explain our method.
+We designed this method to make it as objective as possible.
 If we had multiple effects for the same exposure/outcome combination, and which had the same sample age restrictions and the same study design restrictions, we chose the one with the largest sample size.
-We can certainly see how others might use a different method for eliminating duplicate effects (and we state this in the discussion section), but it is difficult to see how using the sample size could be considered "subjective".
+We can certainly see how others might use a different method for eliminating duplicate effects (and we state this in the discussion section), and we tested whether those methods would have led to different included reviews.
 
 `r get_revision("r3_8")`
+
+`r get_revision("r2_24")`
 
@@
 
-3. We understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
-We chose Pearson's *r* as we wanted to focus not on the precise size of the association, but instead on the *direction* and the *magnitude*.
-We think it is worth considering the counterfactual to our approach: had we not converted effect sizes to a common metric readers would likely still make comparisons, but these would be subjective.
-We agree that readers should interpret the effect sizes carefully, and have included text to this effect in the *Discussion*:
+3. We understand the reviewer's concerns regarding the conversions of the effect sizes.
+We appreciate that making conversions between effect sizes relies upon some assumptions.
+We made the decision what it was better to include these studies rather than omit them, and better to convert the effects rather than presenting different tables for each effect size.
+Still, we agree that readers should interpret the effect sizes carefully, and have included text to this effect in the *Discussion*:
 
@@
 
-We are unclear what the reviewer is referring to here, although we think many of the concerns were addressed in \comment{r2_29}.
-We feel that a qualitative synthesis of more than 200 effect sizes is outside the scope of this paper.
+We agree that the differences between the effects at different ages are important nuances.
+We altered the analytical plan to make it more credible and reliable, but also want to make it so researchers can explore findings that we are less confident in
+While we could offer a narrative synthesis of the 200+ effect sizes that did not meet our credibility criteria, we judged this was beyond the scope of this paper.
+Doing so would involve some filtering and judgement, exacerbating the selection bias the reviewer points to.
+As a result, we have presented those findings in supplementary materials for researchers and practitioners to explore the nuances relevant to them
 
@@
 
-Even within recreational screen time, our findings do not support guidelines which focus just on minimisation. 
+We agree both guidelines focus on merely reducing recreational screen time and have removed "in all instances".
+Even within recreational screen time, however, our findings do not support guidelines which focus just on minimisation. 
 Video games, for example, are a recreational form of screen time which appear to have some benefits for educational and cognitive outcomes.
@@
 Reporting standards differ by discipline, and several of the items in AMSTAR-2 are typically only reported in medical fields.
-While these should maybe be reported in all fields, we felt that the NHLBI was a more appropriate standard for our review.
+AMSTAR-2 and NHLBI overlap on many items, and as AMSTAR-2 taks 20-30min per review we didn't feel that the extra length produced substantially more value.
+We felt that the NHLBI was the appropriate standard for our review.
 

### 2023-03-13 reports/revision_letter.Rmd
Revise to match NHB checklist

@@
 If the results are not collated into a single place, it is difficult to see how the field will begin to progress away from 'screen time' as a concept. 
-We have included this in the *Implications for Future Research* section:
+We have included this in the *Discussion* section:
 
 `r get_revision("r1_1")`
+
+We also note that in reviewing the manuscript, we sometimes used the term 'screen time' and in other places used 'screen use'.
+For the sake of being consistent, we have changed these to all be 'screen use' (which we think is more consistent with what is meant), and we also use this term for the rest of this letter.
+This is just a stylistic change---we don't think that changing between 'time' and 'use' is what the reviewer means.
 
@@
 It is not that the evidence is lacking, per se, but that our *understanding* is weak.
-Our understanding is lacking partly because benefits of screen time (as seen in some educational literature) and reviewed separately from harms.
+Our understanding is lacking partly because benefits of screen use (as seen in some educational literature) and reviewed separately from harms.
 Our review aims to address this (see also Reviewer 1, \comment{r1_2}).
-We think synthesising the trade-offs in one review can help us understand when screen time might be associated with good/poor outcomes, helping to better understand why.
+We think synthesising the trade-offs in one review can help us understand when screen use might be associated with good/poor outcomes, helping to better understand why.
 
@@
 
-We appreciate it is not a direct contrast to compare overall limits of screen time against deleterious effects of screen time over 3-4 hours. As a result, we have removed the words 'in contrast':
+We appreciate it is not a direct contrast to compare overall limits of screen use against deleterious effects of screen use over 3-4 hours. As a result, we have removed the words 'in contrast':
 
@@
 
-We agree that the relationship between some outcomes and screen time may not always be linear.
+We agree that the relationship between some outcomes and screen use may not always be linear.
 However, our previous research (e.g., 10.1186/s12966-019-0881-7) looking at a range of health and education outcomes in a high-quality dataset found little evidence for curvilinear relationships.
@@
 
-We agree both guidelines focus on merely reducing recreational screen time and have removed "in all instances".
-Even within recreational screen time, however, our findings do not support guidelines which focus just on minimisation. 
-Video games, for example, are a recreational form of screen time which appear to have some benefits for educational and cognitive outcomes.
+We agree both guidelines focus on merely reducing recreational screen use and have removed "in all instances".
+Even within recreational screen use, however, our findings do not support guidelines which focus just on minimisation. 
+Video games, for example, are a recreational form of screen use which appear to have some benefits for educational and cognitive outcomes.
 

### 2023-03-13 reports/manuscript.Rmd
Address coauthor comments (#28)
* Address coauthor comments

* Revise to match NHB checklist

@@
 ---
-title             : "Benefits and risks associated with children's and adolescents' interactions with electronic screens: An umbrella review"
+title             : "An umbrella review of the benefits and risks associated with youths' interactions with electronic screens"
 shorttitle        : "Benefits and risks of electronic screens"
@@
 author: 
-  - name          : "Taren Sanders"
+  - name          : "Taren Sanders*"
     affiliation   : "1"
@@
     email         : "Taren.Sanders@acu.edu.au"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Data curation
-      - Writing - Original Draft
   - name          : "Michael Noetel"
     affiliation   : "2"
-    role:
-      - Conceptualization
-      - Writing - Original Draft
   - name          : "Philip Parker"
     affiliation   : "1"
-    role:
-      - Conceptualization
-      - Writing - Original Draft
   - name          : "Borja Del Pozo Cruz"
     affiliation   : "3"
-    role:
-      - Writing - Review & Editing
   - name          : "Stuart Biddle"
     affiliation   : "4"
-    role:
-      - Writing - Review & Editing
   - name          : "Rimante Ronto"
     affiliation   : "5"
-    role:
-      - Writing - Review & Editing
   - name          : "Ryan Hulteen"
     affiliation   : "6"
-    role:
-      - Writing - Review & Editing
   - name          : "Rhiannon Parker"
     affiliation   : "7"
-    role:
-      - Writing - Review & Editing
   - name          : "George Thomas"
     affiliation   : "8"
-    role:
-      - Writing - Review & Editing
   - name          : "Katrien De Cocker"
     affiliation   : "9"
-    role:
-      - Writing - Review & Editing
   - name          : "Jo Salmon"
     affiliation   : "10"
-    role:
-      - Writing - Review & Editing
   - name          : "Kylie Hesketh"
     affiliation   : "10"
-    role:
-      - Writing - Review & Editing
   - name          : "Nicole Weeks"
     affiliation   : "1"
-    role:
-      - Writing - Review & Editing
   - name          : "Hugh Arnott"
     affiliation   : "1"
-    role:
-      - Writing - Review & Editing
   - name          : "Emma Devine"
     affiliation   : "11"
-    role:
-      - Writing - Review & Editing
   - name          : "Roberta Vasconcellos"
     affiliation   : "1"
-    role:
-      - Writing - Review & Editing
   - name          : "Rebecca Pagano"
     affiliation   : "12"
-    role:
-      - Writing - Review & Editing
   - name          : "Jamie Sherson"
     affiliation   : "12"
-    role:
-      - Writing - Review & Editing
   - name          : "James Conigrave"
     affiliation   : "1"
-    role:
-      - Writing - Review & Editing
   - name          : "Chris Lonsdale"
     affiliation   : "1"
-    role:
-      - Conceptualization
-      - Writing - Original Draft
-      - Project Administration
 
@@
   - id            : "1"
-    institution   : "Institute for Positive Psychology and Education, Australian Catholic University"
+    institution   : "Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia"
   - id            : "2"
-    institution   : "School of Health and Behavioural Sciences, Australian Catholic University"
+    institution   : "School of Psychology, University of Queensland, Brisbane, Australia"
   - id            : "3"
-    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark"
+    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark"
   - id            : "4"
-    institution   : "Centre for Health Research, University of Southern Queensland"
+    institution   : "Centre for Health Research, University of Southern Queensland, Springfield, Australia"
   - id            : "5"
-    institution   : "Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University"
+    institution   : "Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia"
   - id            : "6"
-    institution   : "School of Kinesiology, Louisiana State University"
+    institution   : "School of Kinesiology, Louisiana State University, Baton Rouge, USA"
   - id            : "7"
-    institution   : "School of Medicine and Health, Sydney University"
+    institution   : "School of Medicine and Health, Sydney University, Sydney, Australia"
   - id            : "8"
-    institution   : "Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland"
+    institution   : "Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia"
   - id            : "9"
-    institution   : "Department of Movement and Sport Science, Ghent University"
+    institution   : "Department of Movement and Sport Science, Ghent University, Ghent, Belgium"
   - id            : "10"
-    institution   : "Institute for Physical Activity and Nutrition, Deakin University"
+    institution   : "Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia"
   - id            : "11"
-    institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney"
+    institution   : "The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia"
   - id            : "12"
-    institution   : "School of Education, Australian Catholic University"
+    institution   : "School of Education, Australian Catholic University, North Sydney, Australia"
 
 abstract: |
-  Children's engagement in screen time is a complex issue.
-  While some forms of screen time have consistently been associated with harm, others have been associated with gains, making it difficult to weigh the risks and benefits of use.
-  In this umbrella review, we systematically collate and examined meta-analyses examining the effects of screen use on children and youth.
-  We converted results onto a common metric (Pearson's r) to make comparisons simple, and where possible we reanalysed study-level data to standardise the approach across meta-analyses.
-  We identified `r targets::tar_read(manuscript_info)$prisma$included` meta-analyses, and extracted `r targets::tar_read(manuscript_info)$unique_combos` unique combinations of exposures and outcomes.
-  If duplicate effect sizes from the same combination of exposure and outcome were drawn from different age groups or study designs we retained them, otherwise we chose the effect size with the largest total sample size.
-  We removed effect sizes that could not be harmonised, resulting in `r targets::tar_read(manuscript_info)$unique_effects` effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` reviews.
-  These effects represent the findings of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants.
-  When focusing on the meta-analyses with the most statistically robust evidence, we found that general screen use (when content was not indicated), was associated with potential harm on learning, literacy, body composition, and depression.
-  Likewise, social media was consistently associated with risks to health, with no identified benefits.
-  However, we also found that these harms could often be mitigated by certain kinds of content (e.g., educational), or by modifying the context (e.g., co-viewing with a parent).
-  In summary, our findings point to the need for careful and nuanced guidelines that support parents to make the best decisions for their children.
+  The influence of electronic screens on children and adolescents’ health and education is not well understood.
+  In this review, we harmonised `r targets::tar_read(manuscript_info)$unique_effects` effects representing unique combinations of exposures and outcomes from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants).
+  Some types of screen use, such as social media, were consistently correlated with risks to health.
+  However, other forms of screen use showed associations with benefits.
+  For example, experimental evidence showed that video games improve aspects of cognitive function.
+  Some types of screen use have complex associations with outcomes.
+  For example, general screen use (i.e., content not indicated) showed correlations with harm for body composition, depression, and learning.
+  However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
+  More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
 
-keywords          : "screen time; youth; health; education"
 wordcount         : "`r wordcountaddin::word_count(here::here('reports', 'manuscript.Rmd'))`"
@@
 
-floatsintext      : yes
+floatsintext      : no
 figurelist        : no
@@
 
-# Summary
-
-Children's engagement in screen time is a complex issue.
-Parents, policymakers, and educators need to weigh the risks that sedentary use of screens present alongside the potential benefits for learning and social connectedness.
-The lack of comprehensive evidence hampers efforts to make an informed decision.
-As a Lancet editorial [@thelancetSocialMediaScreen2019] suggested, "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."
-In this study, we systematically harmonise data from existing meta-analyses of screen time on a range of outcomes, including health, education, and psychology, and identify the most statistically robust relationships.
-We show that some forms of screen time---such as social media---show consistent evidence of harm for children, with no clear evidence of a benefit.
-Other relationships are more complex.
-Video games, for example, are associated with poorer body composition and learning outcomes.
-However, video games for a specific educational purpose (such as numeracy) are associated with improvements in that subject area.
-Caregivers must therefore weigh the health risk against the educational benefit.
-The findings of this study provide parents and other caregivers with the information to make these informed decisions.
-
-\newpage
-
-# Background
+# Introduction
 
@@
 
-Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen use (e.g., television, mobile phones, and computers) [@wartellaChildrenComputersNew2000].
-Excessive screen time use is the number one concern parents in Western countries have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top].
+Today, the same arguments that were once levelled against reading, schooling, and radio are being made about screen use (e.g., television, mobile phones, and computers) [@wartellaChildrenComputersNew2000].
+Excessive screen use is the number one concern parents in Western countries have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top].
 Yet, the evidence to support parents' concerns is inadequate.
@@
 Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media [@przybylskiLargeScaleTestGoldilocks2017].
-Indeed, educational screen time is positively related to educational outcomes [@sandersTypeScreenTime2019].
-This evidence has led some researchers to argue that a more nuanced approach to screen time guidelines is required [@kayeConceptualMethodologicalMayhem2020].
+Indeed, educational screen use is positively related to educational outcomes [@sandersTypeScreenTime2019].
+This evidence has led some researchers to argue that a more nuanced approach to screen use guidelines is required [@kayeConceptualMethodologicalMayhem2020].
 </span>
@@
 <span id = "r2_9">
-While there have been other overviews of reviews on screen time, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
+While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
 <span id = "r1_2">
@@
 
+# Results
+
+The searches yielded `r format(manuscript_info$prisma$search, big.mark=",")` results, of which `r format(manuscript_info$prisma$duplicates, big.mark=",")` were duplicates.
+After screening titles and abstracts, we assessed `r format(manuscript_info$prisma$full_text, big.mark=",")` full-texts for inclusion.
+Of those, `r manuscript_info$prisma$included` met the inclusion criteria and we extracted the data from all of these meta-analyses.
+Figure 1 presents the full results of the selection process.
+
+The most frequently reported exposures were `r manuscript_info$freq_exposures`.
+Supplementary File 5 provides a list of all exposures identified.
+The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
+<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
+Full characteristics of the included studies are provided in Table 1.</span>
+<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
+These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies, involving `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
+The characteristics of the included effects are available in Supplementary File 9.
+
+**TABLE 1**
+
+The quality of the included meta-analyses was mixed (see Table 1).
+Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
+Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
+Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
+A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
+Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.
+
+There were `r manuscript_info$edu$n_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
+We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
+Effects not meeting one or more of these standards are presented in Supplementary File 6.
+The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure 2.
+These `r manuscript_info$edu$n_certain` effects came from `r manuscript_info$edu$n_unique` meta-analytic reviews analysing data from `r manuscript_info$edu$summary$studies_n` empirical studies with `r format(manuscript_info$edu$summary$total_n, big.mark=",")` individual participants.
+
+Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
+E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
+General screen use was negatively associated with literacy outcomes.
+However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
+Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
+
+As shown in Figure 2, most of the credible results (`r manuscript_info$edu$n_p999` of `r manuscript_info$edu$n_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
+The remaining `r xfun::numbers_to_words(manuscript_info$edu$n_p95)` associations were significant at the 95% confidence level (weak evidence).
+All credible effects related to education outcomes were small-to-moderate.
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
+The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
+Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).
+
+We identified `r manuscript_info$health$n_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
+We removed `r manuscript_info$health$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$health$n_samplesize` effects with samples < 1,000, and `r manuscript_info$health$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
+No remaining studies showed evidence of excessive significance.
+Effects not meeting one or more of these standards are presented in Supplementary File 7.
+The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
+These `r manuscript_info$health$n_certain` effects came from `r manuscript_info$health$n_unique` meta-analytic reviews analysing data from `r manuscript_info$health$summary$studies_n` empirical studies with `r format(manuscript_info$health$summary$total_n, big.mark=",")` individual participants.
+
+Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
+Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
+General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
+All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
+Screen-based interventions which target health behaviours appeared mostly effective.
+
+Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
+However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
+Additionally, most effects were small, with the association between screen use and sleep duration the largest at $r = -0.37$ ($k = 10, N = 56,720$).
+Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.
+
+# Discussion
+
+The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad range of outcomes.
+We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
+However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.
+
+As an example, consider children watching television programs---an often cited form of screen use harm.
+We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
+However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
+Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
+Similar nuanced findings were observed for video games.
+The credible evidence we identified showed that video game playing was associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
+However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 & 7) therefore this hypothesis could not be addressed.
+
+Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
+Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
+These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression [@yoonSocialNetworkSite2019;@vahediAssociationSelfreportedDepressive2021].
+Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls [@seetharamanFacebookKnowsInstagram2021].
+
+One category of exposure appeared to be consistently associated with benefits: screen-based interventions designed to promote learning or health behaviours.
+This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
+Rather, it reinforces that the content of the screen use may be the most important aspect.
+The way that a young person interacts with digital screens may also be important.
+We found evidence that touch screens had strong evidence for benefits on learning [@xieCanTouchscreenDevices2018], as did augmented reality [@tekedereExaminingEffectivenessAugmented2016].
+
+<span id = "r1_5">
+Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
+If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
+For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
+Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups [@marshallRelationshipsMediaUse2004].
+Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
+However, in the absence of this work, our study has shown how children are affected by screens in general.
+</span>
+
+Among studies that met our criteria for statistical certainty heterogeneity was high, with almost all effects having $I^2 > 50\%$.
+Much of this heterogeneity is likely explained by differences in measures across pooled studies, or in some cases, the generic nature of some of the exposures.
+For example, "TV programs and movies" covers a substantial range of content, which may explain the heterogeneous association with education outcomes.
+
+Our results have several implications for policy and practice.
+Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue [@elsonPolicyStatementsMedia2019;@ashtonScreenTimeChildren2019;@royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019].
+Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
+Many current guidelines simplify this complex relationship as something that should be minimised [@australiangovernmentPhysicalActivityExercise2021;@whoGuidelinesPhysicalActivity2019].
+We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.
+
+<span id = "r2_7">
+In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce 'screen use', and instead focusing on the type of screen use.
+For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
+</span>
+
+Our results also have implications for future research.
+Screen use research is extensive, varied, and rapidly growing.
+Reviews tended to be general (e.g., all screen use) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
+<span id = "r2_29">Fewer than 20\% of the effects identified met our criteria for statistical credibility.
+Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
+When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
+It seems that much of the current screen use research is small in scale, and there is a need for larger, high-quality studies.<span>
+
+<span id = "r1_1">Our results highlight the need for the field to more carefully consider if the term 'screen use' remains appropriate for providing advice to parents.
+Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
+Rather than suggesting parents limit 'screen use', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.</span>
+
+Screen use research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
+The vast majority of screen use research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen use, but may also be inaccurate.
+In one systematic review on screen use and sleep [@haleScreenTimeSleep2015], 66 of the 67 included studies used self-reported data for *both* the exposure and outcome variable.
+It has been established that self-reported screen use data has questionable validity.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
+Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity [@byrneMeasurementScreenTime2021].
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras [@smithFeasibilityAutomatedCameras2019] or device-based loggers [@rydingPassiveObjectiveMeasures2020]---these are still not widely adopted.
+It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
+
+There were a number of strengths and limitations to our work.
+Our primary goal for this umbrella review was to provide a high-level synthesis of screen use research, by examining a range of exposures and the associations with a broad scope of outcomes.
+Our results represent the findings from `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
+To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
+
+Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
+For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
+As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
+<span id = "r2_24">In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
+Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (*k*) or the most recent review by publication year.
+However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.</span>
+
+<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
+These likely depend on the specific exposure and outcome.
+It is tempting to draw inferences that the associations are due to screen use causing these outcomes, but we cannot rule out reverse causality, a third variable, or some combination of influences.
+Many of the individual reviews go into more detail about the strength of the evidence for causal associations, but those judgements were difficult to synthesise across more than 200 reviews.
+Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
+
+<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
+Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].
+Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
+Care is needed, therefore, when interpreting the effect sizes.</span>
+<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
+While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>
+
+Screen use is a topic of significant interest, as shown by the wide variety of academic domains involved, parents' concerns, and the growing pervasiveness into society.
+Our findings showed that the influence of screen use can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
+The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen use, with less emphasis on measures that aggregate screen use and instead focus on the content, context, and environment in which the exposure occurs.
+
 # Methods
 
-We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051).
+We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
 We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines [@pagePRISMA2020Statement2020].
@@
 
-*Population*: 
+Population: 
 To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
@@
 
-*Exposure*: 
+Exposure: 
 We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computers, tablets, and mobile phones.
@@
 
-*Publications*: 
+Publications: 
 We included meta-analyses (or meta-regressions) of quantitative evidence.
@@
 
-*Statistical Credibility*.
+Statistical Credibility:
 We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
@@
 
-*Consistency of Effect within the Population*.
+Consistency of Effect within the Population:
 We also examined the consistency of the effect size using the $I^2$ measure.
@@
 
-*Direction of Effect*.
+Direction of Effect:
 Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
@@
 We altered our evidence assessment plan when we identified that, as written, it could not classify precise evidence of null effects (i.e., from large reviews with low heterogeneity and low risk of publication bias) as 'credible' because a highly-significant *P*-value was a criteria.
-This would have significantly harmed knowledge gained from our review as it would have restricted our ability to show where the empirical evidence strongly indicated that there was no association between screen time and a given outcome.
+This would have significantly harmed knowledge gained from our review as it would have restricted our ability to show where the empirical evidence strongly indicated that there was no association between screen use and a given outcome.
 
-# Results
+## Data availability statement
 
-### Search Results
+All data for this review are available from the authors' GitHub repository (https://github.com/motivation-and-Behaviour/screen_umbrella) or from the Open Science Foundation (https://osf.io/3ubqp/).
 
-The searches yielded `r format(manuscript_info$prisma$search, big.mark=",")` results, of which `r format(manuscript_info$prisma$duplicates, big.mark=",")` were duplicates.
-After screening titles and abstracts, we assessed `r format(manuscript_info$prisma$full_text, big.mark=",")` full-texts for inclusion.
-Of those, `r manuscript_info$prisma$included` met the inclusion criteria and we extracted the data from all of these meta-analyses.
-Figure \@ref(fig:prisma) presents the full results of the selection process.
+## Code availability statement
 
-```{r prisma, fig.cap="PRISMA Diagram"}
-knitr::include_graphics("../figures/PRISMA Diagram.pdf", error = FALSE)
-```
-
-The most frequently reported exposures were `r manuscript_info$freq_exposures`.
-Supplementary File 5 provides a list of all exposures identified.
-The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
-<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.</span>
-<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
-These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
-The characteristics of the included effects are available in Supplementary File 9.
-
-**TABLE 1**
-
-The quality of the included meta-analyses was mixed (see Table 1).
-Most assessed heterogeneity `r manuscript_info$qual$low_hetero`, reported the characteristics of the included studies `r manuscript_info$qual$low_char`, and used a comprehensive and systematic search strategy `r manuscript_info$qual$low_search`.
-Most reviews did not clearly report if their eligibility criteria were predefined `r manuscript_info$qual$unclear_elig`.
-Many papers also did not complete dual independent screening of abstracts and full text `r manuscript_info$qual$high_dualscreen` or did not clearly report the method of screening `r manuscript_info$qual$unclear_dualscreen`.
-A similar trend was observed for dual independent quality assessment `r manuscript_info$qual$dualqualstr`.
-Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.
-
-### Education Outcomes
-
-There were `r manuscript_info$edu$n_effect` unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
-We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in Supplementary File 6.
-The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure \@ref(fig:eduplot).
-These `r manuscript_info$edu$n_certain` effects came from `r manuscript_info$edu$n_unique` meta-analytic reviews analysing data from `r manuscript_info$edu$summary$studies_n` empirical studies with `r format(manuscript_info$edu$summary$total_n, big.mark=",")` individual participants.
-
-```{r eduplot, fig.width=edu_certain_params$dims[[1]], fig.height=edu_certain_params$dims[[2]], fig.cap="Education outcomes"}
-plot_edu_certain
-```
-
-Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
-E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
-General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
-
-As shown in Figure \@ref(fig:eduplot), most of the credible results (`r manuscript_info$edu$n_p999` of `r manuscript_info$edu$n_certain` effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
-The remaining `r xfun::numbers_to_words(manuscript_info$edu$n_p95)` associations were significant at the 95% confidence level (weak evidence).
-All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
-The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
-Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).
-
-### Health and Health-related Behaviours
-
-We identified `r manuscript_info$health$n_effect` unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-We removed `r manuscript_info$health$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$health$n_samplesize` effects with samples < 1,000, and `r manuscript_info$health$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in Supplementary File 7.
-The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure \@ref(fig:healthplot)).
-These `r manuscript_info$health$n_certain` effects came from `r manuscript_info$health$n_unique` meta-analytic reviews analysing data from `r manuscript_info$health$summary$studies_n` empirical studies with `r format(manuscript_info$health$summary$total_n, big.mark=",")` individual participants.
-
-```{r healthplot, fig.width=nonedu_certain_params$dims[[1]], fig.height=nonedu_certain_params$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
-plot_nonedu_certain
-```
-
-Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
-General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
-Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
-All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
-Screen-based interventions which target health behaviours appeared mostly effective.
-
-Across the health outcomes, most (`r manuscript_info$health$n_p999` of `r manuscript_info$health$n_certain`) effects were statistically significant at the 99.9\% confidence interval level, with the remaining `r xfun::numbers_to_words(manuscript_info$health$n_p95)` significant at 95\% confidence.
-However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
-Additionally, most effects were small, with the association between screen use and sleep duration the largest at $r = -0.37$ ($k = 10, N = 56,720$).
-Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.
-
-# Discussion
-
-The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad range of outcomes.
-We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
-However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.
-
-As an example, consider children watching television programs---an often cited form of screen time harm.
-We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
-However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
-Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
-Similar nuanced findings were observed for video games.
-The credible evidence we identified showed that video game playing was associated with poorer body composition and learning [@adelantado-renauAssociationScreenMedia2019;@poorolajalBehavioralFactorsInfluencing2020].
-However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 & 7) therefore this hypothesis could not be addressed.
-
-Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
-Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
-These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression [@yoonSocialNetworkSite2019;@vahediAssociationSelfreportedDepressive2021].
-Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls [@seetharamanFacebookKnowsInstagram2021].
-
-One category of exposure appeared to be consistently associated with benefits: screen-based interventions designed to promote learning or health behaviours.
-This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
-Rather, it reinforces that the content of the screen time may be the most important aspect.
-The way that a young person interacts with digital screens may also be important.
-We found evidence that touch screens had strong evidence for benefits on learning [@xieCanTouchscreenDevices2018], as did augmented reality [@tekedereExaminingEffectivenessAugmented2016].
-
-<span id = "r1_5">
-Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
-For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
-Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups [@marshallRelationshipsMediaUse2004].
-Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
-However, in the absence of this work, our study has shown how children are affected by screens in general.
-</span>
-
-Among studies that met our criteria for statistical certainty heterogeneity was high, with almost all effects having $I^2 > 50\%$.
-Much of this heterogeneity is likely explained by differences in measures across pooled studies, or in some cases, the generic nature of some of the exposures.
-For example, "TV programs and movies" covers a substantial range of content, which may explain the heterogeneous association with education outcomes.
-
-## Implications for Policy and Practice
-
-Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue [@elsonPolicyStatementsMedia2019;@ashtonScreenTimeChildren2019;@royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019].
-Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
-Many current guidelines simplify this complex relationship as something that should be minimised [@australiangovernmentPhysicalActivityExercise2021;@whoGuidelinesPhysicalActivity2019].
-We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.
-
-<span id = "r2_7">
-In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce 'screen time', and instead focusing on the type of screen time.
-For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
-Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
-</span>
-
-## Implications for Future Research
-
-Screen use research is extensive, varied, and rapidly growing.
-Reviews tended to be general (e.g., all screen time) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
-<span id = "r2_29">Fewer than 20\% of the effects identified met our criteria for statistical credibility.
-Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
-Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines [@pagePRISMA2020Statement2020].
-When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
-It seems that much of the current screen time research is small in scale, and there is a need for larger, high-quality studies.<span>
-
-<span id = "r1_1">Our results highlight the need for the field to more carefully consider if the term 'screen time' remains appropriate for providing advice to parents.
-Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
-Rather than suggesting parents limit 'screen time', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.</span>
-
-Screen time research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
-The vast majority of screen time research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen time, but may also be inaccurate.
-In one systematic review on screen time and sleep [@haleScreenTimeSleep2015], 66 of the 67 included studies used self-reported data for *both* the exposure and outcome variable.
-It has been established that self-reported screen time data has questionable validity.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al [@parrySystematicReviewMetaanalysis2021] found that the measures were only moderately correlated ($r = 0.38$), with self-reported problematic usage fairing worse ($r = 0.25$).
-Indeed, of 622 studies which measured the screen time of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity [@byrneMeasurementScreenTime2021].
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras [@smithFeasibilityAutomatedCameras2019] or device-based loggers [@rydingPassiveObjectiveMeasures2020]---these are still not widely adopted.
-It may be that the field of screen time research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
-
-## Strengths and Limitations
-
-Our primary goal for this umbrella review was to provide a high-level synthesis of screen time research, by examining a range of exposures and the associations with a broad scope of outcomes.
-Our results represent the findings from `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
-To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
-
-Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
-For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE [@guyattGRADEGuidelinesIntroduction2011]).
-As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
-<span id = "r2_24">In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
-Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (*k*) or the most recent review by publication year.
-However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.</span>
-
-<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
-These likely depend on the specific exposure and outcome.
-It is tempting for people to draw inferences that the associations are due to screen time causing these outcomes, but we cannot rule out reverse causality, a third variable, or some combination of influences.
-Many of the individual reviews go into more detail about the strength of the evidence for causal associations, but those judgements were difficult to synthesise across more than 200 reviews.
-Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
-
-<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
-Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
-However, others have identified instances where non-linear relationships exist, especially for very high levels of screen time [@twengeMoreTimeTechnology2019; @przybylskiLargeScaleTestGoldilocks2017; @kellySocialMediaUse2018].
-Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
-Care is needed, therefore, when interpreting the effect sizes.</span>
-<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
-While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>
-
-## Conclusions
-
-Screen time is a topic of significant interest, as shown by the wide variety of academic domains involved, parents' concerns, and the growing pervasiveness into society.
-Our findings showed that the influence of screen time can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
-The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
-However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen time, with less emphasis on measures that aggregate screen time and instead focus on the content, context, and environment in which the exposure occurs.
+All code used in these analyses are available on the authors' GitHub repository (https://github.com/motivation-and-Behaviour/screen_umbrella).
 
@@
 <div id = "refs"></div>
+
+\newpage
+
+# Acknowledgements
+
+The authors received no specific funding for this work.
+
+# Author contributions
+
+TS, MN, PP, and CL conceptualised the review and drafted the manuscript.
+TS, MN, and PP conducted the analyses.
+All authors contributed to data extraction, interpretation, and editing of the manuscript.
+
+# Competing interests
+
+The authors declare no conflicts of interest.
+
+# Figure legends
+
+*Figure 1: PRISMA Diagram.*
+
+*Figure 2: Education outcomes.
+Results for `r manuscript_info$edu$n_certain` unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations with both 95% and 99.9% confidence intervals.*
+
+*Figure 3: Health and health-related behaviour outcomes.
+Results for `r manuscript_info$health$n_certain` unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations with both 95% and 99.9% confidence intervals.*
+
+# Tables

### 2023-03-13 R/clean_effects.R

@@ -121,7 +121,11 @@ clean_effects <- function(
       by = "effect_size_id"
     ) %>%
     left_join(effects_use, by = "effect_size_id") %>%
-    mutate(use_effect = if_else(is.na(use_effect), FALSE, use_effect), study_level_available = if_else(is.na(study_level_available), FALSE, study_level_available))
+    mutate(
+      use_effect = if_else(is.na(use_effect), FALSE, use_effect),
+      study_level_available =
+        if_else(is.na(study_level_available), FALSE, study_level_available)
+    )
 
   effects_clean_renamed <-
     effects_clean_use %>%

### 2023-03-13 README.Rmd
Revisions for Nature Human Behaviour (#27)

@@
 1. Open directory and run `renv::restore()` to download/update the required packages.
-1. You must run `googledrive::drive_auth()` and `googlesheets4::gs4_auth()` before running targets in order the cache your oAuth token.
 1. To build the project, run `targets::tar_make()`.
-
-### Notes
-
-You should be able to run the analysis to examine the reproducability.
-However, some of the pipeline targets also write data to Google Sheets, which will cause these targets to fail.
-If you are not a project contributor, you may need to manually exclude these targets.
-
-You can also run the build in parallel using `targets::tar_make_clustermq(workers=<num_workers>)`. This can be faster, but not always. There's usually no benefit beyond 3 or 4 workers.
 

### 2023-03-13 reports/manuscript.tex
Revisions for Nature Human Behaviour (#27)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5394}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{colortbl}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

\shorttitle{Benefits and risks of electronic screens}

\authornote{

Correspondence concerning this article should be addressed to Taren Sanders*, 33 Berry St, North Sydney, NSW, Australia. E-mail: \href{mailto:Taren.Sanders@acu.edu.au}{\nolinkurl{Taren.Sanders@acu.edu.au}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} School of Medicine and Health, Sydney University, Sydney, Australia\\\textsuperscript{8} Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia}

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this review, we harmonised 255 effects representing unique combinations of exposures and outcomes from 103 meta-analyses (2,496 primary studies; 2,026,054 participants).
Some types of screen use, such as social media, were consistently correlated with risks to health.
However, other forms of screen use showed associations with benefits.
For example, experimental evidence showed that video games improve aspects of cognitive function.
Some types of screen use have complex associations with outcomes.
For example, general screen use (i.e., content not indicated) showed correlations with harm for body composition, depression, and learning.
However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In the 16th century, hysteria reigned around a new technology that threatened to be ``confusing and harmful'' to the mind.
The cause of such concern?
The widespread availability of books brought about by the invention of the printing press.\textsuperscript{1}
In the early 19th century, concerns about schooling ``exhausting the children's brains'' followed, with the medical community accepting that excessive study could be a cause of madness.\textsuperscript{2}
By the 20th century, the invention of the radio was accompanied by assertions that it would distract children from their reading (which by this point was no longer considered confusing and harmful) leading to impaired learning.\textsuperscript{3}

Today, the same arguments that were once levelled against reading, schooling, and radio are being made about screen use (e.g., television, mobile phones, and computers).\textsuperscript{4}
Excessive screen use is the number one concern parents in Western countries have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity.\textsuperscript{5}
Yet, the evidence to support parents' concerns is inadequate.
A Lancet editorial\textsuperscript{6} suggested that, ``Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking.''

While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing,\textsuperscript{7,8} evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom™) remains less certain and, in some cases, may even be beneficial.\textsuperscript{9,10}
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is ``a defining question of our age''.\textsuperscript{11}
With concerns over the impact of screen use including education, health, social development, and psychological well-being, an overview that identifies potential benefits and risks is needed.

Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation\textsuperscript{12} and numerous government agencies\textsuperscript{13,14} and statements by expert groups\textsuperscript{15} have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
\protect\hypertarget{r2_8}{}{For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
However, recent evidence suggests that longer exposures may not have adverse effects on children's behaviour or mental health---and might, in fact, benefit their well-being---as long as exposure does not reach extreme levels (e.g., 7 hours per day)\textsuperscript{16}.
Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media.\textsuperscript{17}
Indeed, educational screen use is positively related to educational outcomes.\textsuperscript{18}
This evidence has led some researchers to argue that a more nuanced approach to screen use guidelines is required.\textsuperscript{19}
}

In 2016, the American Academy of Pediatrics used a narrative review to examine the benefits and risks of children and adolescents' electronic media\textsuperscript{20} as a basis for updating their guidelines about screen use.\textsuperscript{15}
Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
\protect\hypertarget{r2_9}{}{
While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health\textsuperscript{21}), focus on a particular exposure (e.g., social media\textsuperscript{22,23}) or provide only a narrative summary of the literature.\textsuperscript{24}
\protect\hypertarget{r1_2}{}{
Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
For example, prohibiting screen use might reduce exposure to advertising but may also thwart learning opportunities from interactive educational tools. Reviews on either of these exposures or outcomes would likely miss being able to quantify these trade-offs.
Overviews are one method of evidence synthesis that helps address these trade-offs, by providing `user-friendly' summaries of a field of research.\textsuperscript{25}
These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.
By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.}}

In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
\protect\hypertarget{r2_6}{}{This review synthesises evidence on any outcome of electronic media exposure.
We deliberately did not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.}

\newpage

\hypertarget{results}{%
\section{Results}\label{results}}

The searches yielded 50,649 results, of which 28,675 were duplicates.
After screening titles and abstracts, we assessed 2,557 full-texts for inclusion.
Of those, 218 met the inclusion criteria and we extracted the data from all of these meta-analyses.
Figure 1 presents the full results of the selection process.

The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
Supplementary File 5 provides a list of all exposures identified.
The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
\protect\hypertarget{r2_25}{}{Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
Full characteristics of the included studies are provided in Table 1.}
\protect\hypertarget{r2_23}{}{After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.}
These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
The characteristics of the included effects are available in Supplementary File 9.

\textbf{TABLE 1}

The quality of the included meta-analyses was mixed (see Table 1).
Most assessed heterogeneity (\emph{n} low risk = 94/103, 91\% of meta-analyses), reported the characteristics of the included studies (\emph{n} low risk = 87/103, 84\%), and used a comprehensive and systematic search strategy (\emph{n} low risk = 72/103, 70\%).
Most reviews did not clearly report if their eligibility criteria were predefined (\emph{n} unclear = 72/103, 70\%).
Many papers also did not complete dual independent screening of abstracts and full text (\emph{n} high risk = 20/103, 19\%) or did not clearly report the method of screening (\emph{n} unclear = 38/103, 37\%).
A similar trend was observed for dual independent quality assessment (\emph{n} high risk = 53/103, 51\%; n high risk = 19/103, 18\%).
Overall, only 7 meta-analyses were graded as low risk of bias on all criteria.

There were 89 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
We removed 28 effects that did not provide individual study-level data, 19 effects with samples \textless{} 1,000, and 19 effects with a significant Egger's test or insufficient studies to conduct the test.
Effects not meeting one or more of these standards are presented in Supplementary File 6.
The remaining 23 effects met our criteria for statistical credibility and are described in Figure 2.
These 23 effects came from 18 meta-analytic reviews analysing data from 338 empirical studies with 262,537 individual participants.

Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
General screen use was negatively associated with literacy outcomes.
However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.

As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
The remaining six associations were significant at the 95\% confidence level (weak evidence).
All credible effects related to education outcomes were small-to-moderate.
Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).

We identified 165 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed 41 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies showed evidence of excessive significance.
Effects not meeting one or more of these standards are presented in Supplementary File 7.
The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
These 21 effects came from 15 meta-analytic reviews analysing data from 344 empirical studies with 859,562 individual participants.

Digital advertising of unhealthy foods---both traditional advertising and video games developed by a brand for promotion---were associated with higher unhealthy food intake.
Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
Screen-based interventions which target health behaviours appeared mostly effective.

Across the health outcomes, most (14 of 21) effects were statistically significant at the 99.9\% confidence interval level, with the remaining four significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
Additionally, most effects were small, with the association between screen use and sleep duration the largest at \(r = -0.37\) (\(k = 10, N = 56,720\)).
Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The primary goal of this review was to provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes.
We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.

As an example, consider children watching television programs---an often cited form of screen use harm.
We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
Similar nuanced findings were observed for video games.
The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{27,29}
However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 \& 7) therefore this hypothesis could not be addressed.

Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.\textsuperscript{31}
These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression.\textsuperscript{32,33}
Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls.\textsuperscript{34}

One category of exposure appeared to be consistently associated with benefits: screen-based interventions designed to promote learning or health behaviours.
This finding indicates that interventions can be effectively delivered using electronic media platforms, but does not necessarily indicate that screens are more effective than other methods (e.g., face-to-face, printed material).
Rather, it reinforces that the content of the screen use may be the most important aspect.
The way that a young person interacts with digital screens may also be important.
We found evidence that touch screens had strong evidence for benefits on learning,\textsuperscript{26} as did augmented reality.\textsuperscript{35}

\protect\hypertarget{r1_5}{}{
Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.\textsuperscript{36}
Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.\textsuperscript{37}
Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
However, in the absence of this work, our study has shown how children are affected by screens in general.
}

Among studies that met our criteria for statistical certainty heterogeneity was high, with almost all effects having \(I^2 > 50\%\).
Much of this heterogeneity is likely explained by differences in measures across pooled studies, or in some cases, the generic nature of some of the exposures.
For example, ``TV programs and movies'' covers a substantial range of content, which may explain the heterogeneous association with education outcomes.

Our results have several implications for policy and practice.
Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{38--40}
Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
Many current guidelines simplify this complex relationship as something that should be minimised.\textsuperscript{12,13}
We suggest that future guidelines need to embrace the complexity of the issue, to give parents and clinicians specific information to weigh the pros and cons of interactions with screens.

\protect\hypertarget{r2_7}{}{
In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
}

Our results also have implications for future research.
Screen use research is extensive, varied, and rapidly growing.
Reviews tended to be general (e.g., all screen use) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
Fewer than 20\% of the effects identified met our criteria for statistical credibility.
Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{41}
When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
It seems that much of the current screen use research is small in scale, and there is a need for larger, high-quality studies.

\protect\hypertarget{r1_1}{}{Our results highlight the need for the field to more carefully consider if the term `screen use' remains appropriate for providing advice to parents.
Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
Rather than suggesting parents limit `screen use', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.}

Screen use research has a well-established measurement problem, which impacts the individual studies of this umbrella review.
The vast majority of screen use research relies on self-reported data, which not only lacks the nuance required for understanding the effects of screen use, but may also be inaccurate.
In one systematic review on screen use and sleep,\textsuperscript{7} 66 of the 67 included studies used self-reported data for \emph{both} the exposure and outcome variable.
It has been established that self-reported screen use data has questionable validity.
In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{42} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{43}
While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers\textsuperscript{45}---these are still not widely adopted.
It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.

There were a number of strengths and limitations to our work.
Our primary goal for this umbrella review was to provide a high-level synthesis of screen use research, by examining a range of exposures and the associations with a broad scope of outcomes.
Our results represent the findings from 2,496 primary studies comprised of 2,026,054 participants.
To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{46}).
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
\protect\hypertarget{r2_24}{}{In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.}

\protect\hypertarget{r1_4}{}{Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
These likely depend on the specific exposure and outcome.
It is tempting to draw inferences that the associations are due to screen use causing these outcomes, but we cannot rule out reverse causality, a third variable, or some combination of influences.
Many of the individual reviews go into more detail about the strength of the evidence for causal associations, but those judgements were difficult to synthesise across more than 200 reviews.
Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.}

\protect\hypertarget{r2_16}{}{We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
Some previous research suggests that associations are typically linear.\textsuperscript{18}
However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,47,48}
Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
Care is needed, therefore, when interpreting the effect sizes.}
\protect\hypertarget{r3_2_2}{}{In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.}

Screen use is a topic of significant interest, as shown by the wide variety of academic domains involved, parents' concerns, and the growing pervasiveness into society.
Our findings showed that the influence of screen use can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen use, with less emphasis on measures that aggregate screen use and instead focus on the content, context, and environment in which the exposure occurs.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{41}

\hypertarget{eligibility-criteria}{%
\subsubsection{Eligibility criteria}\label{eligibility-criteria}}

Population:
To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
\protect\hypertarget{r3_5}{}{We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was \textless{} 18 years).
A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
We excluded meta-analyses that only contained evidence gathered from adults (age \textgreater18 years).}

Exposure:
We included meta-analyses examining all types of electronic screens including (but not necessarily limited to) television, gaming consoles, computers, tablets, and mobile phones.
We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content (e.g., television programs, movies, games), homework, and communication (e.g., video chat).
\protect\hypertarget{r3_6}{}{
In this review we focused on electronic media exposure that would be considered typical for children and youth.
That is, exposure that may occur in the home setting, or during schooling.
Consistent with this approach, we excluded technology-based treatments for clinical conditions.
}
However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning) for children and youth with a clinical condition.
For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.
However, a meta-analysis of interventions designed to \emph{treat} clinical depression delivered by a mobile phone app would be excluded.
\protect\hypertarget{r3_7}{}{
\emph{Outcomes}: We included all reported outcomes on benefits and risks.
}

Publications:
We included meta-analyses (or meta-regressions) of quantitative evidence.
To be included, meta-analyses needed to analyse data from studies identified in a systematic review.
For our purposes, a systematic review was one in which the authors attempted to acquire all the research evidence that pertained to their research question(s).
We excluded meta-analyses that did not attempt to summarise all the available evidence (e.g., a meta-analysis of all studies from one laboratory).
We included meta-analyses regardless of the study designs included in the review (e.g., laboratory-based experimental studies, randomised controlled trials, non-randomised controlled trials, longitudinal, cross-sectional, case studies), as long as the studies in the review collected quantitative evidence.
We excluded systematic reviews of qualitative evidence.
We did not formulate inclusion/exclusion criteria related to the risk of bias of the review.
We did, however, employ a risk of bias tool to help interpret the results.
We included full-text, peer-reviewed meta-analyses published or `in-press' in English.
We excluded conference abstracts and meta-analyses that were unpublished.

\hypertarget{information-sources}{%
\subsubsection{Information sources}\label{information-sources}}

We searched records contained in the following databases: Pubmed, MEDLINE, CINAHL, PsycINFO, SPORTDiscus, Education Source, Embase, Cochrane Library, Scopus, Web of Science, ProQuest Social Science Premium Collection, and ERIC.
\protect\hypertarget{r3_2}{}{We conducted an initial search on August 17, 2018 and refreshed the search on September 27, 2022.}
We searched reference lists of included papers in order to identify additional eligible meta-analyses.
We also searched PROSPERO to identify relevant protocols and contacted authors to determine if these reviews have been completed and published.

\hypertarget{search-strategy}{%
\subsubsection{Search strategy}\label{search-strategy}}

The search strategy associated with each of the 12 databases can be found in Supplementary File 1.
We hand searched reference lists from any relevant umbrella reviews to identify systematic meta-analyses that our search may have missed.

\hypertarget{selection-process}{%
\subsubsection{Selection process}\label{selection-process}}

Using Covidence software (Veritas Health Innovation, Melbourne, Australia), two researchers independently screened all titles and abstracts.
Two researchers then independently reviewed full-text articles.
We resolved disagreements at each stage of the process by consensus, with a third researcher employed, when needed.

\hypertarget{data-items}{%
\subsubsection{Data items}\label{data-items}}

From each included meta-analysis, two researchers independently extracted data into a custom-designed database.
We extracted the following items: First author, year of publication, study design restrictions (e.g., cross-sectional, observational, experimental), region restrictions (e.g., specific countries), earliest and latest study publication dates, sample age (mean), lowest and highest mean age reported, outcomes reported, and exposures reported.

\hypertarget{study-risk-of-bias-assessment}{%
\subsubsection{Study risk of bias assessment}\label{study-risk-of-bias-assessment}}

For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{49} (see Table 1).
We resolved disagreements by consensus, with a third researcher employed when needed.
We did not assess risk of bias in the individual studies that were included in each meta-analysis.

\hypertarget{effect-measures}{%
\subsubsection{Effect measures}\label{effect-measures}}

Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
We excluded effect sizes which were reported as relative risk ratios or odds ratios, as meta-analyses did not contain sufficient information to meaningfully convert to a correlation.
We also excluded effect size estimates when the authors did not provide a sample size.
Where possible, we also extracted effect sizes from the primary studies included in each meta-analysis.

To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{50,51}
Effect sizes on the original metric are provided in Supplementary File 2.
\protect\hypertarget{r2_27}{}{Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
These are similar to other interpretations based on empirical data.\textsuperscript{53}}

\hypertarget{synthesis-methods}{%
\subsubsection{Synthesis methods}\label{synthesis-methods}}

\protect\hypertarget{r3_8}{}{After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
In instances where effect sizes from the same combination of exposure and outcome were drawn from different age-groups (e.g., children vs adolescents), or were drawn using different study designs (e.g., cross-sectional vs longitudinal) we retained both estimates in our dataset.
}

We descriptively present the remaining meta-analytic effect sizes.
To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{54} in R\textsuperscript{55} (version 4.2.2) when the meta-analysis's authors provided primary study data associated with these effects.
When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
From our reanalysis we also extracted \(I^2\) values.
To test for publication bias, we conducted Egger's test\textsuperscript{56} when the number of studies within the review was ten or more,\textsuperscript{57} and conducted a test of excess significance.\textsuperscript{58}
\protect\hypertarget{r2_32}{}{We contacted authors who did not provide primary study data in their published article.
Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.}

\hypertarget{evidence-assessment-criteria}{%
\subsubsection{Evidence assessment criteria}\label{evidence-assessment-criteria}}

Statistical Credibility:
We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{59} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.

Consistency of Effect within the Population:
We also examined the consistency of the effect size using the \(I^2\) measure.
We considered \(I^2 < 50\%\) to indicate effects that were relatively consistent across the population of interest.
\(I^2\) values of \(> 50\%\) were taken to indicate an effect was potentially heterogeneous within the population.

Direction of Effect:
Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
We used thresholds of \(P < .05\) for weak evidence and \(P < 10^{-3}\) for strong evidence.
An effect with statistical credibility but with \(P > .05\) was taken to indicate no association of interest.

\hypertarget{deviations-from-protocol}{%
\subsubsection{Deviations from protocol}\label{deviations-from-protocol}}

\protect\hypertarget{r2_20}{}{
As described above, we have summarised the meta-analytic findings from all included systematic reviews.
In our protocol, we originally planned to also conduct a narrative synthesis of all systematic reviews, even those without meta-analyses.
However, we determined that combining results from the meta-analyses alone allow readers to compare relative strength of associations more easily.
Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 4.
}

We altered our evidence assessment plan when we identified that, as written, it could not classify precise evidence of null effects (i.e., from large reviews with low heterogeneity and low risk of publication bias) as `credible' because a highly-significant \emph{P}-value was a criteria.
This would have significantly harmed knowledge gained from our review as it would have restricted our ability to show where the empirical evidence strongly indicated that there was no association between screen use and a given outcome.

\hypertarget{data-availability-statement}{%
\subsection{Data availability statement}\label{data-availability-statement}}

All data for this review are available from the authors' GitHub repository (\url{https://github.com/motivation-and-Behaviour/screen_umbrella}) or from the Open Science Foundation (\url{https://osf.io/3ubqp/}).

\hypertarget{code-availability-statement}{%
\subsection{Code availability statement}\label{code-availability-statement}}

All code used in these analyses are available on the authors' GitHub repository (\url{https://github.com/motivation-and-Behaviour/screen_umbrella}).

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-blairReadingStrategiesCoping2003}{}%
1. Blair, A. Reading Strategies for Coping With Information Overload ca.1550-1700. \emph{Journal of the History of Ideas} \textbf{64}, 11--28 (2003).

\leavevmode\hypertarget{ref-bell1883sanitarian}{}%
2. Bell, A. N. \emph{The sanitarian}. vol. 11 (AN Bell, 1883).

\leavevmode\hypertarget{ref-dill2013oxford}{}%
3. Dill, K. E. \emph{The Oxford handbook of media psychology}. (Oxford University Press, 2013).

\leavevmode\hypertarget{ref-wartellaChildrenComputersNew2000}{}%
4. Wartella, E. A. \& Jennings, N. Children and computers: New technology. Old concerns. \emph{The future of children} 31--43 (2000).

\leavevmode\hypertarget{ref-rhodes2015top}{}%
5. Rhodes, A. \emph{Top ten child health problems: What the public thinks}. (2015).

\leavevmode\hypertarget{ref-thelancetSocialMediaScreen2019}{}%
6. The Lancet. Social media, screen time, and young people's mental health. \emph{The Lancet} \textbf{393}, 611 (2019).

\leavevmode\hypertarget{ref-haleScreenTimeSleep2015}{}%
7. Hale, L. \& Guan, S. Screen time and sleep among school-aged children and adolescents: A systematic literature review. \emph{Sleep Medicine Reviews} \textbf{21}, 50--58 (2015).

\leavevmode\hypertarget{ref-sweetserActivePassiveScreen2012}{}%
8. Sweetser, P., Johnson, D., Ozdowska, A. \& Wyeth, P. Active versus passive screen time for young children. \emph{Australasian Journal of Early Childhood} \textbf{37}, 94--98 (2012).

\leavevmode\hypertarget{ref-liEarlyChildhoodComputer2004}{}%
9. Li, X. \& Atkins, M. S. Early childhood computer experience and cognitive and motor development. \emph{Pediatrics} \textbf{113}, 1715--1722 (2004).

\leavevmode\hypertarget{ref-warburton2017children}{}%
10. Warburton, W. \& Highfield, K. Children and technology in a smart device world. in \emph{Children, Families and Communities} 195--221 (Oxford University Press, 2017).

\leavevmode\hypertarget{ref-naturehumanbehaviourScreenTimeHow2019}{}%
11. Nature Human Behaviour. Screen time: How much is too much? \emph{Nature} \textbf{565}, 265--266 (2019).

\leavevmode\hypertarget{ref-whoGuidelinesPhysicalActivity2019}{}%
12. World Health Organization. \emph{Guidelines on physical activity, sedentary behaviour and sleep for children under 5 years of age}. 33 p. (World Health Organization, 2019).

\leavevmode\hypertarget{ref-australiangovernmentPhysicalActivityExercise2021}{}%
13. Australian Government. \emph{Physical activity and exercise guidelines for all Australians}. (2021).

\leavevmode\hypertarget{ref-Canadian24HourMovement2016}{}%
14. Canadian Society for Exercise Physiology. \emph{Canadian 24-Hour Movement Guidelines for Children and Youth: An Integration of Physical Activity, Sedentary Behaviour, and Sleep}. (2016).

\leavevmode\hypertarget{ref-AAPMediaUseSchoolAged2016}{}%
15. Council On Communication and Media. Media Use in School-Aged Children and Adolescents. \emph{Pediatrics} \textbf{138}, e20162592 (2016).

\leavevmode\hypertarget{ref-fergusonEverythingModerationModerate2017}{}%
16. Ferguson, C. J. Everything in Moderation: Moderate Use of Screens Unassociated with Child Behavior Problems. \emph{Psychiatric Quarterly} \textbf{88}, 797--805 (2017).

\leavevmode\hypertarget{ref-przybylskiLargeScaleTestGoldilocks2017}{}%
17. Przybylski, A. K. \& Weinstein, N. A Large-Scale Test of the Goldilocks Hypothesis: Quantifying the Relations Between Digital-Screen Use and the Mental Well-Being of Adolescents. \emph{Psychological Science} \textbf{28}, 204--215 (2017).

\leavevmode\hypertarget{ref-sandersTypeScreenTime2019}{}%
18. Sanders, T., Parker, P. D., del Pozo-Cruz, B., Noetel, M. \& Lonsdale, C. Type of screen time moderates effects on outcomes in 4013 children: Evidence from the Longitudinal Study of Australian Children. \emph{International Journal of Behavioral Nutrition and Physical Activity} \textbf{16}, 117 (2019).

\leavevmode\hypertarget{ref-kayeConceptualMethodologicalMayhem2020}{}%
19. Kaye, L. K., Orben, A., Ellis, D. A., Hunter, S. C. \& Houghton, S. The Conceptual and Methodological Mayhem of `Screen Time'. \emph{International Journal of Environmental Research and Public Health} \textbf{17}, 3661 (2020).

\leavevmode\hypertarget{ref-chassiakosChildrenAdolescentsDigital2016}{}%
20. Chassiakos, Y. L. R. \emph{et al.} Children and Adolescents and Digital Media. \emph{Pediatrics} \textbf{138}, e20162593 (2016).

\leavevmode\hypertarget{ref-stiglicEffectsScreentimeHealth2019}{}%
21. Stiglic, N. \& Viner, R. M. Effects of screentime on the health and well-being of children and adolescents: A systematic review of reviews. \emph{BMJ Open} \textbf{9}, e023191 (2019).

\leavevmode\hypertarget{ref-valkenburgSocialMediaUse2022}{}%
22. Valkenburg, P. M., Meier, A. \& Beyens, I. Social media use and its impact on adolescent mental health: An umbrella review of the evidence. \emph{Current Opinion in Psychology} \textbf{44}, 58--68 (2022).

\leavevmode\hypertarget{ref-arias-delatorreRelationshipDepressionUse2020}{}%
23. Arias-de la Torre, J. \emph{et al.} Relationship Between Depression and the Use of Mobile Technologies and Social Media Among Adolescents: Umbrella Review. \emph{Journal of Medical Internet Research} \textbf{22}, e16388 (2020).

\leavevmode\hypertarget{ref-orbenTeenagersScreensSocial2020}{}%
24. Orben, A. Teenagers, screens and social media: A narrative review of reviews and key studies. \emph{Social Psychiatry and Psychiatric Epidemiology} \textbf{55}, 407--414 (2020).

\leavevmode\hypertarget{ref-pollockChapterOverviewsReviews2022}{}%
25. Pollock, M., Fernandes, R., Becker, L., Pieper, D. \& Hartling, L. Chapter V: Overviews of Reviews. in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds. Higgins, J. P. et al.) (Cochrane, 2022).

\leavevmode\hypertarget{ref-xieCanTouchscreenDevices2018}{}%
26. Xie, H. \emph{et al.} Can Touchscreen Devices be Used to Facilitate Young Children's Learning? A Meta-Analysis of Touchscreen Learning Effect. \emph{Frontiers in Psychology} \textbf{9}, 2580 (2018).

\leavevmode\hypertarget{ref-adelantado-renauAssociationScreenMedia2019}{}%
27. Adelantado-Renau, M. \emph{et al.} Association Between Screen Media Use and Academic Performance Among Children and Adolescents: A Systematic Review and Meta-analysis. \emph{JAMA Pediatrics} \textbf{173}, 1058 (2019).

\leavevmode\hypertarget{ref-madiganAssociationsScreenUse2020}{}%
28. Madigan, S., McArthur, B. A., Anhorn, C., Eirich, R. \& Christakis, D. A. Associations Between Screen Use and Child Language Skills: A Systematic Review and Meta-analysis. \emph{JAMA Pediatrics} \textbf{174}, 665 (2020).

\leavevmode\hypertarget{ref-poorolajalBehavioralFactorsInfluencing2020}{}%
29. Poorolajal, J., Sahraei, F., Mohamdadi, Y., Doosti-Irani, A. \& Moradi, L. Behavioral factors influencing childhood obesity: A systematic review and meta-analysis. \emph{Obesity Research \& Clinical Practice} \textbf{14}, 109--118 (2020).

\leavevmode\hypertarget{ref-byunDigitalGamebasedLearning2018}{}%
30. Byun, J. \& Joung, E. Digital game-based learning for K-12 mathematics education: A meta-analysis. \emph{School Science and Mathematics} \textbf{118}, 113--126 (2018).

\leavevmode\hypertarget{ref-vannucciSocialMediaUse2020}{}%
31. Vannucci, A., Simpson, E. G., Gagnon, S. \& Ohannessian, C. M. Social media use and risky behaviors in adolescents: A meta-analysis. \emph{Journal of Adolescence} \textbf{79}, 258--274 (2020).

\leavevmode\hypertarget{ref-yoonSocialNetworkSite2019}{}%
32. Yoon, S., Kleinman, M., Mertz, J. \& Brannick, M. Is social network site usage related to depression? A meta-analysis of FacebookDepression relations. \emph{Journal of Affective Disorders} \textbf{248}, 65--72 (2019).

\leavevmode\hypertarget{ref-vahediAssociationSelfreportedDepressive2021}{}%
33. Vahedi, Z. \& Zannella, L. The association between self-reported depressive symptoms and the use of social networking sites (SNS): A meta-analysis. \emph{Current Psychology} \textbf{40}, 2174--2189 (2021).

\leavevmode\hypertarget{ref-seetharamanFacebookKnowsInstagram2021}{}%
34. Seetharaman, G. W., Jeff Horwitz and Deepa. Facebook Knows Instagram Is Toxic for Teen Girls, Company Documents Show. \emph{Wall Street Journal} (2021).

\leavevmode\hypertarget{ref-tekedereExaminingEffectivenessAugmented2016}{}%
35. Tekedere, H. \& Göke, H. Examining the Effectiveness of Augmented Reality Applications in Education: A Meta-Analysis. \emph{International Journal of Environmental and Science Education} \textbf{11}, 9469--9481 (2016).

\leavevmode\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}%
36. Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N. R. C. \& Johnston, B. C. Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials. \emph{Obesity Reviews} \textbf{17}, 945--959 (2016).

\leavevmode\hypertarget{ref-marshallRelationshipsMediaUse2004}{}%
37. Marshall, S. J., Biddle, S. J. H., Gorely, T., Cameron, N. \& Murdey, I. Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis. \emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).

\leavevmode\hypertarget{ref-elsonPolicyStatementsMedia2019}{}%
38. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).

\leavevmode\hypertarget{ref-ashtonScreenTimeChildren2019}{}%
39. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).

\leavevmode\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}%
40. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).

\leavevmode\hypertarget{ref-pagePRISMA2020Statement2020}{}%
41. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.

\leavevmode\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}%
42. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).

\leavevmode\hypertarget{ref-byrneMeasurementScreenTime2021}{}%
43. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).

\leavevmode\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}%
44. Smith, C., Galland, B. C., de Bruin, W. E. \& Taylor, R. W. Feasibility of automated cameras to measure screen use in adolescents. \emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).

\leavevmode\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}%
45. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).

\leavevmode\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}%
46. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).

\leavevmode\hypertarget{ref-twengeMoreTimeTechnology2019}{}%
47. Twenge, J. M. More Time on Technology, Less Happiness? Associations Between Digital-Media Use and Psychological Well-Being. \emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).

\leavevmode\hypertarget{ref-kellySocialMediaUse2018}{}%
48. Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social Media Use and Adolescent Mental Health: Findings From the UK Millennium Cohort Study. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).

\leavevmode\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}%
49. National Health, Lung, and Blood Institute. \emph{Quality Assessment of Systematic Reviews and Meta-Analyses}. (2014).

\leavevmode\hypertarget{ref-bowmanEffectSizesStatistical2012}{}%
50. Bowman, N. A. Effect Sizes and Statistical Methods for Meta-Analysis in Higher Education. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).

\leavevmode\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}%
51. Jacobs, P. \& Viechtbauer, W. Estimation of the biserial correlation and its sampling variance for use in meta-analysis: Biserial Correlation. \emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).

\leavevmode\hypertarget{ref-funderEvaluatingEffectSize2019}{}%
52. Funder, D. C. \& Ozer, D. J. Evaluating Effect Size in Psychological Research: Sense and Nonsense. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).

\leavevmode\hypertarget{ref-gignacEffectSizeGuidelines2016}{}%
53. Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).

\leavevmode\hypertarget{ref-R-metafor}{}%
54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2022).

\leavevmode\hypertarget{ref-R-base}{}%
55. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2022).

\leavevmode\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}%
56. Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).

\leavevmode\hypertarget{ref-pageChapter13Assessing2021}{}%
57. Page, M. J., Higgins, J. P. \& Sterne, J. A. Chapter 13: Assessing risk of bias due to missing results in a synthesis. in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds. Higgins, J. P. et al.) (Cochrane, 2021).

\leavevmode\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}%
58. Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).

\leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
59. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
\end{cslreferences}

\newpage

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

The authors received no specific funding for this work.

\hypertarget{author-contributions}{%
\section{Author contributions}\label{author-contributions}}

TS, MN, PP, and CL conceptualised the review and drafted the manuscript.
TS, MN, and PP conducted the analyses.
All authors contributed to data extraction, interpretation, and editing of the manuscript.

\hypertarget{competing-interests}{%
\section{Competing interests}\label{competing-interests}}

The authors declare no conflicts of interest.

\hypertarget{figure-legends}{%
\section{Figure legends}\label{figure-legends}}

\emph{Figure 1: PRISMA Diagram.}

\emph{Figure 2: Education outcomes. Results for 23 unique effect sizes related to educational outcomes which met the criteria for statistical certainty. Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}

\emph{Figure 3: Health and health-related behaviour outcomes. Results for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty. Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}

\hypertarget{tables}{%
\section{Tables}\label{tables}}

\emph{Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects}

\end{document}

### 2023-03-13 R/clean_reviews.R

@@ -1,0 +1,143 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param reviews_raw
+#' @param effects_raw
+#' @param age_codes
+#' @param demo_codes
+#' @param sample_codes
+#' @param design_codes
+#' @return
+#' @author Taren Sanders
+#' @export
+clean_reviews <- function(
+    reviews_raw, effects_raw, age_codes,
+    demo_codes, sample_codes, design_codes) {
+  zero_effects_ids <-
+    effects_raw %>%
+    group_by(review_id) %>%
+    summarise(n_valid_effects = sum(
+      !is.na(value) & !is.na(combined_n) & use_moderator
+    )) %>%
+    filter(n_valid_effects == 0) %>%
+    pull(review_id)
+
+  reviews_clean <-
+    reviews_raw %>%
+    mutate(
+      demographics_coded = case_when(
+        demographics %in% age_codes$mixed ~ "Mixed",
+        demographics %in% age_codes$adolescents ~ "Adolescents",
+        demographics %in% age_codes$children ~ "Children",
+        demographics %in% age_codes$young_children ~ "Young children",
+        TRUE ~ demographics
+      ),
+      # Tidy up the sample age variables
+      sample_age_lowest_study_mean =
+        as.numeric(case_when(
+          grepl("months", sample_age_lowest_study_mean) ~
+            as.character(as.numeric(
+              str_remove(sample_age_lowest_study_mean, " months")
+            ) / 12),
+          TRUE ~ sample_age_lowest_study_mean
+        )),
+      sample_age_highest_study_mean =
+        as.numeric(case_when(
+          grepl("months", sample_age_highest_study_mean) ~
+            as.character(as.numeric(
+              str_remove(sample_age_highest_study_mean, " months")
+            ) / 12),
+          TRUE ~ sample_age_highest_study_mean
+        )),
+      # Double check the coding based on the age variables
+      demographics_coded = case_when(
+        sample_age_lowest_study_mean < 8 & sample_age_highest_study_mean > 16 ~
+          "Mixed",
+        sample_age_lowest_study_mean < 1 & sample_age_highest_study_mean > 10 ~
+          "Mixed",
+        sample_age_lowest_study_mean >= 12 ~ "Adolescents",
+        sample_age_highest_study_mean < 7 ~ "Young children",
[…]

### 2023-03-13 R/clean_studies.R

@@ -1,0 +1,30 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param studies_raw
+#' @return
+#' @author Taren Sanders
+#' @export
+clean_studies <- function(studies_raw) {
+  studies_clean <-
+    studies_raw %>%
+    mutate(study_name = paste(study_author, study_year)) %>%
+    # Impute missing N. TODO: Test something other than mean imputation
+    group_by(effect_size_id) %>%
+    mutate(
+      study_n = replace_na(study_n, round(mean(study_n, na.rm = TRUE)))
+    ) %>%
+    ungroup()
+
+  data <- studies_clean %>%
+    mutate(converted_metric = translate_tests(metric)) %>%
+    filter(converted_metric %in% c("b", "d", "r", "z", "md")) %>%
+    convert_studies() %>%
+    drop_na(r_estimate, study_n) %>%
+    group_by(effect_size_id) %>%
+    tar_group()
+
+  return(data)
+}

### 2023-03-13 R/codes.R

@@ -1,0 +1,340 @@
+# These are the recoding rules for the variables in the dataset that are used in
+# more than one place.
+
+# nolint start
+
+# Ages ----------------------------------------------------------------------
+age_codes_list <- list(
+  mixed = c(
+    "<=18 years",
+    "<18 years",
+    "<18",
+    "<20 years",
+    "0-21 years old",
+    "1 - 18 years",
+    "1-18 years",
+    "10 - 19 years",
+    "10-19 years",
+    "10-20 years old",
+    "10-24 years",
+    "11-20",
+    "2-19 years",
+    "3-18 years",
+    "5-18 years",
+    "5-19.9",
+    "6-18 years",
+    "6-18 years (or grade 1-12)",
+    "6-19",
+    "6-21 years",
+    "All",
+    "Children; Adolescents",
+    "Children/adolescents",
+    "Include: children and adolescents",
+    "K-12",
+    "mixed",
+    "None specified",
+    "PreK-12th grade",
+    "preschool-college",
+    "Preschool, K-12, undergraduate (graduate), and mixed-stage learners",
+    "Primary or secondary school",
+    "School-age Children",
+    "Under 18"
+  ),
+  adolescents_codes = c(
+    "<=14", # lower bound is 11 in this study
+    "11-18 years",
+    "12-17 years",
+    ">14",
+    "12-30 years",
+    "13-18",
+    "15-30 years old",
+    "adolescence",
+    "adolescents",
+    "Adolescents",
+    "at least 13 years",
+    "School-age Children (High School)",
+    "School-age Children (Middle School)",
+    "School-age Children (Middle/High School)",
+    "school-age_high school",
+    "School-age_High School",
+    "High School",
+    "Lower secondary education",
+    "Middle School",
+    "Middle/High school",
+    "Secondary",
+    "Secondary School",
+    "Upper secondary education"
+  ),
+  children_codes = c(
+    "Kindergarten",
+    "12 or under",
+    "12 or younger",
+    "K-3",
+    "3-12 years",
+    "6-11 years",
+    "7-12",
+    "8-14 years",
+    "Elementary",
+    "Elementary & Kindergarten",
+    "Elementary school",
+    "Average 6 years, all must be less than 8 years",
+    "childhood",
+    "children",
+    "Children",
+    "Early childhood; School-age Children (Primary/Elementary)",
+    "Early childhood/pre-school; School-age Children (Early Primary/Elementary)",
[…]

### 2023-03-13 R/conversions.R

@@ -1,0 +1,18 @@
+#' Functions for converting between effect sizes
+#'
+#' @name conversions
+#' @author Taren Sanders
+NULL
+
+
+#' @describeIn conversions Convert beta to r
+b2r <- function(beta) {
+  # conversion formula from 10.1007/s11162-011-9232-5
+  # TODO: consider if this should be top-coded to |0.5|
+  # (10.1037/0021-9010.90.1.175)
+  b2r_single <- function(beta) {
+    ifelse(!is.na(beta), beta, NA_real_)
+  }
+
+  vapply(beta, b2r_single, numeric(1))
+}

### 2023-03-13 R/convert_studies.R

@@ -1,0 +1,73 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param data
+#' @return
+#' @author Taren Sanders
+#' @export
+convert_studies <- function(data) {
+  data_converted <- data %>%
+    mutate(
+      r_ci_lower = if_else(
+        is.na(lower_ci) & !is.na(standard_error),
+        estimate - 1.96 * standard_error,
+        lower_ci
+      ),
+      r_ci_upper = if_else(
+        is.na(upper_ci) & !is.na(standard_error),
+        estimate + 1.96 * standard_error,
+        upper_ci
+      ),
+      r_estimate = case_when(
+        converted_metric == "r" ~ estimate,
+        converted_metric == "b" ~ b2r(estimate),
+        converted_metric == "d" ~ effectsize::d_to_r(estimate),
+        converted_metric == "z" ~ correlation::z_fisher(z = estimate),
+        # Calculate d from mean difference where possible
+        converted_metric == "md" & !is.na(estimate) &
+          !is.na(standard_deviation) ~
+          effectsize::d_to_r(estimate / standard_deviation),
+        TRUE ~ NA_real_
+      ),
+      r_ci_lower = case_when(
+        converted_metric == "r" ~ lower_ci,
+        converted_metric == "b" ~ b2r(lower_ci),
+        converted_metric == "d" ~ effectsize::d_to_r(lower_ci),
+        converted_metric == "z" ~ correlation::z_fisher(z = lower_ci),
+        # Calculate d from mean difference where possible
+        converted_metric == "md" & !is.na(lower_ci) &
+          !is.na(standard_deviation) ~
+          effectsize::d_to_r(lower_ci / standard_deviation),
+        TRUE ~ NA_real_
+      ),
+      r_ci_upper = case_when(
+        converted_metric == "r" ~ upper_ci,
+        converted_metric == "b" ~ b2r(upper_ci),
+        converted_metric == "d" ~ effectsize::d_to_r(upper_ci),
+        converted_metric == "z" ~ correlation::z_fisher(z = upper_ci),
+        # Calculate d from mean difference where possible
+        converted_metric == "md" & !is.na(upper_ci) &
+          !is.na(standard_deviation) ~
+          effectsize::d_to_r(upper_ci / standard_deviation),
+        TRUE ~ NA_real_
+      ),
[…]

### 2023-03-13 R/make_bibs.R

@@ -1,0 +1,51 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param packages
+#' @param outpath
+#' @return
+#' @author Taren Sanders
+#' @export
+make_packages_bib <- function(packages, outpath) {
+  knitr::write_bib(packages, outpath)
+  return(outpath)
+}
+
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param packages_bib
+#' @param references_bib
+#' @param reviews_raw
+#' @param outpath
+#' @return
+#' @author Taren Sanders
+#' @export
+combine_bibs <- function(packages_bib, references_bib, reviews_raw, outpath) {
+  # Fix UTF-8 encoding
+  refs <- readLines(references_bib, encoding = "UTF-8")
+  refs <- str_replace_all(refs, "[^[:graph:]]", " ")
+  refs <- iconv(refs, from = "UTF-8", to = "ASCII//TRANSLIT")
+  refs_tmp <- tempfile(fileext = ".bib")
+  writeLines(refs, con = refs_tmp)
+
+  paths <- c(packages_bib, refs_tmp)
+  bibs <- lapply(paths, bib2df)
+  full_bib <- bind_rows(bibs)
+
+  full_bib <-
+    full_bib %>%
+    mutate(ANNOTE = if_else(BIBTEXKEY %in% reviews_raw$bibtex_key,
+      "*",
+      ""
+    ))
+
+  df2bib(full_bib, file = outpath)
+
+  rm(refs_tmp)
+  return(outpath)
+}

### 2023-03-13 R/make_forest_plot.R

@@ -1,0 +1,346 @@
+t #' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param combined_effects
+#' @param plot_params
+#' @param debug
+#' @return
+#' @author Taren Sanders
+#' @export
+make_forest_plot <- function(combined_effects, plot_params, debug = FALSE) {
+  if (debug) labsize <- 1 else labsize <- NA
+
+  plot_effects <-
+    combined_effects %>%
+    filter(use_effect) %>%
+    mutate(
+      # Truncate large effects
+      cilb999 = if_else(cilb999 < -1, -1, cilb999),
+      ciub999 = if_else(ciub999 > 1, 1, ciub999),
+      # Overall outcome into a variable and remove that from the sub-variable
+      outcome_lvl_1 = factor(gsub(":.*", "", plain_language_outcome)),
+      plain_language_outcome = gsub(".*: ", "", plain_language_outcome),
+      outcome_category = factor(str_to_title(outcome_category)),
+      plain_language_exposure = str_replace(
+        plain_language_exposure,
+        "^Intervention:",
+        "Screen-based intervention:"
+      ),
+      # Fix long labels
+      plain_language_outcome = trimmer(plain_language_outcome, 40),
+      plain_language_exposure = trimmer(plain_language_exposure, 40),
+      i2 = scales::percent(i2, 2, scale = 1),
+      n = scales::label_comma(accuracy = 1)(n),
+      k = as.character(k),
+      rci = paste(format(round(r, 2), nsmall = 2),
+        " [", format(round(cilb95, 2), nsmall = 2), ", ",
+        format(round(ciub95, 2), nsmall = 2), "]",
+        sep = ""
+      ),
+      indiv_data = fontawesome(if_else(source == "reanalysis",
+        "fa-check", "fa-times"
+      )),
+      eggers = case_when(
+        source == "reported" ~ fontawesome("fa-minus"),
+        reanalysis_eggers_p > 0.05 ~ fontawesome("fa-check"),
+        TRUE ~ fontawesome("fa-times")
+      ),
+      esig = case_when(
+        source == "reported" ~ fontawesome("fa-minus"),
+        reanalysis_tes_p > 0.05 ~ fontawesome("fa-check"),
+        TRUE ~ fontawesome("fa-times")
+      ),
+      font_fam = "fontawesome-webfont",
[…]

### 2023-03-13 R/make_manuscript_info.R

@@ -1,0 +1,396 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param effects_clean
+#' @param prisma
+#' @param tables_df
+#' @param combined_effects
+#' @param studies_clean
+#' @return
+#' @author Taren Sanders
+#' @export
+make_manuscript_info <- function(effects_clean, prisma, tables_df,
+                                 combined_effects, studies_clean) {
+  manuscript_info <- list()
+
+  # Results --------------------------------------------------
+
+  ## List of frequent exposures
+  manuscript_info$freq_exposures <-
+    effects_clean %>%
+    select(review_id, plain_language_outcome, plain_language_exposure) %>%
+    # Each review can only have one combo, so as to not overcount moderators
+    distinct() %>%
+    group_by(plain_language_exposure) %>%
+    summarise(n = n()) %>%
+    arrange(desc(n)) %>%
+    mutate(
+      plain_language_exposure = rename_effects(plain_language_exposure),
+      plain_language_exposure = case_when(
+        plain_language_exposure ==
+          "to promote health intervention" ~
+          "screen-based interventions to promote health",
+        plain_language_exposure == "general tv programs and movies" ~
+          "general TV programs and movies",
+        TRUE ~ plain_language_exposure
+      ),
+      out = paste0(plain_language_exposure, " (*n* = ", n, ")")
+    ) %>%
+    head(4) %>%
+    pull(out) %>%
+    knitr::combine_words()
+
+  ## List of frequent outcomes
+  manuscript_info$freq_outcomes <-
+    effects_clean %>%
+    select(review_id, plain_language_outcome, plain_language_exposure) %>%
+    # Each review can only have one combo, so as to not overcount moderators
+    distinct() %>%
+    group_by(plain_language_outcome) %>%
+    summarise(n = n()) %>%
+    arrange(desc(n)) %>%
+    mutate(
+      plain_language_outcome = rename_effects(plain_language_outcome),
+      plain_language_outcome = case_when(
+        plain_language_outcome == "depression psychological health" ~
+          "depression",
[…]

### 2023-03-13 R/make_table_desc.R

@@ -1,0 +1,325 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param tables_df
+#' @return
+#' @author Taren Sanders
+#' @export
+make_table_desc_gt <- function(tables_df) {
+  rob_cols <- c("#b7e1cd", "#fce8b2", "#f4c7c3")
+
+  desc_df <- tables_df %>%
+    filter(table == "main")
+
+  base_table <-
+    desc_df %>%
+    group_by(review_id) %>%
+    mutate(
+      outcomes_assessed = map(bullet_list(plain_language_outcome), gt::html),
+      exposures_assessed = map(bullet_list(plain_language_exposure), gt::html)
+    ) %>%
+    ungroup() %>%
+    select(
+      -plain_language_outcome,
+      -plain_language_exposure,
+      -use_effect,
+      -table
+    ) %>%
+    distinct() %>%
+    mutate(
+      sample_ages = if_else(
+        (is.na(sample_age_mean_low)) | (is.na(sample_age_mean_high)),
+        demographics_restrictions,
+        paste0(
+          demographics_restrictions,
+          "<br/><small>(",
+          trimws(format(round(
+            sample_age_mean_low, 1
+          ), nsmall = 1)),
+          "-",
+          trimws(format(round(
+            sample_age_mean_high, 1
+          ), nsmall = 1)),
+          ")</small>"
+        )
+      ),
+      sample_ages = map(sample_ages, gt::html)
+    ) %>%
+    mutate(
+      sample_restrictions = case_when(
+        !is.na(sample_incl) & !is.na(sample_excl) ~
+          paste0("Include: ", sample_incl, "\n", "Exclude: ", sample_excl),
+        !is.na(sample_incl) & is.na(sample_excl) ~
+          paste0("Include: ", sample_incl),
+        is.na(sample_incl) & !is.na(sample_excl) ~
+          paste0("Exclude: ", sample_excl),
+        TRUE ~ "None specified"
+      ),
+      sample_restrictions = map(sample_restrictions, gt::html)
+    ) %>%
+    relocate(sample_restrictions, .after = design_restrictions) %>%
+    mutate_at(
+      vars(
+        "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
+      ),
+      ~ case_match(
+        .x,
+        "low" ~ "L",
+        "unclear" ~ "U",
[…]

### 2023-03-13 R/save_plot.R

@@ -1,0 +1,22 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param plot
+#' @param plot_params
+#' @return
+#' @author Taren Sanders
+#' @export
+save_plot <- function(plot, plot_params) {
+  file_name <- plot_params$filename
+
+  ggsave(
+    filename = file_name,
+    plot = plot,
+    width = plot_params$dims[[1]],
+    height = plot_params$dims[[2]]
+  )
+
+  return(file_name)
+}

### 2023-03-13 _targets.R

@@ -1,44 +1,261 @@
-library(targets)
-library(tarchetypes)
-library(here)
-
+# Set options
 options(tidyverse.quiet = TRUE, clustermq.scheduler = "multiprocess")
 
-packages <- c(
-  "base", "broom", "bib2df", "DiagrammeR", "distill", "DT", "esc",
-  "emojifont", "ggh4x", "googledrive", "ggplot2", "ggtext", "gt", "janitor",
-  "knitr", "kableExtra", "magick", "magrittr", "metafor", "papaja", "targets",
-  "tarchetypes", "tidyMB", "tidyverse", "scales", "xfun"
-)
-
-tar_option_set(
-  packages = packages,
-  debug = "yml_base",
-  workspace_on_error = TRUE
-)
-
-googledrive::drive_auth()
-googlesheets4::gs4_auth()
-source(here::here("R", "utils.R"))
-source(here::here("R", "data.R"))
-source(here::here("R", "tables.R"))
-source(here::here("R", "plots.R"))
-source(here::here("R", "supplementary.R"))
-source(here::here("R", "reports.R"))
+# Load required functions and packages
+lapply(list.files("./R", full.names = TRUE), source)
+load_packages()
 
 list(
-  # Fetch and analyse (data.R)
-  fetch_data,
-  clean_and_convert,
-  reanalyse,
-  # Make tables (tables.R)
-  make_tables,
-  # Make plots (plots.R)
-  make_prisma_figure,
-  make_forest_plots,
-  # Make sundry supplementary material (supplementary.R)
-  make_supps,
-  # Create reports (reports.R)
-  generate_bibliography,
-  create_reports
+  # Read data ---------------------------------------------------------------
+  tar_file_read(
+    effects_raw,
+    "data/Effects.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_file_read(
+    reviews_raw,
+    "data/Reviews.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_file_read(
+    studies_raw,
+    "data/Studies.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_file_read(
+    rob_raw,
+    "data/QualityAssessment.csv",
+    read_sheet(file = !!.x)
+  ),
+  tar_target(prisma_path,
+    here::here("data/covidence_prisma.txt"),
+    format = "file"
+  ),
+  # Set params --------------------------------------------------------------
+  tar_target(age_codes, age_codes_list),
+  tar_target(demo_codes, demo_codes_list),
[…]

### 2023-03-13 _targets_packages.R

@@ -1,37 +1,0 @@
-# Generated by targets::tar_renv(): do not edit by hand
-library(base)
-library(bib2df)
-library(broom)
-library(bs4Dash)
-library(clustermq)
-library(DiagrammeR)
-library(distill)
-library(DT)
-library(emojifont)
-library(esc)
-library(future)
-library(ggh4x)
-library(ggplot2)
-library(ggtext)
-library(googledrive)
-library(gt)
-library(janitor)
-library(kableExtra)
-library(knitr)
-library(magick)
-library(magrittr)
-library(markdown)
-library(metafor)
-library(papaja)
-library(pingr)
-library(rstudioapi)
-library(scales)
-library(shiny)
-library(shinybusy)
-library(shinyWidgets)
-library(tarchetypes)
-library(targets)
-library(tidyMB)
-library(tidyverse)
-library(visNetwork)
-library(xfun)

### 2023-03-13 packages.R

@@ -1,0 +1,37 @@
+library(base)
+library(bib2df)
+library(broom)
+library(clustermq)
+library(correlation)
+library(DiagrammeR)
+library(distill)
+library(dplyr)
+library(DT)
+library(effectsize)
+library(emojifont)
+library(esc)
+library(forcats)
+library(future)
+library(ggplot2)
+library(ggh4x)
+library(ggtext)
+library(gt)
+library(gtsummary)
+library(kableExtra)
+library(knitr)
+library(magick)
+library(magrittr)
+library(markdown)
+library(Matrix)
+library(metadat)
+library(metafor)
+library(tinylabels)
+library(papaja)
+library(purrr)
+library(scales)
+library(stringr)
+library(tarchetypes)
+library(targets)
+library(tidyMB)
+library(tidyr)
+library(xfun)

### 2023-03-23 reports/manuscript.tex
Update Stuart's affiliation

@@
   pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
-  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
+  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
   pdflang={en-EN},
@@
 \title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
-\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
+\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} School of Medicine and Health, Sydney University, Sydney, Australia\\\textsuperscript{8} Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} School of Medicine and Health, Sydney University, Sydney, Australia\\\textsuperscript{8} Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}
 

### 2023-03-23 reports/manuscript.Rmd
Revisions for Nature Human Behaviour (#27)
Update Stuart's affiliation

@@
   - name          : "Stuart Biddle"
-    affiliation   : "4"
+    affiliation   : "4, 13"
   - name          : "Rimante Ronto"
@@
     institution   : "School of Education, Australian Catholic University, North Sydney, Australia"
+  - id            : "13"
+    institution   : "Faculty of Sport & Health Sciences, University of Jyväskylä, Finland"
 
@@
 # Tables
+
+*Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects*

### 2023-06-13 reports/manuscript.tex
Rerun pipeline

@@
 We descriptively present the remaining meta-analytic effect sizes.
-To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{54} in R\textsuperscript{55} (version 4.2.2) when the meta-analysis's authors provided primary study data associated with these effects.
+To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{54} in R\textsuperscript{55} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
@@
 \leavevmode\hypertarget{ref-R-base}{}%
-55. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2022).
+55. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).
 

### 2023-06-15 reports/manuscript.Rmd
Update co-author affiliations

@@
   - id            : "5"
-    institution   : "Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia"
+    institution   : "Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia"
   - id            : "6"
@@
   - id            : "7"
-    institution   : "School of Medicine and Health, Sydney University, Sydney, Australia"
+    institution   : "The Centre for Social Impact, University of New South Wales, Sydney, Australia"
   - id            : "8"
-    institution   : "Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia"
+    institution   : "The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia"
   - id            : "9"

### 2023-06-15 reports/manuscript.Rmd
Remove revision letter and associated files

@@
 Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
-<span id = "r2_8">For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
+For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
 They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
@@
 This evidence has led some researchers to argue that a more nuanced approach to screen use guidelines is required [@kayeConceptualMethodologicalMayhem2020].
-</span>
 
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-<span id = "r2_9">
 While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health [@stiglicEffectsScreentimeHealth2019]), focus on a particular exposure (e.g., social media [@valkenburgSocialMediaUse2022;@arias-delatorreRelationshipDepressionUse2020]) or provide only a narrative summary of the literature [@orbenTeenagersScreensSocial2020].
-<span id = "r1_2">
 Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
@@
 These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.
-By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.</span></span>
+By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.
 
 In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
-<span id = "r2_6">This review synthesises evidence on any outcome of electronic media exposure.
+This review synthesises evidence on any outcome of electronic media exposure.
 We deliberately did not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
 Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
-By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.</span>
+By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
 
@@
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
-<span id ="r2_25">Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.</span>
-<span id ="r2_23">After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.</span>
+Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
+Full characteristics of the included studies are provided in Table 1.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.
 These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies, involving `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
@@
 
-<span id = "r1_5">
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
@@
 However, in the absence of this work, our study has shown how children are affected by screens in general.
-</span>
 
@@
 
-<span id = "r2_7">
 In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce 'screen use', and instead focusing on the type of screen use.
@@
 Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
-</span>
 
@@
 Reviews tended to be general (e.g., all screen use) and even when more targeted (e.g., social media) nuances related to specific content (e.g., Instagram vs Facebook) have not been meta-analysed or have not produced credible evidence.
-<span id = "r2_29">Fewer than 20\% of the effects identified met our criteria for statistical credibility.
+Fewer than 20\% of the effects identified met our criteria for statistical credibility.
 Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
@@
 When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
-It seems that much of the current screen use research is small in scale, and there is a need for larger, high-quality studies.<span>
+It seems that much of the current screen use research is small in scale, and there is a need for larger, high-quality studies.
 
-<span id = "r1_1">Our results highlight the need for the field to more carefully consider if the term 'screen use' remains appropriate for providing advice to parents.
+Our results highlight the need for the field to more carefully consider if the term 'screen use' remains appropriate for providing advice to parents.
 Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
-Rather than suggesting parents limit 'screen use', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.</span>
+Rather than suggesting parents limit 'screen use', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.
 
@@
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
-<span id = "r2_24">In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
+In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
 Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (*k*) or the most recent review by publication year.
-However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.</span>
+However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
 
-<span id="r1_4">Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
+Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
 These likely depend on the specific exposure and outcome.
@@
 Many of the individual reviews go into more detail about the strength of the evidence for causal associations, but those judgements were difficult to synthesise across more than 200 reviews.
-Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.</span>
+Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.
 
-<span id="r2_16">We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
+We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
 Some previous research suggests that associations are typically linear [@sandersTypeScreenTime2019].
@@
 Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
-Care is needed, therefore, when interpreting the effect sizes.</span>
-<span id = "r3_2_2">In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
-While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.</span>
+Care is needed, therefore, when interpreting the effect sizes.
+In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
+While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
 
@@
 To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
-<span id = "r3_5">We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was < 18 years).
+We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was < 18 years).
 A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
-We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).</span>
+We excluded meta-analyses that only contained evidence gathered from adults (age >18 years).
 
@@
 We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content (e.g., television programs, movies, games), homework, and communication (e.g., video chat).
-<span id = "r3_6">
 In this review we focused on electronic media exposure that would be considered typical for children and youth.
@@
 Consistent with this approach, we excluded technology-based treatments for clinical conditions.
-</span>
 However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning) for children and youth with a clinical condition.
@@
 However, a meta-analysis of interventions designed to *treat* clinical depression delivered by a mobile phone app would be excluded.
-<span id = "r3_7">
-*Outcomes*: We included all reported outcomes on benefits and risks.
-</span>
+
+Outcomes: We included all reported outcomes on benefits and risks.
 
@@
 We searched records contained in the following databases: Pubmed, MEDLINE, CINAHL, PsycINFO, SPORTDiscus, Education Source, Embase, Cochrane Library, Scopus, Web of Science, ProQuest Social Science Premium Collection, and ERIC.
-<span id = "r3_2">We conducted an initial search on August 17, 2018 and refreshed the search on September 27, 2022.</span>
+We conducted an initial search on August 17, 2018 and refreshed the search on September 27, 2022.
 We searched reference lists of included papers in order to identify additional eligible meta-analyses.
@@
 
-<span id ="r2_17">Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
+Two researchers independently extracted all quantitative meta-analytic effect sizes, including moderation results.
 We excluded effect sizes which were reported as relative risk ratios or odds ratios, as meta-analyses did not contain sufficient information to meaningfully convert to a correlation.
@@
 To facilitate comparisons, we converted effect sizes to Pearson's $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
-Effect sizes on the original metric are provided in Supplementary File 2.</span>
-<span id ="r2_27">Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines [@funderEvaluatingEffectSize2019]: very small (0.05 < r <= 0.1), small (0.1 < r <= 0.2), medium (0.2 < r <= 0.2), large (0.3 < r <= 0.4), and very large (r >= 0.4).
-These are similar to other interpretations based on empirical data [@gignacEffectSizeGuidelines2016].</span>
+Effect sizes on the original metric are provided in Supplementary File 2.
+Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines [@funderEvaluatingEffectSize2019]: very small (0.05 < r <= 0.1), small (0.1 < r <= 0.2), medium (0.2 < r <= 0.2), large (0.3 < r <= 0.4), and very large (r >= 0.4).
+These are similar to other interpretations based on empirical data [@gignacEffectSizeGuidelines2016].
 
@@
 
-<span id = "r3_8">After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
+After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
 In instances where effect sizes from the same combination of exposure and outcome were drawn from different age-groups (e.g., children vs adolescents), or were drawn using different study designs (e.g., cross-sectional vs longitudinal) we retained both estimates in our dataset.
-</span>
 
@@
 To test for publication bias, we conducted Egger's test [@eggerBiasMetaanalysisDetected1997] when the number of studies within the review was ten or more [@pageChapter13Assessing2021], and conducted a test of excess significance [@ioannidisExploratoryTestExcess2007].
-<span id = "r2_32">We contacted authors who did not provide primary study data in their published article.
-Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.</span>
+We contacted authors who did not provide primary study data in their published article.
+Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.
 
@@
 
-<span id = "r2_20">
 As described above, we have summarised the meta-analytic findings from all included systematic reviews.
@@
 Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 4.
-</span>
 

### 2023-06-15 reports/manuscript.tex
Remove revision letter and associated files

@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Systems and Populations, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} School of Medicine and Health, Sydney University, Sydney, Australia\\\textsuperscript{8} Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, University of Queensland, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}
 
@@
 Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation\textsuperscript{12} and numerous government agencies\textsuperscript{13,14} and statements by expert groups\textsuperscript{15} have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
-\protect\hypertarget{r2_8}{}{For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
+For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
 They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
@@
 This evidence has led some researchers to argue that a more nuanced approach to screen use guidelines is required.\textsuperscript{19}
-}
 
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-\protect\hypertarget{r2_9}{}{
 While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health\textsuperscript{21}), focus on a particular exposure (e.g., social media\textsuperscript{22,23}) or provide only a narrative summary of the literature.\textsuperscript{24}
-\protect\hypertarget{r1_2}{}{
 Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
@@
 These overviews provide a reference point for the field and allow for easier comparison of risks and benefits for the same behaviour.
-By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.}}
+By analogy, reading is a sedentary behaviour, and only by comparing the health risks against the educational benefits can researchers and policymakers make clear recommendations about what young people should do.
 
 In order to synthesise the evidence and support further evidence-based guideline development and refinement, we reviewed published meta-analyses examining the effects of screen use on children and youth.
-\protect\hypertarget{r2_6}{}{This review synthesises evidence on any outcome of electronic media exposure.
+This review synthesises evidence on any outcome of electronic media exposure.
 We deliberately did not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
 Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
-By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.}
+By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
 
@@
 The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
-\protect\hypertarget{r2_25}{}{Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.}
-\protect\hypertarget{r2_23}{}{After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.}
+Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
+Full characteristics of the included studies are provided in Table 1.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.
 These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
@@
 
-\protect\hypertarget{r1_5}{}{
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
@@
 However, in the absence of this work, our study has shown how children are affected by screens in general.
-}
 
@@
 
-\protect\hypertarget{r2_7}{}{
 In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
@@
 Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
-}
 
@@
 
-\protect\hypertarget{r1_1}{}{Our results highlight the need for the field to more carefully consider if the term `screen use' remains appropriate for providing advice to parents.
+Our results highlight the need for the field to more carefully consider if the term `screen use' remains appropriate for providing advice to parents.
 Instead, our results suggest that more nuanced and detailed descriptions of the behaviours to be modified may be required.
-Rather than suggesting parents limit `screen use', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.}
+Rather than suggesting parents limit `screen use', for example, it may be better to suggest that parents promote interactive educational experiences but limit exposure to advertising.
 
@@
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
-\protect\hypertarget{r2_24}{}{In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
+In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
 Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
-However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.}
+However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
 
-\protect\hypertarget{r1_4}{}{Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
+Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
 These likely depend on the specific exposure and outcome.
@@
 Many of the individual reviews go into more detail about the strength of the evidence for causal associations, but those judgements were difficult to synthesise across more than 200 reviews.
-Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.}
+Readers who wish to more deeply understand one specific relationship are directed to the cited review for that effect, where the authors could engage more deeply with the mechanisms.
 
-\protect\hypertarget{r2_16}{}{We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
+We converted all effect sizes to a common metric (Pearson's r) to allow for comparisons of magnitude, but acknowledge that this assumes a linear relationship between the variables.
 Some previous research suggests that associations are typically linear.\textsuperscript{18}
@@
 Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
-Care is needed, therefore, when interpreting the effect sizes.}
-\protect\hypertarget{r3_2_2}{}{In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
-While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.}
+Care is needed, therefore, when interpreting the effect sizes.
+In addition, reviews provide only historical evidence which may not keep up with the changing ways children can engage with screens.
+While our synthesis of the existing evidence provides information about how screens might have influenced children in the past, it is difficult to know if these findings will translate to new forms of technology in the future.
 
@@
 To be eligible for inclusion, meta-analyses needed to include meta-analytic effect sizes for children or adolescents (age 0-18 years).
-\protect\hypertarget{r3_5}{}{We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was \textless{} 18 years).
+We included meta-analyses containing studies that combined data from adults and youth if meta-analytic effect size estimates specific to participants aged 18 years or less could be extracted (i.e., the highest mean age for any individual study included in the meta-analysis was \textless{} 18 years).
 A meta-analysis was still included if the age range exceed 18 years, provided that the mean age was less than 18.
-We excluded meta-analyses that only contained evidence gathered from adults (age \textgreater18 years).}
+We excluded meta-analyses that only contained evidence gathered from adults (age \textgreater18 years).
 
@@
 We also included analyses of all types of content on these devices, including (but not necessarily limited to) recreational content (e.g., television programs, movies, games), homework, and communication (e.g., video chat).
-\protect\hypertarget{r3_6}{}{
 In this review we focused on electronic media exposure that would be considered typical for children and youth.
@@
 Consistent with this approach, we excluded technology-based treatments for clinical conditions.
-}
 However, we included studies examining the effect of screen exposure on non-clinical outcomes (e.g., learning) for children and youth with a clinical condition.
@@
 However, a meta-analysis of interventions designed to \emph{treat} clinical depression delivered by a mobile phone app would be excluded.
-\protect\hypertarget{r3_7}{}{
-\emph{Outcomes}: We included all reported outcomes on benefits and risks.
-}
+
+Outcomes: We included all reported outcomes on benefits and risks.
 
@@
 We searched records contained in the following databases: Pubmed, MEDLINE, CINAHL, PsycINFO, SPORTDiscus, Education Source, Embase, Cochrane Library, Scopus, Web of Science, ProQuest Social Science Premium Collection, and ERIC.
-\protect\hypertarget{r3_2}{}{We conducted an initial search on August 17, 2018 and refreshed the search on September 27, 2022.}
+We conducted an initial search on August 17, 2018 and refreshed the search on September 27, 2022.
 We searched reference lists of included papers in order to identify additional eligible meta-analyses.
@@
 Effect sizes on the original metric are provided in Supplementary File 2.
-\protect\hypertarget{r2_27}{}{Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
-These are similar to other interpretations based on empirical data.\textsuperscript{53}}
+Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
+These are similar to other interpretations based on empirical data.\textsuperscript{53}
 
@@
 
-\protect\hypertarget{r3_8}{}{After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
+After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared multiple times (i.e., in multiple meta-analyses, or with multiple sub-groups in the same meta-analysis), keeping the effect with the largest total sample size.
 In instances where effect sizes from the same combination of exposure and outcome were drawn from different age-groups (e.g., children vs adolescents), or were drawn using different study designs (e.g., cross-sectional vs longitudinal) we retained both estimates in our dataset.
-}
 
@@
 To test for publication bias, we conducted Egger's test\textsuperscript{56} when the number of studies within the review was ten or more,\textsuperscript{57} and conducted a test of excess significance.\textsuperscript{58}
-\protect\hypertarget{r2_32}{}{We contacted authors who did not provide primary study data in their published article.
-Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.}
+We contacted authors who did not provide primary study data in their published article.
+Where authors did not provide data in a format that could be re-analysed, we used the published results of their original meta-analysis.
 
@@
 
-\protect\hypertarget{r2_20}{}{
 As described above, we have summarised the meta-analytic findings from all included systematic reviews.
@@
 Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 4.
-}
 

### 2023-06-15 reports/manuscript.Rmd
Move sections around to match required format
Update affiliations

@@
   - name          : "Borja Del Pozo Cruz"
-    affiliation   : "3"
+    affiliation   : "3, 14, 15"
   - name          : "Stuart Biddle"
@@
     institution   : "Faculty of Sport & Health Sciences, University of Jyväskylä, Finland"
+  - id            : "14"
+    institution   : "Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain"
+  - id            : "15"
+    institution   : "Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain"
 
@@
 
-\newpage
-
-# References
-
-<div id = "refs"></div>
-
-\newpage
-
 # Acknowledgements
@@
 
+# Tables
+
+*Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects*
+
 # Figure legends
@@
 
-# Tables
+\newpage
 
-*Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects*
+# References
+
+<div id = "refs"></div>
+
+\newpage

### 2023-06-19 reports/manuscript.tex
Rerun pipeline

@@
   man]{apa6}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
-  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
+  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, 14, 15, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
   pdflang={en-EN},
@@
 \usepackage{colortbl}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \else
-  \usepackage[shorthands=off,main=english]{babel}
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
 \fi
@@
 \setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {}%
-  {\par}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
 \title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
-\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
+\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3, 14, 15}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland\\\textsuperscript{14} Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain\\\textsuperscript{15} Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain}
 
@@
 Since then, a large number of systematic reviews and meta-analyses have provided evidence about the potential benefits and risks of screen use.
-While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health\textsuperscript{21}), focus on a particular exposure (e.g., social media\textsuperscript{22,23}) or provide only a narrative summary of the literature.\textsuperscript{24}
+While there have been other overviews of reviews on screen use, these have tended to focus on a single domain (e.g., health),\textsuperscript{21} focus on a particular exposure (e.g., social media)\textsuperscript{22,23} or provide only a narrative summary of the literature.\textsuperscript{24}
 Focusing on a single domain or exposure makes it difficult to understand what trade-offs are involved in any guidelines around screen use.
@@
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning)\textsuperscript{26} tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning).\textsuperscript{27}
 The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
@@
 Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{43}
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers\textsuperscript{45}---these are still not widely adopted.
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers---\textsuperscript{45}these are still not widely adopted.
 It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
@@
 For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{46}).
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{46}
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
@@
 
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
-\begin{cslreferences}
-\leavevmode\hypertarget{ref-blairReadingStrategiesCoping2003}{}%
-1. Blair, A. Reading Strategies for Coping With Information Overload ca.1550-1700. \emph{Journal of the History of Ideas} \textbf{64}, 11--28 (2003).
-
-\leavevmode\hypertarget{ref-bell1883sanitarian}{}%
-2. Bell, A. N. \emph{The sanitarian}. vol. 11 (AN Bell, 1883).
-
-\leavevmode\hypertarget{ref-dill2013oxford}{}%
-3. Dill, K. E. \emph{The Oxford handbook of media psychology}. (Oxford University Press, 2013).
-
-\leavevmode\hypertarget{ref-wartellaChildrenComputersNew2000}{}%
-4. Wartella, E. A. \& Jennings, N. Children and computers: New technology. Old concerns. \emph{The future of children} 31--43 (2000).
-
-\leavevmode\hypertarget{ref-rhodes2015top}{}%
-5. Rhodes, A. \emph{Top ten child health problems: What the public thinks}. (2015).
-
-\leavevmode\hypertarget{ref-thelancetSocialMediaScreen2019}{}%
-6. The Lancet. Social media, screen time, and young people's mental health. \emph{The Lancet} \textbf{393}, 611 (2019).
-
-\leavevmode\hypertarget{ref-haleScreenTimeSleep2015}{}%
-7. Hale, L. \& Guan, S. Screen time and sleep among school-aged children and adolescents: A systematic literature review. \emph{Sleep Medicine Reviews} \textbf{21}, 50--58 (2015).
-
-\leavevmode\hypertarget{ref-sweetserActivePassiveScreen2012}{}%
-8. Sweetser, P., Johnson, D., Ozdowska, A. \& Wyeth, P. Active versus passive screen time for young children. \emph{Australasian Journal of Early Childhood} \textbf{37}, 94--98 (2012).
-
-\leavevmode\hypertarget{ref-liEarlyChildhoodComputer2004}{}%
-9. Li, X. \& Atkins, M. S. Early childhood computer experience and cognitive and motor development. \emph{Pediatrics} \textbf{113}, 1715--1722 (2004).
-
-\leavevmode\hypertarget{ref-warburton2017children}{}%
-10. Warburton, W. \& Highfield, K. Children and technology in a smart device world. in \emph{Children, Families and Communities} 195--221 (Oxford University Press, 2017).
-
-\leavevmode\hypertarget{ref-naturehumanbehaviourScreenTimeHow2019}{}%
-11. Nature Human Behaviour. Screen time: How much is too much? \emph{Nature} \textbf{565}, 265--266 (2019).
-
-\leavevmode\hypertarget{ref-whoGuidelinesPhysicalActivity2019}{}%
-12. World Health Organization. \emph{Guidelines on physical activity, sedentary behaviour and sleep for children under 5 years of age}. 33 p. (World Health Organization, 2019).
-
-\leavevmode\hypertarget{ref-australiangovernmentPhysicalActivityExercise2021}{}%
-13. Australian Government. \emph{Physical activity and exercise guidelines for all Australians}. (2021).
-
-\leavevmode\hypertarget{ref-Canadian24HourMovement2016}{}%
-14. Canadian Society for Exercise Physiology. \emph{Canadian 24-Hour Movement Guidelines for Children and Youth: An Integration of Physical Activity, Sedentary Behaviour, and Sleep}. (2016).
-
-\leavevmode\hypertarget{ref-AAPMediaUseSchoolAged2016}{}%
-15. Council On Communication and Media. Media Use in School-Aged Children and Adolescents. \emph{Pediatrics} \textbf{138}, e20162592 (2016).
-
-\leavevmode\hypertarget{ref-fergusonEverythingModerationModerate2017}{}%
-16. Ferguson, C. J. Everything in Moderation: Moderate Use of Screens Unassociated with Child Behavior Problems. \emph{Psychiatric Quarterly} \textbf{88}, 797--805 (2017).
-
-\leavevmode\hypertarget{ref-przybylskiLargeScaleTestGoldilocks2017}{}%
-17.
-Przybylski, A.
-K.
-\& Weinstein, N.
-A Large-Scale Test of the Goldilocks Hypothesis: Quantifying the Relations Between Digital-Screen Use and the Mental Well-Being of Adolescents.
-\emph{Psychological Science} \textbf{28}, 204--215 (2017).
-
-\leavevmode\hypertarget{ref-sandersTypeScreenTime2019}{}%
-18.
-Sanders, T., Parker, P.
-D., del Pozo-Cruz, B., Noetel, M.
-\& Lonsdale, C.
-Type of screen time moderates effects on outcomes in 4013 children: Evidence from the Longitudinal Study of Australian Children.
-\emph{International Journal of Behavioral Nutrition and Physical Activity} \textbf{16}, 117 (2019).
-
-\leavevmode\hypertarget{ref-kayeConceptualMethodologicalMayhem2020}{}%
-19.
-Kaye, L.
-K., Orben, A., Ellis, D.
-A., Hunter, S.
-C.
-\& Houghton, S.
-The Conceptual and Methodological Mayhem of `Screen Time'.
-\emph{International Journal of Environmental Research and Public Health} \textbf{17}, 3661 (2020).
-
-\leavevmode\hypertarget{ref-chassiakosChildrenAdolescentsDigital2016}{}%
-20. Chassiakos, Y. L. R. \emph{et al.} Children and Adolescents and Digital Media. \emph{Pediatrics} \textbf{138}, e20162593 (2016).
-
-\leavevmode\hypertarget{ref-stiglicEffectsScreentimeHealth2019}{}%
-21. Stiglic, N. \& Viner, R. M. Effects of screentime on the health and well-being of children and adolescents: A systematic review of reviews. \emph{BMJ Open} \textbf{9}, e023191 (2019).
-
-\leavevmode\hypertarget{ref-valkenburgSocialMediaUse2022}{}%
-22.
-Valkenburg, P.
-M., Meier, A.
-\& Beyens, I.
-Social media use and its impact on adolescent mental health: An umbrella review of the evidence.
-\emph{Current Opinion in Psychology} \textbf{44}, 58--68 (2022).
-
-\leavevmode\hypertarget{ref-arias-delatorreRelationshipDepressionUse2020}{}%
-23.
-Arias-de la Torre, J.
-\emph{et al.} Relationship Between Depression and the Use of Mobile Technologies and Social Media Among Adolescents: Umbrella Review.
-\emph{Journal of Medical Internet Research} \textbf{22}, e16388 (2020).
-
-\leavevmode\hypertarget{ref-orbenTeenagersScreensSocial2020}{}%
-24. Orben, A. Teenagers, screens and social media: A narrative review of reviews and key studies. \emph{Social Psychiatry and Psychiatric Epidemiology} \textbf{55}, 407--414 (2020).
-
-\leavevmode\hypertarget{ref-pollockChapterOverviewsReviews2022}{}%
-25.
-Pollock, M., Fernandes, R., Becker, L., Pieper, D.
-\& Hartling, L.
-Chapter V: Overviews of Reviews.
-in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds.
-Higgins, J.
-P.
-et al.) (Cochrane, 2022).
-
-\leavevmode\hypertarget{ref-xieCanTouchscreenDevices2018}{}%
-26.
-Xie, H.
-\emph{et al.} Can Touchscreen Devices be Used to Facilitate Young Children's Learning?
-A Meta-Analysis of Touchscreen Learning Effect.
-\emph{Frontiers in Psychology} \textbf{9}, 2580 (2018).
-
-\leavevmode\hypertarget{ref-adelantado-renauAssociationScreenMedia2019}{}%
-27.
-Adelantado-Renau, M.
-\emph{et al.} Association Between Screen Media Use and Academic Performance Among Children and Adolescents: A Systematic Review and Meta-analysis.
-\emph{JAMA Pediatrics} \textbf{173}, 1058 (2019).
-
-\leavevmode\hypertarget{ref-madiganAssociationsScreenUse2020}{}%
-28.
-Madigan, S., McArthur, B.
-A., Anhorn, C., Eirich, R.
-\& Christakis, D.
-A.
-Associations Between Screen Use and Child Language Skills: A Systematic Review and Meta-analysis.
-\emph{JAMA Pediatrics} \textbf{174}, 665 (2020).
-
-\leavevmode\hypertarget{ref-poorolajalBehavioralFactorsInfluencing2020}{}%
-29.
-Poorolajal, J., Sahraei, F., Mohamdadi, Y., Doosti-Irani, A.
-\& Moradi, L.
-Behavioral factors influencing childhood obesity: A systematic review and meta-analysis.
-\emph{Obesity Research \& Clinical Practice} \textbf{14}, 109--118 (2020).
-
-\leavevmode\hypertarget{ref-byunDigitalGamebasedLearning2018}{}%
-30. Byun, J. \& Joung, E. Digital game-based learning for K-12 mathematics education: A meta-analysis. \emph{School Science and Mathematics} \textbf{118}, 113--126 (2018).
-
-\leavevmode\hypertarget{ref-vannucciSocialMediaUse2020}{}%
-31. Vannucci, A., Simpson, E. G., Gagnon, S. \& Ohannessian, C. M. Social media use and risky behaviors in adolescents: A meta-analysis. \emph{Journal of Adolescence} \textbf{79}, 258--274 (2020).
-
-\leavevmode\hypertarget{ref-yoonSocialNetworkSite2019}{}%
-32.
-Yoon, S., Kleinman, M., Mertz, J.
-\& Brannick, M.
-Is social network site usage related to depression?
-A meta-analysis of FacebookDepression relations.
-\emph{Journal of Affective Disorders} \textbf{248}, 65--72 (2019).
-
-\leavevmode\hypertarget{ref-vahediAssociationSelfreportedDepressive2021}{}%
-33.
-Vahedi, Z.
-\& Zannella, L.
-The association between self-reported depressive symptoms and the use of social networking sites (SNS): A meta-analysis.
-\emph{Current Psychology} \textbf{40}, 2174--2189 (2021).
-
-\leavevmode\hypertarget{ref-seetharamanFacebookKnowsInstagram2021}{}%
-34. Seetharaman, G. W., Jeff Horwitz and Deepa. Facebook Knows Instagram Is Toxic for Teen Girls, Company Documents Show. \emph{Wall Street Journal} (2021).
-
-\leavevmode\hypertarget{ref-tekedereExaminingEffectivenessAugmented2016}{}%
-35.
-Tekedere, H.
-\& Göke, H.
-Examining the Effectiveness of Augmented Reality Applications in Education: A Meta-Analysis.
-\emph{International Journal of Environmental and Science Education} \textbf{11}, 9469--9481 (2016).
-
-\leavevmode\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}%
-36.
-Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N.
-R.
-C.
-\& Johnston, B.
-C.
-Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials.
-\emph{Obesity Reviews} \textbf{17}, 945--959 (2016).
-
-\leavevmode\hypertarget{ref-marshallRelationshipsMediaUse2004}{}%
-37.
-Marshall, S.
-J., Biddle, S.
-J.
-H., Gorely, T., Cameron, N.
-\& Murdey, I.
-Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis.
-\emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).
-
-\leavevmode\hypertarget{ref-elsonPolicyStatementsMedia2019}{}%
-38. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).
-
-\leavevmode\hypertarget{ref-ashtonScreenTimeChildren2019}{}%
-39. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).
-
-\leavevmode\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}%
-40. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).
-
-\leavevmode\hypertarget{ref-pagePRISMA2020Statement2020}{}%
-41. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.
-
-\leavevmode\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}%
-42. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).
-
-\leavevmode\hypertarget{ref-byrneMeasurementScreenTime2021}{}%
-43. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).
-
-\leavevmode\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}%
-44.
-Smith, C., Galland, B.
-C., de Bruin, W.
-E.
-\& Taylor, R.
-W.
-Feasibility of automated cameras to measure screen use in adolescents.
-\emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).
-
-\leavevmode\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}%
-45. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).
-
-\leavevmode\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}%
-46. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).
-
-\leavevmode\hypertarget{ref-twengeMoreTimeTechnology2019}{}%
-47.
-Twenge, J.
-M.
-More Time on Technology, Less Happiness?
-Associations Between Digital-Media Use and Psychological Well-Being.
-\emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).
-
-\leavevmode\hypertarget{ref-kellySocialMediaUse2018}{}%
-48. Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social Media Use and Adolescent Mental Health: Findings From the UK Millennium Cohort Study. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).
-
-\leavevmode\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}%
-49. National Health, Lung, and Blood Institute. \emph{Quality Assessment of Systematic Reviews and Meta-Analyses}. (2014).
-
-\leavevmode\hypertarget{ref-bowmanEffectSizesStatistical2012}{}%
-50. Bowman, N. A. Effect Sizes and Statistical Methods for Meta-Analysis in Higher Education. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).
-
-\leavevmode\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}%
-51.
-Jacobs, P.
-\& Viechtbauer, W.
-Estimation of the biserial correlation and its sampling variance for use in meta-analysis: Biserial Correlation.
-\emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).
-
-\leavevmode\hypertarget{ref-funderEvaluatingEffectSize2019}{}%
-52. Funder, D. C. \& Ozer, D. J. Evaluating Effect Size in Psychological Research: Sense and Nonsense. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).
-
-\leavevmode\hypertarget{ref-gignacEffectSizeGuidelines2016}{}%
-53. Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).
-
-\leavevmode\hypertarget{ref-R-metafor}{}%
-54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2022).
-
-\leavevmode\hypertarget{ref-R-base}{}%
-55. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).
-
-\leavevmode\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}%
-56. Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).
-
-\leavevmode\hypertarget{ref-pageChapter13Assessing2021}{}%
-57.
-Page, M.
-J., Higgins, J.
-P.
-\& Sterne, J.
-A.
-Chapter 13: Assessing risk of bias due to missing results in a synthesis.
-in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds.
-Higgins, J.
-P.
-et al.) (Cochrane, 2021).
-
-\leavevmode\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}%
-58. Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).
-
-\leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
-59. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
-\end{cslreferences}
-
-\newpage
-
 \hypertarget{acknowledgements}{%
@@
 
+\hypertarget{tables}{%
+\section{Tables}\label{tables}}
+
+\emph{Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects}
+
 \hypertarget{figure-legends}{%
@@
 
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
+\newpage
 
-\emph{Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects}
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-blairReadingStrategiesCoping2003}{}}%
+\CSLLeftMargin{1. }
+\CSLRightInline{Blair, A. Reading {Strategies} for {Coping With Information Overload} ca.1550-1700. \emph{Journal of the History of Ideas} \textbf{64}, 11--28 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bell1883sanitarian}{}}%
+\CSLLeftMargin{2. }
+\CSLRightInline{Bell, A. N. \emph{The sanitarian}. vol. 11 ({AN Bell}, 1883).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dill2013oxford}{}}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Dill, K. E. \emph{The {Oxford} handbook of media psychology}. ({Oxford University Press}, 2013).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wartellaChildrenComputersNew2000}{}}%
+\CSLLeftMargin{4. }
+\CSLRightInline{Wartella, E. A. \& Jennings, N. Children and computers: {New} technology. {Old} concerns. \emph{The future of children} 31--43 (2000).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rhodes2015top}{}}%
+\CSLLeftMargin{5. }
+\CSLRightInline{Rhodes, A. \emph{Top ten child health problems: {What} the public thinks}. (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-thelancetSocialMediaScreen2019}{}}%
+\CSLLeftMargin{6. }
+\CSLRightInline{The Lancet. Social media, screen time, and young people's mental health. \emph{The Lancet} \textbf{393}, 611 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-haleScreenTimeSleep2015}{}}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Hale, L. \& Guan, S. Screen time and sleep among school-aged children and adolescents: {A} systematic literature review. \emph{Sleep Medicine Reviews} \textbf{21}, 50--58 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sweetserActivePassiveScreen2012}{}}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Sweetser, P., Johnson, D., Ozdowska, A. \& Wyeth, P. Active versus passive screen time for young children. \emph{Australasian Journal of Early Childhood} \textbf{37}, 94--98 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-liEarlyChildhoodComputer2004}{}}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Li, X. \& Atkins, M. S. Early childhood computer experience and cognitive and motor development. \emph{Pediatrics} \textbf{113}, 1715--1722 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-warburton2017children}{}}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Warburton, W. \& Highfield, K. Children and technology in a smart device world. in \emph{Children, {Families} and {Communities}} 195--221 ({Oxford University Press}, 2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-naturehumanbehaviourScreenTimeHow2019}{}}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Nature Human Behaviour. Screen time: How much is too much? \emph{Nature} \textbf{565}, 265--266 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-whoGuidelinesPhysicalActivity2019}{}}%
+\CSLLeftMargin{12. }
+\CSLRightInline{World Health Organization. \emph{Guidelines on physical activity, sedentary behaviour and sleep for children under 5 years of age}. 33 p. ({World Health Organization}, 2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-australiangovernmentPhysicalActivityExercise2021}{}}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Australian Government. \emph{Physical activity and exercise guidelines for all {Australians}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Canadian24HourMovement2016}{}}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Canadian Society for Exercise Physiology.
+\emph{Canadian 24-{Hour Movement Guidelines} for {Children} and {Youth}: {An Integration} of {Physical Activity}, {Sedentary Behaviour}, and {Sleep}}.
+(2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-AAPMediaUseSchoolAged2016}{}}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Council On Communication and Media. Media {Use} in {School-Aged Children} and {Adolescents}. \emph{Pediatrics} \textbf{138}, e20162592 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fergusonEverythingModerationModerate2017}{}}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Ferguson, C. J. Everything in {Moderation}: {Moderate Use} of {Screens Unassociated} with {Child Behavior Problems}. \emph{Psychiatric Quarterly} \textbf{88}, 797--805 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-przybylskiLargeScaleTestGoldilocks2017}{}}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Przybylski, A.
+K.
+\& Weinstein, N.
+A {Large-Scale Test} of the {Goldilocks Hypothesis}: {Quantifying} the {Relations Between Digital-Screen Use} and the {Mental Well-Being} of {Adolescents}.
+\emph{Psychological Science} \textbf{28}, 204--215 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sandersTypeScreenTime2019}{}}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Sanders, T., Parker, P.
+D., del Pozo-Cruz, B., Noetel, M.
+\& Lonsdale, C.
+Type of screen time moderates effects on outcomes in 4013 children: Evidence from the {Longitudinal Study} of {Australian Children}.
+\emph{International Journal of Behavioral Nutrition and Physical Activity} \textbf{16}, 117 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kayeConceptualMethodologicalMayhem2020}{}}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Kaye, L.
+K., Orben, A., Ellis, D.
+A., Hunter, S.
+C.
+\& Houghton, S.
+The {Conceptual} and {Methodological Mayhem} of {`{Screen Time}'}.
+\emph{International Journal of Environmental Research and Public Health} \textbf{17}, 3661 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-chassiakosChildrenAdolescentsDigital2016}{}}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Chassiakos, Y. L. R. \emph{et al.} Children and {Adolescents} and {Digital Media}. \emph{Pediatrics} \textbf{138}, e20162593 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-stiglicEffectsScreentimeHealth2019}{}}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Stiglic, N. \& Viner, R. M. Effects of screentime on the health and well-being of children and adolescents: A systematic review of reviews. \emph{BMJ Open} \textbf{9}, e023191 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-valkenburgSocialMediaUse2022}{}}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Valkenburg, P.
+M., Meier, A.
+\& Beyens, I.
+Social media use and its impact on adolescent mental health: {An} umbrella review of the evidence.
+\emph{Current Opinion in Psychology} \textbf{44}, 58--68 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-arias-delatorreRelationshipDepressionUse2020}{}}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Arias-de la Torre, J.
+\emph{et al.} Relationship {Between Depression} and the {Use} of {Mobile Technologies} and {Social Media Among Adolescents}: {Umbrella Review}.
+\emph{Journal of Medical Internet Research} \textbf{22}, e16388 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-orbenTeenagersScreensSocial2020}{}}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Orben, A. Teenagers, screens and social media: A narrative review of reviews and key studies. \emph{Social Psychiatry and Psychiatric Epidemiology} \textbf{55}, 407--414 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pollockChapterOverviewsReviews2022}{}}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Pollock, M., Fernandes, R., Becker, L., Pieper, D.
+\& Hartling, L.
+Chapter {V}: {Overviews} of {Reviews}.
+in \emph{Cochrane {Handbook} for {Systematic Reviews} of {Interventions}} (eds.
+Higgins, J.
+P.
+et al.) ({Cochrane}, 2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xieCanTouchscreenDevices2018}{}}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Xie, H.
+\emph{et al.} Can {Touchscreen Devices} be {Used} to {Facilitate Young Children}'s {Learning}?
+{A Meta-Analysis} of {Touchscreen Learning Effect}.
+\emph{Frontiers in Psychology} \textbf{9}, 2580 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-adelantado-renauAssociationScreenMedia2019}{}}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Adelantado-Renau, M.
+\emph{et al.} Association {Between Screen Media Use} and {Academic Performance Among Children} and {Adolescents}: {A Systematic Review} and {Meta-analysis}.
+\emph{JAMA Pediatrics} \textbf{173}, 1058 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-madiganAssociationsScreenUse2020}{}}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Madigan, S., McArthur, B.
+A., Anhorn, C., Eirich, R.
+\& Christakis, D.
+A.
+Associations {Between Screen Use} and {Child Language Skills}: {A Systematic Review} and {Meta-analysis}.
+\emph{JAMA Pediatrics} \textbf{174}, 665 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-poorolajalBehavioralFactorsInfluencing2020}{}}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Poorolajal, J., Sahraei, F., Mohamdadi, Y., Doosti-Irani, A.
+\& Moradi, L.
+Behavioral factors influencing childhood obesity: A systematic review and meta-analysis.
+\emph{Obesity Research \& Clinical Practice} \textbf{14}, 109--118 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byunDigitalGamebasedLearning2018}{}}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Byun, J. \& Joung, E. Digital game-based learning for {K-12} mathematics education: {A} meta-analysis. \emph{School Science and Mathematics} \textbf{118}, 113--126 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vannucciSocialMediaUse2020}{}}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Vannucci, A., Simpson, E.
+G., Gagnon, S.
+\& Ohannessian, C.
+M.
+Social media use and risky behaviors in adolescents: {A} meta-analysis.
+\emph{Journal of Adolescence} \textbf{79}, 258--274 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-yoonSocialNetworkSite2019}{}}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Yoon, S., Kleinman, M., Mertz, J.
+\& Brannick, M.
+Is social network site usage related to depression?
+{A} meta-analysis of {Facebook}\textendash depression relations.
+\emph{Journal of Affective Disorders} \textbf{248}, 65--72 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vahediAssociationSelfreportedDepressive2021}{}}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Vahedi, Z.
+\& Zannella, L.
+The association between self-reported depressive symptoms and the use of social networking sites ({SNS}): {A} meta-analysis.
+\emph{Current Psychology} \textbf{40}, 2174--2189 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-seetharamanFacebookKnowsInstagram2021}{}}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Seetharaman, G. W., Jeff Horwitz and Deepa. Facebook {Knows Instagram Is Toxic} for {Teen Girls}, {Company Documents Show}. \emph{Wall Street Journal} (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tekedereExaminingEffectivenessAugmented2016}{}}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Tekedere, H.
+\& Göke, H.
+Examining the {Effectiveness} of {Augmented Reality Applications} in {Education}: {A Meta-Analysis}.
+\emph{International Journal of Environmental and Science Education} \textbf{11}, 9469--9481 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N.
+R.
+C.
+\& Johnston, B.
+C.
+Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials.
+\emph{Obesity Reviews} \textbf{17}, 945--959 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-marshallRelationshipsMediaUse2004}{}}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Marshall, S.
+J., Biddle, S.
+J.
+H., Gorely, T., Cameron, N.
+\& Murdey, I.
+Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis.
+\emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-elsonPolicyStatementsMedia2019}{}}%
+\CSLLeftMargin{38. }
+\CSLRightInline{Elson, M.
+\emph{et al.} Do policy statements on media effects faithfully represent the science?
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ashtonScreenTimeChildren2019}{}}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Ashton, J.
+J.
+\& Beattie, R.
+M.
+Screen time in children and adolescents: Is there evidence to guide parents and policy?
+\emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: {A} guide for clinicians and parents.} (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pagePRISMA2020Statement2020}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Page, M.
+J.
+\emph{et al.} \emph{The {PRISMA} 2020 statement: An updated guideline for reporting systematic reviews}.
+(2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Parry, D.
+A.
+\emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use.
+\emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byrneMeasurementScreenTime2021}{}}%
+\CSLLeftMargin{43. }
+\CSLRightInline{Byrne, R., Terranova, C.
+O.
+\& Trost, S.
+G.
+Measurement of screen time among young children aged 0\textendash 6 years: {A} systematic review.
+\emph{Obesity Reviews} \textbf{22}, (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}}%
+\CSLLeftMargin{44. }
+\CSLRightInline{Smith, C., Galland, B.
+C., de Bruin, W.
+E.
+\& Taylor, R.
+W.
+Feasibility of automated cameras to measure screen use in adolescents.
+\emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Ryding, F.
+C.
+\& Kuss, D.
+J.
+Passive objective measures in the assessment of problematic smartphone use: {A} systematic review.
+\emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}}%
+\CSLLeftMargin{46. }
+\CSLRightInline{Guyatt, G.
+\emph{et al.} {GRADE} guidelines: 1.
+{Introduction}\textemdash{{GRADE}} evidence profiles and summary of findings tables.
+\emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-twengeMoreTimeTechnology2019}{}}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Twenge, J.
+M.
+More {Time} on {Technology}, {Less Happiness}?
+{Associations Between Digital-Media Use} and {Psychological Well-Being}.
+\emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kellySocialMediaUse2018}{}}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Kelly, Y., Zilanawala, A., Booker, C.
+\& Sacker, A.
+Social {Media Use} and {Adolescent Mental Health}: {Findings From} the {UK Millennium Cohort Study}.
+\emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}}%
+\CSLLeftMargin{49. }
+\CSLRightInline{National Health, Lung, and Blood Institute. \emph{Quality {Assessment} of {Systematic Reviews} and {Meta-Analyses}}. (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bowmanEffectSizesStatistical2012}{}}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Bowman, N. A. Effect {Sizes} and {Statistical Methods} for {Meta-Analysis} in {Higher Education}. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Jacobs, P.
+\& Viechtbauer, W.
+Estimation of the biserial correlation and its sampling variance for use in meta-analysis: {Biserial Correlation}.
+\emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-funderEvaluatingEffectSize2019}{}}%
+\CSLLeftMargin{52. }
+\CSLRightInline{Funder, D.
+C.
+\& Ozer, D.
+J.
+Evaluating {Effect Size} in {Psychological Research}: {Sense} and {Nonsense}.
+\emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gignacEffectSizeGuidelines2016}{}}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-metafor}{}}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+\CSLLeftMargin{55. }
+\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pageChapter13Assessing2021}{}}%
+\CSLLeftMargin{57. }
+\CSLRightInline{Page, M.
+J., Higgins, J.
+P.
+\& Sterne, J.
+A.
+Chapter 13: {Assessing} risk of bias due to missing results in a synthesis.
+in \emph{Cochrane {Handbook} for {Systematic Reviews} of {Interventions}} (eds.
+Higgins, J.
+P.
+et al.) ({Cochrane}, 2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}}%
+\CSLLeftMargin{58. }
+\CSLRightInline{Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).}
+
+\end{CSLReferences}
+
+\newpage
 

### 2023-06-20 reports/manuscript.Rmd
Address some comment in manuscript

@@
   However, other forms of screen use showed associations with benefits.
-  For example, experimental evidence showed that video games improve aspects of cognitive function.
+  For example, educational screen use was generally associted with better learning outcomes.
   Some types of screen use have complex associations with outcomes.
-  For example, general screen use (i.e., content not indicated) showed correlations with harm for body composition, depression, and learning.
+  For example, television viewing showed harmful correlations with body composition and learning.
   However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
@@
 Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
-General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
-Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents.
 All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
-Additionally, most effects were small, with the association between screen use and sleep duration the largest at $r = -0.37$ ($k = 10, N = 56,720$).
+Additionally, most effects were small, with the association between internet use and depression the largest at $r = 0.25$ ($k = 118, N = 527,696$).
 Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.
@@
 Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
-We used thresholds of $P < .05$ for weak evidence and $P < 10^{-3}$ for strong evidence.
-An effect with statistical credibility but with $P > .05$ was taken to indicate no association of interest.
+We used thresholds of $P < .05$ for weak evidence (i.e., 95% confidence intervals did not cross zero) and $P < 10^{-3}$ (i.e., 99.9% confidence intervals did not cross zero) for strong evidence.
+An effect with statistical credibility but with $P > .05$ (i.e., 95% confidence intervals included zero) was taken to indicate no association of interest.
 

### 2023-06-20 reports/manuscript.Rmd
Unlink table 1 and RoB
Also had to rename all the supp materials

@@
 The most frequently reported exposures were `r manuscript_info$freq_exposures`.
-Supplementary File 5 provides a list of all exposures identified.
+Supplementary File 1 provides a list of all exposures identified.
 The most frequently reported outcomes were `r manuscript_info$freq_outcomes`.
 Of the `r manuscript_info$unique_combos` unique exposure/outcome combinations, `r manuscript_info$freq_combos$n1` occurred in only one review, with `r manuscript_info$freq_combos$n2` appearing twice, and `r manuscript_info$freq_combos$ngt2` appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.
+Full characteristics of the included studies are provided in Supplementary File 2.
 After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.
 These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies, involving `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
-The characteristics of the included effects are available in Supplementary File 9.
+The characteristics of the included effects are available in Supplementary File 3.
 
@@
 We removed `r manuscript_info$edu$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$edu$n_samplesize` effects with samples < 1,000, and `r manuscript_info$edu$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in Supplementary File 6.
+Effects not meeting one or more of these standards are presented in Supplementary File 4.
 The remaining `r manuscript_info$edu$n_certain` effects met our criteria for statistical credibility and are described in Figure 2.
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in Supplementary File 7.
+Effects not meeting one or more of these standards are presented in Supplementary File 5.
 The remaining `r manuscript_info$health$n_certain` meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
@@
 However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits [@byunDigitalGamebasedLearning2018].
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 & 7) therefore this hypothesis could not be addressed.
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 & 5) therefore this hypothesis could not be addressed.
 
@@
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
+If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Files 4 & 5).
 For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
@@
 Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (*k*) or the most recent review by publication year.
-However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+However, we provide the complete results in Supplementary Files 4 & 5, along with the dataset (Supplementary File 6) for others to consider alternative criteria.
 
@@
 
-The search strategy associated with each of the 12 databases can be found in Supplementary File 1.
+The search strategy associated with each of the 12 databases can be found in Supplementary File 7.
 We hand searched reference lists from any relevant umbrella reviews to identify systematic meta-analyses that our search may have missed.
@@
 To facilitate comparisons, we converted effect sizes to Pearson's $r$ using established formulae [@bowmanEffectSizesStatistical2012;@jacobsEstimationBiserialCorrelation2017].
-Effect sizes on the original metric are provided in Supplementary File 2.
+Effect sizes on the original metric are provided in Supplementary File 6.
 Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines [@funderEvaluatingEffectSize2019]: very small (0.05 < r <= 0.1), small (0.1 < r <= 0.2), medium (0.2 < r <= 0.2), large (0.3 < r <= 0.4), and very large (r >= 0.4).
@@
 However, we determined that combining results from the meta-analyses alone allow readers to compare relative strength of associations more easily.
-Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 4.
+Readers interested in the relevant systematic reviews (i.e., without meta-analysis) can consult the list of references in Supplementary File 8.
 

### 2023-06-20 reports/manuscript.tex
Unlink table 1 and RoB
Also had to rename all the supp materials

--- 2023-06-15 reports/manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5394}
+\keywords{\newline\indent Word count: 5405}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
-\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
+\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3, 14, 15}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
 \date{}
@@
 However, other forms of screen use showed associations with benefits.
-For example, experimental evidence showed that video games improve aspects of cognitive function.
+For example, educational screen use was generally associted with better learning outcomes.
 Some types of screen use have complex associations with outcomes.
-For example, general screen use (i.e., content not indicated) showed correlations with harm for body composition, depression, and learning.
+For example, television viewing showed harmful correlations with body composition and learning.
 However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
@@
 The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
-Supplementary File 5 provides a list of all exposures identified.
+Supplementary File 1 provides a list of all exposures identified.
 The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
 Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.
+Full characteristics of the included studies are provided in Supplementary File 2.
 After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.
 These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
-The characteristics of the included effects are available in Supplementary File 9.
+The characteristics of the included effects are available in Supplementary File 3.
 
@@
 We removed 28 effects that did not provide individual study-level data, 19 effects with samples \textless{} 1,000, and 19 effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in Supplementary File 6.
+Effects not meeting one or more of these standards are presented in Supplementary File 4.
 The remaining 23 effects met our criteria for statistical credibility and are described in Figure 2.
@@
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in Supplementary File 7.
+Effects not meeting one or more of these standards are presented in Supplementary File 5.
 The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
-Additionally, most effects were small, with the association between screen use and sleep duration the largest at \(r = -0.37\) (\(k = 10, N = 56,720\)).
+Additionally, most effects were small, with the association between internet use and depression the largest at \(r = 0.25\) (\(k = 118, N = 527,696\)).
 Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).
@@
 However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
-One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 \& 7) therefore this hypothesis could not be addressed.
+One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 \& 5) therefore this hypothesis could not be addressed.
 
@@
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
+If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Files 4 \& 5).
 For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.\textsuperscript{36}
@@
 Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
-However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.
+However, we provide the complete results in Supplementary Files 4 \& 5, along with the dataset (Supplementary File 6) for others to consider alternative criteria.
 
@@
 To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{50,51}
-Effect sizes on the original metric are provided in Supplementary File 2.
+Effect sizes on the original metric are provided in Supplementary File 6.
 Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
@@
 Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
-We used thresholds of \(P < .05\) for weak evidence and \(P < 10^{-3}\) for strong evidence.
-An effect with statistical credibility but with \(P > .05\) was taken to indicate no association of interest.
+We used thresholds of \(P < .05\) for weak evidence (i.e., 95\% confidence intervals did not cross zero) and \(P < 10^{-3}\) (i.e., 99.9\% confidence intervals did not cross zero) for strong evidence.
+An effect with statistical credibility but with \(P > .05\) (i.e., 95\% confidence intervals included zero) was taken to indicate no association of interest.
 
@@
 All code used in these analyses are available on the authors' GitHub repository (\url{https://github.com/motivation-and-Behaviour/screen_umbrella}).
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+The authors received no specific funding for this work.
+
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
+
+TS, MN, PP, and CL conceptualised the review and drafted the manuscript.
+TS, MN, and PP conducted the analyses.
+All authors contributed to data extraction, interpretation, and editing of the manuscript.
+
+\hypertarget{competing-interests}{%
+\section{Competing interests}\label{competing-interests}}
+
+The authors declare no conflicts of interest.
+
+\hypertarget{tables}{%
+\section{Tables}\label{tables}}
+
+\emph{Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects}
+
+\hypertarget{figure-legends}{%
+\section{Figure legends}\label{figure-legends}}
+
+\emph{Figure 1: PRISMA Diagram.}
+
+\emph{Figure 2: Education outcomes.
+Results for 23 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
+
+\emph{Figure 3: Health and health-related behaviour outcomes.
+Results for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
 
@@
 \leavevmode\hypertarget{ref-R-metafor}{}%
-54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2022).
+54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-The authors received no specific funding for this work.
-
-\hypertarget{author-contributions}{%
-\section{Author contributions}\label{author-contributions}}
-
-TS, MN, PP, and CL conceptualised the review and drafted the manuscript.
-TS, MN, and PP conducted the analyses.
-All authors contributed to data extraction, interpretation, and editing of the manuscript.
-
-\hypertarget{competing-interests}{%
-\section{Competing interests}\label{competing-interests}}
-
-The authors declare no conflicts of interest.
-
-\hypertarget{figure-legends}{%
-\section{Figure legends}\label{figure-legends}}
-
-\emph{Figure 1: PRISMA Diagram.}
-
-\emph{Figure 2: Education outcomes.
-Results for 23 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
-
-\emph{Figure 3: Health and health-related behaviour outcomes.
-Results for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
-
-\hypertarget{tables}{%
-\section{Tables}\label{tables}}
-
-\emph{Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects}
-
 \end{document}

### 2023-06-20 R/make_table_rob.R

@@ -1,0 +1,140 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param tables_df
+#' @return
+#' @author Taren Sanders
+#' @export
+make_table_rob <- function(tables_df) {
+  rob_cols <- c("#b7e1cd", "#fce8b2", "#f4c7c3")
+
+  base_table <-
+    tables_df %>%
+    filter(table == "main") %>%
+    select(
+      first_author, year,
+      eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) %>%
+    distinct() %>%
+    mutate_at(
+      vars(
+        "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
+      ),
+      ~ case_match(
+        .x,
+        "low" ~ "L",
+        "unclear" ~ "U",
+        "high" ~ "H"
+      )
+    ) %>%
+    arrange(str_to_lower(first_author), year)
+
+  gt_table <-
+    base_table %>%
+    gt(
+      caption = "Quality assessment for studies providing unique effects"
+    ) %>%
+    tab_header(html("<strong>Quality Assessment</strong>"),
+      subtitle = "Quality assessment for meta-analyses providing unique effects" # nolint
+    ) %>%
+    data_color(
+      columns =
+        eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
+      fn = scales::col_factor(
+        palette = rob_cols,
+        levels = c("L", "U", "H")
+      )
+    ) %>%
+    tab_spanner(
+      label = "Quality Assessment",
+      columns =
+        eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) %>%
+    cols_label(
+      first_author = "First Author",
+      year = "Year",
+      eligibility_criteria_predefined_and_specified = html("Elig. Crit."),
+      literature_search_strategy_comprehensive_and_systematic = "Lit. Search",
+      dual_independent_screening_review = "Dual Screen",
+      dual_independent_quality_assessment = "Dual Qual.",
+      included_studies_listed_with_important_characteristics_and_results_of_each = "Studies Listed", # nolint
+      publication_bias_assessed = "Pub. Bias",
+      heterogeneity_assessed = "Hetero."
+    ) %>%
+    cols_align(
+      columns =
+        first_author:year,
+      align = "left"
+    ) %>%
+    cols_align(
+      columns =
[…]

### 2023-06-20 R/plot_settings.R

@@ -31,7 +31,7 @@ edu_certain <- list(
 
 edu_uncertain <- list(
   filename =
-    "supplementary_files/Supplementary File 6 - Education Outcomes.pdf",
+    "supplementary_files/Supplementary File 4 - Education Outcomes.pdf",
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = FALSE,
@@ -90,7 +90,7 @@ nonedu_certain <- list(
 nonedu_uncertain <-
   list(
     filename =
-      "supplementary_files/Supplementary File 7 - Health-related Outcomes.pdf",
+      "supplementary_files/Supplementary File 5 - Health-related Outcomes.pdf",
     title = "Associations Between Exposures and Health-related Outcomes",
     categories = c("Psychology", "Health Behaviour", "Physical Health"),
     certain = FALSE,

### 2023-06-20 _targets.R

@@ -97,12 +97,23 @@ list(
     make_table_desc_gt(tables_df)
   ),
   tar_target(
-    table_desc_latex,
-    make_table_desc_latex(tables_df)
+    table_rob_gt,
+    make_table_rob(tables_df)
   ),
   tar_target(
     table_desc_saved,
-    save_table(table_desc_gt, "tables/Table 1 - Review characteristics.pdf"),
+    save_table(
+      table_desc_gt,
+      "supplementary_files/Supplementary File 2 - Review characteristics.pdf",
+      method = "webshot"
+    ),
+    format = "file",
+  ),
+  tar_target(
+    table_rob_saved,
+    save_table(table_rob_gt, "tables/Table 1 - Quality assessment.pdf",
+      method = "webshot"
+    ),
     format = "file",
   ),
   tar_target(
@@ -113,7 +124,7 @@ list(
     table_effects_saved,
     save_table(
       table_effects,
-      "supplementary_files/Supplementary File 9 - Effect Characteristics.pdf"
+      "supplementary_files/Supplementary File 3 - Effect Characteristics.pdf"
     ),
     format = "file",
   ),
@@ -221,13 +232,13 @@ list(
     )
   ),
   tar_target(other_supps_files, c(
-    "supplementary_files/Supplementary File 1 - Search Strategy.pdf"
+    "supplementary_files/Supplementary File 7 - Search Strategy.pdf"
   ), format = "file"),
   tar_target(join_supp_py_script, "python/combine_pdfs.py", format = "file"),
   tar_target(joined_supps,
     join_supps(
       other_supps_files, join_supp_py_script, table_effects_saved,
-      supp_exposures, supp_effects
+      supp_exposures, supp_effects, table_desc_saved
     ),
     format = "file"
   ),
@@ -245,7 +256,7 @@ list(
     path = here::here("reports", "references.Rmd"),
     output_file = here::here(
       "supplementary_files",
-      "Supplementary File 8 - Included Studies.pdf"
+      "Supplementary File 9 - Included Studies.pdf"
     ),
     params = list(
       nocite_list =

### 2023-06-20 python/combine_pdfs.py

@@ -9,29 +9,33 @@ from reportlab.pdfgen import canvas
 # list your pdf files here
 # now each value is a tuple with the title and a description
 pdfs = {
-    "supplementary_files/Supplementary File 1 - Search Strategy.pdf": (
-        "Supplementary File 1 - Search Strategy",
-        "The search strategies used in each database",
+    "supplementary_files/Supplementary File 2 - Review characteristics.pdf": (
+        "Supplementary File 2 - Review characteristics",
+        "Table of included meta-analyses and their characteristics.",
     ),
-    "supplementary_files/Supplementary File 3 - Effect Size Codebook.pdf": (
-        "Supplementary File 3 - Effect Size Codebook",
-        "Generated codebook for the dataset.",
+    "supplementary_files/Supplementary File 3 - Effect Characteristics.pdf": (
+        "Supplementary File 3 - Effect Characteristics",
+        "Descriptive table for the included effects.",
     ),
-    "supplementary_files/Supplementary File 6 - Education Outcomes.pdf": (
-        "Supplementary File 6 - Education Outcomes",
+    "supplementary_files/Supplementary File 4 - Education Outcomes.pdf": (
+        "Supplementary File 4 - Education Outcomes",
         "Additional education outcomes which did not meet certainty criteria.",
     ),
-    "supplementary_files/Supplementary File 7 - Health-related Outcomes.pdf": (
-        "Supplementary File 7 - Health-related Outcomes",
+    "supplementary_files/Supplementary File 5 - Health-related Outcomes.pdf": (
+        "Supplementary File 5 - Health-related Outcomes",
         "Additional health-related outcomes which did not meet certainty criteria.",
     ),
-    "supplementary_files/Supplementary File 8 - Included Studies.pdf": (
-        "Supplementary File 8 - Included Studies",
+    "supplementary_files/Supplementary File 7 - Search Strategy.pdf": (
+        "Supplementary File 7 - Search Strategy",
+        "The search strategies used in each database",
+    ),
+    "supplementary_files/Supplementary File 9 - Included Studies.pdf": (
+        "Supplementary File 9 - Included Studies",
         "References for the included studies.",
     ),
-    "supplementary_files/Supplementary File 9 - Effect Characteristics.pdf": (
-        "Supplementary File 9 - Effect Characteristics",
-        "Descriptive table for the included effects.",
+    "supplementary_files/Supplementary File 10 - Effect Size Codebook.pdf": (
[…]

### 2023-06-20 reports/manuscript.Rmd
Update abstract

@@
   The influence of electronic screens on children and adolescents’ health and education is not well understood.
-  In this review, we harmonised `r targets::tar_read(manuscript_info)$unique_effects` effects representing unique combinations of exposures and outcomes from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants).
-  Some types of screen use, such as social media, were consistently correlated with risks to health.
-  However, other forms of screen use showed associations with benefits.
-  For example, educational screen use was generally associted with better learning outcomes.
+  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants) on screen time and any outcome for youths.
+  Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, `r targets::tar_read(manuscript_info)$abstract$social_media`) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, `r targets::tar_read(manuscript_info)$abstract$edu`).
   Some types of screen use have complex associations with outcomes.
-  For example, television viewing showed harmful correlations with body composition and learning.
-  However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
-  More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
+  For example, television viewing showed harmful correlations with learning `r targets::tar_read(manuscript_info)$abstract$tv_edu`.
+  However, when parents watched with their children, general screen use was associated with greater literacy `r targets::tar_read(manuscript_info)$abstract$coview`.
+  These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
 
@@
 options(dplyr.summarise.inform = FALSE)
+
+source(here::here("R", "utils_manuscript.R"))
 ```
@@
 targets::tar_load(
-  c(
-    "manuscript_info", "combined_bib", "prisma", "edu_certain_params",
-    "plot_edu_certain", "nonedu_certain_params", "plot_nonedu_certain"
-  ),
+  c("manuscript_info", "combined_bib", "combined_effects"),
   store = here::here("_targets")
@@
 Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
-The largest effect size observed was for augmented reality-based education interventions on general learning ($r = 0.33, k = 15, N = 1,474$).
+The largest effect size observed was for augmented reality-based education interventions on general learning `r report_effect(combined_effects, "42168_002")`.
 Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
-Additionally, most effects were small, with the association between internet use and depression the largest at $r = 0.25$ ($k = 118, N = 527,696$).
+Additionally, most effects were small, with the association between internet use and depression the largest at `r report_effect(combined_effects, "60496_003", "in-text")`.
 Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.

### 2023-06-20 reports/manuscript.tex
Update abstract

@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5405}
+\keywords{\newline\indent Word count: 5377}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 The influence of electronic screens on children and adolescents' health and education is not well understood.
-In this review, we harmonised 255 effects representing unique combinations of exposures and outcomes from 103 meta-analyses (2,496 primary studies; 2,026,054 participants).
-Some types of screen use, such as social media, were consistently correlated with risks to health.
-However, other forms of screen use showed associations with benefits.
-For example, educational screen use was generally associted with better learning outcomes.
+In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 103 meta-analyses (2,496 primary studies; 2,026,054 participants) on screen time and any outcome for youths.
+Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval 0.05 to 0.19) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% confidence interval 0.02 to 0.31).
 Some types of screen use have complex associations with outcomes.
-For example, television viewing showed harmful correlations with body composition and learning.
-However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
-More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
+For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% confidence interval -0.15 to -0.04).
+However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% confidence interval 0.02 to 0.28).
+These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
 }
@@
 Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
-The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
+The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% confidence interval 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474).
 Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
-Additionally, most effects were small, with the association between internet use and depression the largest at \(r = 0.25\) (\(k = 118, N = 527,696\)).
+Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% confidence interval 0.22 to 0.27, \emph{k} = 118, \emph{N} = 527,696).
 Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).

### 2023-06-20 R/make_manuscript_info.R

@@ -380,6 +380,22 @@ make_manuscript_info <- function(effects_clean, prisma, tables_df,
     filter(abs(r) < 0.2) %>%
     nrow()
 
+  # Abstract Results ---------------------------------------------
+  manuscript_info$abstract$social_media <-
+    report_effect(combined_effects, "53160_001", "short-none")
+
+  manuscript_info$abstract$edu <-
+    report_effect(combined_effects, "61452_004", "short-none")
+
+  manuscript_info$abstract$tv_body <-
+    report_effect(combined_effects, "8556_119", "short-brackets")
+
+  manuscript_info$abstract$tv_edu <-
+    report_effect(combined_effects, "47569_002", "short-brackets")
+
+  manuscript_info$abstract$coview <-
+    report_effect(combined_effects, "47783_022", "short-brackets")
+
   return(manuscript_info)
 }
 

### 2023-06-20 R/utils_manuscript.R

@@ -1,0 +1,49 @@
+report_effect <- function(combined_effects, effect_id, style = "brackets") {
+  row <- combined_effects[combined_effects$effect_size_id == effect_id, ]
+
+  r <- format(round(row$r, 2), nsmall = 2)
+  ci_l <- format(round(row$cilb95, 2), nsmall = 2)
+  ci_u <- format(round(row$ciub95, 2), nsmall = 2)
+  k <- as.character(row$k)
+  n <- scales::label_comma(accuracy = 1)(row$n)
+
+  if (style == "brackets") {
+    outstring <-
+      glue::glue(
+        "(*r* = {r}, 95% confidence interval {ci_l} to {ci_u},",
+        " *k* = {k}, *N* = {n})"
+      )
+  }
+
+  if (style == "in-text") {
+    outstring <-
+      glue::glue(
+        "*r* = {r} (95% confidence interval {ci_l} to {ci_u},",
+        " *k* = {k}, *N* = {n})"
+      )
+  }
+
+  if (style == "none") {
+    outstring <-
+      glue::glue(
+        "*r* = {r}, 95% confidence interval {ci_l} to {ci_u},",
+        " *k* = {k}, *N* = {n}"
+      )
+  }
+
+  if (style == "short-brackets") {
+    outstring <-
+      glue::glue(
+        "(*r* = {r}, 95% confidence interval {ci_l} to {ci_u})"
+      )
+  }
+
+  if (style == "short-none") {
+    outstring <-
+      glue::glue(
+        "*r* = {r}, 95% confidence interval {ci_l} to {ci_u}"
+      )
+  }
+
+  return(outstring)
+}

### 2023-06-20 _targets.R

@@ -237,8 +237,8 @@ list(
   tar_target(join_supp_py_script, "python/combine_pdfs.py", format = "file"),
   tar_target(joined_supps,
     join_supps(
-      other_supps_files, join_supp_py_script, table_effects_saved,
-      supp_exposures, supp_effects, table_desc_saved
+      join_supp_py_script, other_supps_files, table_effects_saved,
+      supp_exposures, supp_effects, references, table_desc_saved
     ),
     format = "file"
   ),

### 2023-06-21 reports/manuscript.Rmd
Update tables

@@
 )
+ce <- combined_effects
 ```
@@
 
-Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
-E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
-General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
+Among the statistically credible effects, general screen use `r report_effect(ce, "47569_001", first = TRUE)`, television viewing `r report_effect(ce, "47569_002")`, and video games `r report_effect(ce, "47569_005")` were all negatively associated with learning.
+E-books that included narration `r report_effect(ce, "20223_015")`, as well as touch screen education interventions `r report_effect(ce, "50271_001")`, and augmented reality education interventions `r report_effect(ce, "42168_002")` were positively associated with learning.
+General screen use was negatively associated with literacy outcomes `r report_effect(ce, "47783_001")`.
+However, if the screen use involved co-viewing (e.g., watching with a parent; `r report_effect(ce, "47783_022", style = "none")`), or the content of television programs was educational `r report_effect(ce, "47783_015")`, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
+Numeracy outcomes were positively associated with screen-based mathematics interventions `r report_effect(ce, "37653_002")` and video games that contained numeracy content `r report_effect(ce, "41430_001")`.
 
@@
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]).
-The largest effect size observed was for augmented reality-based education interventions on general learning `r report_effect(combined_effects, "42168_002")`.
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning [@xieCanTouchscreenDevices2018]; `r report_effect(ce, "50271_001", style = "none")`) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning [@adelantado-renauAssociationScreenMedia2019]; `r report_effect(ce, "47569_002", style = "none")`).
+The largest effect size observed was for augmented reality-based education interventions on general learning `r report_effect(ce, "42168_002")`.
 Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).
@@
 We removed `r manuscript_info$health$n_noindiv` effects that did not provide individual study-level data, `r manuscript_info$health$n_samplesize` effects with samples < 1,000, and `r manuscript_info$health$n_faileggers` effects with a significant Egger's test or insufficient studies to conduct the test.
-No remaining studies showed evidence of excessive significance.
+No remaining studies had statistically significant tests for excess significance.
 Effects not meeting one or more of these standards are presented in Supplementary File 5.
@@
 
-Digital advertising of unhealthy foods—both traditional advertising and video games developed by a brand for promotion—were associated with higher unhealthy food intake.
-Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
-Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents.
-All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
+Digital advertising of unhealthy foods—both traditional advertising `r report_effect(ce, "6739_002")` and video games developed by a brand for promotion `r report_effect(ce, "47594_001")`—were associated with higher unhealthy food intake.
+Social media use and sexual content were positively associated with risky behaviors (e.g., social media and risky sexual behaviour; `r report_effect(ce, "47429_003", style = "none")`).
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents `r report_effect(ce, "6524_005")`.
+Both television and video games were associated with body composition (e.g., television `r report_effect(ce, "8556_119", style = "none")`).
 Screen-based interventions which target health behaviours appeared mostly effective.
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having $I^2 > 75\%$.
-Additionally, most effects were small, with the association between internet use and depression the largest at `r report_effect(combined_effects, "60496_003", "in-text")`.
+Additionally, most effects were small, with the association between internet use and depression the largest at `r report_effect(ce, "60496_003", "in-text")`.
 Most of the effect sizes (`r manuscript_info$health$n_r2`/`r manuscript_info$health$n_certain`) had an absolute value of $r < 0.2$.
@@
 As an example, consider children watching television programs---an often cited form of screen use harm.
-We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
+We found evidence for a small association with poorer academic performance and literacy skills for general television watching[@adelantado-renauAssociationScreenMedia2019].
 However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy [@madiganAssociationsScreenUse2020].
@@
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Files 4 & 5).
-For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups [@sadeghiradInfluenceUnhealthyFood2016].
-Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups [@marshallRelationshipsMediaUse2004].
 Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
@@
 
-In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce 'screen use', and instead focusing on the type of screen use.
-For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
-Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
+Given our results, we support the continuing trend of guidelines moving away from recommendations to reduce 'screen use', and instead focusing on the type of screen use.
+For example, we suggest that guidelines should discourage high levels of social media and internet use.
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity [@markerExploringMythChubby2022].
 
@@
 
-*Figure 1: PRISMA Diagram.*
+*Figure 1: PRISMA flow diagram.*
 
 *Figure 2: Education outcomes.
-Results for `r manuscript_info$edu$n_certain` unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95% and 99.9% confidence intervals.*
+Forest plot for `r manuscript_info$edu$n_certain` unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations (two-sided) with both 95% and 99.9% confidence intervals.*
 
 *Figure 3: Health and health-related behaviour outcomes.
-Results for `r manuscript_info$health$n_certain` unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95% and 99.9% confidence intervals.*
+Forest plot for `r manuscript_info$health$n_certain` unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations (two-sided) with both 95% and 99.9% confidence intervals.*
 

### 2023-06-21 reports/manuscript.tex
Update tables

--- 2023-06-19 reports/manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5394}
+\keywords{\newline\indent Word count: 5369}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 The influence of electronic screens on children and adolescents' health and education is not well understood.
-In this review, we harmonised 255 effects representing unique combinations of exposures and outcomes from 103 meta-analyses (2,496 primary studies; 2,026,054 participants).
-Some types of screen use, such as social media, were consistently correlated with risks to health.
-However, other forms of screen use showed associations with benefits.
-For example, experimental evidence showed that video games improve aspects of cognitive function.
+In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and any outcome for youths.
+Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval 0.05 to 0.19) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% confidence interval 0.02 to 0.31).
 Some types of screen use have complex associations with outcomes.
-For example, general screen use (i.e., content not indicated) showed correlations with harm for body composition, depression, and learning.
-However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
-More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
+For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% confidence interval -0.15 to -0.04).
+However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% confidence interval 0.02 to 0.28).
+These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
 }
@@
 After screening titles and abstracts, we assessed 2,557 full-texts for inclusion.
-Of those, 218 met the inclusion criteria and we extracted the data from all of these meta-analyses.
+Of those, 217 met the inclusion criteria and we extracted the data from all of these meta-analyses.
 Figure 1 presents the full results of the selection process.
@@
 The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
-Supplementary File 5 provides a list of all exposures identified.
-The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
-Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
-Full characteristics of the included studies are provided in Table 1.
-After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.
-These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
-The characteristics of the included effects are available in Supplementary File 9.
+Supplementary File 1 provides a list of all exposures identified.
+The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 24), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
+Of the 273 unique exposure/outcome combinations, 241 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
+Full characteristics of the included studies are provided in Supplementary File 2.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded 252 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 102 reviews.
+These effects represent the findings of 2,451 primary studies, involving 1,937,501 participants.
+The characteristics of the included effects are available in Supplementary File 3.
 
@@
 The quality of the included meta-analyses was mixed (see Table 1).
-Most assessed heterogeneity (\emph{n} low risk = 94/103, 91\% of meta-analyses), reported the characteristics of the included studies (\emph{n} low risk = 87/103, 84\%), and used a comprehensive and systematic search strategy (\emph{n} low risk = 72/103, 70\%).
-Most reviews did not clearly report if their eligibility criteria were predefined (\emph{n} unclear = 72/103, 70\%).
-Many papers also did not complete dual independent screening of abstracts and full text (\emph{n} high risk = 20/103, 19\%) or did not clearly report the method of screening (\emph{n} unclear = 38/103, 37\%).
-A similar trend was observed for dual independent quality assessment (\emph{n} high risk = 53/103, 51\%; n high risk = 19/103, 18\%).
+Most assessed heterogeneity (\emph{n} low risk = 93/102, 91\% of meta-analyses), reported the characteristics of the included studies (\emph{n} low risk = 86/102, 84\%), and used a comprehensive and systematic search strategy (\emph{n} low risk = 71/102, 70\%).
+Most reviews did not clearly report if their eligibility criteria were predefined (\emph{n} unclear = 71/102, 70\%).
+Many papers also did not complete dual independent screening of abstracts and full text (\emph{n} high risk = 20/102, 20\%) or did not clearly report the method of screening (\emph{n} unclear = 37/102, 36\%).
+A similar trend was observed for dual independent quality assessment (\emph{n} high risk = 52/102, 51\%; n high risk = 19/102, 19\%).
 Overall, only 7 meta-analyses were graded as low risk of bias on all criteria.
 
-There were 89 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
+There were 88 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
 We removed 28 effects that did not provide individual study-level data, 19 effects with samples \textless{} 1,000, and 19 effects with a significant Egger's test or insufficient studies to conduct the test.
-Effects not meeting one or more of these standards are presented in Supplementary File 6.
-The remaining 23 effects met our criteria for statistical credibility and are described in Figure 2.
-These 23 effects came from 18 meta-analytic reviews analysing data from 338 empirical studies with 262,537 individual participants.
+Effects not meeting one or more of these standards are presented in Supplementary File 4.
+The remaining 22 effects met our criteria for statistical credibility and are described in Figure 2.
+These 22 effects came from 17 meta-analytic reviews analysing data from 337 empirical studies with 262,497 individual participants.
 
-Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
-E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
-General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
+Among the statistically credible effects, general screen use (\emph{r} = -0.11, 95\% confidence interval {[}CI{]} -0.24 to 0.01, \emph{k} = 18, \emph{N} = 13,100), television viewing (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{k} = 18, \emph{N} = 62,135), and video games (\emph{r} = -0.08, 95\% CI -0.12 to -0.04, \emph{k} = 10, \emph{N} = 4,276) were all negatively associated with learning.
+E-books that included narration (\emph{r} = 0.11, 95\% CI 0.05 to 0.17, \emph{k} = 50, \emph{N} = 2,288), as well as touch screen education interventions (\emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{k} = 79, \emph{N} = 5,810), and augmented reality education interventions (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474) were positively associated with learning.
+General screen use was negatively associated with literacy outcomes (\emph{r} = -0.14, 95\% CI -0.20 to -0.09, \emph{k} = 38, \emph{N} = 18,318).
+However, if the screen use involved co-viewing (e.g., watching with a parent; \emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{k} = 12, \emph{N} = 6,083), or the content of television programs was educational (\emph{r} = 0.13, 95\% CI 0.03 to 0.23, \emph{k} = 13, \emph{N} = 1,955), the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
+Numeracy outcomes were positively associated with screen-based mathematics interventions (\emph{r} = 0.27, 95\% CI 0.21 to 0.33, \emph{k} = 85, \emph{N} = 36,793) and video games that contained numeracy content (\emph{r} = 0.32, 95\% CI 0.21 to 0.43, \emph{k} = 25, \emph{N} = 2,008).
 
-As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
+As shown in Figure 2, most of the credible results (13 of 22 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
 The remaining six associations were significant at the 95\% confidence level (weak evidence).
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning)\textsuperscript{26} tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning).\textsuperscript{27}
-The largest effect size observed was for augmented reality-based education interventions on general learning (\(r = 0.33, k = 15, N = 1,474\)).
-Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning;\textsuperscript{26} \emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{k} = 79, \emph{N} = 5,810) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning;\textsuperscript{27} \emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{k} = 18, \emph{N} = 62,135).
+The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474).
+Most effects showed high levels of heterogeneity (17 of 22 with \(I^2 > 50\%\)).
 
-We identified 165 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-We removed 41 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
+We identified 163 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
+We removed 39 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
 No remaining studies showed evidence of excessive significance.
-Effects not meeting one or more of these standards are presented in Supplementary File 7.
+Effects not meeting one or more of these standards are presented in Supplementary File 5.
 The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
@@
 
-Digital advertising of unhealthy foods---both traditional advertising and video games developed by a brand for promotion---were associated with higher unhealthy food intake.
-Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
-General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
-Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
-All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
+Digital advertising of unhealthy foods---both traditional advertising (\emph{r} = 0.23, 95\% CI 0.10 to 0.37, \emph{k} = 13, \emph{N} = 1,756) and video games developed by a brand for promotion (\emph{r} = 0.18, 95\% CI 0.10 to 0.25, \emph{k} = 15, \emph{N} = 3,842)---were associated with higher unhealthy food intake.
+Social media use and sexual content were positively associated with risky behaviors (e.g., social media and risky sexual behaviour; \emph{r} = 0.21, 95\% CI 0.14 to 0.28, \emph{k} = 14, \emph{N} = 23,096).
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents (\emph{r} = -0.06, 95\% CI -0.10 to -0.01, \emph{k} = 10, \emph{N} = 9,798).
+Both television and video games were associated with body composition (e.g., television \emph{r} = 0.06, 95\% CI 0.03 to 0.10, \emph{k} = 12, \emph{N} = 3,196).
 Screen-based interventions which target health behaviours appeared mostly effective.
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
-Additionally, most effects were small, with the association between screen use and sleep duration the largest at \(r = -0.37\) (\(k = 10, N = 56,720\)).
+Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% CI 0.22 to 0.27, \emph{k} = 118, \emph{N} = 527,696).
 Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).
@@
 
-In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
-For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
-Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
+Given our results, we support the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
+For example, we suggest that guidelines should discourage high levels of social media and internet use.
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{41}
 
@@
 Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
-Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{41}
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{42}
 When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
@@
 It has been established that self-reported screen use data has questionable validity.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{42} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
-Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{43}
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers---\textsuperscript{45}these are still not widely adopted.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{43} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
+Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{44}
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{45} or device-based loggers---\textsuperscript{46}these are still not widely adopted.
 It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
@@
 Our primary goal for this umbrella review was to provide a high-level synthesis of screen use research, by examining a range of exposures and the associations with a broad scope of outcomes.
-Our results represent the findings from 2,496 primary studies comprised of 2,026,054 participants.
+Our results represent the findings from 2,451 primary studies comprised of 1,937,501 participants.
 To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.
@@
 For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{46}
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{47}
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
@@
 Some previous research suggests that associations are typically linear.\textsuperscript{18}
-However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,47,48}
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,48,49}
 Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
@@
 We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
-We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{41}
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{42}
 
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{49} (see Table 1).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{50} (see Table 1).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 
-To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{50,51}
-Effect sizes on the original metric are provided in Supplementary File 2.
-Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
-These are similar to other interpretations based on empirical data.\textsuperscript{53}
+To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{51,52}
+Effect sizes on the original metric are provided in Supplementary File 6.
+Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{53} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
+These are similar to other interpretations based on empirical data.\textsuperscript{54}
 
@@
 We descriptively present the remaining meta-analytic effect sizes.
-To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{54} in R\textsuperscript{55} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
+To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{55} in R\textsuperscript{56} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
 From our reanalysis we also extracted \(I^2\) values.
-To test for publication bias, we conducted Egger's test\textsuperscript{56} when the number of studies within the review was ten or more,\textsuperscript{57} and conducted a test of excess significance.\textsuperscript{58}
+To test for publication bias, we conducted Egger's test\textsuperscript{57} when the number of studies within the review was ten or more,\textsuperscript{58} and conducted a test of excess significance.\textsuperscript{59}
 We contacted authors who did not provide primary study data in their published article.
@@
 We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
-To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{59} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
+To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{60} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 \emph{Figure 2: Education outcomes.
-Results for 23 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
+Results for 22 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
 Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-markerExploringMythChubby2022}{}}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Marker, C., Gnambs, T.
+\& Appel, M.
+Exploring the myth of the chubby gamer: {A} meta-analysis on sedentary video gaming and body mass.
+\emph{Social Science \& Medicine} \textbf{301}, 112325 (2022).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-pagePRISMA2020Statement2020}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Page, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Parry, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-byrneMeasurementScreenTime2021}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Byrne, R., Terranova, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Smith, C., Galland, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Ryding, F.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Guyatt, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-twengeMoreTimeTechnology2019}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Twenge, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kellySocialMediaUse2018}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Kelly, Y., Zilanawala, A., Booker, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{National Health, Lung, and Blood Institute. \emph{Quality {Assessment} of {Systematic Reviews} and {Meta-Analyses}}. (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bowmanEffectSizesStatistical2012}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Bowman, N. A. Effect {Sizes} and {Statistical Methods} for {Meta-Analysis} in {Higher Education}. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Jacobs, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-funderEvaluatingEffectSize2019}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Funder, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gignacEffectSizeGuidelines2016}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-metafor}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pageChapter13Assessing2021}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Page, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).}

### 2023-06-21 _targets.R

@@ -117,6 +117,13 @@ list(
     format = "file",
   ),
   tar_target(
+    table_rob_saved_docx,
+    save_table(table_rob_gt, "tables/Table 1 - Quality assessment.docx",
+      method = "webshot2"
+    ),
+    format = "file",
+  ),
+  tar_target(
     table_effects,
     make_table_effects(combined_effects)
   ),

### 2023-06-21 reports/manuscript.tex
WIP: Fixing plots

@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5369}
+\keywords{\newline\indent Word count: 5295}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 Full characteristics of the included studies are provided in Supplementary File 2.
-After removing reviews with duplicate exposure/outcome combinations, our process yielded 252 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 102 reviews.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded 253 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 102 reviews.
 These effects represent the findings of 2,451 primary studies, involving 1,937,501 participants.
@@
 
-We identified 163 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-We removed 39 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
-No remaining studies showed evidence of excessive significance.
+We identified 164 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
+We removed 40 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
+No remaining studies had statistically significant tests for excess significance.
 Effects not meeting one or more of these standards are presented in Supplementary File 5.
@@
 As an example, consider children watching television programs---an often cited form of screen use harm.
-We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
+We found evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
 However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
@@
 Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
-If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Files 4 \& 5).
-For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.\textsuperscript{36}
-Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.\textsuperscript{37}
 Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
@@
 Our results have several implications for policy and practice.
-Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{38--40}
+Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{36--38}
 Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
@@
 For example, we suggest that guidelines should discourage high levels of social media and internet use.
-Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{41}
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{39}
 
@@
 Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
-Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{42}
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{40}
 When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
@@
 It has been established that self-reported screen use data has questionable validity.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{43} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
-Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{44}
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{45} or device-based loggers---\textsuperscript{46}these are still not widely adopted.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{41} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
+Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{42}
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{43} or device-based loggers---\textsuperscript{44}these are still not widely adopted.
 It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
@@
 For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{47}
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE).\textsuperscript{45}
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
@@
 Some previous research suggests that associations are typically linear.\textsuperscript{18}
-However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,48,49}
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,46,47}
 Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
@@
 We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
-We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{42}
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{40}
 
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{50} (see Table 1).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{48} (see Table 1).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 
-To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{51,52}
+To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{49,50}
 Effect sizes on the original metric are provided in Supplementary File 6.
-Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{53} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
-These are similar to other interpretations based on empirical data.\textsuperscript{54}
+Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{51} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
+These are similar to other interpretations based on empirical data.\textsuperscript{52}
 
@@
 We descriptively present the remaining meta-analytic effect sizes.
-To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{55} in R\textsuperscript{56} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
+To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{53} in R\textsuperscript{54} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
 From our reanalysis we also extracted \(I^2\) values.
-To test for publication bias, we conducted Egger's test\textsuperscript{57} when the number of studies within the review was ten or more,\textsuperscript{58} and conducted a test of excess significance.\textsuperscript{59}
+To test for publication bias, we conducted Egger's test\textsuperscript{55} when the number of studies within the review was ten or more,\textsuperscript{56} and conducted a test of excess significance.\textsuperscript{57}
 We contacted authors who did not provide primary study data in their published article.
@@
 We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
-To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{60} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
+To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{58} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 
-\emph{Figure 1: PRISMA Diagram.}
+\emph{Figure 1: PRISMA flow diagram.}
 
 \emph{Figure 2: Education outcomes.
-Results for 22 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
+Forest plot for 22 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations (two-sided) with both 95\% and 99.9\% confidence intervals.}
 
 \emph{Figure 3: Health and health-related behaviour outcomes.
-Results for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
+Forest plot for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations (two-sided) with both 95\% and 99.9\% confidence intervals.}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-elsonPolicyStatementsMedia2019}{}}%
 \CSLLeftMargin{36. }
-\CSLRightInline{Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N.
-R.
-C.
-\& Johnston, B.
-C.
-Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials.
-\emph{Obesity Reviews} \textbf{17}, 945--959 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-marshallRelationshipsMediaUse2004}{}}%
-\CSLLeftMargin{37. }
-\CSLRightInline{Marshall, S.
-J., Biddle, S.
-J.
-H., Gorely, T., Cameron, N.
-\& Murdey, I.
-Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis.
-\emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-elsonPolicyStatementsMedia2019}{}}%
-\CSLLeftMargin{38. }
 \CSLRightInline{Elson, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ashtonScreenTimeChildren2019}{}}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Ashton, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: {A} guide for clinicians and parents.} (2019).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-markerExploringMythChubby2022}{}}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Marker, C., Gnambs, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pagePRISMA2020Statement2020}{}}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Page, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Parry, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-byrneMeasurementScreenTime2021}{}}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Byrne, R., Terranova, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Smith, C., Galland, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Ryding, F.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Guyatt, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-twengeMoreTimeTechnology2019}{}}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Twenge, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-kellySocialMediaUse2018}{}}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Kelly, Y., Zilanawala, A., Booker, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{48. }
 \CSLRightInline{National Health, Lung, and Blood Institute. \emph{Quality {Assessment} of {Systematic Reviews} and {Meta-Analyses}}. (2014).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-bowmanEffectSizesStatistical2012}{}}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Bowman, N. A. Effect {Sizes} and {Statistical Methods} for {Meta-Analysis} in {Higher Education}. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Jacobs, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-funderEvaluatingEffectSize2019}{}}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Funder, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-gignacEffectSizeGuidelines2016}{}}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-metafor}{}}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{54. }
 \CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pageChapter13Assessing2021}{}}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Page, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).}

### 2023-06-21 R/clean_effects.R

@@ -72,16 +72,16 @@ clean_effects <- function(
       study_design = case_when(
         moderator_category %in% design_moderator_categories &
           moderator_level %in% design_codes$design_unspec ~
-          "Mixed or unspecified",
+          "Mixed or unclear",
         moderator_category %in% design_moderator_categories &
           moderator_level %in% design_codes$design_obs_mixed ~
-          "Observational - mixed",
+          "Observational",
         moderator_category %in% design_moderator_categories &
           moderator_level %in% design_codes$design_obs_cross ~
-          "Cross-sectional only",
+          "Cross-sectional",
         moderator_category %in% design_moderator_categories &
           moderator_level %in% design_codes$design_obs_long ~
-          "Longitudinal only",
+          "Longitudinal",
         moderator_category %in% design_moderator_categories &
           moderator_level %in% design_codes$design_exp ~
           "Experimental",

### 2023-06-21 R/plot_settings.R

@@ -5,7 +5,7 @@ edu_certain <- list(
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = TRUE,
-  dims = c(12, 8),
+  dims = c(9, 6),
   moderators = FALSE,
   caption = FALSE,
   pos =

### 2023-06-21 R/save_plot.R

@@ -15,7 +15,8 @@ save_plot <- function(plot, plot_params) {
     filename = file_name,
     plot = plot,
     width = plot_params$dims[[1]],
-    height = plot_params$dims[[2]]
+    height = plot_params$dims[[2]],
+    dpi = 320
   )
 
   return(file_name)

### 2023-06-21 reports/manuscript.tex
WIP: Figures

--- 2023-06-20 reports/manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5377}
+\keywords{\newline\indent Word count: 5295}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 The influence of electronic screens on children and adolescents' health and education is not well understood.
-In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 103 meta-analyses (2,496 primary studies; 2,026,054 participants) on screen time and any outcome for youths.
+In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and any outcome for youths.
 Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval 0.05 to 0.19) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% confidence interval 0.02 to 0.31).
@@
 Supplementary File 1 provides a list of all exposures identified.
-The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
-Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
+The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 24), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
+Of the 273 unique exposure/outcome combinations, 241 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
 Full characteristics of the included studies are provided in Supplementary File 2.
-After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.
-These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
+After removing reviews with duplicate exposure/outcome combinations, our process yielded 252 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 102 reviews.
+These effects represent the findings of 2,451 primary studies, involving 1,937,501 participants.
 The characteristics of the included effects are available in Supplementary File 3.
@@
 The quality of the included meta-analyses was mixed (see Table 1).
-Most assessed heterogeneity (\emph{n} low risk = 94/103, 91\% of meta-analyses), reported the characteristics of the included studies (\emph{n} low risk = 87/103, 84\%), and used a comprehensive and systematic search strategy (\emph{n} low risk = 72/103, 70\%).
-Most reviews did not clearly report if their eligibility criteria were predefined (\emph{n} unclear = 72/103, 70\%).
-Many papers also did not complete dual independent screening of abstracts and full text (\emph{n} high risk = 20/103, 19\%) or did not clearly report the method of screening (\emph{n} unclear = 38/103, 37\%).
-A similar trend was observed for dual independent quality assessment (\emph{n} high risk = 53/103, 51\%; n high risk = 19/103, 18\%).
+Most assessed heterogeneity (\emph{n} low risk = 93/102, 91\% of meta-analyses), reported the characteristics of the included studies (\emph{n} low risk = 86/102, 84\%), and used a comprehensive and systematic search strategy (\emph{n} low risk = 71/102, 70\%).
+Most reviews did not clearly report if their eligibility criteria were predefined (\emph{n} unclear = 71/102, 70\%).
+Many papers also did not complete dual independent screening of abstracts and full text (\emph{n} high risk = 20/102, 20\%) or did not clearly report the method of screening (\emph{n} unclear = 37/102, 36\%).
+A similar trend was observed for dual independent quality assessment (\emph{n} high risk = 52/102, 51\%; n high risk = 19/102, 19\%).
 Overall, only 7 meta-analyses were graded as low risk of bias on all criteria.
 
-There were 89 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
+There were 88 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
 We removed 28 effects that did not provide individual study-level data, 19 effects with samples \textless{} 1,000, and 19 effects with a significant Egger's test or insufficient studies to conduct the test.
 Effects not meeting one or more of these standards are presented in Supplementary File 4.
-The remaining 23 effects met our criteria for statistical credibility and are described in Figure 2.
-These 23 effects came from 18 meta-analytic reviews analysing data from 338 empirical studies with 262,537 individual participants.
+The remaining 22 effects met our criteria for statistical credibility and are described in Figure 2.
+These 22 effects came from 17 meta-analytic reviews analysing data from 337 empirical studies with 262,497 individual participants.
 
-Among the statistically credible effects, general screen use, television viewing, and video games were all negatively associated with learning.
-E-books that included narration, as well as touch screen education interventions, and augmented reality education interventions were positively associated with learning.
-General screen use was negatively associated with literacy outcomes.
-However, if the screen use involved co-viewing (e.g., watching with a parent), or the content of television programs was educational, the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions and video games that contained numeracy content.
+Among the statistically credible effects, general screen use (\emph{r} = -0.11, 95\% confidence interval {[}CI{]} -0.24 to 0.01, \emph{k} = 18, \emph{N} = 13,100), television viewing (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{k} = 18, \emph{N} = 62,135), and video games (\emph{r} = -0.08, 95\% CI -0.12 to -0.04, \emph{k} = 10, \emph{N} = 4,276) were all negatively associated with learning.
+E-books that included narration (\emph{r} = 0.11, 95\% CI 0.05 to 0.17, \emph{k} = 50, \emph{N} = 2,288), as well as touch screen education interventions (\emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{k} = 79, \emph{N} = 5,810), and augmented reality education interventions (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474) were positively associated with learning.
+General screen use was negatively associated with literacy outcomes (\emph{r} = -0.14, 95\% CI -0.20 to -0.09, \emph{k} = 38, \emph{N} = 18,318).
+However, if the screen use involved co-viewing (e.g., watching with a parent; \emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{k} = 12, \emph{N} = 6,083), or the content of television programs was educational (\emph{r} = 0.13, 95\% CI 0.03 to 0.23, \emph{k} = 13, \emph{N} = 1,955), the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
+Numeracy outcomes were positively associated with screen-based mathematics interventions (\emph{r} = 0.27, 95\% CI 0.21 to 0.33, \emph{k} = 85, \emph{N} = 36,793) and video games that contained numeracy content (\emph{r} = 0.32, 95\% CI 0.21 to 0.43, \emph{k} = 25, \emph{N} = 2,008).
 
-As shown in Figure 2, most of the credible results (14 of 23 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
+As shown in Figure 2, most of the credible results (13 of 22 effects) showed statistically significant associations, with 99.9\% confidence intervals not encompassing zero (strong evidence).
 The remaining six associations were significant at the 95\% confidence level (weak evidence).
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning\textsuperscript{26}) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning\textsuperscript{27}).
-The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% confidence interval 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474).
-Most effects showed high levels of heterogeneity (18 of 23 with \(I^2 > 50\%\)).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning;\textsuperscript{26} \emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{k} = 79, \emph{N} = 5,810) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning;\textsuperscript{27} \emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{k} = 18, \emph{N} = 62,135).
+The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474).
+Most effects showed high levels of heterogeneity (17 of 22 with \(I^2 > 50\%\)).
 
-We identified 165 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
-We removed 41 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
-No remaining studies showed evidence of excessive significance.
+We identified 163 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
+We removed 39 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
+No remaining studies had statistically significant tests for excess significance.
 Effects not meeting one or more of these standards are presented in Supplementary File 5.
@@
 
-Digital advertising of unhealthy foods---both traditional advertising and video games developed by a brand for promotion---were associated with higher unhealthy food intake.
-Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
-Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents.
-All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
+Digital advertising of unhealthy foods---both traditional advertising (\emph{r} = 0.23, 95\% CI 0.10 to 0.37, \emph{k} = 13, \emph{N} = 1,756) and video games developed by a brand for promotion (\emph{r} = 0.18, 95\% CI 0.10 to 0.25, \emph{k} = 15, \emph{N} = 3,842)---were associated with higher unhealthy food intake.
+Social media use and sexual content were positively associated with risky behaviors (e.g., social media and risky sexual behaviour; \emph{r} = 0.21, 95\% CI 0.14 to 0.28, \emph{k} = 14, \emph{N} = 23,096).
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents (\emph{r} = -0.06, 95\% CI -0.10 to -0.01, \emph{k} = 10, \emph{N} = 9,798).
+Both television and video games were associated with body composition (e.g., television \emph{r} = 0.06, 95\% CI 0.03 to 0.10, \emph{k} = 12, \emph{N} = 3,196).
 Screen-based interventions which target health behaviours appeared mostly effective.
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
-Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% confidence interval 0.22 to 0.27, \emph{k} = 118, \emph{N} = 527,696).
+Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% CI 0.22 to 0.27, \emph{k} = 118, \emph{N} = 527,696).
 Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).
@@
 
-In particular, our results support the the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
-For example, our findings suggest that guidelines should discourage high levels of social media and internet use.
-Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.
+Given our results, we support the continuing trend of guidelines moving away from recommendations to reduce `screen use', and instead focusing on the type of screen use.
+For example, we suggest that guidelines should discourage high levels of social media and internet use.
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{39}
 
@@
 Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
-Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{41}
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{40}
 When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
@@
 It has been established that self-reported screen use data has questionable validity.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{42} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
-Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{43}
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{44} or device-based loggers\textsuperscript{45}---these are still not widely adopted.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{41} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
+Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{42}
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{43} or device-based loggers\textsuperscript{44}---these are still not widely adopted.
 It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
@@
 For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{46}).
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{45}).
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
@@
 Some previous research suggests that associations are typically linear.\textsuperscript{18}
-However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,47,48}
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,46,47}
 Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
@@
 We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
-We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{41}
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{40}
 
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{49} (see Table 1).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{48} (see Table 1).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 
-To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{50,51}
+To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{49,50}
 Effect sizes on the original metric are provided in Supplementary File 6.
-Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
-These are similar to other interpretations based on empirical data.\textsuperscript{53}
+Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{51} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
+These are similar to other interpretations based on empirical data.\textsuperscript{52}
 
@@
 We descriptively present the remaining meta-analytic effect sizes.
-To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{54} in R\textsuperscript{55} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
+To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{53} in R\textsuperscript{54} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
 From our reanalysis we also extracted \(I^2\) values.
-To test for publication bias, we conducted Egger's test\textsuperscript{56} when the number of studies within the review was ten or more,\textsuperscript{57} and conducted a test of excess significance.\textsuperscript{58}
+To test for publication bias, we conducted Egger's test\textsuperscript{55} when the number of studies within the review was ten or more,\textsuperscript{56} and conducted a test of excess significance.\textsuperscript{57}
 We contacted authors who did not provide primary study data in their published article.
@@
 We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
-To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{59} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
+To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{58} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 
-\emph{Figure 1: PRISMA Diagram.}
+\emph{Figure 1: PRISMA flow diagram.}
 
 \emph{Figure 2: Education outcomes.
-Results for 23 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
+Forest plot for 22 unique effect sizes related to educational outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations (two-sided) with both 95\% and 99.9\% confidence intervals.}
 
 \emph{Figure 3: Health and health-related behaviour outcomes.
-Results for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
-Findings are presented as correlations with both 95\% and 99.9\% confidence intervals.}
+Forest plot for 21 unique effect sizes related to health and health-related behaviour outcomes which met the criteria for statistical certainty.
+Findings are presented as correlations (two-sided) with both 95\% and 99.9\% confidence intervals.}
 
@@
 
-\leavevmode\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}%
-36.
-Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N.
-R.
-C.
-\& Johnston, B.
-C.
-Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials.
-\emph{Obesity Reviews} \textbf{17}, 945--959 (2016).
-
-\leavevmode\hypertarget{ref-marshallRelationshipsMediaUse2004}{}%
-37.
-Marshall, S.
-J., Biddle, S.
-J.
-H., Gorely, T., Cameron, N.
-\& Murdey, I.
-Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis.
-\emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).
-
 \leavevmode\hypertarget{ref-elsonPolicyStatementsMedia2019}{}%
-38. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).
+36. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).
 
 \leavevmode\hypertarget{ref-ashtonScreenTimeChildren2019}{}%
-39. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).
+37. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).
 
 \leavevmode\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}%
-40. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).
+38. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).
+
+\leavevmode\hypertarget{ref-markerExploringMythChubby2022}{}%
+39. Marker, C., Gnambs, T. \& Appel, M. Exploring the myth of the chubby gamer: A meta-analysis on sedentary video gaming and body mass. \emph{Social Science \& Medicine} \textbf{301}, 112325 (2022).
 
 \leavevmode\hypertarget{ref-pagePRISMA2020Statement2020}{}%
-41. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.
+40. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.
 
 \leavevmode\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}%
-42. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).
+41. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).
 
 \leavevmode\hypertarget{ref-byrneMeasurementScreenTime2021}{}%
-43. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).
+42. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).
 
 \leavevmode\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}%
-44.
+43.
 Smith, C., Galland, B.
@@
 \leavevmode\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}%
-45. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).
+44. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).
 
 \leavevmode\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}%
-46. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).
+45. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).
 
 \leavevmode\hypertarget{ref-twengeMoreTimeTechnology2019}{}%
-47.
+46.
 Twenge, J.
@@
 \leavevmode\hypertarget{ref-kellySocialMediaUse2018}{}%
-48. Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social Media Use and Adolescent Mental Health: Findings From the UK Millennium Cohort Study. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).
+47. Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social Media Use and Adolescent Mental Health: Findings From the UK Millennium Cohort Study. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).
 
 \leavevmode\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}%
-49. National Health, Lung, and Blood Institute. \emph{Quality Assessment of Systematic Reviews and Meta-Analyses}. (2014).
+48. National Health, Lung, and Blood Institute. \emph{Quality Assessment of Systematic Reviews and Meta-Analyses}. (2014).
 
 \leavevmode\hypertarget{ref-bowmanEffectSizesStatistical2012}{}%
-50. Bowman, N. A. Effect Sizes and Statistical Methods for Meta-Analysis in Higher Education. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).
+49. Bowman, N. A. Effect Sizes and Statistical Methods for Meta-Analysis in Higher Education. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).
 
 \leavevmode\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}%
-51.
+50.
 Jacobs, P.
@@
 \leavevmode\hypertarget{ref-funderEvaluatingEffectSize2019}{}%
-52. Funder, D. C. \& Ozer, D. J. Evaluating Effect Size in Psychological Research: Sense and Nonsense. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).
+51. Funder, D. C. \& Ozer, D. J. Evaluating Effect Size in Psychological Research: Sense and Nonsense. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).
 
 \leavevmode\hypertarget{ref-gignacEffectSizeGuidelines2016}{}%
-53. Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).
+52. Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).
 
 \leavevmode\hypertarget{ref-R-metafor}{}%
-54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).
+53. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).
 
 \leavevmode\hypertarget{ref-R-base}{}%
-55. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).
+54. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).
 
 \leavevmode\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}%
-56. Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).
+55. Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).
 
 \leavevmode\hypertarget{ref-pageChapter13Assessing2021}{}%
-57.
+56.
 Page, M.
@@
 \leavevmode\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}%
-58. Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).
+57. Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).
 
 \leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
-59. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
+58. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
 \end{cslreferences}

### 2023-06-21 R/clean_effects.R

@@ -60,7 +60,7 @@ clean_effects <- function(
         moderator_category %in% age_moderator_categories &
           moderator_level %in% age_codes$children ~ "Children",
         moderator_category %in% age_moderator_categories &
-          moderator_level %in% age_codes$young_children ~ "Young children",
+          moderator_level %in% age_codes$young_children ~ "Young",
         TRUE ~ moderator_age
       ),
       sample_type = if_else(

### 2023-06-21 R/plot_settings.R

@@ -5,27 +5,15 @@ edu_certain <- list(
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = TRUE,
-  dims = c(9, 6),
+  dims = c(185, 210),
   moderators = FALSE,
   caption = FALSE,
   pos =
     list(
-      lims = c(-5.0, 0.5),
-      breaks = c(-0.4, -.2, 0, .2, 0.4),
-      esig = NULL,
-      eggers = NULL,
-      indiv_data = NULL,
-      n = -0.55,
-      k = -0.75,
-      i2 = -0.95,
-      rci = -1.3,
-      author_year = -2.2,
-      design = -2.85,
-      pop = -3.2,
-      mod = -3.6,
-      expo = -4.65,
-      outcome = -5.3,
-      tag = NA
+      lims = c(-5, 0.5), breaks = c(-0.2, 0, 0.2, 0.4), esig = NULL,
+      eggers = NULL, indiv_data = NULL, n = -0.5, k = -0.75, i2 = -0.95,
+      rci = -1.35, author_year = -2.2, design = -2.8, pop = -3.15,
+      mod = -3.5, expo = -4.71, outcome = -5.38, tag = NA
     )
 )
 
@@ -35,7 +23,7 @@ edu_uncertain <- list(
   title = "Associations Between Exposures and Education Outcomes",
   categories = "Education",
   certain = FALSE,
-  dims = c(17, 18.5),
+  dims = c(416.50, 453.25),
   moderators = FALSE,
   caption = TRUE,
   pos =
@@ -64,7 +52,7 @@ nonedu_certain <- list(
   title = "Associations Between Exposures and Health-related Outcomes",
   categories = c("Psychology", "Health Behaviour", "Physical Health"),
   certain = TRUE,
-  dims = c(12, 8),
+  dims = c(185, 140),
   moderators = FALSE,
   caption = FALSE,
   pos = list(
@@ -94,7 +82,7 @@ nonedu_uncertain <-
     title = "Associations Between Exposures and Health-related Outcomes",
     categories = c("Psychology", "Health Behaviour", "Physical Health"),
     certain = FALSE,
-    dims = c(17, 49.5),
+    dims = c(416.50, 1212.75),
     moderators = FALSE,
     caption = TRUE,
     pos = list(

### 2023-06-21 R/save_plot.R

@@ -16,6 +16,7 @@ save_plot <- function(plot, plot_params) {
     plot = plot,
     width = plot_params$dims[[1]],
     height = plot_params$dims[[2]],
+    units = "mm",
     dpi = 320
   )
 

### 2023-06-22 R/clean_reviews.R
Minor revisions for NHB (#32)
* Update renv

* Upgrade renv

* Rerun pipeline

* Programatically join supplementary files

Includes a table of contents & description of each file, per reviewer suggestion

* Update co-author affiliations

* Remove revision letter and associated files

* Move sections around to match required format

* Update affiliations

* Fix missing python file

* Rerun pipeline

* Address some comment in manuscript

* Unlink table 1 and RoB

Also had to rename all the supp materials

* Update abstract

* Update renv

* Fix duplicate study

* Update tables

* WIP: Fixing plo

@@ -31,7 +31,7 @@ clean_reviews <- function(
         demographics %in% age_codes$mixed ~ "Mixed",
         demographics %in% age_codes$adolescents ~ "Adolescents",
         demographics %in% age_codes$children ~ "Children",
-        demographics %in% age_codes$young_children ~ "Young children",
+        demographics %in% age_codes$young_children ~ "Young",
         TRUE ~ demographics
       ),
       # Tidy up the sample age variables
@@ -58,7 +58,7 @@ clean_reviews <- function(
         sample_age_lowest_study_mean < 1 & sample_age_highest_study_mean > 10 ~
           "Mixed",
         sample_age_lowest_study_mean >= 12 ~ "Adolescents",
-        sample_age_highest_study_mean < 7 ~ "Young children",
+        sample_age_highest_study_mean < 7 ~ "Young",
         sample_age_lowest_study_mean >= 4 & sample_age_highest_study_mean < 13 ~
           "Children",
         TRUE ~ demographics_coded
@@ -125,10 +125,10 @@ clean_reviews <- function(
     # Add study design
     mutate(
       study_design = case_when( # nolint start
-        study_design_restrictions %in% design_codes$design_unspec ~ "Mixed or unspecified",
-        study_design_restrictions %in% design_codes$design_obs_mixed ~ "Observational - mixed",
-        study_design_restrictions %in% design_codes$design_obs_cross ~ "Cross-sectional only",
-        study_design_restrictions %in% design_codes$design_obs_long ~ "Longitudinal only",
+        study_design_restrictions %in% design_codes$design_unspec ~ "Mixed or unclear",
+        study_design_restrictions %in% design_codes$design_obs_mixed ~ "Observational",
+        study_design_restrictions %in% design_codes$design_obs_cross ~ "Cross-sectional",
+        study_design_restrictions %in% design_codes$design_obs_long ~ "Longitudinal",
         study_design_restrictions %in% design_codes$design_exp ~ "Experimental",
         TRUE ~ study_design_restrictions # nolint end
       )

### 2023-06-22 R/make_table_desc.R

@@ -25,7 +25,8 @@ make_table_desc_gt <- function(tables_df) {
       -plain_language_outcome,
       -plain_language_exposure,
       -use_effect,
-      -table
+      -table,
+      -eligibility_criteria_predefined_and_specified:-heterogeneity_assessed,
     ) %>%
     distinct() %>%
     mutate(
@@ -60,17 +61,6 @@ make_table_desc_gt <- function(tables_df) {
       sample_restrictions = map(sample_restrictions, gt::html)
     ) %>%
     relocate(sample_restrictions, .after = design_restrictions) %>%
-    mutate_at(
-      vars(
-        "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
-      ),
-      ~ case_match(
-        .x,
-        "low" ~ "L",
-        "unclear" ~ "U",
-        "high" ~ "H"
-      )
-    ) %>%
     # Reorder the columns
     select(
       -starts_with("sample_age_mean"),
@@ -94,28 +84,10 @@ make_table_desc_gt <- function(tables_df) {
       caption = "Review characteristics for studies providing unique effects"
     ) %>%
     tab_header(html("<strong>Review Characteristics</strong>"),
-      subtitle = "Review characteristics and quality assessment for meta-analyses providing unique effects" # nolint
-    ) %>%
-    data_color(
-      columns =
-        eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
-      colors = scales::col_factor(
-        palette = rob_cols,
-        levels = c("L", "U", "H")
-      )
+      subtitle = "Review characteristics for meta-analyses providing unique effects" # nolint
     ) %>%
     cols_merge_range(
       col_begin = earliest_study_year, col_end = latest_study_year
-    ) %>%
-    tab_spanner(
-      label = "Review Characteristics",
-      columns =
-        first_author:exposures_assessed
-    ) %>%
-    tab_spanner(
-      label = "Quality Assessment",
-      columns =
-        eligibility_criteria_predefined_and_specified:heterogeneity_assessed
     ) %>%
     cols_label(
       first_author = "First Author",
@@ -129,79 +101,16 @@ make_table_desc_gt <- function(tables_df) {
         "Sample Age Restrictions<br><small>(Age Range)</small>"
       ),
       outcomes_assessed = "Outcomes Assessed",
-      exposures_assessed = "Exposures Assessed",
-      eligibility_criteria_predefined_and_specified = html("Elig. <br>Crit."),
[…]

### 2023-06-22 R/make_table_rob.R

@@ -1,0 +1,140 @@
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param tables_df
+#' @return
+#' @author Taren Sanders
+#' @export
+make_table_rob <- function(tables_df) {
+  rob_cols <- c("#b7e1cd", "#fce8b2", "#f4c7c3")
+
+  base_table <-
+    tables_df %>%
+    filter(table == "main") %>%
+    select(
+      first_author, year,
+      eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) %>%
+    distinct() %>%
+    mutate_at(
+      vars(
+        "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
+      ),
+      ~ case_match(
+        .x,
+        "low" ~ "L",
+        "unclear" ~ "U",
+        "high" ~ "H"
+      )
+    ) %>%
+    arrange(str_to_lower(first_author), year)
+
+  gt_table <-
+    base_table %>%
+    gt(
+      caption = "Quality assessment for studies providing unique effects"
+    ) %>%
+    tab_header(md("**Quality Assessment**"),
+      subtitle = "Quality assessment for meta-analyses providing unique effects" # nolint
+    ) %>%
+    data_color(
+      columns =
+        eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
+      fn = scales::col_factor(
+        palette = rob_cols,
+        levels = c("L", "U", "H")
+      )
+    ) %>%
+    tab_spanner(
+      label = "Quality Assessment",
+      columns =
+        eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) %>%
+    cols_label(
+      first_author = "First Author",
+      year = "Year",
+      eligibility_criteria_predefined_and_specified = html("Elig. Crit."),
+      literature_search_strategy_comprehensive_and_systematic = "Lit. Search",
+      dual_independent_screening_review = "Dual Screen",
+      dual_independent_quality_assessment = "Dual Qual.",
+      included_studies_listed_with_important_characteristics_and_results_of_each = "Studies Listed", # nolint
+      publication_bias_assessed = "Pub. Bias",
+      heterogeneity_assessed = "Hetero."
+    ) %>%
+    cols_align(
+      columns =
+        first_author:year,
+      align = "left"
+    ) %>%
+    cols_align(
+      columns =
[…]

### 2023-06-22 R/save_table.R

@@ -5,23 +5,32 @@
 #' @title
 #' @param table Must be of type
 #' @param filename
+#' @param method
 #' @return
 #' @author Taren Sanders
 #' @export
-save_table <- function(table, filename) {
+save_table <- function(table, filename, method = "webshot2") {
   if (Sys.info()["sysname"] == "Linux") {
     # PhantomJS runs into issues without this
     Sys.setenv("OPENSSL_CONF" = "/dev/null")
   }
 
-  # Note: this only works with gt 0.6.0 (webshot not webshot2)
-  gtsave(
-    data = table,
-    filename = filename,
-    zoom = 1,
-    vwidth = 3440,
-    vheight = 2000,
-  )
+  if (method == "webshot2") {
+    gtsave(
+      data = table,
+      filename = filename,
+      zoom = 1,
+      vwidth = 3440,
+      vheight = 2000,
+    )
+  }
+
+  if (method == "webshot") {
+    temp_path <- tempfile(fileext = ".html")
+    gt:::gt_save_html(data = table, filename = temp_path, path = NULL)
+    webshot::webshot(url = paste0("file:///", temp_path), file = filename)
+    file.remove(temp_path)
+  }
 
   return(filename)
 }

### 2023-06-22 packages.R

@@ -34,4 +34,5 @@ library(tarchetypes)
 library(targets)
 library(tidyMB)
 library(tidyr)
+library(webshot2)
 library(xfun)

### 2023-07-14 reports/manuscript.Rmd
Final rerun of pipeline
Add effects/studies that met criteria to abstract

@@
   The influence of electronic screens on children and adolescents’ health and education is not well understood.
-  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r format(targets::tar_read(manuscript_info)$effects_sum$sum_k, big.mark=",")` primary studies; `r format(targets::tar_read(manuscript_info)$effects_sum$sum_n, big.mark=",")` participants) on screen time and any outcome for youths.
+  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r targets::tar_read(manuscript_info)$effects_sum$sum_k` primary studies; `r targets::tar_read(manuscript_info)$effects_sum$sum_n` participants) on screen time and any outcome for youths.
+  Of these, `r targets::tar_read(manuscript_info)$effects_certain` effects from `r targets::tar_read(manuscript_info)$reviews_certain` met our criteria for statistical certainty.
   Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, `r targets::tar_read(manuscript_info)$abstract$social_media`) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, `r targets::tar_read(manuscript_info)$abstract$edu`).
@@
 After removing reviews with duplicate exposure/outcome combinations, our process yielded `r manuscript_info$unique_effects` unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from `r manuscript_info$prisma$unique_reviews` reviews.
-These effects represent the findings of `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies, involving `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
+These effects represent the findings of `r manuscript_info$effects_sum$sum_k` primary studies, involving `r manuscript_info$effects_sum$sum_n` participants.
 The characteristics of the included effects are available in Supplementary File 3.
@@
 Overall, only `r manuscript_info$qual$all_low` meta-analyses were graded as low risk of bias on all criteria.
+
+## Education Outcomes
 
@@
 Most effects showed high levels of heterogeneity (`r manuscript_info$edu$n_i2` of `r manuscript_info$edu$n_certain` with $I^2 > 50\%$).
+
+## Health-related Outcomes
 
@@
 Our primary goal for this umbrella review was to provide a high-level synthesis of screen use research, by examining a range of exposures and the associations with a broad scope of outcomes.
-Our results represent the findings from `r format(manuscript_info$effects_sum$sum_k, big.mark=",")` primary studies comprised of `r format(manuscript_info$effects_sum$sum_n, big.mark=",")` participants.
+Our results represent the findings from `r manuscript_info$effects_sum$sum_k` primary studies comprised of `r manuscript_info$effects_sum$sum_n` participants.
 To ensure findings could be compared on a common metric, we extracted and reanalysed individual study data where possible.

### 2023-07-20 reports/manuscript.tex
Minor revisions for NHB (#32)
* Update renv

* Upgrade renv

* Rerun pipeline

* Programatically join supplementary files

Includes a table of contents & description of each file, per reviewer suggestion

* Update co-author affiliations

* Remove revision letter and associated files

* Move sections around to match required format

* Update affiliations

* Fix missing python file

* Rerun pipeline

* Address some comment in manuscript

* Unlink table 1 and RoB

Also had to rename all the supp materials

* Update abstract

* Update renv

* Fix duplicate study

* Update tables

* WIP: Fixing plo

@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5295}
+\keywords{\newline\indent Word count: 5299}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and any outcome for youths.
-Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval 0.05 to 0.19) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% confidence interval 0.02 to 0.31).
+Of these, 43 effects from 32 met our criteria for statistical certainty.
+Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval {[}CI{]} 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% CI 0.02 to 0.31, \emph{p} = 0.029, \emph{k} = 10, \emph{N} = 1,183).
 Some types of screen use have complex associations with outcomes.
-For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% confidence interval -0.15 to -0.04).
-However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% confidence interval 0.02 to 0.28).
+For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135).
+However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
 These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
@@
 
+\hypertarget{education-outcomes}{%
+\subsection{Education Outcomes}\label{education-outcomes}}
+
 There were 88 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
@@
 
-Among the statistically credible effects, general screen use (\emph{r} = -0.11, 95\% confidence interval {[}CI{]} -0.24 to 0.01, \emph{k} = 18, \emph{N} = 13,100), television viewing (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{k} = 18, \emph{N} = 62,135), and video games (\emph{r} = -0.08, 95\% CI -0.12 to -0.04, \emph{k} = 10, \emph{N} = 4,276) were all negatively associated with learning.
-E-books that included narration (\emph{r} = 0.11, 95\% CI 0.05 to 0.17, \emph{k} = 50, \emph{N} = 2,288), as well as touch screen education interventions (\emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{k} = 79, \emph{N} = 5,810), and augmented reality education interventions (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474) were positively associated with learning.
-General screen use was negatively associated with literacy outcomes (\emph{r} = -0.14, 95\% CI -0.20 to -0.09, \emph{k} = 38, \emph{N} = 18,318).
-However, if the screen use involved co-viewing (e.g., watching with a parent; \emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{k} = 12, \emph{N} = 6,083), or the content of television programs was educational (\emph{r} = 0.13, 95\% CI 0.03 to 0.23, \emph{k} = 13, \emph{N} = 1,955), the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
-Numeracy outcomes were positively associated with screen-based mathematics interventions (\emph{r} = 0.27, 95\% CI 0.21 to 0.33, \emph{k} = 85, \emph{N} = 36,793) and video games that contained numeracy content (\emph{r} = 0.32, 95\% CI 0.21 to 0.43, \emph{k} = 25, \emph{N} = 2,008).
+Among the statistically credible effects, general screen use (\emph{r} = -0.11, 95\% confidence interval {[}CI{]} -0.24 to 0.01, \emph{p} = 0.071, \emph{k} = 18, \emph{N} = 13,100), television viewing (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135), and video games (\emph{r} = -0.08, 95\% CI -0.12 to -0.04, \emph{p} = \textless0.001, \emph{k} = 10, \emph{N} = 4,276) were all negatively associated with learning.
+E-books that included narration (\emph{r} = 0.11, 95\% CI 0.05 to 0.17, \emph{p} = \textless0.001, \emph{k} = 50, \emph{N} = 2,288), as well as touch screen education interventions (\emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{p} = \textless0.001, \emph{k} = 79, \emph{N} = 5,810), and augmented reality education interventions (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{p} = \textless0.001, \emph{k} = 15, \emph{N} = 1,474) were positively associated with learning.
+General screen use was negatively associated with literacy outcomes (\emph{r} = -0.14, 95\% CI -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318).
+However, if the screen use involved co-viewing (e.g., watching with a parent; \emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083), or the content of television programs was educational (\emph{r} = 0.13, 95\% CI 0.03 to 0.23, \emph{p} = 0.012, \emph{k} = 13, \emph{N} = 1,955), the association with literacy was positive and significant at the 95\% confidence level (weak evidence).
+Numeracy outcomes were positively associated with screen-based mathematics interventions (\emph{r} = 0.27, 95\% CI 0.21 to 0.33, \emph{p} = \textless0.001, \emph{k} = 85, \emph{N} = 36,793) and video games that contained numeracy content (\emph{r} = 0.32, 95\% CI 0.21 to 0.43, \emph{p} = \textless0.001, \emph{k} = 25, \emph{N} = 2,008).
 
@@
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning;\textsuperscript{26} \emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{k} = 79, \emph{N} = 5,810) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning;\textsuperscript{27} \emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{k} = 18, \emph{N} = 62,135).
-The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{k} = 15, \emph{N} = 1,474).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning;\textsuperscript{26} \emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{p} = \textless0.001, \emph{k} = 79, \emph{N} = 5,810) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning;\textsuperscript{27} \emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135).
+The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{p} = \textless0.001, \emph{k} = 15, \emph{N} = 1,474).
 Most effects showed high levels of heterogeneity (17 of 22 with \(I^2 > 50\%\)).
+
+\hypertarget{health-related-outcomes}{%
+\subsection{Health-related Outcomes}\label{health-related-outcomes}}
 
@@
 
-Digital advertising of unhealthy foods---both traditional advertising (\emph{r} = 0.23, 95\% CI 0.10 to 0.37, \emph{k} = 13, \emph{N} = 1,756) and video games developed by a brand for promotion (\emph{r} = 0.18, 95\% CI 0.10 to 0.25, \emph{k} = 15, \emph{N} = 3,842)---were associated with higher unhealthy food intake.
-Social media use and sexual content were positively associated with risky behaviors (e.g., social media and risky sexual behaviour; \emph{r} = 0.21, 95\% CI 0.14 to 0.28, \emph{k} = 14, \emph{N} = 23,096).
-Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents (\emph{r} = -0.06, 95\% CI -0.10 to -0.01, \emph{k} = 10, \emph{N} = 9,798).
-Both television and video games were associated with body composition (e.g., television \emph{r} = 0.06, 95\% CI 0.03 to 0.10, \emph{k} = 12, \emph{N} = 3,196).
+Digital advertising of unhealthy foods---both traditional advertising (\emph{r} = 0.23, 95\% CI 0.10 to 0.37, \emph{p} = \textless0.001, \emph{k} = 13, \emph{N} = 1,756) and video games developed by a brand for promotion (\emph{r} = 0.18, 95\% CI 0.10 to 0.25, \emph{p} = \textless0.001, \emph{k} = 15, \emph{N} = 3,842)---were associated with higher unhealthy food intake.
+Social media use and sexual content were positively associated with risky behaviors (e.g., social media and risky sexual behaviour; \emph{r} = 0.21, 95\% CI 0.14 to 0.28, \emph{p} = \textless0.001, \emph{k} = 14, \emph{N} = 23,096).
+Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents (\emph{r} = -0.06, 95\% CI -0.10 to -0.01, \emph{p} = 0.018, \emph{k} = 10, \emph{N} = 9,798).
+Both television and video games were associated with body composition (e.g., television \emph{r} = 0.06, 95\% CI 0.03 to 0.10, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 3,196).
 Screen-based interventions which target health behaviours appeared mostly effective.
@@
 However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
-Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% CI 0.22 to 0.27, \emph{k} = 118, \emph{N} = 527,696).
+Additionally, most effects were small, with the association between internet use and depression the largest at \emph{r} = 0.25 (95\% CI 0.22 to 0.27, \emph{p} = \textless0.001, \emph{k} = 118, \emph{N} = 527,696).
 Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).

### 2023-07-20 R/combine_effects.R

@@ -58,6 +58,7 @@ combine_effects <- function(effects_clean, studies_results) {
         reanalysis_conf.high_999,
         NA_real_
       ),
+      pval = reanalysis_p.value, # Only report p for reanalysis
       # Statistical certainty indicator
       certainty = case_when(
         # Use reported means unclear

### 2023-07-20 R/make_prisma.R

@@ -9,7 +9,8 @@
 #' @return
 #' @author Taren Sanders
 #' @export
-make_prisma <- function(prisma_path, effects_clean, reviews_clean) {
+make_prisma <- function(
+    prisma_path, effects_clean, reviews_clean, combined_effects) {
   prisma_data <- readr::read_file(prisma_path)
 
   prisma_df_raw <-
@@ -104,6 +105,10 @@ make_prisma <- function(prisma_path, effects_clean, reviews_clean) {
   larger_avail <- reviews_clean %>%
     filter(!review_id %in% c(contributing_reviews, missing_key)) %>%
     pull(review_id)
+  credible_reviews <-
+    combined_effects %>%
+    filter(use_effect & certainty == "meets criteria") %>%
+    distinct(review_id)
 
   prisma_df_cleaned <-
     prisma_df %>%
@@ -127,7 +132,10 @@ make_prisma <- function(prisma_path, effects_clean, reviews_clean) {
       value = length(larger_avail)
     ) %>%
     add_row(
-      text = "studies contributed unique effects",
+      text = glue::glue(
+        "studies contributed unique effects\n",
+        "({nrow(credible_reviews)} provided statistically credible effects)"
+      ),
       type = "main",
       step = prisma_df$step[nrow(prisma_df)] + 1,
       value = length(contributing_reviews)

### 2023-07-20 R/make_table_rob.R

@@ -39,14 +39,6 @@ make_table_rob <- function(tables_df) {
     tab_header(md("**Quality Assessment**"),
       subtitle = "Quality assessment for meta-analyses providing unique effects" # nolint
     ) %>%
-    data_color(
-      columns =
-        eligibility_criteria_predefined_and_specified:heterogeneity_assessed,
-      fn = scales::col_factor(
-        palette = rob_cols,
-        levels = c("L", "U", "H")
-      )
-    ) %>%
     tab_spanner(
       label = "Quality Assessment",
       columns =

### 2023-08-02 reports/manuscript.Rmd
Add Table 1 to manuscript file

@@
 targets::tar_load(
-  c("manuscript_info", "combined_bib", "combined_effects"),
+  c("manuscript_info", "combined_bib", "combined_effects", "table_rob_latex"),
   store = here::here("_targets")
@@
 
+```{r table1, echo = FALSE}
+table_rob_latex
+```
+
+\newpage
+
 # Figure legends

### 2023-08-02 reports/manuscript.Rmd
Update abstract and manuscript text

@@
   The influence of electronic screens on children and adolescents’ health and education is not well understood.
-  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r targets::tar_read(manuscript_info)$effects_sum$sum_k` primary studies; `r targets::tar_read(manuscript_info)$effects_sum$sum_n` participants) on screen time and any outcome for youths.
-  Of these, `r targets::tar_read(manuscript_info)$effects_certain` effects from `r targets::tar_read(manuscript_info)$reviews_certain` met our criteria for statistical certainty.
-  Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, `r targets::tar_read(manuscript_info)$abstract$social_media`) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, `r targets::tar_read(manuscript_info)$abstract$edu`).
-  Some types of screen use have complex associations with outcomes.
-  For example, television viewing showed harmful correlations with learning `r targets::tar_read(manuscript_info)$abstract$tv_edu`.
-  However, when parents watched with their children, general screen use was associated with greater literacy `r targets::tar_read(manuscript_info)$abstract$coview`.
-  These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+  In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from `r targets::tar_read(manuscript_info)$prisma$unique_reviews` meta-analyses (`r targets::tar_read(manuscript_info)$effects_sum$sum_k` primary studies; `r targets::tar_read(manuscript_info)$effects_sum$sum_n` participants) on screen time and outcomes.
+  `r targets::tar_read(manuscript_info)$effects_certain` effects from `r targets::tar_read(manuscript_info)$reviews_certain` meta-analyses met our criteria for statistical certainty.
+  Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects `r targets::tar_read(manuscript_info)$abstract$range`.
+  In education, results were mixed; for example, screen use was negatively associated with literacy `r targets::tar_read(manuscript_info)$abstract$lit_gen`, but this effect was positive when parents watched with their children `r targets::tar_read(manuscript_info)$abstract$coview`.
+  In health, we found evidence for several small negative associations; for example, social media was associated with depression `r targets::tar_read(manuscript_info)$abstract$social_media`.
+  Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in `r targets::tar_read(manuscript_info)$abstract$rob` included meta-analyses and high heterogeneity (`r manuscript_info$edu$n_i2`/`r manuscript_info$edu$n_certain` in education and `r manuscript_info$health$n_i2`/`r manuscript_info$health$n_certain` in health with $I^2 > 50\%$)
+  We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
 
@@
 This review synthesises evidence on any outcome of electronic media exposure.
-We deliberately did not pre-specify outcomes, in order to get a comprehensive list of areas where there is meta-analytical evidence.
+We deliberately did not pre-specify outcomes, in order to get a list of areas where there is meta-analytical evidence.
 Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
@@
 
-Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make strong claims on the directions of causality.
+Our high-level approach also means that we could not engage with the specific mechanisms behind each association, and as such, we cannot make claims on the directions of causality.
 These likely depend on the specific exposure and outcome.
@@
 Screen use is a topic of significant interest, as shown by the wide variety of academic domains involved, parents' concerns, and the growing pervasiveness into society.
-Our findings showed that the influence of screen use can be both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition).
-The interplay of these findings show that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
-However, our findings also suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen use, with less emphasis on measures that aggregate screen use and instead focus on the content, context, and environment in which the exposure occurs.
+Our findings showed that screen use is associated with both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition) outcomes.
+Based on our findings, we recommend that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+However, our findings also lead us to suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen use, with less emphasis on measures that aggregate screen use and instead focus on the content, context, and environment in which the exposure occurs.
 

### 2023-08-02 R/make_manuscript_info.R

@@ -163,6 +163,9 @@ make_manuscript_info <- function(effects_clean, prisma, tables_df,
     filter(count_high_unclear == 7) %>%
     nrow()
 
+  manuscript_info$qual$not_low <-
+    manuscript_info$prisma$unique_reviews - manuscript_info$qual$all_low
+
   reviews_summary <-
     reviews_count %>%
     select(
@@ -391,10 +394,13 @@ make_manuscript_info <- function(effects_clean, prisma, tables_df,
 
   # Abstract Results ---------------------------------------------
   manuscript_info$abstract$social_media <-
-    report_effect(combined_effects, "53160_001", "none", first = TRUE)
+    report_effect(combined_effects, "53160_001", "brackets")
 
   manuscript_info$abstract$edu <-
     report_effect(combined_effects, "61452_004", "none")
+
+  manuscript_info$abstract$lit_gen <-
+    report_effect(combined_effects, "47783_001", "brackets", first = TRUE)
 
   manuscript_info$abstract$tv_body <-
     report_effect(combined_effects, "8556_119", "brackets")
@@ -404,6 +410,17 @@ make_manuscript_info <- function(effects_clean, prisma, tables_df,
 
   manuscript_info$abstract$coview <-
     report_effect(combined_effects, "47783_022", "brackets")
+
+  range_df <- combined_effects %>%
+    filter(certainty == "meets criteria" & use_effect) %>%
+    summarise(min = round(min(r), 2), max = round(max(r), 2))
+
+  manuscript_info$abstract$range <- glue::glue(
+    "(range: *r* = {range_df['min']}-{range_df['max']})"
+  )
+
+  manuscript_info$abstract$rob <-
+    glue::glue("{manuscript_info$qual$not_low}/{manuscript_info$prisma$unique_reviews}") # nolint
 
   return(manuscript_info)
 }

### 2023-08-02 reports/manuscript.tex
Rerun pipeline

@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5299}
+\keywords{\newline\indent Word count: 5300}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 The influence of electronic screens on children and adolescents' health and education is not well understood.
-In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and any outcome for youths.
-Of these, 43 effects from 32 met our criteria for statistical certainty.
-Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval {[}CI{]} 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% CI 0.02 to 0.31, \emph{p} = 0.029, \emph{k} = 10, \emph{N} = 1,183).
-Some types of screen use have complex associations with outcomes.
-For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135).
-However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
-These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and outcomes.
+43 effects from 32 meta-analyses met our criteria for statistical certainty.
+Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects (range: \emph{r} = -0.14-0.33).
+In education, results were mixed; for example, screen use was negatively associated with literacy (\emph{r} = -0.14, 95\% confidence interval {[}CI{]} -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318), but this effect was positive when parents watched with their children (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
+In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
+Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\))
+We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
 }
@@
 \emph{Table 1: Review characteristics and quality assessment for meta-analyses providing unique effects}
+
+\begin{ThreePartTable}
+\begin{TableNotes}
+\item \textit{Note: } 
+\item Items are from the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool.
+Note that we excluded the first item of the tool.
+U = Unclear; L = Low; H = High
+\item[1] Eligibility criteria predefined and specified
+\item[2] Literature search strategy comprehensive and systematic
+\item[3] Dual independent screening and review
+\item[4] Dual independent quality assessment
+\item[5] Included studies listed with important characteristics and results of each
+\item[6] Publication bias assessed
+\item[7] Heterogeneity assessed
+\end{TableNotes}
+\begin{longtable}[t]{ll>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}}
+\caption{Quality assessment for studies providing unique effects}\\
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{7}{c}{Quality Assessment} \\
+\cmidrule(l{3pt}r{3pt}){3-9}
+First Author & Year & Elig.
+Crit.\textsuperscript{1} & Lit.
+Search\textsuperscript{2} & Dual Screen\textsuperscript{3} & Dual Qual.\textsuperscript{4} & Studies Listed\textsuperscript{5} & Pub.
+Bias\textsuperscript{6} & Hetero.\textsuperscript{7}\\
+\midrule
+\endfirsthead
+\caption[]{Quality assessment for studies providing unique effects \textit{(continued)}}\\
+\toprule
+First Author & Year & Elig.
+Crit.\textsuperscript{1} & Lit.
+Search\textsuperscript{2} & Dual Screen\textsuperscript{3} & Dual Qual.\textsuperscript{4} & Studies Listed\textsuperscript{5} & Pub.
+Bias\textsuperscript{6} & Hetero.\textsuperscript{7}\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\insertTableNotes
+\endlastfoot
+Abrami & 2020 & U & U & L & H & L & L & L\\
+Adelantado-Renau & 2019 & L & L & L & L & L & L & L\\
+Andrade & 2019 & U & L & L & U & L & H & L\\
+Arztmann & 2022 & U & H & H & H & H & L & L\\
+Aspiranti & 2020 & U & L & L & H & L & H & L\\
+\addlinespace
+Bartel & 2015 & L & L & U & U & L & U & U\\
+Beck Silva & 2022 & L & L & L & L & L & H & L\\
+Benavides-Varela & 2020 & U & H & L & H & L & L & L\\
+Blok & 2002 & U & L & H & H & L & H & L\\
+Bossen & 2020 & U & L & L & L & L & H & L\\
+\addlinespace
+Boyland & 2016 & H & L & L & U & L & L & L\\
+Byun & 2018 & U & U & U & H & H & H & H\\
+Cao & 2020 & U & H & U & H & L & L & L\\
+Champion & 2019 & L & L & L & L & L & L & L\\
+Chan & 2014 & U & H & H & H & L & L & L\\
+\addlinespace
+Chauhan & 2017 & U & L & U & H & H & L & L\\
+Chen & 2020 & U & H & U & H & H & H & L\\
+Cheung & 2012 & U & L & L & H & H & L & L\\
+Cheung & 2013 & L & H & H & U & L & L & L\\
+Cho & 2018 & U & H & U & H & L & L & L\\
+\addlinespace
+Claussen & 2022 & U & L & U & H & L & H & L\\
+Clinton & 2019 & U & H & U & U & L & L & L\\
+Comeras-Chueca & 2021 & L & U & L & U & L & H & L\\
+Comeras-Chueca & 2021 & L & L & L & U & L & H & L\\
+Coyne & 2018 & L & L & L & H & L & L & L\\
+\addlinespace
+Cunningham & 2021 & U & L & L & H & L & L & L\\
+Cushing & 2010 & U & L & H & H & L & L & L\\
+Darling & 2017 & U & L & U & U & L & H & H\\
+Eirich & 2022 & U & L & L & L & L & L & L\\
+Feng & 2021 & L & L & L & L & L & H & L\\
+\addlinespace
+Ferguson & 2017 & U & L & L & H & L & L & L\\
+Ferguson & 2020 & L & U & L & L & L & L & L\\
+Folkvord & 2018 & U & L & L & U & L & H & L\\
+Furenes & 2021 & H & H & L & U & L & L & L\\
+Gardella & 2017 & U & L & L & U & L & L & L\\
+\addlinespace
+Garzón & 2019 & U & H & U & H & H & L & L\\
+Graham & 2015 & U & L & H & H & L & L & L\\
+Hammersley & 2016 & L & L & H & L & L & H & L\\
+Hao & 2021 & U & L & L & L & L & H & L\\
+Hassan-Saleh & 2019 & U & L & U & U & H & H & L\\
+\addlinespace
+He & 2021 & L & L & L & L & L & L & L\\
+Hernandez-Jimenez & 2019 & U & L & H & L & L & L & L\\
+Hurwitz & 2018 & L & L & H & H & L & L & L\\
+Ivie & 2020 & U & L & L & L & L & L & L\\
+Janssen & 2020 & U & L & L & L & L & U & L\\
+\addlinespace
+Kates & 2018 & U & H & L & H & H & L & L\\
+Kim & 2021 & U & L & U & L & L & L & L\\
+Kroesbergen & 2003 & U & L & U & H & L & H & L\\
+Kucukalkan & 2019 & U & L & U & U & H & L & L\\
+Li & 2010 & U & L & L & U & L & H & L\\
+\addlinespace
+Li & 2022 & L & H & L & L & L & H & L\\
+Li & 2022 & U & H & L & H & L & L & L\\
+Liao & 2008 & L & H & H & L & H & H & H\\
+Liao & 2014 & U & L & H & L & L & L & L\\
+Liu & 2019 & U & L & U & H & L & L & L\\
+\addlinespace
+Liu & 2022 & U & H & U & H & H & L & L\\
+Lu & 2021 & U & L & U & L & L & L & L\\
+Madigan & 2020 & U & L & L & U & L & L & L\\
+Major & 2021 & U & L & L & H & L & L & L\\
+Mallawaarachchi & 2022 & L & L & L & L & L & L & L\\
+\addlinespace
+Mares & 2005 & U & L & H & H & L & H & H\\
+Mares & 2013 & U & H & H & H & L & H & L\\
+Marker & 2022 & U & L & H & L & L & L & L\\
+Marshall & 2004 & U & L & H & H & H & H & L\\
+Martins & 2019 & U & L & U & H & L & L & L\\
+\addlinespace
+Martins & 2022 & L & L & L & L & L & H & L\\
+Mazeas & 2022 & L & L & L & L & L & L & L\\
+McArthur & 2012 & L & L & L & L & L & L & L\\
+McArthur & 2018 & L & L & L & L & L & L & L\\
+Mei & 2018 & U & H & U & L & L & H & L\\
+\addlinespace
+Merchant & 2014 & U & L & H & H & H & H & L\\
+Neitzel & 2022 & U & L & H & H & L & H & H\\
+Oldrati & 2020 & U & L & U & H & L & L & L\\
+Paik & 1994 & U & H & U & H & H & L & H\\
+Pearce & 2016 & U & L & H & H & H & L & L\\
+\addlinespace
+Peng & 2011 & U & L & U & U & L & H & L\\
+Powers & 2013 & U & L & U & H & L & L & L\\
+Prescott & 2018 & U & L & U & H & L & L & L\\
+Reynard & 2022 & H & L & L & L & L & L & L\\
+Rodriguez-Rocha & 2019 & U & L & L & L & L & L & L\\
+\addlinespace
+Sadeghirad & 2016 & H & L & L & L & L & L & L\\
+Scherer & 2020 & U & H & U & H & L & L & L\\
+Schroeder & 2013 & L & L & U & H & L & L & L\\
+Scionti & 2019 & L & L & L & H & L & L & L\\
+Shin & 2019 & U & L & L & L & L & H & L\\
+\addlinespace
+Shin & 2022 & L & H & L & L & L & L & L\\
+Slavin & 2014 & U & H & H & H & L & H & H\\
+Strouse & 2021 & U & L & U & H & H & L & L\\
+Takacs & 2014 & H & L & U & H & L & L & L\\
+Takacs & 2019 & L & L & U & H & L & L & L\\
+\addlinespace
+Tekedere & 2016 & U & H & U & U & L & L & L\\
+Tokac & 2019 & U & H & L & H & L & L & L\\
+Vahedi & 2018 & L & L & U & U & L & L & L\\
+van Ekris & 2016 & U & L & L & L & L & H & L\\
+Vannucci & 2020 & U & L & U & H & L & L & L\\
+\addlinespace
+Williams & 1982 & U & U & H & U & L & H & H\\
+Wouters & 2013 & U & H & U & H & L & L & L\\
+Xie & 2018 & U & L & L & H & L & L & L\\
+Yin & 2019 & U & H & U & H & L & L & L\\
+Zhou & 2020 & U & L & U & H & L & L & L\\
+\addlinespace
+Zucker & 2009 & L & L & U & H & L & H & L\\*
+\end{longtable}
+\end{ThreePartTable}
+
+\newpage
 

### 2023-08-03 reports/manuscript.Rmd
Fix typo in abstract

@@
   In health, we found evidence for several small negative associations; for example, social media was associated with depression `r targets::tar_read(manuscript_info)$abstract$social_media`.
-  Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in `r targets::tar_read(manuscript_info)$abstract$rob` included meta-analyses and high heterogeneity (`r manuscript_info$edu$n_i2`/`r manuscript_info$edu$n_certain` in education and `r manuscript_info$health$n_i2`/`r manuscript_info$health$n_certain` in health with $I^2 > 50\%$)
+  Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in `r targets::tar_read(manuscript_info)$abstract$rob` included meta-analyses and high heterogeneity (`r manuscript_info$edu$n_i2`/`r manuscript_info$edu$n_certain` in education and `r manuscript_info$health$n_i2`/`r manuscript_info$health$n_certain` in health with $I^2 > 50\%$).
   We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.

### 2023-08-03 reports/manuscript.tex
Additional formatting changes (#35)
* Add Table 1 to manuscript file

* Update abstract and manuscript text

* Add word temp files to gitignore

* Remove a word temp file

* Fix typo in abstract

* Rerun pipeline

@@
 In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
-Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\))
+Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\)).
 We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.

### 2023-08-03 R/make_table_rob.R

@@ -7,7 +7,7 @@
 #' @return
 #' @author Taren Sanders
 #' @export
-make_table_rob <- function(tables_df) {
+make_table_rob_gt <- function(tables_df) {
   rob_cols <- c("#b7e1cd", "#fce8b2", "#f4c7c3")
 
   base_table <-
@@ -129,4 +129,85 @@ make_table_rob <- function(tables_df) {
     )
 
   return(gt_table)
+}
+
+#' .. content for \description{} (no empty lines) ..
+#'
+#' .. content for \details{} ..
+#'
+#' @title
+#' @param tables_df
+#' @return
+#' @author Taren Sanders
+#' @export
+make_table_rob_latex <- function(tables_df) {
+  base_table <-
+    tables_df %>%
+    filter(table == "main") %>%
+    select(
+      first_author, year,
+      eligibility_criteria_predefined_and_specified:heterogeneity_assessed
+    ) %>%
+    distinct() %>%
+    mutate_at(
+      vars(
+        "eligibility_criteria_predefined_and_specified":"heterogeneity_assessed"
+      ),
+      ~ case_match(
+        .x,
+        "low" ~ "L",
+        "unclear" ~ "U",
+        "high" ~ "H"
+      )
+    ) %>%
+    arrange(str_to_lower(first_author), year) %>%
+    rename(
+      "First Author" = first_author,
+      "Year" = year,
+      "Elig. Crit." = eligibility_criteria_predefined_and_specified,
+      "Lit. Search" = literature_search_strategy_comprehensive_and_systematic,
+      "Dual Screen" = dual_independent_screening_review,
+      "Dual Qual." = dual_independent_quality_assessment,
+      "Studies Listed" = included_studies_listed_with_important_characteristics_and_results_of_each, # nolint
+      "Pub. Bias" = publication_bias_assessed,
+      "Hetero." = heterogeneity_assessed,
+    )
+
+  latex_table <-
+    knitr::kable(base_table,
+      format = "latex", booktabs = TRUE, longtable = TRUE, escape = FALSE,
+      col.names = c(
+        "First Author", "Year",
+        paste0("Elig. Crit.", footnote_marker_number(1, "latex")),
+        paste0("Lit. Search", footnote_marker_number(2, "latex")),
+        paste0("Dual Screen", footnote_marker_number(3, "latex")),
+        paste0("Dual Qual.", footnote_marker_number(4, "latex")),
[…]

### 2023-08-03 _targets.R

@@ -98,7 +98,11 @@ list(
   ),
   tar_target(
     table_rob_gt,
-    make_table_rob(tables_df)
+    make_table_rob_gt(tables_df)
+  ),
+  tar_target(
+    table_rob_latex,
+    make_table_rob_latex(tables_df)
   ),
   tar_target(
     table_desc_saved,

### 2023-08-14 reports/manuscript.Rmd
Add editor changes to manuscript file

@@
   Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in `r targets::tar_read(manuscript_info)$abstract$rob` included meta-analyses and high heterogeneity (`r manuscript_info$edu$n_i2`/`r manuscript_info$edu$n_certain` in education and `r manuscript_info$health$n_i2`/`r manuscript_info$health$n_certain` in health with $I^2 > 50\%$).
-  We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
+  We recommend that caregivers and policymakers carefully weigh the evidence for potential harms and benefits of specific types of screen use.
 
@@
 
-While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom&trade;) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
+While some forms of screen use (e.g., excessive television viewing) may be detrimental to health and wellbeing [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom&trade;) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children].
 Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is "a defining question of our age" [@naturehumanbehaviourScreenTimeHow2019].
@@
 
-Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
+Citing the negative associations between screen use and health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation [@whoGuidelinesPhysicalActivity2019] and numerous government agencies [@australiangovernmentPhysicalActivityExercise2021;@Canadian24HourMovement2016] and statements by expert groups [@AAPMediaUseSchoolAged2016] have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
 For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
@@
 We deliberately did not pre-specify outcomes, in order to get a list of areas where there is meta-analytical evidence.
-Adopting this broad approach allowed us to provide a holistic perspective on the influence of screens on children's lives.
+Adopting this broad approach allowed us to provide a holistic perspective on the associations between screen time and different aspects of children's lives.
 By synthesising across life domains (e.g., school and home), this review provides evidence to inform guidelines and advice for parents, teachers, pediatricians and other professionals in order to maximise human functioning.
@@
 
-The primary goal of this review was to provide a holistic perspective on the influence of screens on children’s lives across a broad range of outcomes.
+The primary goal of this review was to provide a holistic perspective on the association between screen use and a broad range of health- and education-related aspects of children’s lives.
 We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
@@
 
-Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
+Social media was one type of exposure that showed consistent---albeit small---associations with poor health, with no indication of potential benefit.
 Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse [@vannucciSocialMediaUse2020].
@@
 Our findings showed that screen use is associated with both positive (e.g., educational video games were associated with improved literacy) and negative (e.g., general screen use was associated with poorer body composition) outcomes.
-Based on our findings, we recommend that parents, teachers, and other caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
+Based on our findings, we recommend that parents, teachers, and other caregivers need to carefully weigh the evidence for pros and cons of each specific activity for potential harms and benefits.
 However, our findings also lead us to suggest that in order to aid caregivers to make this judgement, researchers need to conduct more careful and nuanced measurement and analysis of screen use, with less emphasis on measures that aggregate screen use and instead focus on the content, context, and environment in which the exposure occurs.

### 2023-08-14 reports/manuscript.tex
Additional minor editorial changes (#36)
* Add editor changes to manuscript file

* Move included studies into manuscript

* Renumber supp files

* Rerun pipeline

@@
 {}{\PatchFailed}
-\keywords{\newline\indent Word count: 5300}
+\keywords{\newline\indent Word count: 5312}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\)).
-We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
+We recommend that caregivers and policymakers carefully weigh the evidence for potential harms and benefits of specific types of screen use.
 }
@@
 
-While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing,\textsuperscript{7,8} evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom™) remains less certain and, in some cases, may even be beneficial.\textsuperscript{9,10}
+While some forms of screen use (e.g., excessive television viewing) may be detrimental to health and wellbeing,\textsuperscript{7,8} evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom™) remains less certain and, in some cases, may even be beneficial.\textsuperscript{9,10}
 Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is ``a defining question of our age''.\textsuperscript{11}
@@
 
-Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation\textsuperscript{12} and numerous government agencies\textsuperscript{13,14} and statements by expert groups\textsuperscript{15} have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
+Citing the negative associations between screen use and health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation\textsuperscript{12} and numerous government agencies\textsuperscript{13,14} and statements by expert groups\textsuperscript{15} have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
 For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
@@
 
-The primary goal of this review was to provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes.
+The primary goal of this review was to provide a holistic perspective on the association between screen use and a broad range of health- and education-related aspects of children's lives.
 We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
@@
 
-Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
+Social media was one type of exposure that showed consistent---albeit small---associations with poor health, with no indication of potential benefit.
 Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.\textsuperscript{31}
@@
 58. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
+
+\leavevmode\hypertarget{ref-oztopDoesDigitalGeneration2021}{}%
+59.
+Öztop, F.
+\& Nayci, Ö.
+Does the Digital Generation Comprehend Better from the Screen or from the Paper?: A Meta-Analysis.
+\emph{International Online Journal of Education and Teaching} \textbf{8}, 1206--1224 (2021).
+
+\leavevmode\hypertarget{ref-abramiEffectsABRACADABRAReading2015}{}%
+60.
+Abrami, P., Borohkovski, E.
+\& Lysenko, L.
+The effects of ABRACADABRA on reading outcomes: A meta-analysis of applied field research.
+\emph{Journal of Interactive Learning Research} \textbf{26}, 337--367 (2015).
+
+\leavevmode\hypertarget{ref-abramiEffectsABRACADABRAReading2020}{}%
+61.
+Abrami, P.
+C., Lysenko, L.
+\& Borokhovski, E.
+The effects of ABRACADABRA on reading outcomes: An updated meta-analysis and landscape review of applied field research.
+\emph{Journal of Computer Assisted Learning} \textbf{36}, 260--279 (2020).
+
+\leavevmode\hypertarget{ref-aghasiInternetUseRelation2019}{}%
+62.
+Aghasi, M., Matinfar, A., Golzarand, M., Salari-Moghaddam, A.
+\& Ebrahimpour-Koujan, S.
+Internet Use in Relation to Overweight and Obesity: A Systematic Review and Meta-Analysis of Cross-Sectional Studies.
+\emph{Advances in Nutrition} \textbf{11}, 349--356 (2019).
+
+\leavevmode\hypertarget{ref-alimoradiInternetAddictionSleep2019}{}%
+63. Alimoradi, Z. \emph{et al.} Internet addiction and sleep problems: A systematic review and meta-analysis. \emph{Sleep Medicine Reviews} \textbf{47}, 51--61 (2019).
+
+\leavevmode\hypertarget{ref-ameryounImpactGameBasedHealth2018}{}%
+64.
+Ameryoun, A., Sanaeinasab, H., Saffari, M.
+\& Koenig, H.
+G.
+Impact of Game-Based Health Promotion Programs on Body Mass Index in Overweight/Obese Children and Adolescents: A Systematic Review and Meta-Analysis of Randomized Controlled Trials.
+\emph{Childhood Obesity} \textbf{14}, 67--80 (2018).
+
+\leavevmode\hypertarget{ref-andersonViolentVideoGame2010}{}%
+65.
+Anderson, C.
+A.
+\emph{et al.} Violent video game effects on aggression, empathy, and prosocial behavior in Eastern and Western countries: A meta-analytic review.
+\emph{Psychological Bulletin} \textbf{136}, 151--173 (2010).
+
+\leavevmode\hypertarget{ref-andradePsychologicalEffectsExergames2019}{}%
+66.
+Andrade, A., Correia, C.
+K.
+\& Coimbra, D.
+R.
+The Psychological Effects of Exergames for Children and Adolescents with Obesity: A Systematic Review and Meta-Analysis.
+\emph{Cyberpsychology, Behavior, and Social Networking} \textbf{22}, 724--735 (2019).
+
+\leavevmode\hypertarget{ref-arztmannEffectsGamesSTEM2022}{}%
+67.
+Arztmann, M., Hornstra, L., Jeuring, J.
+\& Kester, L.
+Effects of games in STEM education: A meta-analysis on the moderating role of student background characteristics.
+\emph{Studies in Science Education} \textbf{59}, 109--145 (2022).
+
+\leavevmode\hypertarget{ref-aspirantiIPadsTabletsStudents2020}{}%
+68. Aspiranti, K. B., Larwin, K. H. \& Schade, B. P. iPads/tablets and students with autism: A meta-analysis of academic effects. \emph{Assistive Technology} \textbf{32}, 23--30 (2020).
+
+\leavevmode\hypertarget{ref-baradaranmahdaviAssociationSedentaryBehavior2021}{}%
+69.
+Baradaran Mahdavi, S., Riahi, R., Vahdatpour, B.
+\& Kelishadi, R.
+Association between sedentary behavior and low back pain; A systematic review and meta-analysis.
+\emph{Health Promotion Perspectives} \textbf{11}, 393--410 (2021).
+
+\leavevmode\hypertarget{ref-barnettActiveVideoGames2011}{}%
+70. Barnett, A., Cerin, E. \& Baranowski, T. Active Video Games for Youth: A Systematic Review. \emph{Journal of Physical Activity and Health} \textbf{8}, 724--737 (2011).
+
+\leavevmode\hypertarget{ref-bartelProtectiveRiskFactors2015}{}%
+71. Bartel, K. A., Gradisar, M. \& Williamson, P. Protective and risk factors for adolescent sleep: A meta-analytic review. \emph{Sleep Medicine Reviews} \textbf{21}, 72--85 (2015).
+
+\leavevmode\hypertarget{ref-becksilvaEffectsComputerbasedInterventions2022}{}%
+72.
+Beck Silva, K.
+B., Miranda Pereira, E., Santana, M.
+L.
+P.
+de, Costa, P.
+R.
+F.
+\& Silva, R.
+de C.
+R.
+Effects of computer-based interventions on food consumption and anthropometric parameters of adolescents: A systematic review and metanalysis.
+\emph{Critical Reviews in Food Science and Nutrition} 1--13 (2022) doi:\href{https://doi.org/10.1080/10408398.2022.2118227}{10.1080/10408398.2022.2118227}.
+
+\leavevmode\hypertarget{ref-benavides-varelaEffectivenessDigitalbasedInterventions2020}{}%
+73.
+Benavides-Varela, S.
+\emph{et al.} Effectiveness of digital-based interventions for children with mathematical learning difficulties: A meta-analysis.
+\emph{Computers \& Education} \textbf{157}, 103953 (2020).
+
+\leavevmode\hypertarget{ref-beneriaOnlineInterventionsCannabis2021}{}%
+74.
+Beneria, A.
+\emph{et al.} Online interventions for cannabis use among adolescents and young adults: Systematic review and meta-analysis.
+\emph{Early Intervention in Psychiatry} \textbf{16}, 821--844 (2022).
+
+\leavevmode\hypertarget{ref-blokComputerassistedInstructionSupport2002}{}%
+75.
+Blok, H., Oostdam, R., Otter, M.
+E.
+\& Overmaat, M.
+Computer-assisted instruction in support of beginning reading instruction: A review.
+\emph{Review of Educational Research} \textbf{72}, 101--130 (2002).
+
+\leavevmode\hypertarget{ref-bochnerImpactActiveVideo2015}{}%
+76. Bochner, R. E., Sorensen, K. M. \& Belamarich, P. F. The Impact of Active Video Gaming on Weight in Youth: A Meta-Analysis. \emph{Clinical Pediatrics} \textbf{54}, 620--628 (2015).
+
+\leavevmode\hypertarget{ref-bossenEffectivenessSeriousGames2020}{}%
+77.
+Bossen, D.
+\emph{et al.} Effectiveness of Serious Games to Increase Physical Activity in Children With a Chronic Disease: Systematic Review With Meta-Analysis.
+\emph{Journal of Medical Internet Research} \textbf{22}, e14549 (2020).
+
+\leavevmode\hypertarget{ref-boylandAdvertisingCueConsume2016}{}%
+78.
+Boyland, E.
+J.
+\emph{et al.} Advertising as a cue to consume: A systematic review and meta-analysis of the effects of acute exposure to unhealthy food and nonalcoholic beverage advertising on intake in children and adults.
+\emph{American Journal of Clinical Nutrition} \textbf{103}, 519--533 (2016).
+
+\leavevmode\hypertarget{ref-boylandAssociationFoodNonalcoholic2022}{}%
+79.
+Boyland, E.
+\emph{et al.} Association of Food and Nonalcoholic Beverage Marketing With Children and Adolescents' Eating Behaviors and Health: A Systematic Review and Meta-analysis.
+\emph{JAMA Pediatrics} \textbf{176}, e221037 (2022).
+
+\leavevmode\hypertarget{ref-burkhardtMetaAnalysisLongitudinalAgeDependent2022}{}%
+80. Burkhardt, J. \& Lenhard, W. A Meta-Analysis on the Longitudinal, Age-Dependent Effects of Violent Video Games on Aggression. \emph{Media Psychology} \textbf{25}, 499--512 (2022).
+
+\leavevmode\hypertarget{ref-caiAugmentedRealityTechnology2022}{}%
+81. Cai, Y., Pan, Z. \& Liu, M. Augmented reality technology in language learning: A meta-analysis. \emph{Journal of Computer Assisted Learning} \textbf{38}, 929--945 (2022).
+
+\leavevmode\hypertarget{ref-caoEffectsModeratorsComputerBased2020}{}%
+82.
+Cao, Y., Huang, T., Huang, J., Xie, X.
+\& Wang, Y.
+Effects and Moderators of Computer-Based Training on Children's Executive Functions: A Systematic Review and Meta-Analysis.
+\emph{Frontiers in Psychology} \textbf{11}, 580329 (2020).
+
+\leavevmode\hypertarget{ref-caoRiskAccidentsChronic2022}{}%
+83.
+Cao, X.
+\emph{et al.} Risk of Accidents or Chronic Disorders From Improper Use of Mobile Phones: A Systematic Review and Meta-analysis.
+\emph{Journal of Medical Internet Research} \textbf{24}, e21313 (2022).
+
+\leavevmode\hypertarget{ref-casaleMetaanalysisAssociationSelfesteem2022}{}%
+84. Casale, S. \emph{et al.} A meta-analysis on the association between self-esteem and problematic smartphone use. \emph{Computers in Human Behavior} \textbf{134}, 107302 (2022).
+
+\leavevmode\hypertarget{ref-championEffectivenessSchoolbasedEHealth2019}{}%
+85.
+Champion, K.
+E.
+\emph{et al.} Effectiveness of school-based eHealth interventions to prevent multiple lifestyle risk behaviours among adolescents: A systematic review and meta-analysis.
+\emph{The Lancet Digital Health} \textbf{1}, e206--e221 (2019).
+
+\leavevmode\hypertarget{ref-chanDynamicGeometrySoftware2014}{}%
+86.
+Chan, K.
+K.
+\& Leung, S.
+W.
+Dynamic Geometry Software Improves Mathematical Achievement: Systematic Review and Meta-Analysis.
+\emph{Journal of Educational Computing Research} \textbf{51}, 311--325 (2014).
+
+\leavevmode\hypertarget{ref-chanImpactESportsOnline2022}{}%
+87. Chan, G. \emph{et al.} The impact of eSports and online video gaming on lifestyle behaviours in youth: A systematic review. \emph{Computers in Human Behavior} \textbf{126}, 106974 (2022).
+
+\leavevmode\hypertarget{ref-chenMetaanalysisFactorsPredicting2017}{}%
+88.
+Chen, L., Ho, S.
+S.
+\& Lwin, M.
+O.
+A meta-analysis of factors predicting cyberbullying perpetration and victimization: From the social cognitive and media effects approach.
+\emph{New Media \& Society} \textbf{19}, 1194--1213 (2017).
+
+\leavevmode\hypertarget{ref-chenEffectsCompetitionDigital2020}{}%
+89.
+Chen, C.-H., Shih, C.-C.
+\& Law, V.
+The Effects of Competition in Digital Game-Based Learning (DGBL): A Meta-Analysis.
+\emph{Educational Technology Research and Development} \textbf{68}, 1855--1873 (2020).
+
+\leavevmode\hypertarget{ref-cheungHowFeaturesEducational2012}{}%
+90.
+Cheung, A.
+C.
+K.
+\& Slavin, R.
+E.
+How features of educational technology applications affect student reading outcomes: A meta-analysis.
+\emph{Educational Research Review} \textbf{7}, 198--215 (2012).
+
+\leavevmode\hypertarget{ref-cheungEffectivenessEducationalTechnology2013}{}%
+91.
+Cheung, A.
+C.
+K.
+\& Slavin, R.
+E.
+The effectiveness of educational technology applications for enhancing mathematics achievement in K-12 classrooms: A meta-analysis.
+\emph{Educational Research Review} \textbf{9}, 88--113 (2013).
+
+\leavevmode\hypertarget{ref-cheungEffectsEducationalTechnology2013}{}%
+92.
+Cheung, A.
+C.
+K.
+\& Slavin, R.
+E.
+Effects of Educational Technology Applications on Reading Outcomes for Struggling Readers: A Best-Evidence Synthesis.
+\emph{Reading Research Quarterly} \textbf{48}, 277--299 (2013).
+
+\leavevmode\hypertarget{ref-choEffectsUsingMobile2018}{}%
+93. Cho, K., Lee, S., Joo, M.-H. \& Becker, B. The Effects of Using Mobile Devices on Student Achievement in Language Learning: A Meta-Analysis. \emph{Education Sciences} \textbf{8}, 105 (2018).
+
+\leavevmode\hypertarget{ref-choduraInterventionsChildrenMathematical2015}{}%
+94. Chodura, S., Kuhn, J.-T. \& Holling, H. Interventions for Children With Mathematical Difficulties: A Meta-Analysis. \emph{Zeitschrift für Psychologie} \textbf{223}, 129--144 (2015).
+
+\leavevmode\hypertarget{ref-claussenAllFamilySystematic2022}{}%
+95.
+Claussen, A.
+H.
+\emph{et al.} All in the Family?
+A Systematic Review and Meta-analysis of Parenting and Family Environment as Risk Factors for Attention-Deficit/Hyperactivity Disorder (ADHD) in Children.
+\emph{Prevention Science} (2022) doi:\href{https://doi.org/10.1007/s11121-022-01358-4}{10.1007/s11121-022-01358-4}.
+
+\leavevmode\hypertarget{ref-clintonReadingPaperCompared2019}{}%
+96. Clinton, V. Reading from paper compared to screens: A systematic review and meta-analysis. \emph{Journal of Research in Reading} \textbf{42}, 288--325 (2019).
+
+\leavevmode\hypertarget{ref-comeras-chuecaEffectsActiveVideo2021}{}%
+97.
+Comeras-Chueca, C.
+\emph{et al.} The Effects of Active Video Games on Health-Related Physical Fitness and Motor Competence in Children and Adolescents with Healthy Weight: A Systematic Review and Meta-Analysis.
+\emph{International Journal of Environmental Research and Public Health} \textbf{18}, 6965 (2021).
+
+\leavevmode\hypertarget{ref-comeras-chuecaEffectsActiveVideo2021a}{}%
+98.
+Comeras-Chueca, C.
+\emph{et al.} Effects of Active Video Games on Health-Related Physical Fitness and Motor Competence in Children and Adolescents With Overweight or Obesity: Systematic Review and Meta-Analysis.
+\emph{JMIR Serious Games} \textbf{9}, e29981 (2021).
+
+\leavevmode\hypertarget{ref-coxAssociationTelevisionViewing2012}{}%
+99.
+Cox, R., Skouteris, H., Rutherford, L.
+\& Fuller-Tyszkiewicz, M.
+The Association between Television Viewing and Preschool Child Body Mass Index: A systematic review of English papers published from 1995 to 2010.
+\emph{Journal of Children and Media} \textbf{6}, 198--220 (2012).
+
+\leavevmode\hypertarget{ref-coyneMetaanalysisProsocialMedia2018}{}%
+100.
+Coyne, S.
+M.
+\emph{et al.} A meta-analysis of prosocial media on prosocial behavior, aggression, and empathic concern: A multidimensional approach.
+\emph{Developmental Psychology} \textbf{54}, 331--347 (2018).
+
+\leavevmode\hypertarget{ref-cunninghamSocialMediaDepression2021}{}%
+101. Cunningham, S., Hudson, C. C. \& Harkness, K. Social Media and Depression Symptoms: A Meta-Analysis. \emph{Research on Child and Adolescent Psychopathology} \textbf{49}, 241--253 (2021).
+
+\leavevmode\hypertarget{ref-cushingMetaAnalyticReviewEHealth2010}{}%
+102.
+Cushing, C.
+C.
+\& Steele, R.
+G.
+A Meta-Analytic Review of eHealth Interventions for Pediatric Health Promoting and Maintaining Behaviors.
+\emph{Journal of Pediatric Psychology} \textbf{35}, 937--949 (2010).
+
+\leavevmode\hypertarget{ref-darlingSystematicReviewMetaAnalysis2017}{}%
+103.
+Darling, K.
+E.
+\& Sato, A.
+F.
+Systematic Review and Meta-Analysis Examining the Effectiveness of Mobile Health Technologies in Using Self-Monitoring for Pediatric Weight Management.
+\emph{Childhood Obesity} \textbf{13}, 347--355 (2017).
+
+\leavevmode\hypertarget{ref-daveyAssessmentSmartphoneAddiction2014}{}%
+104.
+Davey, S.
+\& Davey, A.
+Assessment of Smartphone Addiction in Indian Adolescents: A Mixed Method Study by Systematic-review and Meta-analysis Approach.
+\emph{International Journal of Preventive Medicine} \textbf{5}, 1500--1511 (2014).
+
+\leavevmode\hypertarget{ref-davidHowEffectiveAre2020}{}%
+105.
+David, O.
+A., Costescu, C., Cardos, R.
+\& Mogoaşe, C.
+How Effective are Serious Games for Promoting Mental Health and Health Behavioral Change in Children and Adolescents?
+A Systematic Review and Meta-analysis.
+\emph{Child \& Youth Care Forum} \textbf{49}, 817--838 (2020).
+
+\leavevmode\hypertarget{ref-oliveiraPhysicalActivitySedentary2016}{}%
+106.
+Oliveira, R.
+G.
+de \& Guedes, D.
+P.
+Physical Activity, Sedentary Behavior, Cardiorespiratory Fitness and Metabolic Syndrome in Adolescents: Systematic Review and Meta-Analysis of Observational Evidence.
+\emph{PLOS ONE} \textbf{11}, e0168503 (2016).
+
+\leavevmode\hypertarget{ref-deriberaCorrelatesYouthViolence2019}{}%
+107.
+de Ribera, O.
+S., Trajtenberg, N., Shenderovich, Y.
+\& Murray, J.
+Correlates of youth violence in low- and middle-income countries: A meta-analysis.
+\emph{Aggression and Violent Behavior} \textbf{49}, 101306 (2019).
+
+\leavevmode\hypertarget{ref-diMetaanalysisImpactVirtual2022}{}%
+108. Di, X. \& Zheng, X. A meta-analysis of the impact of virtual technologies on students' spatial ability. \emph{Educational technology research and development} \textbf{70}, 73--98 (2022).
+
+\leavevmode\hypertarget{ref-eirichAssociationScreenTime2022}{}%
+109.
+Eirich, R.
+\emph{et al.} Association of Screen Time With Internalizing and Externalizing Behavior Problems in Children 12 Years or Younger: A Systematic Review and Meta-analysis.
+\emph{JAMA Psychiatry} \textbf{79}, 393 (2022).
+
+\leavevmode\hypertarget{ref-ercelikEffectivenessActiveVideo2022}{}%
+110.
+Erçelik, Z.
+E.
+\& Çağlar, S.
+Effectiveness of active video games in overweight and obese adolescents: A systematic review and meta-analysis of randomized controlled trials.
+\emph{Annals of Pediatric Endocrinology \& Metabolism} \textbf{27}, 98--104 (2022).
+
+\leavevmode\hypertarget{ref-fangScreenTimeChildhood2019}{}%
+111. Fang, K., Mu, M., Liu, K. \& He, Y. Screen time and childhood overweight/obesity: A systematic review and meta-analysis. \emph{Child: Care, Health and Development} \textbf{45}, 744--753 (2019).
+
+\leavevmode\hypertarget{ref-fedeleMobileHealthInterventions2017}{}%
+112.
+Fedele, D.
+A., Cushing, C.
+C., Fritz, A., Amaro, C.
+M.
+\& Ortega, A.
+Mobile Health Interventions for Improving Health Outcomes in Youth: A Meta-analysis.
+\emph{JAMA Pediatrics} \textbf{171}, 461 (2017).
+
+\leavevmode\hypertarget{ref-fengAssociationsMeeting24hour2021}{}%
+113.
+Feng, J., Zheng, C., Sit, C.
+H.-P., Reilly, J.
+J.
+\& Huang, W.
+Y.
+Associations between meeting 24-hour movement guidelines and health in the early years: A systematic review and meta-analysis.
+\emph{Journal of Sports Sciences} \textbf{39}, 2545--2557 (2021).
+
+\leavevmode\hypertarget{ref-fergusonPublicHealthRisks2009}{}%
+114. Ferguson, C. J. \& Kilburn, J. The Public Health Risks of Media Violence: A Meta-Analytic Review. \emph{The Journal of Pediatrics} \textbf{154}, 759--763 (2009).
+
+\leavevmode\hypertarget{ref-fergusonAngryBirdsMake2015}{}%
+115.
+Ferguson, C.
+J.
+Do Angry Birds Make for Angry Children?
+A Meta-Analysis of Video Game Influences on Children's and Adolescents' Aggression, Mental Health, Prosocial Behavior, and Academic Performance.
+\emph{Perspectives on Psychological Science} \textbf{10}, 646--666 (2015).
+
+\leavevmode\hypertarget{ref-fergusonDoesSexyMedia2017}{}%
+116. Ferguson, C. J., Nielsen, R. K. L. \& Markey, P. M. Does Sexy Media Promote Teen Sex? A Meta-Analytic and Methodological Review. \emph{Psychiatric Quarterly} \textbf{88}, 349--358 (2017).
+
+\leavevmode\hypertarget{ref-ferguson13ReasonsWhy2019}{}%
+117.
+Ferguson, C.
+J.
+13 Reasons Why Not: A Methodological and Meta-Analytic Review of Evidence Regarding Suicide Contagion by Fictional Media.
+\emph{Suicide and Life-Threatening Behavior} \textbf{49}, 1178--1186 (2019).
+
+\leavevmode\hypertarget{ref-fergusonReexaminingFindingsAmerican2020}{}%
+118.
+Ferguson, C.
+J., Copenhaver, A.
+\& Markey, P.
+Reexamining the Findings of the American Psychological Association's 2015 Task Force on Violent Media: A Meta-Analysis.
+\emph{Perspectives on Psychological Science} \textbf{15}, 1423--1443 (2020).
+
+\leavevmode\hypertarget{ref-fergusonThisMetaanalysisScreen2022}{}%
+119. Ferguson, C. J. \emph{et al.} Like this meta-analysis: Screen media and mental health. \emph{Professional Psychology: Research and Practice} \textbf{53}, 205--214 (2022).
+
+\leavevmode\hypertarget{ref-fischerEffectsRiskglorifyingMedia2011}{}%
+120.
+Fischer, P., Greitemeyer, T., Kastenmüller, A., Vogrincic, C.
+\& Sauer, A.
+The effects of risk-glorifying media exposure on risk-positive cognitions, emotions, and behaviors: A meta-analytic review.
+\emph{Psychological Bulletin} \textbf{137}, 367--390 (2011).
+
+\leavevmode\hypertarget{ref-folkvordPersuasiveEffectAdvergames2018}{}%
+121. Folkvord, F. \& van `t Riet, J. The persuasive effect of advergames promoting unhealthy foods among children: A meta-analysis. \emph{Appetite} \textbf{129}, 245--251 (2018).
+
+\leavevmode\hypertarget{ref-foremanAssociationDigitalSmart2021}{}%
+122. Foreman, J. \emph{et al.} Association between digital smart device use and myopia: A systematic review and meta-analysis. \emph{The Lancet Digital Health} \textbf{3}, e806--e818 (2021).
+
+\leavevmode\hypertarget{ref-fowlerHarnessingTechnologicalSolutions2021}{}%
+123.
+Fowler, L.
+A.
+\emph{et al.} Harnessing technological solutions for childhood obesity prevention and treatment: A systematic review and meta-analysis of current applications.
+\emph{International Journal of Obesity} \textbf{45}, 957--981 (2021).
+
+\leavevmode\hypertarget{ref-furenesComparisonChildrenReading2021}{}%
+124. Furenes, M. I., Kucirkova, N. \& Bus, A. G. A Comparison of Children's Reading on Paper versus Screen: A Meta-Analysis. \emph{Review of Educational Research} \textbf{91}, 483--517 (2021).
+
+\leavevmode\hypertarget{ref-gaoMetaanalysisActiveVideo2015}{}%
+125.
+Gao, Z., Chen, S., Pasco, D.
+\& Pope, Z.
+A meta-analysis of active video games on health outcomes among children and adolescents: A meta-analysis of active video games.
+\emph{Obesity Reviews} \textbf{16}, 783--794 (2015).
+
+\leavevmode\hypertarget{ref-gardellaSystematicReviewMetaAnalysis2017}{}%
+126.
+Gardella, J.
+H., Fisher, B.
+W.
+\& Teurbe-Tolon, A.
+R.
+A Systematic Review and Meta-Analysis of Cyber-Victimization and Educational Outcomes for Adolescents.
+\emph{Review of Educational Research} \textbf{87}, 283--308 (2017).
+
+\leavevmode\hypertarget{ref-garzonSystematicReviewMetaanalysis2019}{}%
+127. Garzón, J., Pavón, J. \& Baldiris, S. Systematic review and meta-analysis of augmented reality in educational settings. \emph{Virtual Reality} \textbf{23}, 447--459 (2019).
+
+\leavevmode\hypertarget{ref-garzonMetaanalysisImpactAugmented2019}{}%
+128. Garzón, J. \& Acevedo, J. Meta-analysis of the impact of Augmented Reality on students' learning gains. \emph{Educational Research Review} \textbf{27}, 244--260 (2019).
+
+\leavevmode\hypertarget{ref-ghobadiAssociationEatingTelevision2018}{}%
+129.
+Ghobadi, S.
+\emph{et al.} Association of eating while television viewing and overweight/obesity among children and adolescents: A systematic review and meta-analysis of observational studies: Television viewing, overweight, obesity, children.
+\emph{Obesity Reviews} \textbf{19}, 313--320 (2018).
+
+\leavevmode\hypertarget{ref-grabeRoleMediaBody2008}{}%
+130.
+Grabe, S., Ward, L.
+M.
+\& Hyde, J.
+S.
+The role of the media in body image concerns among women: A meta-analysis of experimental and correlational studies.
+\emph{Psychological Bulletin} \textbf{134}, 460--476 (2008).
+
+\leavevmode\hypertarget{ref-grahamFormativeAssessmentWriting2015}{}%
+131. Graham, S., Hebert, M. \& Harris, K. R. Formative Assessment and Writing: A Meta-Analysis. \emph{The Elementary School Journal} \textbf{115}, 523--547 (2015).
+
+\leavevmode\hypertarget{ref-haoTechnologyAssistedVocabularyLearning2021}{}%
+132. Hao, T., Wang, Z. \& Ardasheva, Y. Technology-Assisted Vocabulary Learning for EFL Learners: A Meta-Analysis. \emph{Journal of Research on Educational Effectiveness} \textbf{14}, 645--667 (2021).
+
+\leavevmode\hypertarget{ref-mahdiEffectivenessComputerAssisted2019}{}%
+133. Mahdi, H. S. \& Al Khateeb, A. A. The effectiveness of computer-assisted pronunciation training: A meta-analysis. \emph{Review of Education} \textbf{7}, 733--753 (2019).
+
+\leavevmode\hypertarget{ref-heEffectsSmartphoneBasedInterventions2021}{}%
+134.
+He, Z.
+\emph{et al.} Effects of Smartphone-Based Interventions on Physical Activity in Children and Adolescents: Systematic Review and Meta-analysis.
+\emph{JMIR mHealth and uHealth} \textbf{9}, e22601 (2021).
+
+\leavevmode\hypertarget{ref-hernandez-jimenezImpactActiveVideo2019}{}%
+135.
+Hernández-Jiménez, C.
+\emph{et al.} Impact of Active Video Games on Body Mass Index in Children and Adolescents: Systematic Review and Meta-Analysis Evaluating the Quality of Primary Studies.
+\emph{International Journal of Environmental Research and Public Health} \textbf{16}, 2424 (2019).
+
+\leavevmode\hypertarget{ref-hoActiveVideoGame2022}{}%
+136.
+Ho, R.
+S.-T., Chan, E.
+K.-Y., Liu, K.
+K.-Y.
+\& Wong, S.
+H.-S.
+Active video game on children and adolescents' physical activity and weight management: A network meta-analysis.
+\emph{Scandinavian Journal of Medicine \& Science in Sports} \textbf{32}, 1268--1286 (2022).
+
+\leavevmode\hypertarget{ref-huangWhenMediaBecome2021}{}%
+137. Huang, Q., Peng, W. \& Ahn, S. When media become the mirror: A meta-analysis on media and body image. \emph{Media Psychology} \textbf{24}, 437--489 (2021).
+
+\leavevmode\hypertarget{ref-hurwitzGettingReadReady2019}{}%
+138. Hurwitz, L. B. Getting a Read on Ready To Learn Media: A Meta-analytic Review of Effects on Literacy. \emph{Child Development} \textbf{90}, 1754--1771 (2019).
+
+\leavevmode\hypertarget{ref-kristensenProblematicGamingSleep2021}{}%
+139.
+Kristensen, J.
+H., Pallesen, S., King, D.
+L., Hysing, M.
+\& Erevik, E.
+K.
+Problematic Gaming and Sleep: A Systematic Review and Meta-Analysis.
+\emph{Frontiers in Psychiatry} \textbf{12}, 675237 (2021).
+
+\leavevmode\hypertarget{ref-ivieMetaanalysisAssociationAdolescent2020}{}%
+140.
+Ivie, E.
+J., Pettitt, A., Moses, L.
+J.
+\& Allen, N.
+B.
+A meta-analysis of the association between adolescent social media use and depressive symptoms.
+\emph{Journal of Affective Disorders} \textbf{275}, 165--174 (2020).
+
+\leavevmode\hypertarget{ref-janssenAssociationsScreenTime2020}{}%
+141.
+Janssen, X.
+\emph{et al.} Associations of screen time, sedentary time and physical activity with sleep in under 5s: A systematic review and meta-analysis.
+\emph{Sleep Medicine Reviews} \textbf{49}, 101226 (2020).
+
+\leavevmode\hypertarget{ref-katesEffectsMobilePhone2018}{}%
+142. Kates, A. W., Wu, H. \& Coryn, C. L. S. The effects of mobile phone use on academic performance: A meta-analysis. \emph{Computers \& Education} \textbf{127}, 107--112 (2018).
+
+\leavevmode\hypertarget{ref-kimMeasuresMatterMetaAnalysis2021}{}%
+143.
+Kim, J., Gilbert, J., Yu, Q.
+\& Gale, C.
+Measures Matter: A Meta-Analysis of the Effects of Educational Apps on Preschool to Grade 3 Children's Literacy and Math Skills.
+\emph{AERA Open} \textbf{7}, 233285842110041 (2021).
+
+\leavevmode\hypertarget{ref-kongComparisonReadingPerformance2018}{}%
+144. Kong, Y., Seo, Y. S. \& Zhai, L. Comparison of reading performance on screen and on paper: A meta-analysis. \emph{Computers \& Education} \textbf{123}, 138--149 (2018).
+
+\leavevmode\hypertarget{ref-kroesbergenMathematicsInterventionsChildren2003}{}%
+145. Kroesbergen, E. H. \& Van Luit, J. E. H. Mathematics Interventions for Children with Special Educational Needs: A Meta-Analysis. \emph{Remedial and Special Education} \textbf{24}, 97--114 (2003).
+
+\leavevmode\hypertarget{ref-kucukalkanExaminationEffectsComputerbased2019}{}%
+146.
+Küçükalkan, K., Beyazsaçlı, M.
+\& Öz, A.
+Ş.
+Examination of the effects of computer-based mathematics instruction methods in children with mathematical learning difficulties: A meta-analysis.
+\emph{Behaviour \& Information Technology} \textbf{38}, 913--923 (2019).
+
+\leavevmode\hypertarget{ref-lambMetaanalysisExaminationModerators2018}{}%
+147.
+Lamb, R.
+L., Annetta, L., Firestone, J.
+\& Etopio, E.
+A meta-analysis with examination of moderators of student cognition, affect, and learning outcomes while using serious educational games, serious games, and simulations.
+\emph{Computers in Human Behavior} \textbf{80}, 158--167 (2018).
+
+\leavevmode\hypertarget{ref-lancaAssociationDigitalScreen2020}{}%
+148. Lanca, C. \& Saw, S.-M. The association between digital screen time and myopia: A systematic review. \emph{Ophthalmic and Physiological Optics} \textbf{40}, 216--229 (2020).
+
+\leavevmode\hypertarget{ref-larwinMeasuringAcademicOutcomes2019}{}%
+149.
+Larwin, K.
+H.
+\& Aspiranti, K.
+B.
+Measuring the Academic Outcomes of iPads for Students with Autism: A Meta-Analysis.
+\emph{Review Journal of Autism and Developmental Disorders} \textbf{6}, 233--241 (2019).
+
+\leavevmode\hypertarget{ref-leeSystematicReviewMetaanalysis2016}{}%
+150.
+Lee, J., Piao, M., Byun, A.
+\& Kim, J.
+A systematic review and meta-analysis of intervention for pediatric obesity using mobile technology.
+\emph{Nursing Informatics 2016} \textbf{225}, 491--494 (2016).
+
+\leavevmode\hypertarget{ref-liMetaanalysisEffectsComputer2010}{}%
+151. Li, Q. \& Ma, X. A Meta-analysis of the Effects of Computer Technology on School Students' Mathematics Learning. \emph{Educational Psychology Review} \textbf{22}, 215--243 (2010).
+
+\leavevmode\hypertarget{ref-liRelationshipsScreenUse2020}{}%
+152.
+Li, C., Cheng, G., Sha, T., Cheng, W.
+\& Yan, Y.
+The Relationships between Screen Use and Health Indicators among Infants, Toddlers, and Preschoolers: A Meta-Analysis and Systematic Review.
+\emph{International Journal of Environmental Research and Public Health} \textbf{17}, 7324 (2020).
+
+\leavevmode\hypertarget{ref-liAreActiveVideo2022}{}%
+153.
+Li, S., Song, Y., Cai, Z.
+\& Zhang, Q.
+Are active video games useful in the development of gross motor skills among non-typically developing children?
+A meta-analysis.
+\emph{BMC Sports Science, Medicine and Rehabilitation} \textbf{14}, 140 (2022).
+
+\leavevmode\hypertarget{ref-liEffectivenessUnpluggedActivities2022}{}%
+154.
+Li, F., Wang, X., He, X., Cheng, L.
+\& Wang, Y.
+The effectiveness of unplugged activities and programming exercises in computational thinking education: A Meta-analysis.
+\emph{Education and Information Technologies} \textbf{27}, 7993--8013 (2022).
+
+\leavevmode\hypertarget{ref-liaoEffectsComputerassistedInstruction1992}{}%
+155. Liao, Y.-K. Effects of Computer-Assisted Instruction on Cognitive Outcomes: A Meta-Analysis. \emph{Journal of Research on Computing in Education} \textbf{24}, 367--80 (1992).
+
+\leavevmode\hypertarget{ref-liaoEffectsComputerApplications2007}{}%
+156.
+Liao, Y.-k.
+C., Chang, H.-w.
+\& Chen, Y.-w.
+Effects of Computer Application on Elementary Schook Student's Achievement: A Meta-Analysis of Students in Taiwan.
+\emph{Computers in the Schools} \textbf{24}, 43--64 (2007).
+
+\leavevmode\hypertarget{ref-liaoWhichTypeSedentary2014}{}%
+157.
+Liao, Y., Liao, J., Durand, C.
+P.
+\& Dunton, G.
+F.
+Which type of sedentary behaviour intervention is more effective at reducing body mass index in children?
+A meta-analytic review: Sedentary behaviour intervention effects.
+\emph{Obesity Reviews} \textbf{15}, 159--168 (2014).
+
+\leavevmode\hypertarget{ref-liuDoseResponseAssociation2016}{}%
+158.
+Liu, M., Wu, L.
+\& Yao, S.
+DoseResponse association of screen time-based sedentary behaviour in children and adolescents and depression: A meta-analysis of observational studies.
+\emph{British Journal of Sports Medicine} \textbf{50}, 1252--1258 (2016).
+
+\leavevmode\hypertarget{ref-liuSocialNetworkingOnline2016}{}%
+159. Liu, D. \& Baumeister, R. F. Social networking online and personality of self-worth: A meta-analysis. \emph{Journal of Research in Personality} \textbf{64}, 79--89 (2016).
+
+\leavevmode\hypertarget{ref-liuMetaanalysisSocialNetworking2016}{}%
+160. Liu, D., Ainsworth, S. E. \& Baumeister, R. F. A Meta-Analysis of Social Networking Online and Social Capital. \emph{Review of General Psychology} \textbf{20}, 369--391 (2016).
+
+\leavevmode\hypertarget{ref-liuDigitalCommunicationMedia2019}{}%
+161.
+Liu, D., Baumeister, R.
+F., Yang, C.-c.
+\& Hu, B.
+Digital Communication Media Use and Psychological Well-Being: A Meta-Analysis.
+\emph{Journal of Computer-Mediated Communication} \textbf{24}, 259--273 (2019).
+
+\leavevmode\hypertarget{ref-liuMetaanalysisEffectMultimedia2022}{}%
+162.
+Liu, M., Pang, W., Guo, J.
+\& Zhang, Y.
+A Meta-analysis of the Effect of Multimedia Technology on Creative Performance.
+\emph{Education and Information Technologies} \textbf{27}, 8603--8630 (2022).
+
+\leavevmode\hypertarget{ref-liuTimeSpentSocial2022}{}%
+163.
+Liu, M.
+\emph{et al.} Time Spent on Social Media and Risk of Depression in Adolescents: A DoseResponse Meta-Analysis.
+\emph{International Journal of Environmental Research and Public Health} \textbf{19}, 5164 (2022).
+
+\leavevmode\hypertarget{ref-luCorrelationMobilePhone2021}{}%
+164.
+Lu, G.-L.
+\emph{et al.} The correlation between mobile phone addiction and coping style among Chinese adolescents: A meta-analysis.
+\emph{Child and Adolescent Psychiatry and Mental Health} \textbf{15}, 60 (2021).
+
+\leavevmode\hypertarget{ref-lucknerEffectivenessInterventionsPromote2012}{}%
+165.
+Luckner, H., Moss, J.
+R.
+\& Gericke, C.
+A.
+Effectiveness of interventions to promote healthy weight in general populations of children and adults: A meta-analysis.
+\emph{European Journal of Public Health} \textbf{22}, 491--497 (2012).
+
+\leavevmode\hypertarget{ref-luoIncreasedVideoGame2022}{}%
+166.
+Luo, Y.
+\emph{et al.} Is Increased Video Game Participation Associated With Reduced Sense of Loneliness?
+A Systematic Review and Meta-Analysis.
+\emph{Frontiers in Public Health} \textbf{10}, 898338 (2022).
+
+\leavevmode\hypertarget{ref-majorEffectivenessTechnologySupported2021}{}%
+167.
+Major, L., Francis, G.
+A.
+\& Tsapali, M.
+The effectiveness of technology-supported personalised learning in low- and middle-income countries: A meta-analysis.
+\emph{British Journal of Educational Technology} \textbf{52}, 1935--1964 (2021).
+
+\leavevmode\hypertarget{ref-mallawaarachchiAssociationsSmartphoneTablet2022}{}%
+168.
+Mallawaarachchi, S.
+R., Anglim, J., Hooley, M.
+\& Horwood, S.
+Associations of smartphone and tablet use in early childhood with psychosocial, cognitive and sleep factors: A systematic review and meta-analysis.
+\emph{Early Childhood Research Quarterly} \textbf{60}, 13--33 (2022).
+
+\leavevmode\hypertarget{ref-marcianoCyberbullyingPerpetrationVictimization2020}{}%
+169.
+Marciano, L., Schulz, P.
+J.
+\& Camerini, A.-L.
+Cyberbullying Perpetration and Victimization in Youth: A Meta-Analysis of Longitudinal Studies.
+\emph{Journal of Computer-Mediated Communication} \textbf{25}, 163--181 (2020).
+
+\leavevmode\hypertarget{ref-marcianoDigitalMediaUse2021}{}%
+170.
+Marciano, L., Ostroumova, M., Schulz, P.
+J.
+\& Camerini, A.-L.
+Digital Media Use and Adolescents' Mental Health During the Covid-19 Pandemic: A Systematic Review and Meta-Analysis.
+\emph{Frontiers in Public Health} \textbf{9}, 793868 (2022).
+
+\leavevmode\hypertarget{ref-maresPositiveEffectsTelevision2005}{}%
+171. Mares, M.-L. \& Woodard, E. Positive Effects of Television on Children's Social Interactions: A Meta-Analysis. \emph{Media Psychology} \textbf{7}, 301--322 (2005).
+
+\leavevmode\hypertarget{ref-maresEffectsSesameStreet2013}{}%
+172. Mares, M.-L. \& Pan, Z. Effects of Sesame Street: A meta-analysis of children's learning in 15 countries. \emph{Journal of Applied Developmental Psychology} \textbf{34}, 140--151 (2013).
+
+\leavevmode\hypertarget{ref-marinoAssociationsProblematicFacebook2018}{}%
+173.
+Marino, C., Gini, G., Vieno, A.
+\& Spada, M.
+M.
+The associations between problematic Facebook use, psychological distress and well-being among adolescents and young adults: A systematic review and meta-analysis.
+\emph{Journal of Affective Disorders} \textbf{226}, 274--281 (2018).
+
+\leavevmode\hypertarget{ref-marshallRelationshipsMediaUse2004}{}%
+174.
+Marshall, S.
+J., Biddle, S.
+J.
+H., Gorely, T., Cameron, N.
+\& Murdey, I.
+Relationships between media use, body fatness and physical activity in children and youth: A meta-analysis.
+\emph{International Journal of Obesity} \textbf{28}, 1238--1246 (2004).
+
+\leavevmode\hypertarget{ref-martinsRoleMediaExposure2019}{}%
+175. Martins, N. \& Weaver, A. The role of media exposure on relational aggression: A meta-analysis. \emph{Aggression and Violent Behavior} \textbf{47}, 90--99 (2019).
+
+\leavevmode\hypertarget{ref-martinsInfluenceEatingDistractors2022}{}%
+176.
+Martins, N.
+C.
+\emph{et al.} Influence of eating with distractors on caloric intake of children and adolescents: A systematic review and meta-analysis of interventional controlled studies.
+\emph{Critical Reviews in Food Science and Nutrition} 1--10 (2022) doi:\href{https://doi.org/10.1080/10408398.2022.2055525}{10.1080/10408398.2022.2055525}.
+
+\leavevmode\hypertarget{ref-mazeasEvaluatingEffectivenessGamification2022}{}%
+177.
+Mazeas, A., Duclos, M., Pereira, B.
+\& Chalabaev, A.
+Evaluating the Effectiveness of Gamification on Physical Activity: Systematic Review and Meta-analysis of Randomized Controlled Trials.
+\emph{Journal of Medical Internet Research} \textbf{24}, e26779 (2022).
+
+\leavevmode\hypertarget{ref-mcarthurPhonicsTrainingEnglishspeaking2012}{}%
+178.
+McArthur, G.
+\emph{et al.} Phonics training for English-speaking poor readers.
+\emph{Cochrane Database of Systematic Reviews} (2012) doi:\href{https://doi.org/10.1002/14651858.CD009115.pub2}{10.1002/14651858.CD009115.pub2}.
+
+\leavevmode\hypertarget{ref-mcarthurPhonicsTrainingEnglishspeaking2018}{}%
+179. McArthur, G. \emph{et al.} Phonics training for English-speaking poor readers. \emph{Cochrane Database of Systematic Reviews} \textbf{2018}, (2018).
+
+\leavevmode\hypertarget{ref-meiSleepProblemsExcessive2018}{}%
+180. Mei, X. \emph{et al.} Sleep problems in excessive technology use among adolescent: A systemic review and meta-analysis. \emph{Sleep Science and Practice} \textbf{2}, 9 (2018).
+
+\leavevmode\hypertarget{ref-merchantEffectivenessVirtualRealitybased2014}{}%
+181.
+Merchant, Z., Goetz, E.
+T., Cifuentes, L., Keeney-Kennicutt, W.
+\& Davis, T.
+J.
+Effectiveness of virtual reality-based instruction on students' learning outcomes in K-12 and higher education: A meta-analysis.
+\emph{Computers \& Education} \textbf{70}, 29--40 (2014).
+
+\leavevmode\hypertarget{ref-moranTechnologyReadingPerformance2008}{}%
+182.
+Moran, J., Ferdig, R.
+E., Pearson, P.
+D., Wardrop, J.
+\& Blomeyer, R.
+L.
+Technology and Reading Performance in the Middle-School Grades: A Meta-Analysis with Recommendations for Policy and Practice.
+\emph{Journal of Literacy Research} \textbf{40}, 6--58 (2008).
+
+\leavevmode\hypertarget{ref-moriAssociationSextingSexual2019}{}%
+183.
+Mori, C., Temple, J.
+R., Browne, D.
+\& Madigan, S.
+Association of Sexting With Sexual Behaviors and Mental Health Among Adolescents: A Systematic Review and Meta-analysis.
+\emph{JAMA Pediatrics} \textbf{173}, 770 (2019).
+
+\leavevmode\hypertarget{ref-neitzelSynthesisQuantitativeResearch2022}{}%
+184.
+Neitzel, A.
+J., Lake, C., Pellegrini, M.
+\& Slavin, R.
+E.
+A Synthesis of Quantitative Research on Programs for Struggling Readers in Elementary Schools.
+\emph{Reading Research Quarterly} \textbf{57}, 149--179 (2022).
+
+\leavevmode\hypertarget{ref-nesiSocialMediaUse2021}{}%
+185. Nesi, J. \emph{et al.} Social media use and self-injurious thoughts and behaviors: A systematic review and meta-analysis. \emph{Clinical Psychology Review} \textbf{87}, 102038 (2021).
+
+\leavevmode\hypertarget{ref-nikkelenMediaUseADHDrelated2014}{}%
+186.
+Nikkelen, S.
+W.
+C., Valkenburg, P.
+M., Huizinga, M.
+\& Bushman, B.
+J.
+Media use and ADHD-related behaviors in children and adolescents: A meta-analysis.
+\emph{Developmental Psychology} \textbf{50}, 2228--2241 (2014).
+
+\leavevmode\hypertarget{ref-ohDigitalInterventionsUniversal2022}{}%
+187.
+Oh, C., Carducci, B., Vaivada, T.
+\& Bhutta, Z.
+A.
+Digital Interventions for Universal Health Promotion in Children and Adolescents: A Systematic Review.
+\emph{Pediatrics} \textbf{149}, e2021053852H (2022).
+
+\leavevmode\hypertarget{ref-oldratiEffectivenessComputerizedCognitive2020}{}%
+188.
+Oldrati, V.
+\emph{et al.} Effectiveness of Computerized Cognitive Training Programs (CCTP) with Game-like Features in Children with or without Neuropsychological Disorders: A Meta-Analytic Investigation.
+\emph{Neuropsychology Review} \textbf{30}, 126--141 (2020).
+
+\leavevmode\hypertarget{ref-oliveiraEffectsActiveVideo2020}{}%
+189.
+Oliveira, C.
+B.
+\emph{et al.} Effects of active video games on children and adolescents: A systematic review with meta-analysis.
+\emph{Scandinavian Journal of Medicine \& Science in Sports} \textbf{30}, 4--12 (2020).
+
+\leavevmode\hypertarget{ref-ozdemirEffectAugmentedReality2018}{}%
+190.
+Ozdemir, M., Sahin, C., Arcagok, S.
+\& Demir, M.
+K.
+The Effect of Augmented Reality Applications in the Learning Process: A MetaAnalysis Study.
+\emph{Eurasian Journal of Educational Research} \textbf{18}, 1--22 (2018).
+
+\leavevmode\hypertarget{ref-paikEffectsTelevisionViolence1994}{}%
+191. Paik, H. \& Comstock, G. The Effects of Television Violence on Antisocial Behavior: A Meta-Analysis. \emph{Communication Research} \textbf{21}, 516--546 (1994).
+
+\leavevmode\hypertarget{ref-parkEffectivenessInformationCommunication2021}{}%
+192.
+Park, J., Park, M.-J.
+\& Seo, Y.-G.
+Effectiveness of Information and Communication Technology on Obesity in Childhood and Adolescence: Systematic Review and Meta-analysis.
+\emph{Journal of Medical Internet Research} \textbf{23}, e29003 (2021).
+
+\leavevmode\hypertarget{ref-pearceImpactScaryTV2016}{}%
+193. Pearce, L. J. \& Field, A. P. The Impact of `Scary' TV and Film on Children's Internalizing Emotions: A Meta-Analysis. \emph{Human Communication Research} \textbf{42}, 98--121 (2016).
+
+\leavevmode\hypertarget{ref-pengPlayingExergamesReally2011}{}%
+194.
+Peng, W., Lin, J.-H.
+\& Crouse, J.
+Is Playing Exergames Really Exercising?
+A Meta-Analysis of Energy Expenditure in Active Video Games.
+\emph{Cyberpsychology, Behavior, and Social Networking} \textbf{14}, 681--688 (2011).
+
+\leavevmode\hypertarget{ref-powersEffectsVideogamePlay2013}{}%
+195.
+Powers, K.
+L., Brooks, P.
+J., Aldrich, N.
+J., Palladino, M.
+A.
+\& Alfieri, L.
+Effects of video-game play on information processing: A meta-analytic investigation.
+\emph{Psychonomic Bulletin \& Review} \textbf{20}, 1055--1079 (2013).
+
+\leavevmode\hypertarget{ref-prescottMetaanalysisRelationshipViolent2018}{}%
+196.
+Prescott, A.
+T., Sargent, J.
+D.
+\& Hull, J.
+G.
+Metaanalysis of the relationship between violent video game play and physical aggression over time.
+\emph{Proceedings of the National Academy of Sciences} \textbf{115}, 9882--9888 (2018).
+
+\leavevmode\hypertarget{ref-prizant-passalSocialAnxietyInternet2016}{}%
+197.
+Prizant-Passal, S., Shechner, T.
+\& Aderka, I.
+M.
+Social anxiety and internet use A meta-analysis: What do we know?
+What are we missing?
+\emph{Computers in Human Behavior} \textbf{62}, 221--229 (2016).
+
+\leavevmode\hypertarget{ref-reynardDigitalInterventionsEmotion2022}{}%
+198.
+Reynard, S., Dias, J., Mitic, M., Schrank, B.
+\& Woodcock, K.
+A.
+Digital Interventions for Emotion Regulation in Children and Early Adolescents: Systematic Review and Meta-analysis.
+\emph{JMIR Serious Games} \textbf{10}, e31456 (2022).
+
+\leavevmode\hypertarget{ref-rodriguezrochaEHealthInterventionsFruit2019}{}%
+199. Rodriguez Rocha, N. P. \& Kim, H. eHealth Interventions for Fruit and Vegetable Intake: A Meta-Analysis of Effectiveness. \emph{Health Education \& Behavior} \textbf{46}, 947--959 (2019).
+
+\leavevmode\hypertarget{ref-russellEffectScreenAdvertising2019}{}%
+200.
+Russell, S.
+J., Croker, H.
+\& Viner, R.
+M.
+The effect of screen advertising on children's dietary intake: A systematic review and meta-analysis.
+\emph{Obesity Reviews} \textbf{20}, 554--568 (2019).
+
+\leavevmode\hypertarget{ref-ryanMetaAnalysisAchievementEffects1991}{}%
+201. Ryan, A. W. Meta-Analysis of Achievement Effects of Microcomputer Applications in Elementary Schools. \emph{Educational Administration Quarterly} \textbf{27}, 161--184 (1991).
+
+\leavevmode\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}%
+202.
+Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N.
+R.
+C.
+\& Johnston, B.
+C.
+Influence of unhealthy food and beverage marketing on children's dietary intake and preference: A systematic review and meta-analysis of randomized trials.
+\emph{Obesity Reviews} \textbf{17}, 945--959 (2016).
+
+\leavevmode\hypertarget{ref-saiphooSocialNetworkingSite2020}{}%
+203. Saiphoo, A. N., Dahoah Halevi, L. \& Vahedi, Z. Social networking site use and self-esteem: A meta-analytic review. \emph{Personality and Individual Differences} \textbf{153}, 109639 (2020).
+
+\leavevmode\hypertarget{ref-schererMetaanalysisTeachingLearning2020}{}%
+204.
+Scherer, R., Siddiq, F.
+\& Sánchez Viveros, B.
+A meta-analysis of teaching and learning computer programming: Effective instructional approaches and conditions.
+\emph{Computers in Human Behavior} \textbf{109}, 106349 (2020).
+
+\leavevmode\hypertarget{ref-schererCognitiveBenefitsLearning2019}{}%
+205.
+Scherer, R., Siddiq, F.
+\& Sánchez Viveros, B.
+The cognitive benefits of learning computer programming: A meta-analysis of transfer effects.
+\emph{Journal of Educational Psychology} \textbf{111}, 764--792 (2019).
+
+\leavevmode\hypertarget{ref-schroederHowEffectiveAre2013}{}%
+206.
+Schroeder, N.
+L., Adesope, O.
+O.
+\& Gilbert, R.
+B.
+How Effective are Pedagogical Agents for Learning?
+A Meta-Analytic Review.
+\emph{Journal of Educational Computing Research} \textbf{49}, 1--39 (2013).
+
+\leavevmode\hypertarget{ref-sciontiCognitiveTrainingEffective2020}{}%
+207.
+Scionti, N., Cavallero, M., Zogmaister, C.
+\& Marzocchi, G.
+M.
+Is Cognitive Training Effective for Improving Executive Functions in Preschoolers?
+A Systematic Review and Meta-Analysis.
+\emph{Frontiers in Psychology} \textbf{10}, 2812 (2020).
+
+\leavevmode\hypertarget{ref-shahabOnlineSupportSmoking2009}{}%
+208. Shahab, L. \& McEwen, A. Online support for smoking cessation: A systematic review of the literature. \emph{Addiction} \textbf{104}, 1792--1804 (2009).
+
+\leavevmode\hypertarget{ref-shannonProblematicSocialMedia2022}{}%
+209.
+Shannon, H., Bush, K., Villeneuve, P.
+J., Hellemans, K.
+G.
+\& Guimond, S.
+Problematic Social Media Use in Adolescents and Young Adults: Systematic Review and Meta-analysis.
+\emph{JMIR Mental Health} \textbf{9}, e33450 (2022).
+
+\leavevmode\hypertarget{ref-shinMobilePhoneInterventions2019}{}%
+210.
+Shin, Y., Kim, S.
+K.
+\& Lee, M.
+Mobile phone interventions to improve adolescents' physical health: A systematic review and meta-analysis.
+\emph{Public Health Nursing} \textbf{36}, 787--799 (2019).
+
+\leavevmode\hypertarget{ref-shinOnlineMediaConsumption2022}{}%
+211.
+Shin, M., Juventin, M., Wai Chu, J.
+T., Manor, Y.
+\& Kemps, E.
+Online media consumption and depression in young people: A systematic review and meta-analysis.
+\emph{Computers in Human Behavior} \textbf{128}, 107129 (2022).
+
+\leavevmode\hypertarget{ref-slavinReadingEffectsIBM1991}{}%
+212. Slavin, R. E. Reading Effects of IBM's "Writing to Read" Program: A Review of Evaluations. \emph{Educational Evaluation and Policy Analysis} \textbf{13}, 1 (1991).
+
+\leavevmode\hypertarget{ref-slavinEffectiveProgramsElementary2008}{}%
+213. Slavin, R. E. \& Lake, C. Effective Programs in Elementary Mathematics: A Best-Evidence Synthesis. \emph{Review of Educational Research} \textbf{78}, 427--515 (2008).
+
+\leavevmode\hypertarget{ref-slavinEffectiveProgramsMiddle2009}{}%
+214. Slavin, R. E., Lake, C. \& Groff, C. Effective Programs in Middle and High School Mathematics: A Best-Evidence Synthesis. \emph{Review of Educational Research} \textbf{79}, 839--911 (2009).
+
+\leavevmode\hypertarget{ref-slavinExperimentalEvaluationsElementary2014}{}%
+215.
+Slavin, R.
+E., Lake, C., Hanley, P.
+\& Thurston, A.
+Experimental evaluations of elementary science programs: A best-evidence synthesis.
+\emph{Journal of Research in Science Teaching} \textbf{51}, 870--901 (2014).
+
+\leavevmode\hypertarget{ref-soojungSynthesisComputerAssistedMathematical2022}{}%
+216.
+Soo Jung, K.
+\& Yan Ping, X.
+A Synthesis of Computer-Assisted Mathematical Word Problem-Solving Instruction for Students with Learning Disabilities or Difficulties.
+\emph{Learning Disabilities: A Contemporary Journal} \textbf{20}, 27--45 (2022).
+
+\leavevmode\hypertarget{ref-stavrinosDistractedWalkingBicycling2018}{}%
+217.
+Stavrinos, D., Pope, C.
+N., Shen, J.
+\& Schwebel, D.
+C.
+Distracted Walking, Bicycling, and Driving: Systematic Review and Meta-Analysis of Mobile Technology and Youth Crash Risk.
+\emph{Child Development} \textbf{89}, 118--128 (2018).
+
+\leavevmode\hypertarget{ref-steeleEducationIncarceratedJuveniles2016}{}%
+218. Steele, J. L., Bozick, R. \& Davis, L. M. Education for Incarcerated Juveniles: A Meta-Analysis. \emph{Journal of Education for Students Placed at Risk (JESPAR)} \textbf{21}, 65--89 (2016).
+
+\leavevmode\hypertarget{ref-strongSystematicMetaanalyticReview2011}{}%
+219.
+Strong, G.
+K., Torgerson, C.
+J., Torgerson, D.
+\& Hulme, C.
+A systematic meta-analytic review of evidence for the effectiveness of the `Fast ForWord' language intervention program.
+\emph{Journal of Child Psychology and Psychiatry} \textbf{52}, 224--235 (2011).
+
+\leavevmode\hypertarget{ref-strouseLearningVideoMetaAnalysis2021}{}%
+220. Strouse, G. A. \& Samson, J. E. Learning From Video: A Meta-Analysis of the Video Deficit in Children Ages 0 to 6 Years. \emph{Child Development} \textbf{92}, E20--E38 (2021).
+
+\leavevmode\hypertarget{ref-suleiman-martosGamificationImprovementDiet2021}{}%
+221.
+Suleiman-Martos, N.
+\emph{et al.} Gamification for the Improvement of Diet, Nutritional Habits, and Body Composition in Children and Adolescents: A Systematic Review and Meta-Analysis.
+\emph{Nutrients} \textbf{13}, 2478 (2021).
+
+\leavevmode\hypertarget{ref-sunWhichWayDesign2021}{}%
+222.
+Sun, L., Hu, L.
+\& Zhou, D.
+Which way of design programming activities is more effective to promote K-12 students' computational thinking skills?
+A meta-analysis.
+\emph{Journal of Computer Assisted Learning} \textbf{37}, 1048--1062 (2021).
+
+\leavevmode\hypertarget{ref-sungHowEffectiveAre2015}{}%
+223. Sung, Y.-T., Chang, K.-E. \& Yang, J.-M. How effective are mobile devices for language learning? A meta-analysis. \emph{Educational Research Review} \textbf{16}, 68--84 (2015).
+
+\leavevmode\hypertarget{ref-takacsCanComputerReplace2014}{}%
+224.
+Takacs, Z.
+K., Swart, E.
+K.
+\& Bus, A.
+G.
+Can the computer replace the adult for storybook reading?
+A meta-analysis on the effects of multimedia stories as compared to sharing print stories with an adult.
+\emph{Frontiers in Psychology} \textbf{5}, (2014).
+
+\leavevmode\hypertarget{ref-takacsBenefitsPitfallsMultimedia2015}{}%
+225.
+Takacs, Z.
+K., Swart, E.
+K.
+\& Bus, A.
+G.
+Benefits and Pitfalls of Multimedia and Interactive Features in Technology-Enhanced Storybooks: A Meta-Analysis.
+\emph{Review of Educational Research} \textbf{85}, 698--739 (2015).
+
+\leavevmode\hypertarget{ref-takacsEfficacyDifferentInterventions2019}{}%
+226.
+Takacs, Z.
+K.
+\& Kassai, R.
+The efficacy of different interventions to foster children's executive function skills: A series of meta-analyses.
+\emph{Psychological Bulletin} \textbf{145}, 653--697 (2019).
+
+\leavevmode\hypertarget{ref-tamimWhatFortyYears2011}{}%
+227.
+Tamim, R.
+M., Bernard, R.
+M., Borokhovski, E., Abrami, P.
+C.
+\& Schmid, R.
+F.
+What Forty Years of Research Says About the Impact of Technology on Learning: A Second-Order Meta-Analysis and Validation Study.
+\emph{Review of Educational Research} \textbf{81}, 4--28 (2011).
+
+\leavevmode\hypertarget{ref-tingirEffectsMobileDevices2017}{}%
+228.
+Tingir, S., Cavlazoglu, B., Caliskan, O., Koklu, O.
+\& Intepe-Tingir, S.
+Effects of mobile devices on K-12 students' achievement: A meta-analysis: Effects of mobile devices.
+\emph{Journal of Computer Assisted Learning} \textbf{33}, 355--369 (2017).
+
+\leavevmode\hypertarget{ref-tokacEffectsGamebasedLearning2019}{}%
+229.
+Tokac, U., Novak, E.
+\& Thompson, C.
+G.
+Effects of game-based learning on students' mathematics achievement: A meta-analysis.
+\emph{Journal of Computer Assisted Learning} \textbf{35}, 407--420 (2019).
+
+\leavevmode\hypertarget{ref-tokunagaMetaanalysisRelationshipsPsychosocial2017}{}%
+230.
+Tokunaga, R.
+S.
+A meta-analysis of the relationships between psychosocial problems and internet habits: Synthesizing internet addiction, problematic internet use, and deficient self-regulation research.
+\emph{Communication Monographs} \textbf{84}, 423--446 (2017).
+
+\leavevmode\hypertarget{ref-tremblaySystematicReviewSedentary2011}{}%
+231.
+Tremblay, M.
+S.
+\emph{et al.} Systematic review of sedentary behaviour and health indicators in school-aged children and youth.
+\emph{International Journal of Behavioral Nutrition and Physical Activity} \textbf{8}, 98 (2011).
+
+\leavevmode\hypertarget{ref-tsaiDigitalGamebasedSecondlanguage2018}{}%
+232.
+Tsai, Y.-L.
+\& Tsai, C.-C.
+Digital game-based second-language vocabulary learning and conditions of research designs: A meta-analysis study.
+\emph{Computers \& Education} \textbf{125}, 345--357 (2018).
+
+\leavevmode\hypertarget{ref-vahediAreMediaLiteracy2018}{}%
+233.
+Vahedi, Z., Sibalis, A.
+\& Sutherland, J.
+E.
+Are media literacy interventions effective at changing attitudes and intentions towards risky health behaviors in adolescents?
+A meta-analytic review.
+\emph{Journal of Adolescence} \textbf{67}, 140--152 (2018).
+
+\leavevmode\hypertarget{ref-vantrietHowEffectiveAre2014}{}%
+234.
+van 't Riet, J., Crutzen, R.
+\& Lu, A.
+S.
+How Effective Are Active Videogames Among the Young and the Old?
+Adding Meta-analyses to Two Recent Systematic Reviews.
+\emph{Games for Health Journal} \textbf{3}, 311--318 (2014).
+
+\leavevmode\hypertarget{ref-vanekrisEvidenceupdateProspectiveRelationship2016}{}%
+235.
+van Ekris, E.
+\emph{et al.} An evidence-update on the prospective relationship between childhood sedentary behaviour and biomedical health indicators: A systematic review and meta-analysis.
+\emph{Obesity Reviews} \textbf{17}, 833--849 (2016).
+
+\leavevmode\hypertarget{ref-vangriekenPrimaryPreventionOverweight2012}{}%
+236.
+van Grieken, A., Ezendam, N.
+P., Paulis, W.
+D., van der Wouden, J.
+C.
+\& Raat, H.
+Primary prevention of overweight in children and adolescents: A meta-analysis of the effectiveness of interventions aiming to decrease sedentary behaviour.
+\emph{International Journal of Behavioral Nutrition and Physical Activity} \textbf{9}, 61 (2012).
+
+\leavevmode\hypertarget{ref-villegas-navasEffectsFoodsEmbedded2020}{}%
+237.
+Villegas-Navas, V., Montero-Simo, M.-J.
+\& Araque-Padilla, R.
+A.
+The Effects of Foods Embedded in Entertainment Media on Children's Food Choices and Food Intake: A Systematic Review and Meta-Analyses.
+\emph{Nutrients} \textbf{12}, 964 (2020).
+
+\leavevmode\hypertarget{ref-wahiEffectivenessInterventionsAimed2011}{}%
+238.
+Wahi, G.
+Effectiveness of Interventions Aimed at Reducing Screen Time in Children: A Systematic Review and Meta-analysis of Randomized Controlled Trials.
+\emph{Archives of Pediatrics \& Adolescent Medicine} \textbf{165}, 979 (2011).
+
+\leavevmode\hypertarget{ref-shudongwangComparabilityComputerBasedPaperandPencil2008}{}%
+239.
+Shudong Wang, Hong Jiao, Young, M.
+J., Brooks, T.
+\& Olson, J.
+Comparability of Computer-Based and Paper-and-Pencil Testing in K Reading Assessments: A Meta-Analysis of Testing Mode Effects.
+\emph{Educational and Psychological Measurement} \textbf{68}, 5--24 (2008).
+
+\leavevmode\hypertarget{ref-wangSmartphoneOveruseVisual2020}{}%
+240.
+Wang, J., Li, M., Zhu, D.
+\& Cao, Y.
+Smartphone Overuse and Visual Impairment in Children and Young Adults: Systematic Review and Meta-Analysis.
+\emph{Journal of Medical Internet Research} \textbf{22}, e21923 (2020).
+
+\leavevmode\hypertarget{ref-wangEffects3DVirtual2020}{}%
+241.
+Wang, C.-p., Lan, Y.-J., Tseng, W.-T., Lin, Y.-T.
+R.
+\& Gupta, K.
+C.-L.
+On the effects of 3D virtual worlds in language learning a meta-analysis.
+\emph{Computer Assisted Language Learning} \textbf{33}, 891--915 (2020).
+
+\leavevmode\hypertarget{ref-wengEffectivenessCognitiveSkillsbased2014}{}%
+242.
+Weng, P.-L., Maeda, Y.
+\& Bouck, E.
+C.
+Effectiveness of Cognitive Skills-Based Computer-Assisted Instruction for Students With Disabilities: A Synthesis.
+\emph{Remedial and Special Education} \textbf{35}, 167--180 (2014).
+
+\leavevmode\hypertarget{ref-williamsImpactLeisuretimeTelevision1982}{}%
+243.
+Williams, P.
+A., Haertel, E.
+H., Haertel, G.
+D.
+\& Walberg, H.
+J.
+The Impact of Leisure-Time Television on School Learning: A Research Synthesis.
+\emph{American Educational Research Journal} \textbf{19}, 19--50 (1982).
+
+\leavevmode\hypertarget{ref-woodEffectsMediaViolence1991}{}%
+244. Wood, W., Wong, F. Y. \& Chachere, J. G. Effects of media violence on viewers' aggression in unconstrained social interaction. \emph{Psychological Bulletin} \textbf{109}, 371--383 (1991).
+
+\leavevmode\hypertarget{ref-woutersMetaanalysisCognitiveMotivational2013}{}%
+245.
+Wouters, P., van Nimwegen, C., van Oostendorp, H.
+\& van der Spek, E.
+D.
+A meta-analysis of the cognitive and motivational effects of serious games.
+\emph{Journal of Educational Psychology} \textbf{105}, 249--265 (2013).
+
+\leavevmode\hypertarget{ref-woutersMetaanalyticReviewRole2013}{}%
+246. Wouters, P. \& van Oostendorp, H. A meta-analytic review of the role of instructional support in game-based learning. \emph{Computers \& Education} \textbf{60}, 412--425 (2013).
+
+\leavevmode\hypertarget{ref-wuScreenTimeBody2022}{}%
+247.
+Wu, Y., Amirfakhraei, A., Ebrahimzadeh, F., Jahangiry, L.
+\& Abbasalizad-Farhangi, M.
+Screen Time and Body Mass Index Among Children and Adolescents: A Systematic Review and Meta-Analysis.
+\emph{Frontiers in Pediatrics} \textbf{10}, 822108 (2022).
+
+\leavevmode\hypertarget{ref-yangAssociationSocialNetwork2022}{}%
+248.
+Yang, Q., Liu, J.
+\& Rui, J.
+Association between social network sites use and mental illness: A meta-analysis.
+\emph{Cyberpsychology: Journal of Psychosocial Research on Cyberspace} \textbf{16}, (2022).
+
+\leavevmode\hypertarget{ref-yinCulturalBackgroundMeasurement2019}{}%
+249.
+Yin, X.-Q., de Vries, D.
+A., Gentile, D.
+A.
+\& Wang, J.-L.
+Cultural Background and Measurement of Usage Moderate the Association Between Social Networking Sites (SNSs) Usage and Mental Health: A Meta-Analysis.
+\emph{Social Science Computer Review} \textbf{37}, 631--648 (2019).
+
+\leavevmode\hypertarget{ref-zhangTelevisionWatchingRisk2016}{}%
+250. Zhang, G., Wu, L., Zhou, L., Lu, W. \& Mao, C. Television watching and risk of childhood obesity: A meta-analysis. \emph{The European Journal of Public Health} \textbf{26}, 13--18 (2016).
+
+\leavevmode\hypertarget{ref-zhangRelationshipSocialMedia2021}{}%
+251. Zhang, Y., Li, S. \& Yu, G. The relationship between social media use and fear of missing out: A meta-analysis. \emph{Acta Psychologica Sinica} \textbf{53}, 273--290 (2021).
+
+\leavevmode\hypertarget{ref-zhangInfluenceSedentaryBehaviour2022}{}%
+252.
+Zhang, J., Yang, S.
+X., Wang, L., Han, L.
+H.
+\& Wu, X.
+Y.
+The influence of sedentary behaviour on mental health among children and adolescents: A systematic review and meta-analysis of longitudinal studies.
+\emph{Journal of Affective Disorders} \textbf{306}, 90--114 (2022).
+
+\leavevmode\hypertarget{ref-zhangScreenTimeHealth2022}{}%
+253.
+Zhang, Y., Tian, S., Zou, D., Zhang, H.
+\& Pan, C.-W.
+Screen time and health issues in Chinese school-aged children and adolescents: A systematic review and meta-analysis.
+\emph{BMC Public Health} \textbf{22}, 810 (2022).
+
+\leavevmode\hypertarget{ref-zhangUpdatedMetaanalysisRelationship2022}{}%
+254. Zhang, J. \emph{et al.} An updated of meta-analysis on the relationship between mobile phone addiction and sleep disorder. \emph{Journal of Affective Disorders} \textbf{305}, 94--101 (2022).
+
+\leavevmode\hypertarget{ref-zhengLearningOnetoOneLaptop2016}{}%
+255.
+Zheng, B., Warschauer, M., Lin, C.-H.
+\& Chang, C.
+Learning in One-to-One Laptop Environments: A Meta-Analysis and Research Synthesis.
+\emph{Review of Educational Research} \textbf{86}, 1052--1084 (2016).
+
+\leavevmode\hypertarget{ref-zhouMetaanalysisNarrativeGamebased2020}{}%
+256. Zhou, C., Occa, A., Kim, S. \& Morgan, S. A Meta-analysis of Narrative Game-based Interventions for Promoting Healthy Behaviors. \emph{Journal of Health Communication} \textbf{25}, 54--65 (2020).
+
+\leavevmode\hypertarget{ref-zuckerEffectsElectronicBooks2009}{}%
+257.
+Zucker, T.
+A., Moody, A.
+K.
+\& McKenna, M.
+C.
+The Effects of Electronic Books on Pre-Kindergarten-to-Grade 5 Students' Literacy and Language Outcomes: A Research Synthesis.
+\emph{Journal of Educational Computing Research} \textbf{40}, 47--87 (2009).
 \end{cslreferences}

### 2023-09-14 reports/manuscript.tex
Fix small error in citations
Also removes the `nocite` param and instead just cites in text.

@@
 After screening titles and abstracts, we assessed 2,557 full-texts for inclusion.
-Of those, 217 met the inclusion criteria and we extracted the data from all of these meta-analyses.
+Of those, 217 met the inclusion criteria\textsuperscript{26--242} and we extracted the data from all of these meta-analyses.
 Figure 1 presents the full results of the selection process.
@@
 All credible effects related to education outcomes were small-to-moderate.
-Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning;\textsuperscript{26} \emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{p} = \textless0.001, \emph{k} = 79, \emph{N} = 5,810) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning;\textsuperscript{27} \emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135).
+Screen-based interventions designed to influence an outcome (e.g., a computer based program designed to enhance learning;\textsuperscript{230} \emph{r} = 0.21, 95\% CI 0.15 to 0.28, \emph{p} = \textless0.001, \emph{k} = 79, \emph{N} = 5,810) tended to have larger effect sizes than exposures that were not specifically intended to influence any of the measured outcomes (e.g., the association between television viewing and learning;\textsuperscript{29} \emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135).
 The largest effect size observed was for augmented reality-based education interventions on general learning (\emph{r} = 0.33, 95\% CI 0.25 to 0.42, \emph{p} = \textless0.001, \emph{k} = 15, \emph{N} = 1,474).
@@
 As an example, consider children watching television programs---an often cited form of screen use harm.
-We found evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
-However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
+We found evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{29}.
+However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{143}
 Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
 Similar nuanced findings were observed for video games.
-The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{27,29}
-However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
+The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{29,173}
+However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{52}
 One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 \& 5) therefore this hypothesis could not be addressed.
@@
 Social media was one type of exposure that showed consistent---albeit small---associations with poor health, with no indication of potential benefit.
-Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.\textsuperscript{31}
-These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression.\textsuperscript{32,33}
-Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls.\textsuperscript{34}
+Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.\textsuperscript{218}
+These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression.\textsuperscript{214,233}
+Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls.\textsuperscript{243}
 
@@
 The way that a young person interacts with digital screens may also be important.
-We found evidence that touch screens had strong evidence for benefits on learning,\textsuperscript{26} as did augmented reality.\textsuperscript{35}
+We found evidence that touch screens had strong evidence for benefits on learning,\textsuperscript{230} as did augmented reality.\textsuperscript{207}
 
@@
 Our results have several implications for policy and practice.
-Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{36--38}
+Broadly, our findings align with the recommendations of others who suggest that current guidelines may be too simplistic, mischaracterise the strength of the evidence, or do not acknowledge the important nuances of the issue.\textsuperscript{244--246}
 Our findings suggest that screen use is a complex issue, with associations based not just on duration and device type, but also on the content and the environment in which the exposure occurs.
@@
 For example, we suggest that guidelines should discourage high levels of social media and internet use.
-Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{39}
+Guidelines may also consider adapting recommendations that promote the use of educational apps and video games, although these recommendations need to be balanced against the (very small) risks to adiposity.\textsuperscript{151}
 
@@
 Most studies which did not meet our criteria failed to provide study-level data (or did not provide sufficient data, such as including effect estimates but not sample sizes).
-Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{40}
+Newer reviews were more likely to provide this information than older reviews, but it highlights the importance of data and code sharing as recommended in the PRISMA guidelines.\textsuperscript{247}
 When study level data was available, many effects were removed because the pooled sample size was small, or because there were fewer than ten studies on which to perform an Egger's test.
@@
 It has been established that self-reported screen use data has questionable validity.
-In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{41} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
-Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{42}
-While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{43} or device-based loggers\textsuperscript{44}---these are still not widely adopted.
+In a meta-analysis of 47 studies comparing self-reported media use with logged measures, Parry et al\textsuperscript{248} found that the measures were only moderately correlated (\(r = 0.38\)), with self-reported problematic usage fairing worse (\(r = 0.25\)).
+Indeed, of 622 studies which measured the screen use of 0---6 year-olds, only 69 provided any sort of psychometric properties for their measure, with only 19 studies reporting validity.\textsuperscript{249}
+While some researchers have started using newer methods of capturing screen behaviours---such as wearable cameras\textsuperscript{250} or device-based loggers\textsuperscript{251}---these are still not widely adopted.
 It may be that the field of screen use research cannot be sufficiently advanced until accurate, validated, and nuanced measures are more widely available and adopted.
@@
 For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
-Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{45}).
+Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{252}).
 As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
@@
 Some previous research suggests that associations are typically linear.\textsuperscript{18}
-However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,46,47}
+However, others have identified instances where non-linear relationships exist, especially for very high levels of screen use.\textsuperscript{17,253,254}
 Additionally, our conversion may not always adequately account for differences in study design or measures of exposures and outcomes.
@@
 We prospectively registered our methods on the International Prospective Register of Systematic Reviews (PROSPERO; CRD42017076051) in October 2017.
-We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{40}
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) guidelines.\textsuperscript{247}
 
@@
 
-For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{48} (see Table 1).
+For each meta-analysis, two researchers independently completed the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool\textsuperscript{255} (see Table 1).
 We resolved disagreements by consensus, with a third researcher employed when needed.
@@
 
-To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{49,50}
+To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{256,257}
 Effect sizes on the original metric are provided in Supplementary File 6.
-Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{51} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
-These are similar to other interpretations based on empirical data.\textsuperscript{52}
+Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{258} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
+These are similar to other interpretations based on empirical data.\textsuperscript{259}
 
@@
 We descriptively present the remaining meta-analytic effect sizes.
-To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{53} in R\textsuperscript{54} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
+To remove the differences in approach to meta-analyses across the reviews, we reran the effect size estimate using a random effects meta-analysis via the metafor package\textsuperscript{260} in R\textsuperscript{261} (version 4.3.0) when the meta-analysis's authors provided primary study data associated with these effects.
 When required, we imputed missing sample sizes using mean imputation from the other studies within that review.
 From our reanalysis we also extracted \(I^2\) values.
-To test for publication bias, we conducted Egger's test\textsuperscript{55} when the number of studies within the review was ten or more,\textsuperscript{56} and conducted a test of excess significance.\textsuperscript{57}
+To test for publication bias, we conducted Egger's test\textsuperscript{262} when the number of studies within the review was ten or more,\textsuperscript{263} and conducted a test of excess significance.\textsuperscript{264}
 We contacted authors who did not provide primary study data in their published article.
@@
 We employed a statistical classification approach to grade the credibility of the effect sizes in the literature.
-To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{58} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
+To be considered `credible' an effect needed to be derived from a combined sample of \textgreater1,000 participants\textsuperscript{265} and have non-significant tests of publication bias (i.e., Egger's test and excess significance test).
 We performed these analyses, and therefore the review needed to provide usable study-level data in order to be included.
@@
 
-\leavevmode\hypertarget{ref-xieCanTouchscreenDevices2018}{}%
+\leavevmode\hypertarget{ref-oztopDoesDigitalGeneration2021}{}%
 26.
-Xie, H.
-\emph{et al.} Can Touchscreen Devices be Used to Facilitate Young Children's Learning?
-A Meta-Analysis of Touchscreen Learning Effect.
-\emph{Frontiers in Psychology} \textbf{9}, 2580 (2018).
-
-\leavevmode\hypertarget{ref-adelantado-renauAssociationScreenMedia2019}{}%
-27.
-Adelantado-Renau, M.
-\emph{et al.} Association Between Screen Media Use and Academic Performance Among Children and Adolescents: A Systematic Review and Meta-analysis.
-\emph{JAMA Pediatrics} \textbf{173}, 1058 (2019).
-
-\leavevmode\hypertarget{ref-madiganAssociationsScreenUse2020}{}%
-28.
-Madigan, S., McArthur, B.
-A., Anhorn, C., Eirich, R.
-\& Christakis, D.
-A.
-Associations Between Screen Use and Child Language Skills: A Systematic Review and Meta-analysis.
-\emph{JAMA Pediatrics} \textbf{174}, 665 (2020).
-
-\leavevmode\hypertarget{ref-poorolajalBehavioralFactorsInfluencing2020}{}%
-29.
-Poorolajal, J., Sahraei, F., Mohamdadi, Y., Doosti-Irani, A.
-\& Moradi, L.
-Behavioral factors influencing childhood obesity: A systematic review and meta-analysis.
-\emph{Obesity Research \& Clinical Practice} \textbf{14}, 109--118 (2020).
-
-\leavevmode\hypertarget{ref-byunDigitalGamebasedLearning2018}{}%
-30. Byun, J. \& Joung, E. Digital game-based learning for K-12 mathematics education: A meta-analysis. \emph{School Science and Mathematics} \textbf{118}, 113--126 (2018).
-
-\leavevmode\hypertarget{ref-vannucciSocialMediaUse2020}{}%
-31. Vannucci, A., Simpson, E. G., Gagnon, S. \& Ohannessian, C. M. Social media use and risky behaviors in adolescents: A meta-analysis. \emph{Journal of Adolescence} \textbf{79}, 258--274 (2020).
-
-\leavevmode\hypertarget{ref-yoonSocialNetworkSite2019}{}%
-32.
-Yoon, S., Kleinman, M., Mertz, J.
-\& Brannick, M.
-Is social network site usage related to depression?
-A meta-analysis of FacebookDepression relations.
-\emph{Journal of Affective Disorders} \textbf{248}, 65--72 (2019).
-
-\leavevmode\hypertarget{ref-vahediAssociationSelfreportedDepressive2021}{}%
-33.
-Vahedi, Z.
-\& Zannella, L.
-The association between self-reported depressive symptoms and the use of social networking sites (SNS): A meta-analysis.
-\emph{Current Psychology} \textbf{40}, 2174--2189 (2021).
-
-\leavevmode\hypertarget{ref-seetharamanFacebookKnowsInstagram2021}{}%
-34. Seetharaman, G. W., Jeff Horwitz and Deepa. Facebook Knows Instagram Is Toxic for Teen Girls, Company Documents Show. \emph{Wall Street Journal} (2021).
-
-\leavevmode\hypertarget{ref-tekedereExaminingEffectivenessAugmented2016}{}%
-35.
-Tekedere, H.
-\& Göke, H.
-Examining the Effectiveness of Augmented Reality Applications in Education: A Meta-Analysis.
-\emph{International Journal of Environmental and Science Education} \textbf{11}, 9469--9481 (2016).
-
-\leavevmode\hypertarget{ref-elsonPolicyStatementsMedia2019}{}%
-36. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).
-
-\leavevmode\hypertarget{ref-ashtonScreenTimeChildren2019}{}%
-37. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).
-
-\leavevmode\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}%
-38. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).
-
-\leavevmode\hypertarget{ref-markerExploringMythChubby2022}{}%
-39. Marker, C., Gnambs, T. \& Appel, M. Exploring the myth of the chubby gamer: A meta-analysis on sedentary video gaming and body mass. \emph{Social Science \& Medicine} \textbf{301}, 112325 (2022).
-
-\leavevmode\hypertarget{ref-pagePRISMA2020Statement2020}{}%
-40. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.
-
-\leavevmode\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}%
-41. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).
-
-\leavevmode\hypertarget{ref-byrneMeasurementScreenTime2021}{}%
-42. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).
-
-\leavevmode\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}%
-43.
-Smith, C., Galland, B.
-C., de Bruin, W.
-E.
-\& Taylor, R.
-W.
-Feasibility of automated cameras to measure screen use in adolescents.
-\emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).
-
-\leavevmode\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}%
-44. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).
-
-\leavevmode\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}%
-45. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).
-
-\leavevmode\hypertarget{ref-twengeMoreTimeTechnology2019}{}%
-46.
-Twenge, J.
-M.
-More Time on Technology, Less Happiness?
-Associations Between Digital-Media Use and Psychological Well-Being.
-\emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).
-
-\leavevmode\hypertarget{ref-kellySocialMediaUse2018}{}%
-47. Kelly, Y., Zilanawala, A., Booker, C. \& Sacker, A. Social Media Use and Adolescent Mental Health: Findings From the UK Millennium Cohort Study. \emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).
-
-\leavevmode\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}%
-48. National Health, Lung, and Blood Institute. \emph{Quality Assessment of Systematic Reviews and Meta-Analyses}. (2014).
-
-\leavevmode\hypertarget{ref-bowmanEffectSizesStatistical2012}{}%
-49. Bowman, N. A. Effect Sizes and Statistical Methods for Meta-Analysis in Higher Education. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).
-
-\leavevmode\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}%
-50.
-Jacobs, P.
-\& Viechtbauer, W.
-Estimation of the biserial correlation and its sampling variance for use in meta-analysis: Biserial Correlation.
-\emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).
-
-\leavevmode\hypertarget{ref-funderEvaluatingEffectSize2019}{}%
-51. Funder, D. C. \& Ozer, D. J. Evaluating Effect Size in Psychological Research: Sense and Nonsense. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).
-
-\leavevmode\hypertarget{ref-gignacEffectSizeGuidelines2016}{}%
-52. Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).
-
-\leavevmode\hypertarget{ref-R-metafor}{}%
-53. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).
-
-\leavevmode\hypertarget{ref-R-base}{}%
-54. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).
-
-\leavevmode\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}%
-55. Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).
-
-\leavevmode\hypertarget{ref-pageChapter13Assessing2021}{}%
-56.
-Page, M.
-J., Higgins, J.
-P.
-\& Sterne, J.
-A.
-Chapter 13: Assessing risk of bias due to missing results in a synthesis.
-in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds.
-Higgins, J.
-P.
-et al.) (Cochrane, 2021).
-
-\leavevmode\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}%
-57. Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).
-
-\leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
-58. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
-
-\leavevmode\hypertarget{ref-oztopDoesDigitalGeneration2021}{}%
-59.
 Öztop, F.
@@
 \leavevmode\hypertarget{ref-abramiEffectsABRACADABRAReading2015}{}%
-60.
+27.
 Abrami, P., Borohkovski, E.
@@
 \leavevmode\hypertarget{ref-abramiEffectsABRACADABRAReading2020}{}%
-61.
+28.
 Abrami, P.
@@
 
+\leavevmode\hypertarget{ref-adelantado-renauAssociationScreenMedia2019}{}%
+29.
+Adelantado-Renau, M.
+\emph{et al.} Association Between Screen Media Use and Academic Performance Among Children and Adolescents: A Systematic Review and Meta-analysis.
+\emph{JAMA Pediatrics} \textbf{173}, 1058 (2019).
+
 \leavevmode\hypertarget{ref-aghasiInternetUseRelation2019}{}%
-62.
+30.
 Aghasi, M., Matinfar, A., Golzarand, M., Salari-Moghaddam, A.
@@
 \leavevmode\hypertarget{ref-alimoradiInternetAddictionSleep2019}{}%
-63. Alimoradi, Z. \emph{et al.} Internet addiction and sleep problems: A systematic review and meta-analysis. \emph{Sleep Medicine Reviews} \textbf{47}, 51--61 (2019).
+31. Alimoradi, Z. \emph{et al.} Internet addiction and sleep problems: A systematic review and meta-analysis. \emph{Sleep Medicine Reviews} \textbf{47}, 51--61 (2019).
+
+\leavevmode\hypertarget{ref-allenSedentaryBehaviourRisk2019}{}%
+32. Allen, M. S., Walter, E. E. \& Swann, C. Sedentary behaviour and risk of anxiety: A systematic review and meta-analysis. \emph{Journal of Affective Disorders} \textbf{242}, 5--13 (2019).
 
 \leavevmode\hypertarget{ref-ameryounImpactGameBasedHealth2018}{}%
-64.
+33.
 Ameryoun, A., Sanaeinasab, H., Saffari, M.
@@
 \leavevmode\hypertarget{ref-andersonViolentVideoGame2010}{}%
-65.
+34.
 Anderson, C.
@@
 \leavevmode\hypertarget{ref-andradePsychologicalEffectsExergames2019}{}%
-66.
+35.
 Andrade, A., Correia, C.
@@
 \leavevmode\hypertarget{ref-arztmannEffectsGamesSTEM2022}{}%
-67.
+36.
 Arztmann, M., Hornstra, L., Jeuring, J.
@@
 \leavevmode\hypertarget{ref-aspirantiIPadsTabletsStudents2020}{}%
-68. Aspiranti, K. B., Larwin, K. H. \& Schade, B. P. iPads/tablets and students with autism: A meta-analysis of academic effects. \emph{Assistive Technology} \textbf{32}, 23--30 (2020).
+37. Aspiranti, K. B., Larwin, K. H. \& Schade, B. P. iPads/tablets and students with autism: A meta-analysis of academic effects. \emph{Assistive Technology} \textbf{32}, 23--30 (2020).
 
 \leavevmode\hypertarget{ref-baradaranmahdaviAssociationSedentaryBehavior2021}{}%
-69.
+38.
 Baradaran Mahdavi, S., Riahi, R., Vahdatpour, B.
@@
 \leavevmode\hypertarget{ref-barnettActiveVideoGames2011}{}%
-70. Barnett, A., Cerin, E. \& Baranowski, T. Active Video Games for Youth: A Systematic Review. \emph{Journal of Physical Activity and Health} \textbf{8}, 724--737 (2011).
+39. Barnett, A., Cerin, E. \& Baranowski, T. Active Video Games for Youth: A Systematic Review. \emph{Journal of Physical Activity and Health} \textbf{8}, 724--737 (2011).
 
 \leavevmode\hypertarget{ref-bartelProtectiveRiskFactors2015}{}%
-71. Bartel, K. A., Gradisar, M. \& Williamson, P. Protective and risk factors for adolescent sleep: A meta-analytic review. \emph{Sleep Medicine Reviews} \textbf{21}, 72--85 (2015).
+40. Bartel, K. A., Gradisar, M. \& Williamson, P. Protective and risk factors for adolescent sleep: A meta-analytic review. \emph{Sleep Medicine Reviews} \textbf{21}, 72--85 (2015).
+
+\leavevmode\hypertarget{ref-baumannMHealthInterventionsReduce2022}{}%
+41.
+Baumann, H., Fiedler, J., Wunsch, K., Woll, A.
+\& Wollesen, B.
+mHealth Interventions to Reduce Physical Inactivity and Sedentary Behavior in Children and Adolescents: Systematic Review and Meta-analysis of Randomized Controlled Trials.
+\emph{JMIR mHealth and uHealth} \textbf{10}, e35920 (2022).
+
+\leavevmode\hypertarget{ref-bayraktarMetaanalysisEffectivenessComputerassisted2001}{}%
+42. Bayraktar, S. A Meta-analysis of the Effectiveness of Computer-Assisted Instruction in Science Education. \emph{Journal of Research on Technology in Education} \textbf{34}, 173--188 (2001).
 
 \leavevmode\hypertarget{ref-becksilvaEffectsComputerbasedInterventions2022}{}%
-72.
+43.
 Beck Silva, K.
@@
 \leavevmode\hypertarget{ref-benavides-varelaEffectivenessDigitalbasedInterventions2020}{}%
-73.
+44.
 Benavides-Varela, S.
@@
 \leavevmode\hypertarget{ref-beneriaOnlineInterventionsCannabis2021}{}%
-74.
+45.
 Beneria, A.
@@
 \leavevmode\hypertarget{ref-blokComputerassistedInstructionSupport2002}{}%
-75.
+46.
 Blok, H., Oostdam, R., Otter, M.
@@
 \leavevmode\hypertarget{ref-bochnerImpactActiveVideo2015}{}%
-76. Bochner, R. E., Sorensen, K. M. \& Belamarich, P. F. The Impact of Active Video Gaming on Weight in Youth: A Meta-Analysis. \emph{Clinical Pediatrics} \textbf{54}, 620--628 (2015).
+47. Bochner, R. E., Sorensen, K. M. \& Belamarich, P. F. The Impact of Active Video Gaming on Weight in Youth: A Meta-Analysis. \emph{Clinical Pediatrics} \textbf{54}, 620--628 (2015).
 
 \leavevmode\hypertarget{ref-bossenEffectivenessSeriousGames2020}{}%
-77.
+48.
 Bossen, D.
@@
 \leavevmode\hypertarget{ref-boylandAdvertisingCueConsume2016}{}%
-78.
+49.
 Boyland, E.
@@
 \leavevmode\hypertarget{ref-boylandAssociationFoodNonalcoholic2022}{}%
-79.
+50.
 Boyland, E.
@@
 \leavevmode\hypertarget{ref-burkhardtMetaAnalysisLongitudinalAgeDependent2022}{}%
-80. Burkhardt, J. \& Lenhard, W. A Meta-Analysis on the Longitudinal, Age-Dependent Effects of Violent Video Games on Aggression. \emph{Media Psychology} \textbf{25}, 499--512 (2022).
+51. Burkhardt, J. \& Lenhard, W. A Meta-Analysis on the Longitudinal, Age-Dependent Effects of Violent Video Games on Aggression. \emph{Media Psychology} \textbf{25}, 499--512 (2022).
+
+\leavevmode\hypertarget{ref-byunDigitalGamebasedLearning2018}{}%
+52. Byun, J. \& Joung, E. Digital game-based learning for K-12 mathematics education: A meta-analysis. \emph{School Science and Mathematics} \textbf{118}, 113--126 (2018).
 
 \leavevmode\hypertarget{ref-caiAugmentedRealityTechnology2022}{}%
-81. Cai, Y., Pan, Z. \& Liu, M. Augmented reality technology in language learning: A meta-analysis. \emph{Journal of Computer Assisted Learning} \textbf{38}, 929--945 (2022).
+53. Cai, Y., Pan, Z. \& Liu, M. Augmented reality technology in language learning: A meta-analysis. \emph{Journal of Computer Assisted Learning} \textbf{38}, 929--945 (2022).
 
 \leavevmode\hypertarget{ref-caoEffectsModeratorsComputerBased2020}{}%
-82.
+54.
 Cao, Y., Huang, T., Huang, J., Xie, X.
@@
 \leavevmode\hypertarget{ref-caoRiskAccidentsChronic2022}{}%
-83.
+55.
 Cao, X.
@@
 
+\leavevmode\hypertarget{ref-carterAssociationPortableScreenbased2016}{}%
+56.
+Carter, B., Rees, P., Hale, L., Bhattacharjee, D.
+\& Paradkar, M.
+S.
+Association Between Portable Screen-Based Media Device Access or Use and Sleep Outcomes: A Systematic Review and Meta-analysis.
+\emph{JAMA Pediatrics} \textbf{170}, 1202 (2016).
+
 \leavevmode\hypertarget{ref-casaleMetaanalysisAssociationSelfesteem2022}{}%
-84. Casale, S. \emph{et al.} A meta-analysis on the association between self-esteem and problematic smartphone use. \emph{Computers in Human Behavior} \textbf{134}, 107302 (2022).
+57. Casale, S. \emph{et al.} A meta-analysis on the association between self-esteem and problematic smartphone use. \emph{Computers in Human Behavior} \textbf{134}, 107302 (2022).
 
 \leavevmode\hypertarget{ref-championEffectivenessSchoolbasedEHealth2019}{}%
-85.
+58.
 Champion, K.
@@
 \leavevmode\hypertarget{ref-chanDynamicGeometrySoftware2014}{}%
-86.
+59.
 Chan, K.
@@
 \leavevmode\hypertarget{ref-chanImpactESportsOnline2022}{}%
-87. Chan, G. \emph{et al.} The impact of eSports and online video gaming on lifestyle behaviours in youth: A systematic review. \emph{Computers in Human Behavior} \textbf{126}, 106974 (2022).
+60. Chan, G. \emph{et al.} The impact of eSports and online video gaming on lifestyle behaviours in youth: A systematic review. \emph{Computers in Human Behavior} \textbf{126}, 106974 (2022).
+
+\leavevmode\hypertarget{ref-chauhanMetaanalysisImpactTechnology2017}{}%
+61. Chauhan, S. A meta-analysis of the impact of technology on learning effectiveness of elementary students. \emph{Computers \& Education} \textbf{105}, 14--30 (2017).
 
 \leavevmode\hypertarget{ref-chenMetaanalysisFactorsPredicting2017}{}%
-88.
+62.
 Chen, L., Ho, S.
@@
 \leavevmode\hypertarget{ref-chenEffectsCompetitionDigital2020}{}%
-89.
+63.
 Chen, C.-H., Shih, C.-C.
@@
 \leavevmode\hypertarget{ref-cheungHowFeaturesEducational2012}{}%
-90.
+64.
 Cheung, A.
@@
 \leavevmode\hypertarget{ref-cheungEffectivenessEducationalTechnology2013}{}%
-91.
+65.
 Cheung, A.
@@
 \leavevmode\hypertarget{ref-cheungEffectsEducationalTechnology2013}{}%
-92.
+66.
 Cheung, A.
@@
 \leavevmode\hypertarget{ref-choEffectsUsingMobile2018}{}%
-93. Cho, K., Lee, S., Joo, M.-H. \& Becker, B. The Effects of Using Mobile Devices on Student Achievement in Language Learning: A Meta-Analysis. \emph{Education Sciences} \textbf{8}, 105 (2018).
+67. Cho, K., Lee, S., Joo, M.-H. \& Becker, B. The Effects of Using Mobile Devices on Student Achievement in Language Learning: A Meta-Analysis. \emph{Education Sciences} \textbf{8}, 105 (2018).
 
 \leavevmode\hypertarget{ref-choduraInterventionsChildrenMathematical2015}{}%
-94. Chodura, S., Kuhn, J.-T. \& Holling, H. Interventions for Children With Mathematical Difficulties: A Meta-Analysis. \emph{Zeitschrift für Psychologie} \textbf{223}, 129--144 (2015).
+68. Chodura, S., Kuhn, J.-T. \& Holling, H. Interventions for Children With Mathematical Difficulties: A Meta-Analysis. \emph{Zeitschrift für Psychologie} \textbf{223}, 129--144 (2015).
 
 \leavevmode\hypertarget{ref-claussenAllFamilySystematic2022}{}%
-95.
+69.
 Claussen, A.
@@
 \leavevmode\hypertarget{ref-clintonReadingPaperCompared2019}{}%
-96. Clinton, V. Reading from paper compared to screens: A systematic review and meta-analysis. \emph{Journal of Research in Reading} \textbf{42}, 288--325 (2019).
+70. Clinton, V. Reading from paper compared to screens: A systematic review and meta-analysis. \emph{Journal of Research in Reading} \textbf{42}, 288--325 (2019).
 
 \leavevmode\hypertarget{ref-comeras-chuecaEffectsActiveVideo2021}{}%
-97.
+71.
 Comeras-Chueca, C.
@@
 \leavevmode\hypertarget{ref-comeras-chuecaEffectsActiveVideo2021a}{}%
-98.
+72.
 Comeras-Chueca, C.
@@
 \leavevmode\hypertarget{ref-coxAssociationTelevisionViewing2012}{}%
-99.
+73.
 Cox, R., Skouteris, H., Rutherford, L.
@@
 \leavevmode\hypertarget{ref-coyneMetaanalysisProsocialMedia2018}{}%
-100.
+74.
 Coyne, S.
@@
 \leavevmode\hypertarget{ref-cunninghamSocialMediaDepression2021}{}%
-101. Cunningham, S., Hudson, C. C. \& Harkness, K. Social Media and Depression Symptoms: A Meta-Analysis. \emph{Research on Child and Adolescent Psychopathology} \textbf{49}, 241--253 (2021).
+75. Cunningham, S., Hudson, C. C. \& Harkness, K. Social Media and Depression Symptoms: A Meta-Analysis. \emph{Research on Child and Adolescent Psychopathology} \textbf{49}, 241--253 (2021).
 
 \leavevmode\hypertarget{ref-cushingMetaAnalyticReviewEHealth2010}{}%
-102.
+76.
 Cushing, C.
@@
 \leavevmode\hypertarget{ref-darlingSystematicReviewMetaAnalysis2017}{}%
-103.
+77.
 Darling, K.
@@
 \leavevmode\hypertarget{ref-daveyAssessmentSmartphoneAddiction2014}{}%
-104.
+78.
 Davey, S.
@@
 \leavevmode\hypertarget{ref-davidHowEffectiveAre2020}{}%
-105.
+79.
 David, O.
@@
 \leavevmode\hypertarget{ref-oliveiraPhysicalActivitySedentary2016}{}%
-106.
+80.
 Oliveira, R.
@@
 \leavevmode\hypertarget{ref-deriberaCorrelatesYouthViolence2019}{}%
-107.
+81.
 de Ribera, O.
@@
 \leavevmode\hypertarget{ref-diMetaanalysisImpactVirtual2022}{}%
-108. Di, X. \& Zheng, X. A meta-analysis of the impact of virtual technologies on students' spatial ability. \emph{Educational technology research and development} \textbf{70}, 73--98 (2022).
+82. Di, X. \& Zheng, X. A meta-analysis of the impact of virtual technologies on students' spatial ability. \emph{Educational technology research and development} \textbf{70}, 73--98 (2022).
 
 \leavevmode\hypertarget{ref-eirichAssociationScreenTime2022}{}%
-109.
+83.
 Eirich, R.
@@
 \leavevmode\hypertarget{ref-ercelikEffectivenessActiveVideo2022}{}%
-110.
+84.
 Erçelik, Z.
@@
 \leavevmode\hypertarget{ref-fangScreenTimeChildhood2019}{}%
-111. Fang, K., Mu, M., Liu, K. \& He, Y. Screen time and childhood overweight/obesity: A systematic review and meta-analysis. \emph{Child: Care, Health and Development} \textbf{45}, 744--753 (2019).
+85. Fang, K., Mu, M., Liu, K. \& He, Y. Screen time and childhood overweight/obesity: A systematic review and meta-analysis. \emph{Child: Care, Health and Development} \textbf{45}, 744--753 (2019).
 
 \leavevmode\hypertarget{ref-fedeleMobileHealthInterventions2017}{}%
-112.
+86.
 Fedele, D.
@@
 \leavevmode\hypertarget{ref-fengAssociationsMeeting24hour2021}{}%
-113.
+87.
 Feng, J., Zheng, C., Sit, C.
@@
 \leavevmode\hypertarget{ref-fergusonPublicHealthRisks2009}{}%
-114. Ferguson, C. J. \& Kilburn, J. The Public Health Risks of Media Violence: A Meta-Analytic Review. \emph{The Journal of Pediatrics} \textbf{154}, 759--763 (2009).
+88. Ferguson, C. J. \& Kilburn, J. The Public Health Risks of Media Violence: A Meta-Analytic Review. \emph{The Journal of Pediatrics} \textbf{154}, 759--763 (2009).
 
 \leavevmode\hypertarget{ref-fergusonAngryBirdsMake2015}{}%
-115.
+89.
 Ferguson, C.
@@
 \leavevmode\hypertarget{ref-fergusonDoesSexyMedia2017}{}%
-116. Ferguson, C. J., Nielsen, R. K. L. \& Markey, P. M. Does Sexy Media Promote Teen Sex? A Meta-Analytic and Methodological Review. \emph{Psychiatric Quarterly} \textbf{88}, 349--358 (2017).
+90. Ferguson, C. J., Nielsen, R. K. L. \& Markey, P. M. Does Sexy Media Promote Teen Sex? A Meta-Analytic and Methodological Review. \emph{Psychiatric Quarterly} \textbf{88}, 349--358 (2017).
 
 \leavevmode\hypertarget{ref-ferguson13ReasonsWhy2019}{}%
-117.
+91.
 Ferguson, C.
@@
 \leavevmode\hypertarget{ref-fergusonReexaminingFindingsAmerican2020}{}%
-118.
+92.
 Ferguson, C.
@@
 \leavevmode\hypertarget{ref-fergusonThisMetaanalysisScreen2022}{}%
-119. Ferguson, C. J. \emph{et al.} Like this meta-analysis: Screen media and mental health. \emph{Professional Psychology: Research and Practice} \textbf{53}, 205--214 (2022).
+93. Ferguson, C. J. \emph{et al.} Like this meta-analysis: Screen media and mental health. \emph{Professional Psychology: Research and Practice} \textbf{53}, 205--214 (2022).
 
 \leavevmode\hypertarget{ref-fischerEffectsRiskglorifyingMedia2011}{}%
-120.
+94.
 Fischer, P., Greitemeyer, T., Kastenmüller, A., Vogrincic, C.
@@
 \leavevmode\hypertarget{ref-folkvordPersuasiveEffectAdvergames2018}{}%
-121. Folkvord, F. \& van `t Riet, J. The persuasive effect of advergames promoting unhealthy foods among children: A meta-analysis. \emph{Appetite} \textbf{129}, 245--251 (2018).
+95. Folkvord, F. \& van `t Riet, J. The persuasive effect of advergames promoting unhealthy foods among children: A meta-analysis. \emph{Appetite} \textbf{129}, 245--251 (2018).
 
 \leavevmode\hypertarget{ref-foremanAssociationDigitalSmart2021}{}%
-122. Foreman, J. \emph{et al.} Association between digital smart device use and myopia: A systematic review and meta-analysis. \emph{The Lancet Digital Health} \textbf{3}, e806--e818 (2021).
+96. Foreman, J. \emph{et al.} Association between digital smart device use and myopia: A systematic review and meta-analysis. \emph{The Lancet Digital Health} \textbf{3}, e806--e818 (2021).
 
 \leavevmode\hypertarget{ref-fowlerHarnessingTechnologicalSolutions2021}{}%
-123.
+97.
 Fowler, L.
@@
 \leavevmode\hypertarget{ref-furenesComparisonChildrenReading2021}{}%
-124. Furenes, M. I., Kucirkova, N. \& Bus, A. G. A Comparison of Children's Reading on Paper versus Screen: A Meta-Analysis. \emph{Review of Educational Research} \textbf{91}, 483--517 (2021).
+98. Furenes, M. I., Kucirkova, N. \& Bus, A. G. A Comparison of Children's Reading on Paper versus Screen: A Meta-Analysis. \emph{Review of Educational Research} \textbf{91}, 483--517 (2021).
 
 \leavevmode\hypertarget{ref-gaoMetaanalysisActiveVideo2015}{}%
-125.
+99.
 Gao, Z., Chen, S., Pasco, D.
@@
 \leavevmode\hypertarget{ref-gardellaSystematicReviewMetaAnalysis2017}{}%
-126.
+100.
 Gardella, J.
@@
 \leavevmode\hypertarget{ref-garzonSystematicReviewMetaanalysis2019}{}%
-127. Garzón, J., Pavón, J. \& Baldiris, S. Systematic review and meta-analysis of augmented reality in educational settings. \emph{Virtual Reality} \textbf{23}, 447--459 (2019).
+101. Garzón, J., Pavón, J. \& Baldiris, S. Systematic review and meta-analysis of augmented reality in educational settings. \emph{Virtual Reality} \textbf{23}, 447--459 (2019).
 
 \leavevmode\hypertarget{ref-garzonMetaanalysisImpactAugmented2019}{}%
-128. Garzón, J. \& Acevedo, J. Meta-analysis of the impact of Augmented Reality on students' learning gains. \emph{Educational Research Review} \textbf{27}, 244--260 (2019).
+102. Garzón, J. \& Acevedo, J. Meta-analysis of the impact of Augmented Reality on students' learning gains. \emph{Educational Research Review} \textbf{27}, 244--260 (2019).
 
 \leavevmode\hypertarget{ref-ghobadiAssociationEatingTelevision2018}{}%
-129.
+103.
 Ghobadi, S.
@@
 \leavevmode\hypertarget{ref-grabeRoleMediaBody2008}{}%
-130.
+104.
 Grabe, S., Ward, L.
@@
 \leavevmode\hypertarget{ref-grahamFormativeAssessmentWriting2015}{}%
-131. Graham, S., Hebert, M. \& Harris, K. R. Formative Assessment and Writing: A Meta-Analysis. \emph{The Elementary School Journal} \textbf{115}, 523--547 (2015).
+105. Graham, S., Hebert, M. \& Harris, K. R. Formative Assessment and Writing: A Meta-Analysis. \emph{The Elementary School Journal} \textbf{115}, 523--547 (2015).
+
+\leavevmode\hypertarget{ref-haghjooScreenTimeIncreases2022}{}%
+106.
+Haghjoo, P., Siri, G., Soleimani, E., Farhangi, M.
+A.
+\& Alesaeidi, S.
+Screen time increases overweight and obesity risk among adolescents: A systematic review and dose-response meta-analysis.
+\emph{BMC Primary Care} \textbf{23}, 161 (2022).
+
+\leavevmode\hypertarget{ref-hammersleyParentfocusedChildhoodAdolescent2016}{}%
+107.
+Hammersley, M.
+L., Jones, R.
+A.
+\& Okely, A.
+D.
+Parent-Focused Childhood and Adolescent Overweight and Obesity eHealth Interventions: A Systematic Review and Meta-Analysis.
+\emph{Journal of Medical Internet Research} \textbf{18}, e203 (2016).
 
 \leavevmode\hypertarget{ref-haoTechnologyAssistedVocabularyLearning2021}{}%
-132. Hao, T., Wang, Z. \& Ardasheva, Y. Technology-Assisted Vocabulary Learning for EFL Learners: A Meta-Analysis. \emph{Journal of Research on Educational Effectiveness} \textbf{14}, 645--667 (2021).
+108. Hao, T., Wang, Z. \& Ardasheva, Y. Technology-Assisted Vocabulary Learning for EFL Learners: A Meta-Analysis. \emph{Journal of Research on Educational Effectiveness} \textbf{14}, 645--667 (2021).
 
 \leavevmode\hypertarget{ref-mahdiEffectivenessComputerAssisted2019}{}%
-133. Mahdi, H. S. \& Al Khateeb, A. A. The effectiveness of computer-assisted pronunciation training: A meta-analysis. \emph{Review of Education} \textbf{7}, 733--753 (2019).
+109. Mahdi, H. S. \& Al Khateeb, A. A. The effectiveness of computer-assisted pronunciation training: A meta-analysis. \emph{Review of Education} \textbf{7}, 733--753 (2019).
 
 \leavevmode\hypertarget{ref-heEffectsSmartphoneBasedInterventions2021}{}%
-134.
+110.
 He, Z.
@@
 \leavevmode\hypertarget{ref-hernandez-jimenezImpactActiveVideo2019}{}%
-135.
+111.
 Hernández-Jiménez, C.
@@
 \leavevmode\hypertarget{ref-hoActiveVideoGame2022}{}%
-136.
+112.
 Ho, R.
@@
 \leavevmode\hypertarget{ref-huangWhenMediaBecome2021}{}%
-137. Huang, Q., Peng, W. \& Ahn, S. When media become the mirror: A meta-analysis on media and body image. \emph{Media Psychology} \textbf{24}, 437--489 (2021).
+113. Huang, Q., Peng, W. \& Ahn, S. When media become the mirror: A meta-analysis on media and body image. \emph{Media Psychology} \textbf{24}, 437--489 (2021).
 
 \leavevmode\hypertarget{ref-hurwitzGettingReadReady2019}{}%
-138. Hurwitz, L. B. Getting a Read on Ready To Learn Media: A Meta-analytic Review of Effects on Literacy. \emph{Child Development} \textbf{90}, 1754--1771 (2019).
+114. Hurwitz, L. B. Getting a Read on Ready To Learn Media: A Meta-analytic Review of Effects on Literacy. \emph{Child Development} \textbf{90}, 1754--1771 (2019).
 
 \leavevmode\hypertarget{ref-kristensenProblematicGamingSleep2021}{}%
-139.
+115.
 Kristensen, J.
@@
 \leavevmode\hypertarget{ref-ivieMetaanalysisAssociationAdolescent2020}{}%
-140.
+116.
 Ivie, E.
@@
 \leavevmode\hypertarget{ref-janssenAssociationsScreenTime2020}{}%
-141.
+117.
 Janssen, X.
@@
 \leavevmode\hypertarget{ref-katesEffectsMobilePhone2018}{}%
-142. Kates, A. W., Wu, H. \& Coryn, C. L. S. The effects of mobile phone use on academic performance: A meta-analysis. \emph{Computers \& Education} \textbf{127}, 107--112 (2018).
+118. Kates, A. W., Wu, H. \& Coryn, C. L. S. The effects of mobile phone use on academic performance: A meta-analysis. \emph{Computers \& Education} \textbf{127}, 107--112 (2018).
 
 \leavevmode\hypertarget{ref-kimMeasuresMatterMetaAnalysis2021}{}%
-143.
+119.
 Kim, J., Gilbert, J., Yu, Q.
@@
 \leavevmode\hypertarget{ref-kongComparisonReadingPerformance2018}{}%
-144. Kong, Y., Seo, Y. S. \& Zhai, L. Comparison of reading performance on screen and on paper: A meta-analysis. \emph{Computers \& Education} \textbf{123}, 138--149 (2018).
+120. Kong, Y., Seo, Y. S. \& Zhai, L. Comparison of reading performance on screen and on paper: A meta-analysis. \emph{Computers \& Education} \textbf{123}, 138--149 (2018).
 
 \leavevmode\hypertarget{ref-kroesbergenMathematicsInterventionsChildren2003}{}%
-145. Kroesbergen, E. H. \& Van Luit, J. E. H. Mathematics Interventions for Children with Special Educational Needs: A Meta-Analysis. \emph{Remedial and Special Education} \textbf{24}, 97--114 (2003).
+121. Kroesbergen, E. H. \& Van Luit, J. E. H. Mathematics Interventions for Children with Special Educational Needs: A Meta-Analysis. \emph{Remedial and Special Education} \textbf{24}, 97--114 (2003).
 
 \leavevmode\hypertarget{ref-kucukalkanExaminationEffectsComputerbased2019}{}%
-146.
+122.
 Küçükalkan, K., Beyazsaçlı, M.
@@
 \leavevmode\hypertarget{ref-lambMetaanalysisExaminationModerators2018}{}%
-147.
+123.
 Lamb, R.
@@
 \leavevmode\hypertarget{ref-lancaAssociationDigitalScreen2020}{}%
-148. Lanca, C. \& Saw, S.-M. The association between digital screen time and myopia: A systematic review. \emph{Ophthalmic and Physiological Optics} \textbf{40}, 216--229 (2020).
+124. Lanca, C. \& Saw, S.-M. The association between digital screen time and myopia: A systematic review. \emph{Ophthalmic and Physiological Optics} \textbf{40}, 216--229 (2020).
 
 \leavevmode\hypertarget{ref-larwinMeasuringAcademicOutcomes2019}{}%
-149.
+125.
 Larwin, K.
@@
 \leavevmode\hypertarget{ref-leeSystematicReviewMetaanalysis2016}{}%
-150.
+126.
 Lee, J., Piao, M., Byun, A.
@@
 \leavevmode\hypertarget{ref-liMetaanalysisEffectsComputer2010}{}%
-151. Li, Q. \& Ma, X. A Meta-analysis of the Effects of Computer Technology on School Students' Mathematics Learning. \emph{Educational Psychology Review} \textbf{22}, 215--243 (2010).
+127. Li, Q. \& Ma, X. A Meta-analysis of the Effects of Computer Technology on School Students' Mathematics Learning. \emph{Educational Psychology Review} \textbf{22}, 215--243 (2010).
 
 \leavevmode\hypertarget{ref-liRelationshipsScreenUse2020}{}%
-152.
+128.
 Li, C., Cheng, G., Sha, T., Cheng, W.
@@
 \leavevmode\hypertarget{ref-liAreActiveVideo2022}{}%
-153.
+129.
 Li, S., Song, Y., Cai, Z.
@@
 \leavevmode\hypertarget{ref-liEffectivenessUnpluggedActivities2022}{}%
-154.
+130.
 Li, F., Wang, X., He, X., Cheng, L.
@@
 \leavevmode\hypertarget{ref-liaoEffectsComputerassistedInstruction1992}{}%
-155. Liao, Y.-K. Effects of Computer-Assisted Instruction on Cognitive Outcomes: A Meta-Analysis. \emph{Journal of Research on Computing in Education} \textbf{24}, 367--80 (1992).
+131. Liao, Y.-K. Effects of Computer-Assisted Instruction on Cognitive Outcomes: A Meta-Analysis. \emph{Journal of Research on Computing in Education} \textbf{24}, 367--80 (1992).
 
 \leavevmode\hypertarget{ref-liaoEffectsComputerApplications2007}{}%
-156.
+132.
 Liao, Y.-k.
@@
 \leavevmode\hypertarget{ref-liaoWhichTypeSedentary2014}{}%
-157.
+133.
 Liao, Y., Liao, J., Durand, C.
@@
 \leavevmode\hypertarget{ref-liuDoseResponseAssociation2016}{}%
-158.
+134.
 Liu, M., Wu, L.
@@
 \leavevmode\hypertarget{ref-liuSocialNetworkingOnline2016}{}%
-159. Liu, D. \& Baumeister, R. F. Social networking online and personality of self-worth: A meta-analysis. \emph{Journal of Research in Personality} \textbf{64}, 79--89 (2016).
+135. Liu, D. \& Baumeister, R. F. Social networking online and personality of self-worth: A meta-analysis. \emph{Journal of Research in Personality} \textbf{64}, 79--89 (2016).
 
 \leavevmode\hypertarget{ref-liuMetaanalysisSocialNetworking2016}{}%
-160. Liu, D., Ainsworth, S. E. \& Baumeister, R. F. A Meta-Analysis of Social Networking Online and Social Capital. \emph{Review of General Psychology} \textbf{20}, 369--391 (2016).
+136. Liu, D., Ainsworth, S. E. \& Baumeister, R. F. A Meta-Analysis of Social Networking Online and Social Capital. \emph{Review of General Psychology} \textbf{20}, 369--391 (2016).
 
 \leavevmode\hypertarget{ref-liuDigitalCommunicationMedia2019}{}%
-161.
+137.
 Liu, D., Baumeister, R.
@@
 \leavevmode\hypertarget{ref-liuMetaanalysisEffectMultimedia2022}{}%
-162.
+138.
 Liu, M., Pang, W., Guo, J.
@@
 \leavevmode\hypertarget{ref-liuTimeSpentSocial2022}{}%
-163.
+139.
 Liu, M.
@@
 \leavevmode\hypertarget{ref-luCorrelationMobilePhone2021}{}%
-164.
+140.
 Lu, G.-L.
@@
 \leavevmode\hypertarget{ref-lucknerEffectivenessInterventionsPromote2012}{}%
-165.
+141.
 Luckner, H., Moss, J.
@@
 \leavevmode\hypertarget{ref-luoIncreasedVideoGame2022}{}%
-166.
+142.
 Luo, Y.
@@
 
+\leavevmode\hypertarget{ref-madiganAssociationsScreenUse2020}{}%
+143.
+Madigan, S., McArthur, B.
+A., Anhorn, C., Eirich, R.
+\& Christakis, D.
+A.
+Associations Between Screen Use and Child Language Skills: A Systematic Review and Meta-analysis.
+\emph{JAMA Pediatrics} \textbf{174}, 665 (2020).
+
 \leavevmode\hypertarget{ref-majorEffectivenessTechnologySupported2021}{}%
-167.
+144.
 Major, L., Francis, G.
@@
 \leavevmode\hypertarget{ref-mallawaarachchiAssociationsSmartphoneTablet2022}{}%
-168.
+145.
 Mallawaarachchi, S.
@@
 \leavevmode\hypertarget{ref-marcianoCyberbullyingPerpetrationVictimization2020}{}%
-169.
+146.
 Marciano, L., Schulz, P.
@@
 \leavevmode\hypertarget{ref-marcianoDigitalMediaUse2021}{}%
-170.
+147.
 Marciano, L., Ostroumova, M., Schulz, P.
@@
 \leavevmode\hypertarget{ref-maresPositiveEffectsTelevision2005}{}%
-171. Mares, M.-L. \& Woodard, E. Positive Effects of Television on Children's Social Interactions: A Meta-Analysis. \emph{Media Psychology} \textbf{7}, 301--322 (2005).
+148. Mares, M.-L. \& Woodard, E. Positive Effects of Television on Children's Social Interactions: A Meta-Analysis. \emph{Media Psychology} \textbf{7}, 301--322 (2005).
 
 \leavevmode\hypertarget{ref-maresEffectsSesameStreet2013}{}%
-172. Mares, M.-L. \& Pan, Z. Effects of Sesame Street: A meta-analysis of children's learning in 15 countries. \emph{Journal of Applied Developmental Psychology} \textbf{34}, 140--151 (2013).
+149. Mares, M.-L. \& Pan, Z. Effects of Sesame Street: A meta-analysis of children's learning in 15 countries. \emph{Journal of Applied Developmental Psychology} \textbf{34}, 140--151 (2013).
 
 \leavevmode\hypertarget{ref-marinoAssociationsProblematicFacebook2018}{}%
-173.
+150.
 Marino, C., Gini, G., Vieno, A.
@@
 
+\leavevmode\hypertarget{ref-markerExploringMythChubby2022}{}%
+151. Marker, C., Gnambs, T. \& Appel, M. Exploring the myth of the chubby gamer: A meta-analysis on sedentary video gaming and body mass. \emph{Social Science \& Medicine} \textbf{301}, 112325 (2022).
+
 \leavevmode\hypertarget{ref-marshallRelationshipsMediaUse2004}{}%
-174.
+152.
 Marshall, S.
@@
 \leavevmode\hypertarget{ref-martinsRoleMediaExposure2019}{}%
-175. Martins, N. \& Weaver, A. The role of media exposure on relational aggression: A meta-analysis. \emph{Aggression and Violent Behavior} \textbf{47}, 90--99 (2019).
+153. Martins, N. \& Weaver, A. The role of media exposure on relational aggression: A meta-analysis. \emph{Aggression and Violent Behavior} \textbf{47}, 90--99 (2019).
 
 \leavevmode\hypertarget{ref-martinsInfluenceEatingDistractors2022}{}%
-176.
+154.
 Martins, N.
@@
 \leavevmode\hypertarget{ref-mazeasEvaluatingEffectivenessGamification2022}{}%
-177.
+155.
 Mazeas, A., Duclos, M., Pereira, B.
@@
 \leavevmode\hypertarget{ref-mcarthurPhonicsTrainingEnglishspeaking2012}{}%
-178.
+156.
 McArthur, G.
@@
 \leavevmode\hypertarget{ref-mcarthurPhonicsTrainingEnglishspeaking2018}{}%
-179. McArthur, G. \emph{et al.} Phonics training for English-speaking poor readers. \emph{Cochrane Database of Systematic Reviews} \textbf{2018}, (2018).
+157. McArthur, G. \emph{et al.} Phonics training for English-speaking poor readers. \emph{Cochrane Database of Systematic Reviews} \textbf{2018}, (2018).
 
 \leavevmode\hypertarget{ref-meiSleepProblemsExcessive2018}{}%
-180. Mei, X. \emph{et al.} Sleep problems in excessive technology use among adolescent: A systemic review and meta-analysis. \emph{Sleep Science and Practice} \textbf{2}, 9 (2018).
+158. Mei, X. \emph{et al.} Sleep problems in excessive technology use among adolescent: A systemic review and meta-analysis. \emph{Sleep Science and Practice} \textbf{2}, 9 (2018).
 
 \leavevmode\hypertarget{ref-merchantEffectivenessVirtualRealitybased2014}{}%
-181.
+159.
 Merchant, Z., Goetz, E.
@@
 \leavevmode\hypertarget{ref-moranTechnologyReadingPerformance2008}{}%
-182.
+160.
 Moran, J., Ferdig, R.
@@
 \leavevmode\hypertarget{ref-moriAssociationSextingSexual2019}{}%
-183.
+161.
 Mori, C., Temple, J.
@@
 \leavevmode\hypertarget{ref-neitzelSynthesisQuantitativeResearch2022}{}%
-184.
+162.
 Neitzel, A.
@@
 \leavevmode\hypertarget{ref-nesiSocialMediaUse2021}{}%
-185. Nesi, J. \emph{et al.} Social media use and self-injurious thoughts and behaviors: A systematic review and meta-analysis. \emph{Clinical Psychology Review} \textbf{87}, 102038 (2021).
+163. Nesi, J. \emph{et al.} Social media use and self-injurious thoughts and behaviors: A systematic review and meta-analysis. \emph{Clinical Psychology Review} \textbf{87}, 102038 (2021).
 
 \leavevmode\hypertarget{ref-nikkelenMediaUseADHDrelated2014}{}%
-186.
+164.
 Nikkelen, S.
@@
 \leavevmode\hypertarget{ref-ohDigitalInterventionsUniversal2022}{}%
-187.
+165.
 Oh, C., Carducci, B., Vaivada, T.
@@
 \leavevmode\hypertarget{ref-oldratiEffectivenessComputerizedCognitive2020}{}%
-188.
+166.
 Oldrati, V.
@@
 \leavevmode\hypertarget{ref-oliveiraEffectsActiveVideo2020}{}%
-189.
+167.
 Oliveira, C.
@@
 \leavevmode\hypertarget{ref-ozdemirEffectAugmentedReality2018}{}%
-190.
+168.
 Ozdemir, M., Sahin, C., Arcagok, S.
@@
 \leavevmode\hypertarget{ref-paikEffectsTelevisionViolence1994}{}%
-191. Paik, H. \& Comstock, G. The Effects of Television Violence on Antisocial Behavior: A Meta-Analysis. \emph{Communication Research} \textbf{21}, 516--546 (1994).
+169. Paik, H. \& Comstock, G. The Effects of Television Violence on Antisocial Behavior: A Meta-Analysis. \emph{Communication Research} \textbf{21}, 516--546 (1994).
 
 \leavevmode\hypertarget{ref-parkEffectivenessInformationCommunication2021}{}%
-192.
+170.
 Park, J., Park, M.-J.
@@
 \leavevmode\hypertarget{ref-pearceImpactScaryTV2016}{}%
-193. Pearce, L. J. \& Field, A. P. The Impact of `Scary' TV and Film on Children's Internalizing Emotions: A Meta-Analysis. \emph{Human Communication Research} \textbf{42}, 98--121 (2016).
+171. Pearce, L. J. \& Field, A. P. The Impact of `Scary' TV and Film on Children's Internalizing Emotions: A Meta-Analysis. \emph{Human Communication Research} \textbf{42}, 98--121 (2016).
 
 \leavevmode\hypertarget{ref-pengPlayingExergamesReally2011}{}%
-194.
+172.
 Peng, W., Lin, J.-H.
@@
 
+\leavevmode\hypertarget{ref-poorolajalBehavioralFactorsInfluencing2020}{}%
+173.
+Poorolajal, J., Sahraei, F., Mohamdadi, Y., Doosti-Irani, A.
+\& Moradi, L.
+Behavioral factors influencing childhood obesity: A systematic review and meta-analysis.
+\emph{Obesity Research \& Clinical Practice} \textbf{14}, 109--118 (2020).
+
 \leavevmode\hypertarget{ref-powersEffectsVideogamePlay2013}{}%
-195.
+174.
 Powers, K.
@@
 \leavevmode\hypertarget{ref-prescottMetaanalysisRelationshipViolent2018}{}%
-196.
+175.
 Prescott, A.
@@
 \leavevmode\hypertarget{ref-prizant-passalSocialAnxietyInternet2016}{}%
-197.
+176.
 Prizant-Passal, S., Shechner, T.
@@
 \leavevmode\hypertarget{ref-reynardDigitalInterventionsEmotion2022}{}%
-198.
+177.
 Reynard, S., Dias, J., Mitic, M., Schrank, B.
@@
 \leavevmode\hypertarget{ref-rodriguezrochaEHealthInterventionsFruit2019}{}%
-199. Rodriguez Rocha, N. P. \& Kim, H. eHealth Interventions for Fruit and Vegetable Intake: A Meta-Analysis of Effectiveness. \emph{Health Education \& Behavior} \textbf{46}, 947--959 (2019).
+178. Rodriguez Rocha, N. P. \& Kim, H. eHealth Interventions for Fruit and Vegetable Intake: A Meta-Analysis of Effectiveness. \emph{Health Education \& Behavior} \textbf{46}, 947--959 (2019).
 
 \leavevmode\hypertarget{ref-russellEffectScreenAdvertising2019}{}%
-200.
+179.
 Russell, S.
@@
 \leavevmode\hypertarget{ref-ryanMetaAnalysisAchievementEffects1991}{}%
-201. Ryan, A. W. Meta-Analysis of Achievement Effects of Microcomputer Applications in Elementary Schools. \emph{Educational Administration Quarterly} \textbf{27}, 161--184 (1991).
+180. Ryan, A. W. Meta-Analysis of Achievement Effects of Microcomputer Applications in Elementary Schools. \emph{Educational Administration Quarterly} \textbf{27}, 161--184 (1991).
 
 \leavevmode\hypertarget{ref-sadeghiradInfluenceUnhealthyFood2016}{}%
-202.
+181.
 Sadeghirad, B., Duhaney, T., Motaghipisheh, S., Campbell, N.
@@
 \leavevmode\hypertarget{ref-saiphooSocialNetworkingSite2020}{}%
-203. Saiphoo, A. N., Dahoah Halevi, L. \& Vahedi, Z. Social networking site use and self-esteem: A meta-analytic review. \emph{Personality and Individual Differences} \textbf{153}, 109639 (2020).
+182. Saiphoo, A. N., Dahoah Halevi, L. \& Vahedi, Z. Social networking site use and self-esteem: A meta-analytic review. \emph{Personality and Individual Differences} \textbf{153}, 109639 (2020).
 
 \leavevmode\hypertarget{ref-schererMetaanalysisTeachingLearning2020}{}%
-204.
+183.
 Scherer, R., Siddiq, F.
@@
 \leavevmode\hypertarget{ref-schererCognitiveBenefitsLearning2019}{}%
-205.
+184.
 Scherer, R., Siddiq, F.
@@
 \leavevmode\hypertarget{ref-schroederHowEffectiveAre2013}{}%
-206.
+185.
 Schroeder, N.
@@
 \leavevmode\hypertarget{ref-sciontiCognitiveTrainingEffective2020}{}%
-207.
+186.
 Scionti, N., Cavallero, M., Zogmaister, C.
@@
 \leavevmode\hypertarget{ref-shahabOnlineSupportSmoking2009}{}%
-208. Shahab, L. \& McEwen, A. Online support for smoking cessation: A systematic review of the literature. \emph{Addiction} \textbf{104}, 1792--1804 (2009).
+187. Shahab, L. \& McEwen, A. Online support for smoking cessation: A systematic review of the literature. \emph{Addiction} \textbf{104}, 1792--1804 (2009).
 
 \leavevmode\hypertarget{ref-shannonProblematicSocialMedia2022}{}%
-209.
+188.
 Shannon, H., Bush, K., Villeneuve, P.
@@
 \leavevmode\hypertarget{ref-shinMobilePhoneInterventions2019}{}%
-210.
+189.
 Shin, Y., Kim, S.
@@
 \leavevmode\hypertarget{ref-shinOnlineMediaConsumption2022}{}%
-211.
+190.
 Shin, M., Juventin, M., Wai Chu, J.
@@
 \leavevmode\hypertarget{ref-slavinReadingEffectsIBM1991}{}%
-212. Slavin, R. E. Reading Effects of IBM's "Writing to Read" Program: A Review of Evaluations. \emph{Educational Evaluation and Policy Analysis} \textbf{13}, 1 (1991).
+191. Slavin, R. E. Reading Effects of IBM's "Writing to Read" Program: A Review of Evaluations. \emph{Educational Evaluation and Policy Analysis} \textbf{13}, 1 (1991).
 
 \leavevmode\hypertarget{ref-slavinEffectiveProgramsElementary2008}{}%
-213. Slavin, R. E. \& Lake, C. Effective Programs in Elementary Mathematics: A Best-Evidence Synthesis. \emph{Review of Educational Research} \textbf{78}, 427--515 (2008).
+192. Slavin, R. E. \& Lake, C. Effective Programs in Elementary Mathematics: A Best-Evidence Synthesis. \emph{Review of Educational Research} \textbf{78}, 427--515 (2008).
 
 \leavevmode\hypertarget{ref-slavinEffectiveProgramsMiddle2009}{}%
-214. Slavin, R. E., Lake, C. \& Groff, C. Effective Programs in Middle and High School Mathematics: A Best-Evidence Synthesis. \emph{Review of Educational Research} \textbf{79}, 839--911 (2009).
+193. Slavin, R. E., Lake, C. \& Groff, C. Effective Programs in Middle and High School Mathematics: A Best-Evidence Synthesis. \emph{Review of Educational Research} \textbf{79}, 839--911 (2009).
 
 \leavevmode\hypertarget{ref-slavinExperimentalEvaluationsElementary2014}{}%
-215.
+194.
 Slavin, R.
@@
 \leavevmode\hypertarget{ref-soojungSynthesisComputerAssistedMathematical2022}{}%
-216.
+195.
 Soo Jung, K.
@@
 \leavevmode\hypertarget{ref-stavrinosDistractedWalkingBicycling2018}{}%
-217.
+196.
 Stavrinos, D., Pope, C.
@@
 \leavevmode\hypertarget{ref-steeleEducationIncarceratedJuveniles2016}{}%
-218. Steele, J. L., Bozick, R. \& Davis, L. M. Education for Incarcerated Juveniles: A Meta-Analysis. \emph{Journal of Education for Students Placed at Risk (JESPAR)} \textbf{21}, 65--89 (2016).
+197. Steele, J. L., Bozick, R. \& Davis, L. M. Education for Incarcerated Juveniles: A Meta-Analysis. \emph{Journal of Education for Students Placed at Risk (JESPAR)} \textbf{21}, 65--89 (2016).
 
 \leavevmode\hypertarget{ref-strongSystematicMetaanalyticReview2011}{}%
-219.
+198.
 Strong, G.
@@
 \leavevmode\hypertarget{ref-strouseLearningVideoMetaAnalysis2021}{}%
-220. Strouse, G. A. \& Samson, J. E. Learning From Video: A Meta-Analysis of the Video Deficit in Children Ages 0 to 6 Years. \emph{Child Development} \textbf{92}, E20--E38 (2021).
+199. Strouse, G. A. \& Samson, J. E. Learning From Video: A Meta-Analysis of the Video Deficit in Children Ages 0 to 6 Years. \emph{Child Development} \textbf{92}, E20--E38 (2021).
 
 \leavevmode\hypertarget{ref-suleiman-martosGamificationImprovementDiet2021}{}%
-221.
+200.
 Suleiman-Martos, N.
@@
 \leavevmode\hypertarget{ref-sunWhichWayDesign2021}{}%
-222.
+201.
 Sun, L., Hu, L.
@@
 \leavevmode\hypertarget{ref-sungHowEffectiveAre2015}{}%
-223. Sung, Y.-T., Chang, K.-E. \& Yang, J.-M. How effective are mobile devices for language learning? A meta-analysis. \emph{Educational Research Review} \textbf{16}, 68--84 (2015).
+202. Sung, Y.-T., Chang, K.-E. \& Yang, J.-M. How effective are mobile devices for language learning? A meta-analysis. \emph{Educational Research Review} \textbf{16}, 68--84 (2015).
 
 \leavevmode\hypertarget{ref-takacsCanComputerReplace2014}{}%
-224.
+203.
 Takacs, Z.
@@
 \leavevmode\hypertarget{ref-takacsBenefitsPitfallsMultimedia2015}{}%
-225.
+204.
 Takacs, Z.
@@
 \leavevmode\hypertarget{ref-takacsEfficacyDifferentInterventions2019}{}%
-226.
+205.
 Takacs, Z.
@@
 \leavevmode\hypertarget{ref-tamimWhatFortyYears2011}{}%
-227.
+206.
 Tamim, R.
@@
 
+\leavevmode\hypertarget{ref-tekedereExaminingEffectivenessAugmented2016}{}%
+207.
+Tekedere, H.
+\& Göke, H.
+Examining the Effectiveness of Augmented Reality Applications in Education: A Meta-Analysis.
+\emph{International Journal of Environmental and Science Education} \textbf{11}, 9469--9481 (2016).
+
 \leavevmode\hypertarget{ref-tingirEffectsMobileDevices2017}{}%
-228.
+208.
 Tingir, S., Cavlazoglu, B., Caliskan, O., Koklu, O.
@@
 \leavevmode\hypertarget{ref-tokacEffectsGamebasedLearning2019}{}%
-229.
+209.
 Tokac, U., Novak, E.
@@
 \leavevmode\hypertarget{ref-tokunagaMetaanalysisRelationshipsPsychosocial2017}{}%
-230.
+210.
 Tokunaga, R.
@@
 \leavevmode\hypertarget{ref-tremblaySystematicReviewSedentary2011}{}%
-231.
+211.
 Tremblay, M.
@@
 \leavevmode\hypertarget{ref-tsaiDigitalGamebasedSecondlanguage2018}{}%
-232.
+212.
 Tsai, Y.-L.
@@
 \leavevmode\hypertarget{ref-vahediAreMediaLiteracy2018}{}%
-233.
+213.
 Vahedi, Z., Sibalis, A.
@@
 
+\leavevmode\hypertarget{ref-vahediAssociationSelfreportedDepressive2021}{}%
+214.
+Vahedi, Z.
+\& Zannella, L.
+The association between self-reported depressive symptoms and the use of social networking sites (SNS): A meta-analysis.
+\emph{Current Psychology} \textbf{40}, 2174--2189 (2021).
+
 \leavevmode\hypertarget{ref-vantrietHowEffectiveAre2014}{}%
-234.
+215.
 van 't Riet, J., Crutzen, R.
@@
 \leavevmode\hypertarget{ref-vanekrisEvidenceupdateProspectiveRelationship2016}{}%
-235.
+216.
 van Ekris, E.
@@
 \leavevmode\hypertarget{ref-vangriekenPrimaryPreventionOverweight2012}{}%
-236.
+217.
 van Grieken, A., Ezendam, N.
@@
 
+\leavevmode\hypertarget{ref-vannucciSocialMediaUse2020}{}%
+218. Vannucci, A., Simpson, E. G., Gagnon, S. \& Ohannessian, C. M. Social media use and risky behaviors in adolescents: A meta-analysis. \emph{Journal of Adolescence} \textbf{79}, 258--274 (2020).
+
 \leavevmode\hypertarget{ref-villegas-navasEffectsFoodsEmbedded2020}{}%
-237.
+219.
 Villegas-Navas, V., Montero-Simo, M.-J.
@@
 \leavevmode\hypertarget{ref-wahiEffectivenessInterventionsAimed2011}{}%
-238.
+220.
 Wahi, G.
@@
 \leavevmode\hypertarget{ref-shudongwangComparabilityComputerBasedPaperandPencil2008}{}%
-239.
+221.
 Shudong Wang, Hong Jiao, Young, M.
@@
 \leavevmode\hypertarget{ref-wangSmartphoneOveruseVisual2020}{}%
-240.
+222.
 Wang, J., Li, M., Zhu, D.
@@
 \leavevmode\hypertarget{ref-wangEffects3DVirtual2020}{}%
-241.
+223.
 Wang, C.-p., Lan, Y.-J., Tseng, W.-T., Lin, Y.-T.
@@
 \leavevmode\hypertarget{ref-wengEffectivenessCognitiveSkillsbased2014}{}%
-242.
+224.
 Weng, P.-L., Maeda, Y.
@@
 \leavevmode\hypertarget{ref-williamsImpactLeisuretimeTelevision1982}{}%
-243.
+225.
 Williams, P.
@@
 \leavevmode\hypertarget{ref-woodEffectsMediaViolence1991}{}%
-244. Wood, W., Wong, F. Y. \& Chachere, J. G. Effects of media violence on viewers' aggression in unconstrained social interaction. \emph{Psychological Bulletin} \textbf{109}, 371--383 (1991).
+226. Wood, W., Wong, F. Y. \& Chachere, J. G. Effects of media violence on viewers' aggression in unconstrained social interaction. \emph{Psychological Bulletin} \textbf{109}, 371--383 (1991).
 
 \leavevmode\hypertarget{ref-woutersMetaanalysisCognitiveMotivational2013}{}%
-245.
+227.
 Wouters, P., van Nimwegen, C., van Oostendorp, H.
@@
 \leavevmode\hypertarget{ref-woutersMetaanalyticReviewRole2013}{}%
-246. Wouters, P. \& van Oostendorp, H. A meta-analytic review of the role of instructional support in game-based learning. \emph{Computers \& Education} \textbf{60}, 412--425 (2013).
+228. Wouters, P. \& van Oostendorp, H. A meta-analytic review of the role of instructional support in game-based learning. \emph{Computers \& Education} \textbf{60}, 412--425 (2013).
 
 \leavevmode\hypertarget{ref-wuScreenTimeBody2022}{}%
-247.
+229.
 Wu, Y., Amirfakhraei, A., Ebrahimzadeh, F., Jahangiry, L.
@@
 
+\leavevmode\hypertarget{ref-xieCanTouchscreenDevices2018}{}%
+230.
+Xie, H.
+\emph{et al.} Can Touchscreen Devices be Used to Facilitate Young Children's Learning?
+A Meta-Analysis of Touchscreen Learning Effect.
+\emph{Frontiers in Psychology} \textbf{9}, 2580 (2018).
+
 \leavevmode\hypertarget{ref-yangAssociationSocialNetwork2022}{}%
-248.
+231.
 Yang, Q., Liu, J.
@@
 \leavevmode\hypertarget{ref-yinCulturalBackgroundMeasurement2019}{}%
-249.
+232.
 Yin, X.-Q., de Vries, D.
@@
 
+\leavevmode\hypertarget{ref-yoonSocialNetworkSite2019}{}%
+233.
+Yoon, S., Kleinman, M., Mertz, J.
+\& Brannick, M.
+Is social network site usage related to depression?
+A meta-analysis of FacebookDepression relations.
+\emph{Journal of Affective Disorders} \textbf{248}, 65--72 (2019).
+
 \leavevmode\hypertarget{ref-zhangTelevisionWatchingRisk2016}{}%
-250. Zhang, G., Wu, L., Zhou, L., Lu, W. \& Mao, C. Television watching and risk of childhood obesity: A meta-analysis. \emph{The European Journal of Public Health} \textbf{26}, 13--18 (2016).
+234. Zhang, G., Wu, L., Zhou, L., Lu, W. \& Mao, C. Television watching and risk of childhood obesity: A meta-analysis. \emph{The European Journal of Public Health} \textbf{26}, 13--18 (2016).
 
 \leavevmode\hypertarget{ref-zhangRelationshipSocialMedia2021}{}%
-251. Zhang, Y., Li, S. \& Yu, G. The relationship between social media use and fear of missing out: A meta-analysis. \emph{Acta Psychologica Sinica} \textbf{53}, 273--290 (2021).
+235. Zhang, Y., Li, S. \& Yu, G. The relationship between social media use and fear of missing out: A meta-analysis. \emph{Acta Psychologica Sinica} \textbf{53}, 273--290 (2021).
 
 \leavevmode\hypertarget{ref-zhangInfluenceSedentaryBehaviour2022}{}%
-252.
+236.
 Zhang, J., Yang, S.
@@
 \leavevmode\hypertarget{ref-zhangScreenTimeHealth2022}{}%
-253.
+237.
 Zhang, Y., Tian, S., Zou, D., Zhang, H.
@@
 \leavevmode\hypertarget{ref-zhangUpdatedMetaanalysisRelationship2022}{}%
-254. Zhang, J. \emph{et al.} An updated of meta-analysis on the relationship between mobile phone addiction and sleep disorder. \emph{Journal of Affective Disorders} \textbf{305}, 94--101 (2022).
+238. Zhang, J. \emph{et al.} An updated of meta-analysis on the relationship between mobile phone addiction and sleep disorder. \emph{Journal of Affective Disorders} \textbf{305}, 94--101 (2022).
 
 \leavevmode\hypertarget{ref-zhengLearningOnetoOneLaptop2016}{}%
-255.
+239.
 Zheng, B., Warschauer, M., Lin, C.-H.
@@
 \leavevmode\hypertarget{ref-zhouMetaanalysisNarrativeGamebased2020}{}%
-256. Zhou, C., Occa, A., Kim, S. \& Morgan, S. A Meta-analysis of Narrative Game-based Interventions for Promoting Healthy Behaviors. \emph{Journal of Health Communication} \textbf{25}, 54--65 (2020).
+240. Zhou, C., Occa, A., Kim, S. \& Morgan, S. A Meta-analysis of Narrative Game-based Interventions for Promoting Healthy Behaviors. \emph{Journal of Health Communication} \textbf{25}, 54--65 (2020).
+
+\leavevmode\hypertarget{ref-zouAssociationScreenTimebased2021}{}%
+241.
+Zou, Z., Xiang, J., Wang, H., Wen, Q.
+\& Luo, X.
+Association of screen time-based sedentary behavior and the risk of depression in children and adolescents: Dose-response meta-analysis.
+\emph{Archives of Clinical Psychiatry (São Paulo)} \textbf{48}, 235--244 (2022).
 
 \leavevmode\hypertarget{ref-zuckerEffectsElectronicBooks2009}{}%
-257.
+242.
 Zucker, T.
@@
 \emph{Journal of Educational Computing Research} \textbf{40}, 47--87 (2009).
+
+\leavevmode\hypertarget{ref-seetharamanFacebookKnowsInstagram2021}{}%
+243. Seetharaman, G. W., Jeff Horwitz and Deepa. Facebook Knows Instagram Is Toxic for Teen Girls, Company Documents Show. \emph{Wall Street Journal} (2021).
+
+\leavevmode\hypertarget{ref-elsonPolicyStatementsMedia2019}{}%
+244. Elson, M. \emph{et al.} Do policy statements on media effects faithfully represent the science? \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 12--25 (2019).
+
+\leavevmode\hypertarget{ref-ashtonScreenTimeChildren2019}{}%
+245. Ashton, J. J. \& Beattie, R. M. Screen time in children and adolescents: Is there evidence to guide parents and policy? \emph{The Lancet Child \& Adolescent Health} \textbf{3}, 292--294 (2019).
+
+\leavevmode\hypertarget{ref-royalcollegeofpaediatricsandchildhealthHealthImpactsScreen2019}{}%
+246. Royal College of Paediatrics and Child Health. \emph{The health impacts of screen time: A guide for clinicians and parents.} (2019).
+
+\leavevmode\hypertarget{ref-pagePRISMA2020Statement2020}{}%
+247. Page, M. J. \emph{et al.} \emph{The PRISMA 2020 statement: An updated guideline for reporting systematic reviews}. (2020) doi:\href{https://doi.org/10.31222/osf.io/v7gm2}{10.31222/osf.io/v7gm2}.
+
+\leavevmode\hypertarget{ref-parrySystematicReviewMetaanalysis2021}{}%
+248. Parry, D. A. \emph{et al.} A systematic review and meta-analysis of discrepancies between logged and self-reported digital media use. \emph{Nature Human Behaviour} \textbf{5}, 1535--1547 (2021).
+
+\leavevmode\hypertarget{ref-byrneMeasurementScreenTime2021}{}%
+249. Byrne, R., Terranova, C. O. \& Trost, S. G. Measurement of screen time among young children aged 0 years: A systematic review. \emph{Obesity Reviews} \textbf{22}, (2021).
+
+\leavevmode\hypertarget{ref-smithFeasibilityAutomatedCameras2019}{}%
+250.
+Smith, C., Galland, B.
+C., de Bruin, W.
+E.
+\& Taylor, R.
+W.
+Feasibility of automated cameras to measure screen use in adolescents.
+\emph{American journal of preventive medicine} \textbf{57}, 417--424 (2019).
+
+\leavevmode\hypertarget{ref-rydingPassiveObjectiveMeasures2020}{}%
+251. Ryding, F. C. \& Kuss, D. J. Passive objective measures in the assessment of problematic smartphone use: A systematic review. \emph{Addictive Behaviors Reports} \textbf{11}, 100257 (2020).
+
+\leavevmode\hypertarget{ref-guyattGRADEGuidelinesIntroduction2011}{}%
+252. Guyatt, G. \emph{et al.} GRADE guidelines: 1. IntroductionGRADE evidence profiles and summary of findings tables. \emph{Journal of Clinical Epidemiology} \textbf{64}, 383--394 (2011).
+
+\leavevmode\hypertarget{ref-twengeMoreTimeTechnology2019}{}%
+253.
+Twenge, J.
+M.
+More Time on Technology, Less Happiness?
+Associations Between Digital-Media Use and Psychological Well-Being.
+\emph{Current Directions in Psychological Science} \textbf{28}, 372--379 (2019).
+
+\leavevmode\hypertarget{ref-kellySocialMediaUse2018}{}%
+254.
+Kelly, Y., Zilanawala, A., Booker, C.
+\& Sacker, A.
+Social Media Use and Adolescent Mental Health: Findings From the UK Millennium Cohort Study.
+\emph{EClinicalMedicine} \textbf{6}, 59--68 (2018).
+
+\leavevmode\hypertarget{ref-NHLBIQualityAssessmentSystematic2014}{}%
+255. National Health, Lung, and Blood Institute. \emph{Quality Assessment of Systematic Reviews and Meta-Analyses}. (2014).
+
+\leavevmode\hypertarget{ref-bowmanEffectSizesStatistical2012}{}%
+256. Bowman, N. A. Effect Sizes and Statistical Methods for Meta-Analysis in Higher Education. \emph{Research in Higher Education} \textbf{53}, 375--382 (2012).
+
+\leavevmode\hypertarget{ref-jacobsEstimationBiserialCorrelation2017}{}%
+257.
+Jacobs, P.
+\& Viechtbauer, W.
+Estimation of the biserial correlation and its sampling variance for use in meta-analysis: Biserial Correlation.
+\emph{Research Synthesis Methods} \textbf{8}, 161--180 (2017).
+
+\leavevmode\hypertarget{ref-funderEvaluatingEffectSize2019}{}%
+258. Funder, D. C. \& Ozer, D. J. Evaluating Effect Size in Psychological Research: Sense and Nonsense. \emph{Advances in Methods and Practices in Psychological Science} \textbf{2}, 156--168 (2019).
+
+\leavevmode\hypertarget{ref-gignacEffectSizeGuidelines2016}{}%
+259. Gignac, G. E. \& Szodorai, E. T. Effect size guidelines for individual differences researchers. \emph{Personality and Individual Differences} \textbf{102}, 74--78 (2016).
+
+\leavevmode\hypertarget{ref-R-metafor}{}%
+260. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).
+
+\leavevmode\hypertarget{ref-R-base}{}%
+261. R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2023).
+
+\leavevmode\hypertarget{ref-eggerBiasMetaanalysisDetected1997}{}%
+262. Egger, M., Smith, G. D., Schneider, M. \& Minder, C. Bias in meta-analysis detected by a simple, graphical test. \emph{BMJ} \textbf{315}, 629--634 (1997).
+
+\leavevmode\hypertarget{ref-pageChapter13Assessing2021}{}%
+263.
+Page, M.
+J., Higgins, J.
+P.
+\& Sterne, J.
+A.
+Chapter 13: Assessing risk of bias due to missing results in a synthesis.
+in \emph{Cochrane Handbook for Systematic Reviews of Interventions} (eds.
+Higgins, J.
+P.
+et al.) (Cochrane, 2021).
+
+\leavevmode\hypertarget{ref-ioannidisExploratoryTestExcess2007}{}%
+264. Ioannidis, J. P. \& Trikalinos, T. A. An exploratory test for an excess of significant findings. \emph{Clinical Trials} \textbf{4}, 245--253 (2007).
+
+\leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
+265. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
 \end{cslreferences}
